---
title: "template_similarity"
output: html_document
date: "2025-11-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../../load_libraries.R")
source("../helper/template_similarity_utils.R")

fmri3_data_2probes <- readr::read_csv(
  mid_pupil_resolve_data("fmri3", "derivatives", "fmri3_data_2probes.csv"),
  show_col_types = FALSE
)

theme_set(theme_blank() +
            theme(text = element_text(family = "Helvetica", size = 12)))
redOrange_palette6 <- c("red", "salmon", "darkred", "goldenrod3", "orange", "gold")

thresh_str <- THRESH_STR
thresh <- THRESH
splits <- SPLITS
model_grid_split <- make_model_grid(include_split = TRUE)
model_grid_pooled <- make_model_grid(include_split = FALSE)
```

## first, look at correlation between two regressors
```{r warning = F, message = F}
subjects_list <- load_fmri3_subjects()

reg_corr_list <- NULL
all_reg <- NULL
for (sub in subjects_list$X1) {
  file_pupil <- file.path(MIDAFFEMO_ROOT, "regs_corr", paste0(sub, "_pupil_scaled_c.1D"))
  pupil_reg <- read_delim(file_pupil, delim = "\t", col_names = FALSE)
  file_rating <- file.path(MIDAFFEMO_ROOT, "regs_corr", paste0(sub, "_report_param_arous_c.1D"))
  rating_reg <- read_delim(file_rating, delim = "\t", col_names = FALSE)
  reg_corr_list <- rbind(
    reg_corr_list,
    summary(lm(scale(pupil_reg$X1) ~ scale(rating_reg$X1)))$coefficients[2, ]
  )
  all_reg <- rbind(all_reg, cbind(pupil_reg, rating_reg, subject = sub))
}

reg_corr_list <- as.data.frame(reg_corr_list)
reg_corr_list$subject <- subjects_list$X1
mean(reg_corr_list$Estimate)
sd(reg_corr_list$Estimate)
t.test(reg_corr_list$Estimate,mu=0)

all_reg <- as.data.frame(all_reg)
names(all_reg) <- c("pupil","rating","subject")
summary(lmer(scale(pupil)~scale(rating)+ (1|subject),all_reg))
```

# read in motion data
```{r warning = F, message = F}
all_sub_beh_data <- load_motion_censor(subjects_list)
```


## split-half validation

### make dataframe of all similarities, all thresholds
#### first half (using h2 template)
```{r warning = F, message = F}
glm_arrays_run12 <- load_fmri3_glm_arrays("h2", 1:490, subjects_list)
timing_run12 <- build_trial_timing_template(c("run-01", "run-02"))

my_array_s1_run12 <- join_glm_arrays_with_timing(
  glm_arrays_run12, timing_run12, "run12"
)
```

#### second half (using h1 template)
```{r warning = F, message = F}
glm_arrays_run34 <- load_fmri3_glm_arrays("h1", 491:980, subjects_list)
timing_run34 <- build_trial_timing_template(c("run-03", "run-04"))

my_array_s1_run34 <- join_glm_arrays_with_timing(
  glm_arrays_run34, timing_run34, "run34", tr_offset = 490L
)
```

```{r}
my_array_s1 <- rbind(my_array_s1_run12,my_array_s1_run34) %>% 
  left_join(all_sub_beh_data, by = c("subject","tr")) %>%  #combine censor file
  filter(censor == 1) #motion censoring
```


## get self-reported arousal template
```{r}
my_array_s1__ <- prepare_template_long(
  my_array_s1, TS_COL$glm_arousal, fmri3_data_2probes
)
my_array_s1__ <- add_pupil_lag2(my_array_s1__, my_array_s1)

lm.beta::lm.beta(lm(glmArousal ~ pupil_lag2, my_array_s1__))
```


## plot as function of cue value / outcome value
```{r}
d1<-my_array_s1__ %>% 
         filter(!is.na(hit)) %>% 
         group_by(tr_in_trial,subject,threshold,probe) %>% 
         summarise(glmArousal = mean(glmArousal,na.rm = T)) %>% 
         group_by(tr_in_trial,threshold,probe) %>% 
         summarise(mean = mean(glmArousal,na.rm = T),
                   se = sd(glmArousal,na.rm = T)/sqrt(n()))

p1m2a<-plot_spacer()+ggplot(d1 %>% filter(probe == "anticipation probe",threshold == 0.5, tr_in_trial <= PLOT_TR_ANT),
       aes(x = tr_in_trial, y = mean))+
  geom_vline(xintercept = c(3.5,4.5,5.5,9.5,10.5,11.5,12.5), size = 1, color = "grey")+
  annotate("text",x = 4,y = 0.08, label = "C")+
  annotate("text",x = 5,y = 0.08, label = "F")+
  annotate("text",x = 10,y = 0.08, label = "F")+
  annotate("text",x = 11,y = 0.08, label = "T")+
  annotate("text",x = 12,y = 0.08, label = "O")+
  annotate("text",x = 7.5,y = 0.08, label = "R")+
  geom_line(size = 0.5) +
  geom_point()+
  geom_errorbar(aes(x = tr_in_trial, ymin = mean-se,ymax = mean+se), width = 0.3)+
  labs(y = "Simalirty",
       x = "time (s)",
       subtitle = "anticipation probe")+
  scale_color_manual(values = redOrange_palette6)+
  theme(legend.position = "top")+
  ylim(-0.12,0.1)+
  scale_x_continuous(
    limits = trial_tr_scale(PLOT_TR_ANT)$limits,
    breaks = trial_tr_scale(PLOT_TR_ANT)$breaks,
    labels = trial_tr_scale(PLOT_TR_ANT)$labels
  ) +
plot_spacer()+
ggplot(d1 %>% filter(probe == "outcome probe",threshold == 0.5, tr_in_trial <= PLOT_TR_OUT),
       aes(x = tr_in_trial, y = mean))+
  geom_vline(xintercept = c(3.5,4.5,5.5,6.5,7.5,11.5), size = 1, color = "grey")+
  annotate("text",x = 4,y = 0.08, label = "C")+
  annotate("text",x = 5,y = 0.08, label = "F")+
  annotate("text",x = 6,y = 0.08, label = "T")+
  annotate("text",x = 7,y = 0.08, label = "O")+
  annotate("text",x = 10,y = 0.08, label = "R")+
  geom_line(size = 0.5) +
  geom_point()+
  geom_errorbar(aes(x = tr_in_trial, ymin = mean-se,ymax = mean+se), width = 0.3)+
  labs(y = "Simalirty",
       x = "time (s)",
       subtitle = "outcome probe",
      caption = "C = Cue, F = Fixation, \nT = Target, O = Outcome, R = Rating")+
  scale_color_manual(values = redOrange_palette6)+
  theme(legend.position = "top")+
  ylim(-0.1,0.1)+
  scale_x_continuous(
    limits = trial_tr_scale(PLOT_TR_OUT)$limits,
    breaks = trial_tr_scale(PLOT_TR_OUT)$breaks,
    labels = trial_tr_scale(PLOT_TR_OUT)$labels
  ) + plot_spacer() +
  plot_layout(widths = c(0.3,1,0.3,1,0.3))

d2<-my_array_s1__ %>% 
         filter(!is.na(hit),
                tr_in_trial == 5) %>% 
         group_by(subject,threshold,cue_value) %>% 
         summarise(glmArousal = mean(glmArousal,na.rm = T)) %>% 
         group_by(threshold,cue_value) %>% 
         summarise(mean = mean(glmArousal,na.rm = T),
                   se = sd(glmArousal,na.rm = T)/sqrt(n())) %>% 
  mutate(cue_value = factor(cue_value, levels = c("-$5","-$1","-$0","+$0","+$1","+$5")))

summary(l1<-lmer(scale(glmArousal) ~ cue_value + (1|split),
                   my_array_s1__ %>% 
                   filter(tr_in_trial == 5, threshold == 0.5)))

# Get effect size (standardized beta)
r2   <- r.squaredGLMM(l1)[1]

p2m2a<-ggplot(d2 %>% filter(threshold == 0.5),
       aes(x = cue_value, y = mean,color = cue_value))+
  geom_point(size = 0.5) +
  geom_point()+
  geom_errorbar(aes(x = cue_value, ymin = mean-se,ymax = mean+se), width = 0.3)+
  labs(y = "Simalirty",
       x = "time (s)",
       subtitle = "Inferred arousal (8s)")+
  scale_color_manual(values = redOrange_palette6)+
  theme(legend.position = "none")+  # show shape legend
  scale_x_discrete(breaks =c("-$5","-$1","-$0","+$0","+$1","+$5"))+
  annotate("text",x = Inf, y = -Inf, label = paste0("R² = ", round(r2, 2)),
    hjust = 1.1, vjust = -1.5, size = 4)

d3<-my_array_s1__ %>% 
         filter(!is.na(hit),
                ifelse(probe == "anticipation probe", tr_in_trial == 12,
                       ifelse(probe == "outcome probe",tr_in_trial == 7,NA))) %>% 
         group_by(subject,threshold,hit,cue_value) %>% 
         summarise(glmArousal = mean(glmArousal,na.rm = T)) %>% 
         group_by(threshold,hit,cue_value) %>% 
         summarise(mean = mean(glmArousal,na.rm = T),
                   se = sd(glmArousal,na.rm = T)/sqrt(n())) %>% 
  mutate(cue_value = factor(cue_value, levels = c("-$5","-$1","-$0","+$0","+$1","+$5")))

ggplot(d3 %>% filter(threshold == 0.5),
       aes(x = cue_value, y = mean, color = cue_value, shape = hit)) +
  geom_point(position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(x = cue_value, group = hit, ymin = mean - se, ymax = mean + se),
                width = 0.3, position = position_dodge(width = 0.5)) +
  labs(y = "Similarity",
       x = "time (s)",
       subtitle = "arousal index during outcome") +
  theme(legend.position = "top") +
  scale_color_manual(values = redOrange_palette6) +
  guides(color = "none",  # hide color legend
         shape = guide_legend())+  # show shape legend
  scale_x_discrete(breaks =c("-$5","-$1","-$0","+$0","+$1","+$5"))

summary(l2<-lmer(glmArousal~cue_value*hit+(1|split),my_array_s1__ %>% filter(ifelse(
  probe == "anticipation probe", tr_in_trial == 12,
                       ifelse(probe == "outcome probe",tr_in_trial == 7,NA)))))
anova(l2)
```

#### predicting performance
```{r warning=F}
df_performance <- fit_hit_grid(my_array_s1__, model_grid_split, TS_COL$glm_arousal)

ggplot(df_performance, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe,linetype = split))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  facet_wrap(~threshold)+
  scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = seq_len(TR_DELAY))

ggplot(df_performance %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_line(aes(color= probe,linetype = split))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = seq_len(TR_DELAY))

summary(l1 <- glmer(
  hit_num ~ scale(glmArousal) + (1 | split),
  family = binomial,
  my_array_s1__ %>%
    filter(tr_in_trial == 5, threshold == 0.5) %>%
    mutate(hit_num = as.integer(hit == "Hit"))
))
## controlling for pupil size
summary(glmer(
  hit_num ~ scale(glmArousal) + scale(pupil_lag2) + (1 | split),
  family = binomial,
  my_array_s1__ %>%
    filter(tr_in_trial == 5, threshold == 0.5) %>%
    mutate(hit_num = as.integer(hit == "Hit"))
))

# Get effect size (standardized beta)
beta <- summary(l1)$coefficients["scale(glmArousal)", "Estimate"]
r2   <- r.squaredGLMM(l1)[1,1]

# Create base plot
p3m2a <- plot_model(l1, type = "pred", terms = "glmArousal[all]",color = "darkgrey") +
  labs(x = "similarity (z-score)",
       y = "p(hit)",title = "p(hit)") +
  annotate("text",x = Inf, y = -Inf, label = paste0("β = ", round(beta, 2), "\nR²m = ", round(r2, 2)),
    hjust = 1.1, vjust = -0.5, size = 4)
```

```{r warning=F}
df_performance <- fit_rt_grid(my_array_s1__, model_grid_split, TS_COL$glm_arousal)

ggplot(df_performance, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe,linetype = split))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  facet_wrap(~threshold)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = seq_len(TR_DELAY))

ggplot(df_performance %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_line(aes(color= probe,linetype = split))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = seq_len(TR_DELAY))

summary(l1<-lmer(scale(rt_log) ~ scale(glmArousal) + (1|split),
                   my_array_s1__ %>% 
                   filter(tr_in_trial == 5, hit == "Hit",threshold == 0.5)))
#controlling for pupil size
summary(lmer(scale(rt_log) ~ scale(glmArousal) + scale(pupil_lag2) + (1|split),
                   my_array_s1__ %>% 
                   filter(tr_in_trial == 5, hit == "Hit",threshold == 0.5)))

# Get effect size (standardized beta)
beta <- summary(l1)$coefficients["scale(glmArousal)", "Estimate"]
r2   <- r.squaredGLMM(l1)[1]

# Create base plot
p4m2a <- plot_model(l1, type = "pred", terms = "glmArousal",color = "darkgrey") +
  labs(x = "similarity (z-score)",
    y = "log rt (z-score)",
    title = "log rt (hit trials)"
  ) +
  annotate("text",x = Inf, y = -Inf, label = paste0("β = ", round(beta, 2), "\nR²m = ", round(r2, 2)),
    hjust = 1.1, vjust = -1.5, size = 4)

```


#### predicting cue value (abs)
```{r warning=F}
df_cue <- fit_cue_grid(my_array_s1__, model_grid_split, TS_COL$glm_arousal)


ggplot(df_cue, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe,linetype = split))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  facet_wrap(~threshold)+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = seq_len(TR_DELAY))

ggplot(df_cue %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_line(aes(color= probe,linetype = split))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = seq_len(TR_DELAY))

summary(l1 <- lmer(
  scale(cue_value_abs) ~ scale(glmArousal) + (1 | split),
  my_array_s1__ %>%
    filter(tr_in_trial == 5, threshold == 0.5) %>%
    mutate(cue_value_abs = cue_value_to_abs(cue_value))
))
## controlling for pupil size

summary(lmer(
  scale(cue_value_abs) ~ scale(glmArousal) + scale(pupil_lag2) + (1 | split),
  my_array_s1__ %>%
    filter(tr_in_trial == 5, threshold == 0.5) %>%
    mutate(cue_value_abs = cue_value_to_abs(cue_value))
))
# Get effect size (standardized beta)
beta <- summary(l1)$coefficients["scale(glmArousal)", "Estimate"]
r2   <- r.squaredGLMM(l1)[1]

# Create base plot
p5m2a <- plot_model(l1, type = "pred", terms = "glmArousal") +
  labs(x = "similarity to arousal template (z-score)",
    y = "abs. cue value (z-score)",
    title = "abs. cue value (z-score)"
  ) +
  annotate("text",x = Inf, y = -Inf, label = paste0("β = ", round(beta, 2), ", R²m = ", round(r2, 2)),
    hjust = 1.1, vjust = -1.5, size = 4)
```

#### predicting self-reports
```{r}
df_rating <- fit_rating_grid(my_array_s1__, model_grid_split, TS_COL$glm_arousal)


ggplot(df_rating, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe,linetype= split))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  # geom_ribbon(aes(x = tr, ymin = Estimate - se,
  #                   ymax = Estimate + se,fill = probe),
  #             alpha = 0.1)+
  facet_wrap(~threshold)+
  labs(title = "FMRI study")+
  scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  scale_x_continuous(breaks = seq_len(TR_DELAY))+
  geom_vline(xintercept = 5, color = "purple",label = "F")+
  geom_vline(xintercept = 6, color = "skyblue",label = "T")+
  geom_vline(xintercept = 7, color = "purple", linetype = "dashed")+
  geom_vline(xintercept = 9, color = "skyblue", linetype = "dashed")

ggplot(df_rating %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_line(aes(color= probe,linetype= split))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = seq_len(TR_DELAY))


```

#### visualize peak correlation
```{r}
# Prepare data
d1 <- my_array_s1__ %>% filter(tr_in_trial == 5, threshold == 0.5)
d2 <- my_array_s1__ %>% filter(tr_in_trial == 5, probe == "anticipation probe", threshold == 0.5)
d3 <- my_array_s1__ %>% filter(tr_in_trial == 7, probe == "outcome probe", threshold == 0.5)

# Fit models
l1 <- lmer(scale(arousal_scaled) ~ scale(glmArousal) + (1|split), d1)
l2 <- lmer(scale(arousal_scaled) ~ scale(glmArousal) + (1|split), d2)
l3 <- lmer(scale(arousal_scaled) ~ scale(glmArousal) + (1|split), d3)
# Extract coefficients and p-values
get_stats <- function(model) {
  b <- coef(summary(model))["scale(glmArousal)", "Estimate"]
  p <- coef(summary(model))["scale(glmArousal)", "Pr(>|t|)"]
  list(beta = round(b, 3), p = signif(p, 3))
}

s1 <- get_stats(l1)
s2 <- get_stats(l2)
s3 <- get_stats(l3)

## controlling for pupil size
summary(ll<-lmer(scale(arousal_scaled) ~ scale(glmArousal) + scale(pupil_lag2)+ (1|split), d1))
summary(lmer(scale(arousal_scaled) ~ scale(glmArousal) + scale(pupil_lag2)+ (1|split), d2))
summary(lmer(scale(arousal_scaled) ~ scale(glmArousal) + scale(pupil_lag2)+ (1|split), d3))

new1_dat <- d1 %>%
  summarise(
    glmArousal = seq(min(glmArousal, na.rm = TRUE),
                     max(glmArousal, na.rm = TRUE),
                     length.out = 100)
  )

new2_dat <- d2 %>%
  summarise(
    glmArousal = seq(min(glmArousal, na.rm = TRUE),
                     max(glmArousal, na.rm = TRUE),
                     length.out = 100)
  )

new3_dat <- d3 %>%
  summarise(
    glmArousal = seq(min(glmArousal, na.rm = TRUE),
                     max(glmArousal, na.rm = TRUE),
                     length.out = 100)
  )

new1 <- predict_ci(l1, new1_dat)
new2 <- predict_ci(l2, new2_dat)
new3 <- predict_ci(l3, new3_dat)


# Plot
p_m2_arousal_c <- ggplot() +
  ## Model 1 -- black
  geom_ribbon(data = new1,
              aes(x = scale(glmArousal), ymin = lwr, ymax = upr),
              fill = "black", alpha = 0.15) +
  geom_line(data = new1,
            aes(x = scale(glmArousal), y = fit),
            color = "black", size = 1) +

  ## Model 2 -- purple
  geom_ribbon(data = new2,
              aes(x = scale(glmArousal), ymin = lwr, ymax = upr),
              fill = "purple", alpha = 0.15) +
  geom_line(data = new2,
            aes(x = scale(glmArousal), y = fit),
            color = "purple", size = 1) +

  ## Model 3 -- skyblue
  geom_ribbon(data = new3,
              aes(x = scale(glmArousal), ymin = lwr, ymax = upr),
              fill = "skyblue", alpha = 0.15) +
  geom_line(data = new3,
            aes(x = scale(glmArousal), y = fit),
            color = "skyblue", size = 1) +

  # Add beta + p-value text with < .001 formatting
  annotate("text", x = -1.5, y = max(new1$upr)+0.6, size=3.5,
           label = paste0("both (8s): β=", round(s1$beta,2), 
                          ", p", ifelse(s1$p < 0.001, "< .001", paste0("=",round(s1$p, 3)))),
           color = "black", hjust = 0) +
  annotate("text", x = -1.5, y = max(new1$upr)+0.2, size=3.5,
           label = paste0("ant (8s): β=", round(s2$beta,2), 
                          ", p", ifelse(s2$p < 0.001, "< .001", paste0("=",round(s2$p, 3)))),
           color = "purple", hjust = 0) +
  annotate("text", x = -1.5, y = max(new1$upr)+0.4, size=3.5,
           label = paste0("out (12s): β=", round(s3$beta,2), 
                          ", p", ifelse(s3$p < 0.001, "< .001", paste0("=",round(s3$p, 3)))),
           color = "skyblue", hjust = 0)+
  labs(
    x = "similarity (scaled)",
    y = "Predicted arousal (scaled)"
  )
```

```{r}
(p1m2a)/
(p2m2a+p3m2a+p4m2a+p_m2_arousal_c+plot_layout(widths = c(1.2,1,1,1.2)))+
plot_annotation(title = "Arousal template",
                  tag_levels = "A")

ggsave("../../../figures/fig_glmArousal.png", dpi = 300, height = 6, width = 11)
```

## get pupil glm template
```{r}
my_array_s1_ <- prepare_template_long(
  my_array_s1, TS_COL$glm_pupil, fmri3_data_2probes
)
my_array_s1_ <- add_pupil_lag2(my_array_s1_, my_array_s1)

lm.beta::lm.beta(lm(glmPupil ~ pupil_lag2, my_array_s1_))
```

## plot as function of cue value / outcome value
```{r}
d1<-my_array_s1_ %>% 
         filter(!is.na(hit)) %>% 
         group_by(tr_in_trial,subject,threshold,probe) %>% 
         summarise(glmPupil = mean(glmPupil,na.rm = T)) %>% 
         group_by(tr_in_trial,threshold,probe) %>% 
         summarise(mean = mean(glmPupil,na.rm = T),
                   se = sd(glmPupil,na.rm = T)/sqrt(n()))

p1m2p<-plot_spacer()+ggplot(d1 %>% filter(probe == "anticipation probe",threshold == 0.5, tr_in_trial <= PLOT_TR_ANT),
       aes(x = tr_in_trial, y = mean))+
  geom_vline(xintercept = c(3.5,4.5,5.5,9.5,10.5,11.5,12.5), size = 1, color = "grey")+
  geom_hline(yintercept = 0, color = "grey")+
  annotate("text",x = 4,y = 0.08, label = "C")+
  annotate("text",x = 5,y = 0.08, label = "F")+
  annotate("text",x = 10,y = 0.08, label = "F")+
  annotate("text",x = 11,y = 0.08, label = "T")+
  annotate("text",x = 12,y = 0.08, label = "O")+
  annotate("text",x = 7.5,y = 0.08, label = "R")+
  geom_line(size = 0.5) +
  geom_point()+
  geom_errorbar(aes(x = tr_in_trial, ymin = mean-se,ymax = mean+se), width = 0.3)+
  labs(y = "Simalirty",
       x = "time (s)",
       subtitle = "anticipation probe")+
  scale_color_manual(values = redOrange_palette6)+
  theme(legend.position = "top")+
  ylim(-0.1,0.1)+
  scale_x_continuous(
    limits = trial_tr_scale(PLOT_TR_ANT)$limits,
    breaks = trial_tr_scale(PLOT_TR_ANT)$breaks,
    labels = trial_tr_scale(PLOT_TR_ANT)$labels
  ) +
ggplot(d1 %>% filter(probe == "outcome probe",threshold == 0.5, tr_in_trial <= PLOT_TR_OUT),
       aes(x = tr_in_trial, y = mean))+
  geom_vline(xintercept = c(3.5,4.5,5.5,6.5,7.5,11.5), size = 1, color = "grey")+
    geom_hline(yintercept = 0, color = "grey")+
  annotate("text",x = 4,y = 0.08, label = "C")+
  annotate("text",x = 5,y = 0.08, label = "F")+
  annotate("text",x = 6,y = 0.08, label = "T")+
  annotate("text",x = 7,y = 0.08, label = "O")+
  annotate("text",x = 10,y = 0.08, label = "R")+
  geom_line(size = 0.5) +
  geom_point()+
  geom_errorbar(aes(x = tr_in_trial, ymin = mean-se,ymax = mean+se), width = 0.3)+
  labs(y = "Simalirty",
       x = "time (s)",
       subtitle = "outcome probe",
      caption = "C = Cue, F = Fixation, \nT = Target, O = Outcome, R = Rating")+
  scale_color_manual(values = redOrange_palette6)+
  theme(legend.position = "top")+
  ylim(-0.1,0.1)+
  scale_x_continuous(
    limits = trial_tr_scale(PLOT_TR_OUT)$limits,
    breaks = trial_tr_scale(PLOT_TR_OUT)$breaks,
    labels = trial_tr_scale(PLOT_TR_OUT)$labels
  ) +
  plot_layout(widths = c(0.3, 1, 1))

d2<-my_array_s1_ %>% 
         filter(!is.na(hit),
                tr_in_trial == 5) %>% 
         group_by(subject,threshold,cue_value) %>% 
         summarise(glmPupil = mean(glmPupil,na.rm = T)) %>% 
         group_by(threshold,cue_value) %>% 
         summarise(mean = mean(glmPupil,na.rm = T),
                   se = sd(glmPupil,na.rm = T)/sqrt(n())) %>% 
  mutate(cue_value = factor(cue_value, levels = c("-$5","-$1","-$0","+$0","+$1","+$5")))

summary(l1<-lmer(scale(glmPupil) ~ cue_value + (1|split),
                   my_array_s1_ %>% 
                   filter(tr_in_trial == 5, threshold == 0.5)))
anova(l1)
# Get effect size 
r2   <- r.squaredGLMM(l1)[1]

p2m2p<-ggplot(d2 %>% filter(threshold == 0.5),
       aes(x = cue_value, y = mean,color = cue_value))+
  geom_point(size = 0.5) +
  geom_point()+
  geom_errorbar(aes(x = cue_value, ymin = mean-se,ymax = mean+se), width = 0.3)+
  labs(y = "Simalirty",
       x = "time (s)",
       subtitle = "Inferred arousal at fixation")+
  scale_color_manual(values = redOrange_palette6)+
  theme(legend.position = "none")+  # show shape legend
  scale_x_discrete(breaks =c("-$5","-$1","-$0","+$0","+$1","+$5"))+
  annotate("text",x = Inf, y = -Inf, label = paste0("R² = ", round(r2, 2)),
    hjust = 1.1, vjust = -1.5, size = 4)

d3<-my_array_s1_ %>% 
         filter(!is.na(hit),
                ifelse(probe == "anticipation probe", tr_in_trial == 12,
                       ifelse(probe == "outcome probe",tr_in_trial == 7,NA))) %>% 
         group_by(subject,threshold,hit,cue_value) %>% 
         summarise(glmPupil = mean(glmPupil,na.rm = T)) %>% 
         group_by(threshold,hit,cue_value) %>% 
         summarise(mean = mean(glmPupil,na.rm = T),
                   se = sd(glmPupil,na.rm = T)/sqrt(n())) %>% 
  mutate(cue_value = factor(cue_value, levels = c("-$5","-$1","-$0","+$0","+$1","+$5")))

ggplot(d3 %>% filter(threshold == 0.5),
       aes(x = cue_value, y = mean, color = cue_value, shape = hit)) +
  geom_point(position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(x = cue_value, group = hit, ymin = mean - se, ymax = mean + se),
                width = 0.3, position = position_dodge(width = 0.5)) +
  labs(y = "Similarity",
       x = "time (s)",
       subtitle = "arousal index during outcome") +
  theme(legend.position = "top") +
  scale_color_manual(values = redOrange_palette6) +
  guides(color = "none",  # hide color legend
         shape = guide_legend())+  # show shape legend
  scale_x_discrete(breaks =c("-$5","-$1","-$0","+$0","+$1","+$5"))

summary(l2<-lmer(glmPupil~cue_value*hit+(1|split),my_array_s1_ %>% filter(ifelse(
  probe == "anticipation probe", tr_in_trial == 12,
                       ifelse(probe == "outcome probe",tr_in_trial == 7,NA)))))
anova(l2)
```

#### predicting performance
```{r warning=F}
df_performance <- fit_hit_grid_pooled(my_array_s1_, model_grid_pooled, TS_COL$glm_pupil)

ggplot(df_performance, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  facet_wrap(~threshold)+
  scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = seq_len(TR_DELAY))

p_thresh_hit<-ggplot(df_performance %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_point(aes(color= probe))+
  geom_errorbar(aes(color= probe, x = threshold, ymin = Estimate - se,
                    ymax = Estimate + se), width = 0.1)+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "p(hit)")+
  scale_x_continuous(breaks = seq_len(TR_DELAY))+
  annotate("rect",xmin = 0.25,xmax = 0.75, ymin = -0.05,ymax = 0.4,alpha = 0.1)

summary(l1_hit <- glmer(
  hit_num ~ scale(glmPupil) + (1 | split),
  family = binomial,
  my_array_s1_ %>%
    filter(tr_in_trial == 5, threshold == 0.5) %>%
    mutate(hit_num = as.integer(hit == "Hit"))
))
## controlling for pupil size
summary(glmer(
  hit_num ~ scale(glmPupil) + scale(pupil_lag2) + (1 | split),
  family = binomial,
  my_array_s1_ %>%
    filter(tr_in_trial == 5, threshold == 0.5) %>%
    mutate(hit_num = as.integer(hit == "Hit"))
))
# Get effect size (standardized beta)
beta <- summary(l1_hit)$coefficients["scale(glmPupil)", "Estimate"]
r2   <- r.squaredGLMM(l1_hit)[1,1]

# Create base plot
p3m2p <- plot_model(l1_hit, type = "pred", terms = "glmPupil[all]",color = "darkgrey") +
  labs(x = "similarity (z-score)",
       y = "p(hit)",title = "p(hit)") +
  annotate("text",x = Inf, y = -Inf, label = paste0("β = ", round(beta, 2), "\nR²m = ", round(r2, 2)),
    hjust = 1.1, vjust = -0.5, size = 4)
```

### predictive performance
```{r}
data_used <- my_array_s1_ %>%
  filter(tr_in_trial == 5, threshold == 0.5) %>%
  mutate(hit_num = as.integer(hit == "Hit")) %>%
  filter(!is.na(glmPupil), !is.na(hit_num))

# Refit the hit model in this chunk so predictions are not affected by
# other chunks that reuse l1 (e.g. RT or cue-value models).
l1_hit <- glmer(
  hit_num ~ scale(glmPupil) + (1 | split),
  family = binomial,
  data = data_used
)

pred_probs <- predict(
  l1_hit,
  newdata = data_used,
  type = "response",
  re.form = NA
)

pred_class <- as.integer(pred_probs > 0.5)
actual_class <- data_used$hit_num

accuracy <- mean(pred_class == actual_class)
accuracy

table(Predicted = pred_class, Actual = actual_class)

roc_obj <- pROC::roc(actual_class, pred_probs)
pROC::auc(roc_obj)

set.seed(777)
ci <- pROC::ci.auc(roc_obj, method = "bootstrap", boot.n = 2000)
ci
```


```{r warning=F}
df_performance <- fit_rt_grid_pooled(my_array_s1_, model_grid_pooled, TS_COL$glm_pupil)

ggplot(df_performance, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  facet_wrap(~threshold)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = seq_len(TR_DELAY))

p_thresh_rt<-ggplot(df_performance %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_point(aes(color= probe))+
  geom_errorbar(aes(color= probe, x = threshold, ymin = Estimate - se,
                    ymax = Estimate + se), width = 0.1)+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "log RT")+
  scale_x_continuous(breaks = seq_len(TR_DELAY))+
  annotate("rect",xmin = 0.25,xmax = 0.75, ymin = -0.3,ymax = 0,alpha = 0.1)+
  theme(legend.position = "none")

summary(l1<-lmer(scale(rt_log) ~ scale(glmPupil) + (1|split),
                   my_array_s1_ %>% 
                   filter(tr_in_trial == 5, hit == "Hit",threshold == 0.5)))

## controlling for pupil size
summary(lmer(scale(rt_log) ~ scale(glmPupil) + scale(pupil_lag2) + (1|split),
                   my_array_s1_ %>% 
                   filter(tr_in_trial == 5, hit == "Hit",threshold == 0.5)))
# Get effect size (standardized beta)
beta <- summary(l1)$coefficients["scale(glmPupil)", "Estimate"]
r2   <- r.squaredGLMM(l1)[1]

# Create base plot
p4m2p <- plot_model(l1, type = "pred", terms = "glmPupil",color = "darkgrey") +
  labs(x = "similarity (z-score)",
    y = "log rt (z-score)",
    title = "log rt (hit trials)"
  ) +
  annotate("text",x = Inf, y = -Inf, label = paste0("β = ", round(beta, 2), "\nR²m = ", round(r2, 2)),
    hjust = 1.1, vjust = -1.5, size = 4)

```

#### predicting cue value (abs)
```{r warning=F}
df_cue <- fit_cue_grid(
  my_array_s1_, model_grid_pooled, TS_COL$glm_pupil, use_glmer = TRUE
)


ggplot(df_cue, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  facet_wrap(~threshold)+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = seq_len(TR_DELAY))

p_thresh_cue<-ggplot(df_cue %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_point(aes(color= probe))+
  geom_errorbar(aes(color= probe, x = threshold, ymin = Estimate - se,
                    ymax = Estimate + se), width = 0.1)+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "Abs cue value")+
  scale_x_continuous(breaks = seq_len(TR_DELAY))+
  annotate("rect",xmin = 0.25,xmax = 0.75, ymin = 0.1,ymax = 0.8,alpha = 0.1)+
  theme(legend.position = "none")

summary(l1 <- lmer(
  scale(cue_value_abs) ~ scale(glmPupil) + (1 | split),
  my_array_s1_ %>%
    filter(tr_in_trial == 5, threshold == 0.5) %>%
    mutate(cue_value_abs = cue_value_to_abs(cue_value))
))

summary(lmer(
  scale(cue_value_abs) ~ scale(glmPupil) + scale(pupil_lag2) + (1 | split),
  my_array_s1_ %>%
    filter(tr_in_trial == 5, threshold == 0.5) %>%
    mutate(cue_value_abs = cue_value_to_abs(cue_value))
))
# Get effect size (standardized beta)
beta <- summary(l1)$coefficients["scale(glmPupil)", "Estimate"]
r2   <- r.squaredGLMM(l1)[1]

# Create base plot
p5m2p <- plot_model(l1, type = "pred", terms = "glmPupil") +
  labs(x = "similarity to arousal template (z-score)",
    y = "abs. cue value (z-score)",
    title = "abs. cue value (z-score)"
  ) +
  annotate("text",x = Inf, y = -Inf, label = paste0("β = ", round(beta, 2), ", R²m = ", round(r2, 2)),
    hjust = 1.1, vjust = -1.5, size = 4)
```

#### predicting self-reports
```{r}
df_rating <- fit_rating_grid(
  my_array_s1_, model_grid_pooled, TS_COL$glm_pupil, use_glmer = TRUE
)


ggplot(df_rating, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  # geom_ribbon(aes(x = tr, ymin = Estimate - se,
  #                   ymax = Estimate + se,fill = probe),
  #             alpha = 0.1)+
  facet_wrap(~threshold)+
  labs(title = "FMRI study")+
  scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  scale_x_continuous(breaks = seq_len(TR_DELAY))+
  geom_vline(xintercept = 5, color = "purple",label = "F")+
  geom_vline(xintercept = 6, color = "skyblue",label = "T")+
  geom_vline(xintercept = 7, color = "purple", linetype = "dashed")+
  geom_vline(xintercept = 9, color = "skyblue", linetype = "dashed")

p_thresh_rate<-ggplot(df_rating %>% filter(tr <= 14), aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_point(aes(color= probe))+
  geom_errorbar(aes(color= probe, x = tr, ymin = Estimate - se,
                    ymax = Estimate + se), width = 0.1)+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "Arousal rating")+
  scale_x_continuous(breaks = seq_len(TR_DELAY))+
  theme(legend.position = "none")+
  facet_wrap(~threshold,nrow = 2)
```

```{r}
(p_thresh_hit+p_thresh_cue+p_thresh_rt)/
  p_thresh_rate+
  plot_layout(heights = c(1,2))+
  plot_annotation(tag_levels = "A")

ggsave("../../../figures/si_pattern_threshold.png", dpi = 300, height = 5, width = 8)
```

#### visualize peak correlation
```{r}
# Prepare data
d1 <- my_array_s1_ %>% filter(tr_in_trial == 5, threshold == 0.5)
d2 <- my_array_s1_ %>% filter(tr_in_trial == 5, probe == "anticipation probe", threshold == 0.5)
d3 <- my_array_s1_ %>% filter(tr_in_trial == 7, probe == "outcome probe", threshold == 0.5)

# Fit models
l1 <- lmer(scale(arousal_scaled) ~ scale(glmPupil) + (1|split), d1)
l2 <- lmer(scale(arousal_scaled) ~ scale(glmPupil) + (1|split), d2)
l3 <- lmer(scale(arousal_scaled) ~ scale(glmPupil) + (1|split), d3)
# Extract coefficients and p-values
get_stats <- function(model) {
  b <- coef(summary(model))["scale(glmPupil)", "Estimate"]
  p <- coef(summary(model))["scale(glmPupil)", "Pr(>|t|)"]
  list(beta = round(b, 3), p = signif(p, 3))
}

s1 <- get_stats(l1)
s2 <- get_stats(l2)
s3 <- get_stats(l3)

## controlling for pupil size
summary(lmer(scale(arousal_scaled) ~ scale(glmPupil) + scale(pupil_lag2) + (1|split), d1))
summary(lmer(scale(arousal_scaled) ~ scale(glmPupil) + scale(pupil_lag2) + (1|split), d2))
summary(lmer(scale(arousal_scaled) ~ scale(glmPupil) + scale(pupil_lag2) + (1|split), d3))

new1_dat <- d1 %>%
  summarise(
    glmPupil = seq(min(glmPupil, na.rm = TRUE),
                     max(glmPupil, na.rm = TRUE),
                     length.out = 100)
  )

new2_dat <- d2 %>%
  summarise(
    glmPupil = seq(min(glmPupil, na.rm = TRUE),
                     max(glmPupil, na.rm = TRUE),
                     length.out = 100)
  )

new3_dat <- d3 %>%
  summarise(
    glmPupil = seq(min(glmPupil, na.rm = TRUE),
                     max(glmPupil, na.rm = TRUE),
                     length.out = 100)
  )

new1 <- predict_ci(l1, new1_dat)
new2 <- predict_ci(l2, new2_dat)
new3 <- predict_ci(l3, new3_dat)


# Plot
p_m2_pupil_c <- ggplot() +
  ## Model 1 -- black
  geom_ribbon(data = new1,
              aes(x = scale(glmPupil), ymin = lwr, ymax = upr),
              fill = "black", alpha = 0.15) +
  geom_line(data = new1,
            aes(x = scale(glmPupil), y = fit),
            color = "black", size = 1) +

  ## Model 2 -- purple
  geom_ribbon(data = new2,
              aes(x = scale(glmPupil), ymin = lwr, ymax = upr),
              fill = "purple", alpha = 0.15) +
  geom_line(data = new2,
            aes(x = scale(glmPupil), y = fit),
            color = "purple", size = 1) +

  ## Model 3 -- skyblue
  geom_ribbon(data = new3,
              aes(x = scale(glmPupil), ymin = lwr, ymax = upr),
              fill = "skyblue", alpha = 0.15) +
  geom_line(data = new3,
            aes(x = scale(glmPupil), y = fit),
            color = "skyblue", size = 1) +

  # Add beta + p-value text with < .001 formatting
  annotate("text", x = -1.5, y = max(new1$upr)+0.6, size=3.5,
           label = paste0("both (fix): β=", round(s1$beta,2), 
                          ", p", ifelse(s1$p < 0.001, "< .001", paste0("= ",round(s1$p, 3)))),
           color = "black", hjust = 0) +
  annotate("text", x = -1.5, y = max(new1$upr)+0.2, size=3.5,
           label = paste0("ant (fix): β=", round(s2$beta,2), 
                          ", p", ifelse(s2$p < 0.001, "< .001",paste0("= ",round(s2$p, 3)))),
           color = "purple", hjust = 0) +
  annotate("text", x = -1.5, y = max(new1$upr)+0.4, size=3.5,
           label = paste0("out (out): β=", round(s3$beta,2), 
                          ", p", ifelse(s3$p < 0.001, "< .001", paste0("= ",round(s3$p, 3)))),
           color = "skyblue", hjust = 0)+
  labs(
    x = "similarity (scaled)",
    y = "Predicted arousal (scaled)"
  )
```


#### correlation with pupil size
```{r}
cor(my_array_s1 %>% 
      filter(threshold == 0.5) %>% 
      group_by(subject,split) %>% 
      mutate(pupil_lag2= lag(pupil,2))%>% 
      ungroup() %>% 
      select(glmPupil,glmArousal,pupil_lag2),use = "complete.obs")

# get the cross-correlogram
lags <- -3:8


lag_results <- lapply(lags, function(l){

  dat_lag <- my_array_s1 %>%
    filter(threshold == 0.5) %>%
    group_by(subject, split) %>%
    mutate(pupil_lag = if (l >= 0) {lag(pupil,  l)} 
           else {lead(pupil, -l)}
    ) %>%
    ungroup() %>%
    filter(!is.na(pupil_lag), !is.na(glmPupil))

  m <- lmer(
    scale(glmPupil) ~ scale(pupil_lag) + (1 | split),
    data = dat_lag,
    REML = FALSE
  )

  broom.mixed::tidy(m) %>%
    filter(term == "scale(pupil_lag)") %>%
    mutate(lag = l)
})

lag_df <- bind_rows(lag_results)

lag_df <- lag_df %>% 
  mutate(lag_new = lag -3)

# continuous correlation
#the neural arousal index needs to be lagged for 3 TRs, and pupil 1TR. Thus, it's a relative lag of 2TRs.
summary(lmer(scale(glmPupil) ~ scale(pupil_lag2) + (1|split),my_array_s1 %>% 
              filter(threshold == 0.5) %>% 
          group_by(subject,split) %>% mutate(pupil_lag2= lag(pupil,2))))

# TR5 with the pre-defined window's pupil size
summary(lmer(scale(glmPupil) ~ scale(mean_pupil_nobc)+ (1|split),my_array_s1_ %>% 
              filter(threshold == 0.5,tr_in_trial == 4)))

corr_mat <- my_array_s1 %>%
  filter(threshold == 0.5) %>%
  group_by(subject) %>%
  mutate(pupil_lag2 = lag(pupil, 2)) %>%
  ungroup() %>%
  select(glmPupil, glmArousal, pupil_lag2) %>%
  cor(use = "complete.obs")

# Convert to long format for ggplot
corr_long <- reshape2::melt(corr_mat)

# Plot correlation heatmap
ggplot(corr_long, aes(Var1, Var2, fill = value)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(value, 2)), color = "black", size = 5) +
  scale_fill_gradient2(low = "blue", high = "red", mid = "white",
                       midpoint = 0, limit = c(-1, 1), name = "Correlation") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    panel.grid = element_blank()
  ) +
  coord_fixed() +
  labs(x = "", y = "", title = "Correlation Matrix (threshold = 0.5)")

ggsave("../../../figures/arousal_index_corr_s1.png", dpi = 300, height = 5, width = 6)


corr_mat1 <- my_array_s1 %>%
  filter(threshold == 0.5,split == "run12") %>%
  group_by(subject) %>%
  mutate(pupil_lag2 = lag(pupil, 2)) %>%
  ungroup() %>%
  select(glmPupil, glmArousal, pupil_lag2) %>%
  cor(use = "complete.obs")
corr_mat2 <- my_array_s1 %>%
  filter(threshold == 0.5,split == "run34") %>%
  group_by(subject) %>%
  mutate(pupil_lag2 = lag(pupil, 2)) %>%
  ungroup() %>%
  select(glmPupil, glmArousal, pupil_lag2) %>%
  cor(use = "complete.obs")
# Convert to long format for ggplot
corr_long1 <- reshape2::melt(corr_mat1)
corr_long2 <- reshape2::melt(corr_mat2)
# Plot correlation heatmap
new_labels <- c("glm_pupil", "glm_arousal", "pupil_size")

  
ggplot(corr_long1, aes(Var1, Var2, fill = value)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(value, 2)), color = "black", size = 5) +
  scale_fill_gradient2(
    low = "blue", high = "red", mid = "white",
    midpoint = 0, limit = c(-1, 1), name = "Correlation"
  ) +
  scale_x_discrete(labels = new_labels) +
  scale_y_discrete(labels = new_labels) +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    panel.grid = element_blank()
  ) +
  coord_fixed() +
  labs(x = "", y = "", title = "Correlation Matrix (threshold = 0.5)",
       subtitle = "test 1st half")+


ggplot(corr_long2, aes(Var1, Var2, fill = value)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(value, 2)), color = "black", size = 5) +
  scale_fill_gradient2(
    low = "blue", high = "red", mid = "white",
    midpoint = 0, limit = c(-1, 1), name = "Correlation"
  ) +
  scale_x_discrete(labels = new_labels) +
  scale_y_discrete(labels = new_labels) +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    panel.grid = element_blank()
  ) +
  coord_fixed() +
  labs(x = "", y = "",
       subtitle = "test 2nd half")+
  plot_annotation(tag_levels = "A")


ggsave("../../../figures/arousal_index_corr_s2_split.png", dpi = 300, height = 5, width = 10)

p_cc <- 
ggplot(lag_df, aes(x = lag_new, y = estimate)) +
  geom_hline(yintercept = 0,  color = "grey") +
    geom_vline(xintercept = 0, color = "grey", size = 1)+
  geom_line() +
  geom_point(size = 2) +
  geom_errorbar(
    aes(ymin = estimate - std.error,
        ymax = estimate + std.error),
    width = 0.2
  ) +
  labs(
    x = "Lag (s)",
    y = "β",
    title = "Cross-correlation",
    subtitle = "pupil's lag relative to the arousal index"
  ) +
  annotate("text",x = -4, y = 0.05, label = "pupil leads", color = "darkgrey")+
  annotate("text",x = 3, y = 0.05, label = "pupil follows", color = "darkgrey")+
  scale_x_continuous(breaks = lag_df$lag_new, labels = 2*(lag_df$lag_new))#lags + 3 because the arousal index was lagged for 3TRs

```

```{r}
brain_img <- image_read("../../../figures/brain_fig_a.png")

# Convert to raster
brain_raster <- as.raster(brain_img)

# Turn it into a ggplot object
p_brain <- ggplot() +
  annotation_raster(brain_raster, xmin = -Inf, xmax = Inf,
                    ymin = -Inf, ymax = Inf) +
  theme_void()
```

```{r}
p_brain/
(p_cc+p1m2p+
  plot_layout(nrow=1,widths = c(1.2,3.5)))/
(p2m2p+p3m2p+p4m2p+p_m2_pupil_c+
  plot_layout(nrow=1,widths = c(1.2,1,1,1.2)))+
plot_annotation(
                  tag_levels = "A")+
  plot_layout(heights = c(1.5,1,1))


ggsave("../../../figures/fig_glmPupil.png", dpi = 300, height = 9.5, width = 12)
```
