---
title: "manipulation_check_cue"
output: html_document
date: "2025-11-12"
---

```{r setup, include=FALSE}
source("../helper/save_figure.R")
```

Checking if affect and pupil size responds to cue value and outcome
# rating behavior on affective circumplex
```{r}
aff_traj_avg_ant_noRotat <- vrmid1_data_antprobe%>%
  mutate(probe == "anti") %>% 
  ungroup()%>%
  group_by(Subject,trial_type,probe)%>%
  summarise(valence = mean(valence, na.rm = T),
            arousal = mean(arousal, na.rm = T)) %>% 
  group_by(trial_type,probe)%>%
  summarise(valence_mean = mean(valence, na.rm = T),
            arousal_mean = mean(arousal, na.rm = T),
            valence_sd = sd(valence, na.rm = T)/sqrt(n()),
            arousal_sd = sd(arousal, na.rm = T)/sqrt(n()))%>%
  mutate(report_type = "anticipation")%>%
  select(report_type,trial_type,valence_mean:arousal_sd)

aff_traj_avg_out_noRotat <- vrmid1_data_outprobe%>%
  mutate(probe == "out") %>% 
  ungroup()%>%
    group_by(Subject,trial_type,probe,reaction_outcome)%>%
  summarise(valence = mean(valence, na.rm = T),
            arousal = mean(arousal, na.rm = T)) %>% 
  group_by(trial_type,probe,reaction_outcome)%>%
  summarise(valence_mean = mean(valence, na.rm = T),
            arousal_mean = mean(arousal, na.rm = T),
            valence_sd = sd(valence, na.rm = T)/sqrt(n()),
            arousal_sd = sd(arousal, na.rm = T)/sqrt(n()))%>%
  select(reaction_outcome,trial_type,valence_mean:arousal_sd)%>%
  mutate(report_type = ifelse(reaction_outcome == "Hit","hit","miss"))

aff_traj_avg_noRotat <- rbind(aff_traj_avg_ant_noRotat,aff_traj_avg_out_noRotat)

p1<-ggplot(data = aff_traj_avg_noRotat, aes(x = valence_mean, y = arousal_mean, color = trial_type, 
                                        group = report_type))+
    geom_segment(aes(x = 1, y = 3,
                   xend =5, yend = 3),
               size = 0.5, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  geom_segment(aes(x = 3, y = 1,
                   xend =3, yend = 5),
               size = 0.5, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  geom_point(aes(shape = report_type),
             size = 2)+
    scale_shape_manual(values = c("hit" = 15, "miss" = 17,"anticipation" = 16)) +
  geom_segment(aes(y=arousal_mean-arousal_sd, yend=arousal_mean+arousal_sd,
                    x=valence_mean, xend = valence_mean, group = report_type), width=.5)+
  geom_segment(aes(y=arousal_mean, yend=arousal_mean,
                    x=valence_mean + valence_sd, xend = valence_mean - valence_sd,
                   group = report_type),
               width=.5)+
  scale_color_manual(values = redOrange_palette6)+
  geom_line(aes(group = trial_type, color = trial_type), linetype = "dotted")+
  labs(title = "VR Study",
       x = "",
       y = "",
       color = "cue value")+
  annotate("text",x = 5.2, y = 3, label = "valence",size = unit(4,"pt"),
           color = "grey", angle = 90)+
  annotate("text",x = 3, y = 0.8, label = "arousal",size = unit(4,"pt"),
           color = "grey")+
  theme_blank()+
  theme(legend.position = "left")+
  guides(linetype = "none")

aff_traj_avg_ant_noRotat <- fmri3_data_antprobe%>%
  mutate(probe == 1) %>% 
  ungroup()%>%
    group_by(subject,cue_value,probe)%>%
  summarise(valence = mean(valence, na.rm = T),
            arousal = mean(arousal, na.rm = T)) %>% 
  group_by(cue_value,probe)%>%
  summarise(valence_mean = mean(valence, na.rm = T),
            arousal_mean = mean(arousal, na.rm = T),
            valence_sd = sd(valence, na.rm = T)/sqrt(n()),
            arousal_sd = sd(arousal, na.rm = T)/sqrt(n()))%>%
  mutate(report_type = "anticipation")%>%
  select(report_type,cue_value,valence_mean:arousal_sd)

aff_traj_avg_out_noRotat <- fmri3_data_outprobe%>%
  ungroup()%>%
    group_by(subject,cue_value,probe,hit)%>%
  summarise(valence = mean(valence, na.rm = T),
            arousal = mean(arousal, na.rm = T)) %>% 
  group_by(cue_value,probe, hit)%>%
  summarise(valence_mean = mean(valence, na.rm = T),
            arousal_mean = mean(arousal, na.rm = T),
            valence_sd = sd(valence, na.rm = T)/sqrt(30),
            arousal_sd = sd(arousal, na.rm = T)/sqrt(30))%>%
  mutate(report_type = ifelse(hit==1,"hit","miss"))%>%
  select(report_type,cue_value,valence_mean:arousal_sd)

aff_traj_avg_noRotat <- rbind(aff_traj_avg_ant_noRotat,aff_traj_avg_out_noRotat)

p3<-ggplot(data = aff_traj_avg_noRotat, aes(x = valence_mean, y = arousal_mean, color = cue_value, 
                                        group = report_type))+
    geom_segment(aes(x = 1, y = 3,
                   xend =5, yend = 3),
               size = 0.5, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  geom_segment(aes(x = 3, y = 1,
                   xend =3, yend = 5),
               size = 0.5, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  geom_point(aes(shape = report_type),
             size = 2)+
      scale_shape_manual(values = c("hit" = 15, "miss" = 17,"anticipation" = 16)) +
  geom_segment(aes(y=arousal_mean-arousal_sd, yend=arousal_mean+arousal_sd,
                    x=valence_mean, xend = valence_mean, group = report_type), width=.5)+
  geom_segment(aes(y=arousal_mean, yend=arousal_mean,
                    x=valence_mean + valence_sd, xend = valence_mean - valence_sd,
                   group = report_type),
               width=.5)+
  scale_color_manual(values = redOrange_palette6)+
  geom_line(aes(group = cue_value, color = cue_value), linetype = "dotted")+
  labs(title = "FMRI study",
       x = "",
       y = "",
       color = "cue value")+
  annotate("text",x = 5.2, y = 3, label = "valence",size = unit(4,"pt"),
           color = "grey", angle = 90)+
  annotate("text",x = 3, y = 0.8, label = "arousal",size = unit(4,"pt"),
           color = "grey")+
  theme_blank()+
  theme(legend.position = "none")

p1+p3
```

# pupil by cue value and hit
```{r}
# study 1
pupil_avg_ant <- rbind(vrmid1_data_antprobe %>% 
                         select(Subject,probe,trial_type,mean_pupil_nobc_ant,mean_pupil_nobc_out),
                       vrmid1_data_outprobe %>% 
                         select(Subject,probe,trial_type,mean_pupil_nobc_ant,mean_pupil_nobc_out))%>%
  ungroup()%>%
  group_by(Subject,trial_type,probe)%>%
  summarise(mean_pupil_nobc_ant = mean(mean_pupil_nobc_ant, na.rm = T)) %>% 
  group_by(trial_type)%>%
  summarise(pupil_mean = mean(mean_pupil_nobc_ant, na.rm = T),
            pupil_sd = sd(mean_pupil_nobc_ant, na.rm = T)/sqrt(n()))%>%
  select(trial_type,pupil_mean,pupil_sd) %>% 
  mutate(probe = "anticipation")

pupil_avg_out <- rbind(vrmid1_data_antprobe %>% 
                         select(Subject,probe,reaction_outcome,trial_type,mean_pupil_nobc_ant,mean_pupil_nobc_out),
                       vrmid1_data_outprobe %>% 
                         select(Subject,probe,reaction_outcome,trial_type,mean_pupil_nobc_ant,mean_pupil_nobc_out))%>%
  ungroup()%>%
  group_by(Subject,trial_type,probe,reaction_outcome)%>%
  summarise(mean_pupil_nobc_out = mean(mean_pupil_nobc_out, na.rm = T)) %>% 
  # filter(probe == "out") %>% 
  group_by(trial_type,reaction_outcome)%>%
  summarise(pupil_mean = mean(mean_pupil_nobc_out, na.rm = T),
            pupil_sd = sd(mean_pupil_nobc_out, na.rm = T)/sqrt(n()))%>%
  select(trial_type,reaction_outcome,pupil_mean,pupil_sd) %>% 
  mutate(probe = ifelse(reaction_outcome == "Hit","hit","miss"),
         probe = factor(probe,levels = c("miss","hit")))

combined_pupil_avg <- rbind(pupil_avg_ant,pupil_avg_out %>% select(-reaction_outcome))
# Apply small horizontal offsets by probe (like dodging)
combined_pupil_avg <- combined_pupil_avg %>% 
  mutate(x_pos = ifelse(probe == "hit",as.numeric(trial_type)+1/4,
                        ifelse(probe == "miss",as.numeric(trial_type)-1/4,as.numeric(trial_type))))

p1a<-ggplot() +
  # Anticipatory points and error bars (not dodged)
  geom_point(data = pupil_avg_ant,
             aes(x = trial_type, y = pupil_mean, color = trial_type, shape = probe),
             size = 2) +
  geom_errorbar(data = pupil_avg_ant,
                aes(x = trial_type, ymin = pupil_mean - pupil_sd, ymax = pupil_mean + pupil_sd, color = trial_type),
                width = 0.25) +
  # Outcome points and error bars, dodged by probe
  geom_point(data = pupil_avg_out,
             aes(x = trial_type, y = pupil_mean, color = trial_type, shape = probe),
             position = position_dodge(width = 1),
             size = 2) +
  scale_shape_manual(values = c("hit" = 15, "miss" = 17,"anticipation" = 16)) + 
  geom_errorbar(data = pupil_avg_out,
                aes(x = trial_type, ymin = pupil_mean - pupil_sd, ymax = pupil_mean + pupil_sd, 
                    color = trial_type, group = probe),  # Include group = probe
                position = position_dodge(width = 1),
                width = 0.5) +
  scale_color_manual(values = redOrange_palette6) +
  guides(color = "none") +
  labs(y = "z-scored pupil",
       title = "VR Study",
       x = "",
       shape = "") +
  theme(legend.position = "none")+
  geom_line(data= combined_pupil_avg,
            aes(x = x_pos, y = pupil_mean, color = trial_type), linetype = "dotted")+
  ylim(-0.5,1.5)
  



# study 3
pupil_avg_ant <- rbind(fmri3_data_antprobe %>% 
                         select(subject,probe,cue_value,mean_pupil_nobc_scaled_ant,mean_pupil_nobc_scaled_out),
                       fmri3_data_outprobe %>% 
                         select(subject,probe,cue_value,mean_pupil_nobc_scaled_ant,mean_pupil_nobc_scaled_out))%>%
  ungroup()%>%
    group_by(subject,cue_value,probe)%>%
  summarise(mean_pupil_nobc_scaled_ant = mean(mean_pupil_nobc_scaled_ant, na.rm = T)) %>% 
  group_by(cue_value)%>%
  summarise(pupil_mean = mean(mean_pupil_nobc_scaled_ant, na.rm = T),
            pupil_sd = sd(mean_pupil_nobc_scaled_ant, na.rm = T)/sqrt(n()))%>%
  select(cue_value,pupil_mean,pupil_sd) %>% 
  mutate(probe = "anticipation")

pupil_avg_out <- rbind(fmri3_data_antprobe %>% 
                         select(subject,probe,hit,cue_value,mean_pupil_nobc_scaled_ant,mean_pupil_nobc_scaled_out),
                       fmri3_data_outprobe %>% 
                         select(subject,probe,hit,cue_value,mean_pupil_nobc_scaled_ant,mean_pupil_nobc_scaled_out))%>%
  ungroup()%>%
      group_by(subject,cue_value,probe,hit)%>%
  summarise(mean_pupil_nobc_scaled_out = mean(mean_pupil_nobc_scaled_out, na.rm = T)) %>% 
  # filter(probe == "out") %>% 
  group_by(cue_value,hit)%>%
  summarise(pupil_mean = mean(mean_pupil_nobc_scaled_out, na.rm = T),
            pupil_sd = sd(mean_pupil_nobc_scaled_out, na.rm = T)/sqrt(n()))%>%
  select(cue_value,hit,pupil_mean,pupil_sd) %>% 
  mutate(probe = ifelse(hit == "Hit","hit","miss"),
         probe = factor(probe,levels = c("miss","hit")))

combined_pupil_avg <- rbind(pupil_avg_ant,pupil_avg_out %>% select(-hit))
# Apply small horizontal offsets by probe (like dodging)
combined_pupil_avg <- combined_pupil_avg %>% 
  mutate(x_pos = ifelse(probe == "hit",as.numeric(cue_value)+1/4,
                        ifelse(probe == "miss",as.numeric(cue_value)-1/4,as.numeric(cue_value))))

p3a<-ggplot() +
  # Anticipatory points and error bars (not dodged)
  geom_point(data = pupil_avg_ant,
             aes(x = cue_value, y = pupil_mean, color = cue_value, shape = probe),
             size = 2) +
  geom_errorbar(data = pupil_avg_ant,
                aes(x = cue_value, ymin = pupil_mean - pupil_sd, ymax = pupil_mean + pupil_sd, color = cue_value),
                width = 0.25) +
  # Outcome points and error bars, dodged by probe
  geom_point(data = pupil_avg_out,
             aes(x = cue_value, y = pupil_mean, color = cue_value, shape = probe),
             position = position_dodge(width = 1),
             size = 2) +
    scale_shape_manual(values = c("hit" = 15, "miss" = 17,"anticipation" = 16)) +
  geom_errorbar(data = pupil_avg_out,
                aes(x = cue_value, ymin = pupil_mean - pupil_sd, ymax = pupil_mean + pupil_sd, 
                    color = cue_value, group = probe),  # Include group = probe
                position = position_dodge(width = 1),
                width = 0.5) +
  scale_color_manual(values = redOrange_palette6)+
  labs(y = "z-scored pupil",
       title = "FMRI study",
       x = "")+
  theme(legend.position = "none")+
  geom_line(data= combined_pupil_avg,
            aes(x = x_pos, y = pupil_mean, color = cue_value), linetype = "dotted")+
  ylim(-0.5,1.5)
  

p1a+p3a

# Create titles as separate elements
title1 <- wrap_elements(full = grid::textGrob("Rating Behavior", gp = grid::gpar(fontsize = 14), just = "left"))
title2 <- wrap_elements(full = grid::textGrob("Pupillometry", gp =  grid::gpar(fontsize = 14), just = "left"))


# Combine plots with titles using plot_layout
(
  title1 /                        # Title for the first row
  (p1  + p3) /                # First row
  title2 /                        # Title for the second row
  (p1a  + p3a)             # Second row
) + plot_layout(nrow = 4, heights = c(0.1, 1.5, 0.1, 1.5))  # Adjust heights for title rows
save_figure("s3_manipulation_check", height = 6, width = 7)

fig1 <- image_read(mid_pupil_figure_path("s3_manipulation_check", "png"))
fig1 <- image_annotate(fig1, "A", size = 55, location = "+400+00", color = "black", gravity = "northwest")
fig1 <- image_annotate(fig1, "B", size = 55, location = "+400+950", color = "black", gravity = "northwest")

save_figure_image("s3_manipulation_check", fig1)
```

### asymmetry
```{r}
# anticipation stats 
summary(lmer(mean_pupil_nobc_ant ~ as.factor(trial_type) + (1|Subject) 
             + (1|condition),rbind(vrmid1_data_antprobe %>% 
                         select(Subject,probe,trial_type,mean_pupil_nobc_ant,condition),
                       vrmid1_data_outprobe %>% 
                         select(Subject,probe,trial_type,mean_pupil_nobc_ant,condition))%>% 
             filter(trial_type %in% c("-$5","+$5"))))

summary(lmer(mean_pupil_nobc_scaled_ant ~ as.factor(cue_value) + (1|subject)
             + (1|cue_size),rbind(fmri3_data_antprobe %>% 
                         select(subject,probe,cue_value,mean_pupil_nobc_scaled_ant,cue_size),
                       fmri3_data_outprobe %>% 
                         select(subject,probe,cue_value,mean_pupil_nobc_scaled_ant,cue_size))%>% 
             filter(cue_value %in% c("-$5","+$5"))))

summary(lmer(scale(arousal_scaled) ~ as.factor(trial_type) + (1|Subject) 
             + (1|condition),vrmid1_data_antprobe%>% 
             filter(trial_type %in% c("-$5","+$5"))))

summary(lmer(scale(arousal_scaled) ~ as.factor(cue_value) + (1|subject) 
             + (1|cue_size),fmri3_data_antprobe%>% 
             filter(cue_value %in% c("-$5","+$5"))))
```

```{r}
# outcome stats 
summary(lmer(mean_pupil_nobc_out ~ as.factor(trial_outcome) + (1|Subject) + (1|condition),rbind(vrmid1_data_antprobe %>% 
                         select(Subject,probe,trial_outcome,condition,mean_pupil_nobc_out),
                       vrmid1_data_outprobe %>% 
                         select(Subject,probe,trial_outcome,condition,mean_pupil_nobc_out))%>% 
             filter(trial_outcome %in% c(-5,5))))

summary(lmer(mean_pupil_nobc_scaled_out ~ as.factor(trial_outcome) + (1|subject) + (1|cue_size),rbind(fmri3_data_antprobe %>% 
                         select(subject,probe,cue_size,trial_outcome,mean_pupil_nobc_scaled_out),
                       fmri3_data_outprobe %>% 
                         select(subject,probe,cue_size,trial_outcome,mean_pupil_nobc_scaled_out))%>% 
             filter(trial_outcome %in% c(-5,5))))


summary(lmer(scale(arousal_scaled) ~ as.factor(trial_outcome) + (1|Subject) 
             + (1|condition),vrmid1_data_outprobe%>% 
             filter(trial_outcome %in% c(-5,5))))

summary(lmer(scale(arousal_scaled) ~ as.factor(trial_outcome) + (1|subject) 
             + (1|cue_size),fmri3_data_outprobe%>% 
             filter(trial_outcome %in% c(-5,5))))
```

## How much of the ratings are explained by just the affective induction?
### anticipation
```{r}
summary(l1<-lmer(scale(arousal_scaled) ~ trial_type + (1|Subject) + (1|condition),vrmid1_data_antprobe))
pp1 <- plot_model(l1,type= "pred", terms = "trial_type")+
  labs(title = "Anticipatory arousal", x = "", y = "z-scored arousal",
       subtitle = "VR Study")+
  ylim(-1.2,1.2)
round(anova(l1),2)
round(r.squaredGLMM(l1)*100,2)
effectsize::eta_squared(anova(l1), partial = TRUE)    # partial η²

summary(l1<-lmer(scale(arousal_scaled) ~ cue_value + (1|subject)+ (1|cue_size),fmri3_data_antprobe))
round(anova(l1),2)
pp2 <- plot_model(l1,type= "pred", terms = "cue_value")+
  labs(title = "Anticipatory arousal", x = "", y = "z-scored arousal",
       subtitle = "FMRI Study")+
  ylim(-1.2,1.2)
round(r.squaredGLMM(l1)*100,2)
effectsize::eta_squared(anova(l1), partial = TRUE)    # partial η²

summary(l1<-lmer(valence_scaled ~ trial_type + (1|Subject) + (1|condition),vrmid1_data_antprobe))
round(anova(l1),2)
pp3 <- plot_model(l1,type= "pred", terms = "trial_type")+
  labs(title = "Anticipatory valence", x = "", y = "z-scored valence",
       subtitle = "VR Study")+
  ylim(-1.5,1.2)
round(r.squaredGLMM(l1)*100,2)
round(r.squaredGLMM(l1)*100,2)
effectsize::eta_squared(anova(l1), partial = TRUE)    # partial η²

summary(l1<-lmer(valence_scaled ~ cue_value + (1|subject) + (1|cue_size),fmri3_data_antprobe))
round(anova(l1),2)
round(r.squaredGLMM(l1)*100,2)
pp4 <- plot_model(l1,type= "pred", terms = "cue_value")+
  labs(title = "Anticipatory valence", x = "", y = "z-scored valence",
       subtitle = "FMRI Study")+
  ylim(-1.5,1.2)
effectsize::eta_squared(anova(l1), partial = TRUE)    # partial η²
```


### outcome
```{r}
summary(l1<-lmer(scale(arousal_scaled) ~ trial_type * reaction_outcome + (1|Subject) + (1|condition),vrmid1_data_outprobe %>% 
                   filter(!is.na(arousal_scaled))))
round(anova(l1),2)
round(r.squaredGLMM(l1)*100,2)
summary(lmer(scale(arousal_scaled) ~ as.factor(trial_outcome) + (1|Subject) + (1|condition),vrmid1_data_outprobe))
effectsize::eta_squared(anova(l1), partial = TRUE)    # partial η²
pp5 <- plot_model(l1,type= "pred", terms = c("trial_type","reaction_outcome"))+
  labs(title = "Outcome arousal", x = "", y = "z-scored arousal",
       subtitle = "VR Study")+
  ylim(-1.2,1.2)


summary(l1<-lmer(scale(arousal_scaled) ~ cue_value *  hit + (1|subject)+ (1|cue_size),fmri3_data_outprobe))
round(anova(l1),2)
round(r.squaredGLMM(l1)*100,2)
plot_model(l1,type = "pred", terms = "hit")
summary(lmer(scale(arousal_scaled) ~ as.factor(trial_outcome) + (1|subject) + (1|cue_size),fmri3_data_outprobe))
effectsize::eta_squared(anova(l1), partial = TRUE)    # partial η²
pp6 <- plot_model(l1,type= "pred", terms = c("cue_value","hit"))+
  labs(title = "Outcome arousal", x = "", y = "z-scored arousal",
       subtitle = "FMRI Study")+
  ylim(-1.2,1.2)

summary(l1<-lmer(valence ~ trial_type * reaction_outcome + (1|Subject) + (1|condition),vrmid1_data_outprobe))
plot_model(l1,type = "pred", terms = c("trial_type","reaction_outcome"))
round(anova(l1),2)
r.squaredGLMM(l1)
effectsize::eta_squared(anova(l1), partial = TRUE)    # partial η²
pp7 <- plot_model(l1,type= "pred", terms = c("trial_type","reaction_outcome"))+
  labs(title = "Outcome valence", x = "", y = "z-scored valence",
       subtitle = "VR Study")+
  ylim(1,5)

summary(l1<-lmer(valence ~ cue_value * hit + (1|subject) + (1|cue_size),fmri3_data_outprobe))
round(anova(l1),2)
r.squaredGLMM(l1)
effectsize::eta_squared(anova(l1), partial = TRUE)    # partial η²
pp8 <- plot_model(l1,type= "pred", terms = c("cue_value","hit"))+
  labs(title = "Outcome valence", x = "", y = "z-scored valence",
       subtitle = "FMRI Study")+
  ylim(1,5)
```

```{r}
pp1+pp2+pp5+pp6
save_figure("s3_si_arousal_timecourse", dpi = 300, height = 5, width = 8)

pp3+pp4+pp7+pp8
save_figure("s3_si_valence_timecourse", dpi = 300, height = 5, width = 8)

```


## were affect induction effective for pupil diameter?
### anticipation
```{r}
summary(l1<-lmer(scale(mean_pupil_nobc_ant) ~ trial_type + (1|Subject) + (1|condition),vrmid1_data_antprobe))
round(anova(l1),2)
pp1 <- plot_model(l1,type= "pred", terms = c("trial_type"))+
  labs(title = "Anticipatory pupil", x = "", y = "z-scored pupil",
       subtitle = "VR Study")+
  ylim(-1,1)
round(r.squaredGLMM(l1)*100,2)
effectsize::eta_squared(anova(l1), partial = TRUE)    # partial η²
anova(l2<-lmer(scale(mean_pupil_nobc_ant) ~ trial_type + arousal + (1+trial_type+arousal|Subject) + (1|condition),vrmid1_data_antprobe))

summary(l1<-lmer(scale(mean_pupil_nobc_scaled_ant) ~ cue_value + (1|subject)+ (1|cue_size),fmri3_data_antprobe))
round(anova(l1),2)
effectsize::eta_squared(anova(l1), partial = TRUE)    # partial η²
round(r.squaredGLMM(l1)*100,2)
anova(l2<-lmer(mean_pupil_nobc_scaled_ant ~ cue_value + arousal + (1+ cue_value + arousal|subject) + (1|cue_size),fmri3_data_antprobe))
pp2 <- plot_model(l1,type= "pred", terms = c("cue_value"))+
  labs(title = "Anticipatory pupil", x = "", y = "z-scored pupil",
       subtitle = "FMRI Study")+
  ylim(-1,1)

```

### outcome
```{r}
summary(l1<-lmer(scale(mean_pupil_nobc_out) ~ trial_type * reaction_outcome + (1|Subject) + (1|condition),vrmid1_data_outprobe))
plot_model(l1, type = "pred", terms = "reaction_outcome")
round(anova(l1),2)
pp3 <- plot_model(l1,type= "pred", terms = c("trial_type","reaction_outcome"))+
  labs(title = "Outcome pupil", x = "", y = "z-scored pupil",
       subtitle = "VR Study")+
  ylim(-1.5,1)
effectsize::eta_squared(anova(l1), partial = TRUE)    # partial η²
round(r.squaredGLMM(l1)*100,2)
anova(lmer(mean_pupil_nobc_out ~ trial_type * reaction_outcome + arousal + (1|Subject) + (1|condition),vrmid1_data_outprobe))
summary(lmer(scale(mean_pupil_nobc_out) ~ as.factor(trial_outcome) + (1|Subject) + (1|condition),vrmid1_data_outprobe))

summary(l1<-lmer(scale(mean_pupil_nobc_scaled_out) ~ cue_value * hit + (1|subject)+ (1|cue_size),fmri3_data_antprobe))
round(anova(l1),2)
pp4 <- plot_model(l1,type= "pred", terms = c("cue_value","hit"))+
  labs(title = "Outcome pupil", x = "", y = "z-scored pupil",
       subtitle = "FMRI Study")+
  ylim(-1.5,1)

effectsize::eta_squared(anova(l1), partial = TRUE)    # partial η²
round(r.squaredGLMM(l1)*100,2)
anova(lmer(mean_pupil_nobc_scaled_out ~ cue_value * hit +arousal + (1|subject)+ (1|cue_size),fmri3_data_antprobe))
summary(lmer(scale(mean_pupil_nobc_scaled_out) ~ as.factor(trial_outcome) + (1|subject) + (1|cue_size),fmri3_data_antprobe))
```

```{r}
pp1+pp2+pp3+pp4
save_figure("s3_si_pupil_timecourse", dpi = 300, height = 5, width = 8)

```


## was luminance related to self-reported arousal? YES

```{r}
summary(lmer(arousal_scaled ~ luminance_convolved_mean_ant + (1|subject),fmri3_data_antprobe))
summary(lmer(arousal_scaled ~ luminance_convolved_mean_ant + (1|subject),fmri3_data_outprobe))

summary(lmer(arousal_scaled ~ luminance_convolved_mean_out + (1|subject),fmri3_data_antprobe))
summary(lmer(arousal_scaled ~ luminance_convolved_mean_out + (1|subject),fmri3_data_outprobe))

summary(lmer(arousal_scaled ~ luminance_convolved_mean_ant + (1|subject) + (1|probe),rbind(fmri3_data_antprobe,
                                                                     fmri3_data_outprobe)))

summary(lmer(arousal_scaled ~ luminance_convolved_mean_out + (1|subject) + (1|probe),rbind(fmri3_data_antprobe,
                                                                     fmri3_data_outprobe)))
```

## do pupil size and self-reports differ by cue size?

```{r}
# Align VR cue-size factor order with Set2 coloring used in s2 timecourse plots
vrmid1_data_antprobe <- vrmid1_data_antprobe %>%
  mutate(condition = factor(condition, levels = c("large", "looming", "receding", "small")))
vrmid1_data_outprobe <- vrmid1_data_outprobe %>%
  mutate(condition = factor(condition, levels = c("large", "looming", "receding", "small")))

# Connect predicted points within each cue-size level
add_cuesize_lines <- function(p) {
  p + geom_line(aes(group = group), linewidth = 0.8)
}
```

### anticipation
```{r}
# VR: cue value on x, cue size as color
summary(l1 <- lmer(scale(mean_pupil_nobc_ant) ~ trial_type * condition + (1|Subject),
                   vrmid1_data_antprobe))
round(anova(l1), 2)
round(r.squaredGLMM(l1) * 100, 2)
effectsize::eta_squared(anova(l1), partial = TRUE)
pp_cs_pupil_ant_vr <- add_cuesize_lines(
  plot_model(l1, type = "pred", terms = c("trial_type", "condition")) +
    labs(title = "Anticipatory pupil", x = "", y = "z-scored pupil",
         subtitle = "VR Study", color = "cue size") +
    scale_color_brewer(palette = "Set2")
)

summary(l1 <- lmer(scale(arousal_scaled) ~ trial_type * condition + (1|Subject),
                   vrmid1_data_antprobe))
round(anova(l1), 2)
round(r.squaredGLMM(l1) * 100, 2)
effectsize::eta_squared(anova(l1), partial = TRUE)
pp_cs_arousal_ant_vr <- add_cuesize_lines(
  plot_model(l1, type = "pred", terms = c("trial_type", "condition")) +
    labs(title = "Anticipatory arousal", x = "", y = "z-scored arousal",
         subtitle = "VR Study", color = "cue size") +
    scale_color_brewer(palette = "Set2")
)

summary(l1 <- lmer(scale(valence_scaled) ~ trial_type * condition + (1|Subject),
                   vrmid1_data_antprobe))
round(anova(l1), 2)
round(r.squaredGLMM(l1) * 100, 2)
effectsize::eta_squared(anova(l1), partial = TRUE)
pp_cs_valence_ant_vr <- add_cuesize_lines(
  plot_model(l1, type = "pred", terms = c("trial_type", "condition")) +
    labs(title = "Anticipatory valence", x = "", y = "z-scored valence",
         subtitle = "VR Study", color = "cue size") +
    scale_color_brewer(palette = "Set2")
)

# FMRI: cue value on x, cue size as color (2 levels; Set2 colors match s2)
summary(l1 <- lmer(scale(mean_pupil_nobc_scaled_ant) ~ cue_value * cue_size + (1|subject),
                   fmri3_data_antprobe))
round(anova(l1), 2)
round(r.squaredGLMM(l1) * 100, 2)
effectsize::eta_squared(anova(l1), partial = TRUE)
pp_cs_pupil_ant_fmri <- add_cuesize_lines(
  plot_model(l1, type = "pred", terms = c("cue_value", "cue_size")) +
    labs(title = "Anticipatory pupil", x = "", y = "z-scored pupil",
         subtitle = "FMRI Study", color = "cue size") +
    scale_color_brewer(palette = "Set2")
)

summary(l1 <- lmer(scale(arousal_scaled) ~ cue_value * cue_size + (1|subject),
                   fmri3_data_antprobe))
round(anova(l1), 2)
round(r.squaredGLMM(l1) * 100, 2)
effectsize::eta_squared(anova(l1), partial = TRUE)
pp_cs_arousal_ant_fmri <- add_cuesize_lines(
  plot_model(l1, type = "pred", terms = c("cue_value", "cue_size")) +
    labs(title = "Anticipatory arousal", x = "", y = "z-scored arousal",
         subtitle = "FMRI Study", color = "cue size") +
    scale_color_brewer(palette = "Set2")
)

summary(l1 <- lmer(scale(valence_scaled) ~ cue_value * cue_size + (1|subject),
                   fmri3_data_antprobe))
round(anova(l1), 2)
round(r.squaredGLMM(l1) * 100, 2)
effectsize::eta_squared(anova(l1), partial = TRUE)
pp_cs_valence_ant_fmri <- add_cuesize_lines(
  plot_model(l1, type = "pred", terms = c("cue_value", "cue_size")) +
    labs(title = "Anticipatory valence", x = "", y = "z-scored valence",
         subtitle = "FMRI Study", color = "cue size") +
    scale_color_brewer(palette = "Set2")
)
```

### outcome
```{r}
# VR
summary(l1 <- lmer(scale(mean_pupil_nobc_out) ~ trial_type * condition * reaction_outcome + (1|Subject),
                   vrmid1_data_outprobe))
round(anova(l1), 2)
round(r.squaredGLMM(l1) * 100, 2)
effectsize::eta_squared(anova(l1), partial = TRUE)
pp_cs_pupil_out_vr <- add_cuesize_lines(
  plot_model(l1, type = "pred", terms = c("trial_type", "condition")) +
    labs(title = "Outcome pupil", x = "", y = "z-scored pupil",
         subtitle = "VR Study", color = "cue size") +
    scale_color_brewer(palette = "Set2")
)

summary(l1 <- lmer(scale(arousal_scaled) ~ trial_type * condition * reaction_outcome + (1|Subject),
                   vrmid1_data_outprobe %>% filter(!is.na(arousal_scaled))))
round(anova(l1), 2)
round(r.squaredGLMM(l1) * 100, 2)
effectsize::eta_squared(anova(l1), partial = TRUE)
pp_cs_arousal_out_vr <- add_cuesize_lines(
  plot_model(l1, type = "pred", terms = c("trial_type", "condition")) +
    labs(title = "Outcome arousal", x = "", y = "z-scored arousal",
         subtitle = "VR Study", color = "cue size") +
    scale_color_brewer(palette = "Set2")
)

summary(l1 <- lmer(scale(valence_scaled) ~ trial_type * condition * reaction_outcome + (1|Subject),
                   vrmid1_data_outprobe))
round(anova(l1), 2)
round(r.squaredGLMM(l1) * 100, 2)
effectsize::eta_squared(anova(l1), partial = TRUE)
pp_cs_valence_out_vr <- add_cuesize_lines(
  plot_model(l1, type = "pred", terms = c("trial_type", "condition")) +
    labs(title = "Outcome valence", x = "", y = "z-scored valence",
         subtitle = "VR Study", color = "cue size") +
    scale_color_brewer(palette = "Set2")
)

# FMRI
summary(l1 <- lmer(scale(mean_pupil_nobc_scaled_out) ~ cue_value * cue_size * hit + (1|subject),
                   fmri3_data_outprobe))
round(anova(l1), 2)
round(r.squaredGLMM(l1) * 100, 2)
effectsize::eta_squared(anova(l1), partial = TRUE)
pp_cs_pupil_out_fmri <- add_cuesize_lines(
  plot_model(l1, type = "pred", terms = c("cue_value", "cue_size")) +
    labs(title = "Outcome pupil", x = "", y = "z-scored pupil",
         subtitle = "FMRI Study", color = "cue size") +
    scale_color_brewer(palette = "Set2")
)

summary(l1 <- lmer(scale(arousal_scaled) ~ cue_value * cue_size * hit + (1|subject),
                   fmri3_data_outprobe))
round(anova(l1), 2)
round(r.squaredGLMM(l1) * 100, 2)
effectsize::eta_squared(anova(l1), partial = TRUE)
pp_cs_arousal_out_fmri <- add_cuesize_lines(
  plot_model(l1, type = "pred", terms = c("cue_value", "cue_size")) +
    labs(title = "Outcome arousal", x = "", y = "z-scored arousal",
         subtitle = "FMRI Study", color = "cue size") +
    scale_color_brewer(palette = "Set2")
)

summary(l1 <- lmer(scale(valence_scaled) ~ cue_value * cue_size * hit + (1|subject),
                   fmri3_data_outprobe))
round(anova(l1), 2)
round(r.squaredGLMM(l1) * 100, 2)
effectsize::eta_squared(anova(l1), partial = TRUE)
pp_cs_valence_out_fmri <- add_cuesize_lines(
  plot_model(l1, type = "pred", terms = c("cue_value", "cue_size")) +
    labs(title = "Outcome valence", x = "", y = "z-scored valence",
         subtitle = "FMRI Study", color = "cue size") +
    scale_color_brewer(palette = "Set2")
)
```

```{r}
# rows: pupil / arousal / valence; cols: VR ant | FMRI ant | VR out | FMRI out
(pp_cs_pupil_ant_vr + pp_cs_pupil_ant_fmri + pp_cs_pupil_out_vr + pp_cs_pupil_out_fmri +
  pp_cs_arousal_ant_vr + pp_cs_arousal_ant_fmri + pp_cs_arousal_out_vr + pp_cs_arousal_out_fmri +
  pp_cs_valence_ant_vr + pp_cs_valence_ant_fmri + pp_cs_valence_out_vr + pp_cs_valence_out_fmri) +
  plot_layout(ncol = 4)
save_figure("s3_si_cuesize_effects", dpi = 300, height = 8, width = 14)
```

## is OBJECTIVE or SUBJECTIVE model better?

### ant probe
#### pupil
```{r}
common_data <- vrmid1_data_antprobe %>% 
  filter(
    !is.na(arousal),
    !is.na(trial_type),
    !is.na(mean_pupil_baseline_ant),
    !is.na(mean_pupil_bc_ant),
    !is.na(mean_pupil_nobc_ant)
  )

summary(l1<-lmer(arousal_scaled ~ trial_type + (1|Subject) + (1|condition),common_data))
summary(l2<-lmer(arousal_scaled ~ trial_type + mean_pupil_baseline_ant + (1|Subject) + (1|condition),common_data))
summary(l3<-lmer(arousal_scaled ~ trial_type + mean_pupil_bc_ant + (1|Subject) + (1|condition),common_data))
summary(l4<-lmer(arousal_scaled ~ trial_type + mean_pupil_nobc_ant + (1|Subject) + (1|condition) ,common_data))
summary(l5<-lmer(arousal_scaled ~ mean_pupil_nobc_ant + (1|Subject) + (1|condition) ,common_data))

anova(l1,l2,l3,l4,l5)
r.squaredGLMM(l2)-r.squaredGLMM(l1)

# FMRI 3
summary(l1<-lmer(arousal_scaled ~ cue_value + (1|subject) + (1|cue_size),fmri3_data_antprobe %>% filter(!is.na(arousal))))
summary(l2<-lmer(arousal_scaled ~ cue_value + mean_pupil_baseline_scaled + (1|subject) + (1|cue_size),fmri3_data_antprobe%>% filter(!is.na(arousal))))
summary(l3<-lmer(arousal_scaled ~ cue_value + mean_pupil_bc_scaled_ant + (1|subject) + (1|cue_size),fmri3_data_antprobe%>% filter(!is.na(arousal))))
summary(l4<-lmer(arousal_scaled ~ cue_value + mean_pupil_nobc_scaled_ant + (1|subject) + (1|cue_size),fmri3_data_antprobe%>% filter(!is.na(arousal))))
summary(l5<-lmer(arousal_scaled ~ mean_pupil_nobc_scaled_ant + (1|subject) + (1|cue_size),fmri3_data_antprobe%>% filter(!is.na(arousal))))


anova(l1,l2,l3,l4,l5)
r.squaredGLMM(l2)-r.squaredGLMM(l1)
BIC(l2)-BIC(l1)
```

### out probe
```{r}
common_data <- vrmid1_data_outprobe %>%
  filter(!is.na(arousal),
         !is.na(mean_pupil_bc_out),
         !is.na(mean_pupil_baseline_out),
         !is.na(mean_pupil_nobc_out))

summary(l1<-lmer(arousal_scaled ~ trial_type * reaction_outcome + (1|Subject) + (1|condition),common_data))
summary(l2<-lmer(arousal_scaled ~ trial_type* reaction_outcome + mean_pupil_baseline_out + (1|Subject) + (1|condition),common_data))
summary(l3<-lmer(arousal_scaled ~ trial_type* reaction_outcome + mean_pupil_bc_out + (1|Subject) + (1|condition),common_data))
summary(l4<-lmer(arousal_scaled ~ trial_type* reaction_outcome + mean_pupil_nobc_out + (1|Subject) + (1|condition) ,common_data))
summary(l5<-lmer(arousal_scaled ~ mean_pupil_nobc_out + (1|Subject) + (1|condition) ,common_data))

anova(l1,l2,l3,l4,l5)
r.squaredGLMM(l2)-r.squaredGLMM(l1)

# FMRI 3
summary(l1<-lmer(arousal_scaled ~ cue_value * hit + (1|subject) + (1|cue_size),fmri3_data_outprobe %>% filter(!is.na(arousal) & !is.na(mean_pupil_baseline_scaled))))
summary(l2<-lmer(arousal_scaled ~ cue_value * hit + mean_pupil_baseline_scaled + (1|subject) + (1|cue_size),fmri3_data_outprobe%>% filter(!is.na(arousal)& !is.na(mean_pupil_baseline_scaled))))
summary(l3<-lmer(arousal_scaled ~ cue_value * hit + mean_pupil_bc_scaled_out + (1|subject) + (1|cue_size),fmri3_data_outprobe%>% filter(!is.na(arousal)& !is.na(mean_pupil_baseline_scaled))))
summary(l4<-lmer(arousal_scaled ~ cue_value * hit + mean_pupil_nobc_scaled_out + (1|subject) + (1|cue_size),fmri3_data_outprobe%>% filter(!is.na(arousal)& !is.na(mean_pupil_baseline_scaled))))
summary(l5<-lmer(arousal_scaled ~ mean_pupil_nobc_scaled_out + (1|subject) + (1|cue_size),fmri3_data_outprobe%>% filter(!is.na(arousal)& !is.na(mean_pupil_baseline_scaled))))

anova(l1,l2,l3,l4,l5)
r.squaredGLMM(l2)-r.squaredGLMM(l1)
```
