---
title: "pupilAvg_vs_xyvar_comparison"
output: html_document
date: "2026-04-27"
---

# Gaze location over time: individual trials (all cue values pooled)
```{r}
# 25° left/right/down and 20° up — one faint line per trial; data piped straight into ggplot (no summary tibble)

vr1_x_rng <- c(0, 20)

p_vr1_sum_x <- ggplot(
  vrmid1_pupil_data %>% dplyr::filter(probe == "anti", dplyr::between(sample_in_trial_t, vr1_x_rng[1], vr1_x_rng[2])),
  aes(x = sample_in_trial_t, y = AvgPPos_x_preproc, group = interaction(Subject, trial))
) +
  geom_line(linewidth = 0.1, alpha = 0.1, color = "grey25") +
  geom_vline(xintercept = c(0, 4, 6, 14, 16, 18), linewidth = 1, color = "grey") +
  geom_vline(xintercept = c(0, 4, 6), linewidth = 1, color = "grey") +
  annotate("text", x = 2, y = 0.5, label = "C", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 5, y = 0.5, label = "F", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 15, y = 0.5, label = "T", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 17, y = 0.5, label = "O", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 10, y = 0.5, label = "R", color = "black", size = unit(4, "pt")) +
  labs(
    title = "VR study",
    subtitle = "anticipation probe (individual trials)",
    x = "time (s)",
    y = "normalized gaze location (x)"
  ) +
  theme(legend.position = "none") +
  ggplot(
    vrmid1_pupil_data %>% dplyr::filter(probe == "out", dplyr::between(sample_in_trial_t, vr1_x_rng[1], vr1_x_rng[2])),
    aes(x = sample_in_trial_t, y = AvgPPos_x_preproc, group = interaction(Subject, trial))
  ) +
  geom_line(linewidth = 0.1, alpha = 0.1, color = "grey25") +
  geom_vline(xintercept = c(0, 4, 6, 8, 10, 18), linewidth = 1, color = "grey") +
  geom_vline(xintercept = c(0, 4, 6), linewidth = 1, color = "grey") +
  annotate("text", x = 2, y = 0.5, label = "C", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 5, y = 0.5, label = "F", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 7, y = 0.5, label = "T", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 9, y = 0.5, label = "O", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 14, y = 0.5, label = "R", color = "black", size = unit(4, "pt")) +
  labs(
    title = "VR study",
    subtitle = "outcome probe (individual trials)",
    x = "time (s)",
    y = "normalized gaze location (x)"
  ) 

p_vr1_sum_y <- ggplot(
  vrmid1_pupil_data %>% dplyr::filter(probe == "anti", dplyr::between(sample_in_trial_t, vr1_x_rng[1], vr1_x_rng[2])),
  aes(x = sample_in_trial_t, y = AvgPPos_y_preproc, group = interaction(Subject, trial))
) +
  geom_line(linewidth = 0.1, alpha = 0.1, color = "grey25") +
  geom_vline(xintercept = c(0, 4, 6, 14, 16, 18), linewidth = 1, color = "grey") +
  geom_vline(xintercept = c(0, 4, 6), linewidth = 1, color = "grey") +
  annotate("text", x = 2, y = 0.5, label = "C", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 5, y = 0.5, label = "F", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 15, y = 0.5, label = "T", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 17, y = 0.5, label = "O", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 10, y = 0.5, label = "R", color = "black", size = unit(4, "pt")) +
  labs(
    title = "VR study",
    subtitle = "anticipation probe (individual trials)",
    x = "time (s)",
    y = "normalized gaze location (y)"
  ) +
  theme(legend.position = "none") +
  ggplot(
    vrmid1_pupil_data %>% dplyr::filter(probe == "out", dplyr::between(sample_in_trial_t, vr1_x_rng[1], vr1_x_rng[2])),
    aes(x = sample_in_trial_t, y = AvgPPos_y_preproc, group = interaction(Subject, trial))
  ) +
  geom_line(linewidth = 0.1, alpha = 0.1, color = "grey25") +
  geom_vline(xintercept = c(0, 4, 6, 8, 10, 18), linewidth = 1, color = "grey") +
  geom_vline(xintercept = c(0, 4, 6), linewidth = 1, color = "grey") +
  annotate("text", x = 2, y = 0.5, label = "C", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 5, y = 0.5, label = "F", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 7, y = 0.5, label = "T", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 9, y = 0.5, label = "O", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 14, y = 0.5, label = "R", color = "black", size = unit(4, "pt")) +
  labs(
    title = "VR study",
    subtitle = "outcome probe (individual trials)",
    x = "time (s)",
    y = "normalized gaze location (y)"
  )

p_vr1_sum_x / p_vr1_sum_y
```

```{r}
# Same pattern as chunk 1: pipe fmri3_pupil_data into ggplot (gaze in [0,1]; no summary tibble)

fmri3_x_rng <- c(0, 20)

p_fmri3_sum_x <- ggplot(
  fmri3_pupil_data %>%
    dplyr::filter(
      probe == 1,
      dplyr::between(sample_in_trial_t, fmri3_x_rng[1], fmri3_x_rng[2])
    ),
  aes(x = sample_in_trial_t, y = pupil_x_preproc_norm, group = interaction(subject, trial))
) +
  geom_line(linewidth = 0.1, alpha = 0.1, color = "grey25") +
  geom_vline(xintercept = c(0, 2, 4, 12, 14, 16, 18), linewidth = 1, color = "grey") +
  annotate("text", x = 1, y = 0.5, label = "C", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 3, y = 0.5, label = "F", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 13, y = 0.5, label = "F", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 15, y = 0.5, label = "T", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 17, y = 0.5, label = "O", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 8, y = 0.5, label = "R", color = "black", size = unit(4, "pt")) +
  labs(
    title = "FMRI study",
    subtitle = "anticipation probe (individual trials)",
    x = "time (s)",
    y = "normalized gaze location (x)"
  ) +
  theme(legend.position = "none") +
  ggplot(
    fmri3_pupil_data %>%
      dplyr::filter(
        probe == 2,
        dplyr::between(sample_in_trial_t, fmri3_x_rng[1], fmri3_x_rng[2])
      ),
    aes(x = sample_in_trial_t, y = pupil_x_preproc_norm, group = interaction(subject, trial))
  ) +
  geom_line(linewidth = 0.1, alpha = 0.1, color = "grey25") +
  geom_vline(xintercept = c(0, 2, 4, 6, 8, 16), linewidth = 1, color = "grey") +
  annotate("text", x = 1, y = 0.5, label = "C", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 3, y = 0.5, label = "F", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 5, y = 0.5, label = "T", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 7, y = 0.5, label = "O", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 12, y = 0.5, label = "R", color = "black", size = unit(4, "pt")) +
  labs(
    title = "FMRI study",
    subtitle = "outcome probe (individual trials)",
    x = "time (s)",
    y = "normalized gaze location (x)"
  )

p_fmri3_sum_y <- ggplot(
  fmri3_pupil_data %>%
    dplyr::filter(
      probe == 1,
      dplyr::between(sample_in_trial_t, fmri3_x_rng[1], fmri3_x_rng[2])
    ),
  aes(x = sample_in_trial_t, y = pupil_y_preproc_norm, group = interaction(subject, trial))
) +
  geom_line(linewidth = 0.1, alpha = 0.1, color = "grey25") +
  geom_vline(xintercept = c(0, 2, 4, 12, 14, 16, 18), linewidth = 1, color = "grey") +
  annotate("text", x = 1, y = 0.5, label = "C", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 3, y = 0.5, label = "F", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 13, y = 0.5, label = "F", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 15, y = 0.5, label = "T", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 17, y = 0.5, label = "O", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 8, y = 0.5, label = "R", color = "black", size = unit(4, "pt")) +
  labs(
    title = "FMRI study",
    subtitle = "anticipation probe (individual trials)",
    x = "time (s)",
    y = "normalized gaze location (y)"
  ) +
  theme(legend.position = "none") +
  ggplot(
    fmri3_pupil_data %>%
      dplyr::filter(
        probe == 2,
        dplyr::between(sample_in_trial_t, fmri3_x_rng[1], fmri3_x_rng[2])
      ),
    aes(x = sample_in_trial_t, y = pupil_y_preproc_norm, group = interaction(subject, trial))
  ) +
  geom_line(linewidth = 0.1, alpha = 0.1, color = "grey25") +
  geom_vline(xintercept = c(0, 2, 4, 6, 8, 16), linewidth = 1, color = "grey") +
  annotate("text", x = 1, y = 0.5, label = "C", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 3, y = 0.5, label = "F", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 5, y = 0.5, label = "T", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 7, y = 0.5, label = "O", color = "black", size = unit(4, "pt")) +
  annotate("text", x = 12, y = 0.5, label = "R", color = "black", size = unit(4, "pt")) +
  labs(
    title = "FMRI study",
    subtitle = "outcome probe (individual trials)",
    x = "time (s)",
    y = "normalized gaze location (y)"
  ) 

p_fmri3_sum_x / p_fmri3_sum_y
```

```{r}
(p_vr1_sum_x | p_vr1_sum_y) /
(p_fmri3_sum_x | p_fmri3_sum_y)

ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/xyloc.png"),dpi = 300, height = 6, width = 13)

```

# plot avg gaze location (x&y) during the time windows of interest
```{r}
make_xyloc_with_marginals <- function(d, x_col, y_col, xlim = NULL, ylim = NULL,
                                      title = NULL, subtitle = NULL, show_rect = FALSE,
                                      subplot_expansion = FALSE) {
  d <- dplyr::filter(d, !is.na(.data[[x_col]]), !is.na(.data[[y_col]]))
  if (!is.null(xlim)) {
    d <- dplyr::filter(d, .data[[x_col]] >= xlim[1], .data[[x_col]] <= xlim[2])
  }
  if (!is.null(ylim)) {
    d <- dplyr::filter(d, .data[[y_col]] >= ylim[1], .data[[y_col]] <= ylim[2])
  }
  if (!nrow(d)) {
    return(patchwork::plot_spacer())
  }

  xr <- if (is.null(xlim)) range(d[[x_col]], na.rm = TRUE) else xlim
  yr <- if (is.null(ylim)) range(d[[y_col]], na.rm = TRUE) else ylim
  bins <- 50L

  ax_exp <- if (subplot_expansion) ggplot2::expansion(mult = 0.02) else ggplot2::expansion(mult = 0)

  p <- ggplot2::ggplot(d, ggplot2::aes(.data[[x_col]], .data[[y_col]])) +
    ggplot2::geom_point(alpha = 0.01, size = 0.1) +
    ggside::geom_xsidehistogram(
      bins = bins, fill = "gray55", color = "gray92",
      linewidth = 0.08, na.rm = TRUE
    ) +
    ggside::geom_ysidehistogram(
      bins = bins, fill = "gray55", color = "gray92",
      linewidth = 0.08, na.rm = TRUE
    ) +
    ggplot2::scale_x_continuous(limits = xr, expand = ax_exp) +
    ggplot2::scale_y_continuous(limits = yr, expand = ax_exp) +
    ggside::scale_xsidey_continuous(guide = "none") +
    ggside::scale_ysidex_continuous(guide = "none") +
    ggplot2::theme_classic() +
    ggplot2::theme(
      ggside.panel.scale.x = 0.22,
      ggside.panel.scale.y = 0.22
    ) +
    ggplot2::labs(
      title = title,
      subtitle = subtitle,
      x = "normalized gaze location (x)",
      y = "normalized gaze location (y)"
    )
  if (show_rect) {
    p <- p 
      # ggplot2::annotate("rect", xmin = 0, xmax = 1, ymin = 0, ymax = 1,
      #                  fill = NA, color = "grey")
  }
  p
}

vr_xy_ant <- vrmid1_pupil_data %>%
  dplyr::filter(
    probe == "anti",
    sample_in_trial_t >= vrmid1_ant_window[1],
    sample_in_trial_t <= vrmid1_ant_window[2]
  )
vr_xy_out <- vrmid1_pupil_data %>%
  dplyr::mutate(probe = factor(probe)) %>%
  dplyr::filter(dplyr::if_else(
    probe == "out",
    sample_in_trial_t >= vrmid1_outprobe_out_window[1] &
      sample_in_trial_t <= vrmid1_outprobe_out_window[2],
    dplyr::if_else(
      probe == "anti",
      sample_in_trial_t >= vrmid1_antprobe_out_window[1] &
        sample_in_trial_t <= vrmid1_antprobe_out_window[2],
      FALSE
    )
  ))

fmri_xy_ant <- fmri3_pupil_data %>%
  dplyr::filter(
    probe == 1,
    sample_in_trial_t >= fmri3_ant_window[1],
    sample_in_trial_t <= fmri3_ant_window[2]
  )
fmri_xy_out <- fmri3_pupil_data %>%
  dplyr::filter(dplyr::if_else(
    probe == 2,
    sample_in_trial_t >= fmri3_outprobe_out_window[1] &
      sample_in_trial_t <= fmri3_outprobe_out_window[2],
    dplyr::if_else(
      probe == 1,
      sample_in_trial_t >= fmri3_antprobe_out_window[1] &
        sample_in_trial_t <= fmri3_antprobe_out_window[2],
      FALSE
    )
  )) %>%
  dplyr::mutate(probe = factor(probe, levels = c(1, 2), labels = c("anticipation", "outcome")))

p_xy_vrmid1 <- make_xyloc_with_marginals(
  vr_xy_ant, "AvgPPos_x_preproc", "AvgPPos_y_preproc",
  xlim = c(0, 1), ylim = c(0, 1), subplot_expansion = FALSE,
  title = "VR Study", subtitle = "anticipation time window"
) /
  make_xyloc_with_marginals(
    vr_xy_out, "AvgPPos_x_preproc", "AvgPPos_y_preproc",
    xlim = c(0, 1), ylim = c(0, 1), subplot_expansion = FALSE,
    subtitle = "outcome time window"
  )

p_xy_fmri3 <- make_xyloc_with_marginals(
  fmri_xy_ant, "pupil_x_preproc_norm", "pupil_y_preproc_norm",
  show_rect = TRUE, subplot_expansion = TRUE,
  title = "FMRI study", subtitle = "anticipation time window"
) /
  make_xyloc_with_marginals(
    fmri_xy_out, "pupil_x_preproc_norm", "pupil_y_preproc_norm",
    show_rect = TRUE, subplot_expansion = TRUE,
    subtitle = "outcome time window"
  )

p_xy_xyloc_combined <- (p_xy_vrmid1 | p_xy_fmri3) +
  patchwork::plot_layout(ncol = 2, nrow = 1)

p_xy_xyloc_combined

ggsave(
  paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/xyloc_combined.png"),
  plot = p_xy_xyloc_combined,
  dpi = 300, height = 8, width = 8
)
```

# visualize pupil data quality for out of bound gaze
```{r}
mean(
  fmri3_pupil_data$pupil_x_preproc_norm < 0 |
    fmri3_pupil_data$pupil_x_preproc_norm > 1 |
    fmri3_pupil_data$pupil_y_preproc_norm < 0 |
    fmri3_pupil_data$pupil_y_preproc_norm > 1,
  na.rm = TRUE
)

fmri3_gaze_pupil <- fmri3_pupil_data %>%
  mutate(
    gaze_region = dplyr::if_else(
      is.na(pupil_x_preproc_norm) | is.na(pupil_y_preproc_norm),
      NA_character_,
      dplyr::if_else(
        pupil_x_preproc_norm < 0 | pupil_x_preproc_norm > 1 |
          pupil_y_preproc_norm < 0 | pupil_y_preproc_norm > 1,
        "gaze outside [0, 1] (x or y)",
        "gaze inside [0, 1]"
      )
    )
  ) %>%
  filter(!is.na(pupilDiameter_scaled), !is.na(gaze_region))

ggplot(fmri3_gaze_pupil, aes(x = pupilDiameter_scaled, fill = gaze_region)) +
  geom_density(alpha = 0.4, linewidth = 0.35, color = "gray20", na.rm = TRUE) +
  facet_wrap(vars(subject), scales = "free", ncol = 6) +
  theme_classic() +
  theme(legend.position = "bottom") +
  scale_fill_manual(
    values = c("gaze inside [0, 1]" = "gray65", "gaze outside [0, 1] (x or y)" = "firebrick2")
  ) +
  labs(
    title = "fMRI study 3 — pupil size vs gaze position",
    subtitle = "Scaled pupil diameter when normalized gaze (x or y) is outside vs inside [0, 1]",
    x = "z-scored pupil diameter",
    y = "density",
    fill = NULL
  )

ggplot(fmri3_gaze_pupil, aes(x = pupilDiameter_scaled, fill = gaze_region)) +
  geom_density(alpha = 0.4, linewidth = 0.35, color = "gray20", na.rm = TRUE) +
  theme_classic() +
  theme(legend.position = "bottom") +
  scale_fill_manual(
    values = c("gaze inside [0, 1]" = "gray65", "gaze outside [0, 1] (x or y)" = "firebrick2")
  ) +
  labs(
    title = "fMRI study 3 — pupil size vs gaze position",
    subtitle = "Scaled pupil diameter when normalized gaze (x or y) is outside vs inside [0, 1]",
    x = "z-scored pupil diameter",
    y = "density",
    fill = NULL
  )
```

# visualize pupil data quality for outliers
```{r}
# Per subject: 95% CI for mean normalized gaze x and mean gaze y (lm intercept + confint each axis).
# Axis-aligned box [x_CI] x [y_CI] is the product of those marginal CIs for the mean (not a bivariate ellipse).
# Samples whose gaze (x,y) lies outside that box get "outside"; pupil densities are split by that gaze rule.
fmri3_gaze_ci_bounds <- fmri3_pupil_data %>%
  dplyr::filter(!is.na(pupil_x_preproc_norm), !is.na(pupil_y_preproc_norm)) %>%
  dplyr::group_by(subject) %>%
  dplyr::group_modify(function(.x, .y) {
    if (nrow(.x) < 10L) {
      return(tibble::tibble(
        xlo = NA_real_, xhi = NA_real_,
        ylo = NA_real_, yhi = NA_real_
      ))
    }
    fx <- stats::lm(pupil_x_preproc_norm ~ 1, data = .x)
    fy <- stats::lm(pupil_y_preproc_norm ~ 1, data = .x)
    cx <- stats::confint(fx, level = 0.95)
    cy <- stats::confint(fy, level = 0.95)
    tibble::tibble(
      xlo = as.numeric(cx[1L, 1L]), xhi = as.numeric(cx[1L, 2L]),
      ylo = as.numeric(cy[1L, 1L]), yhi = as.numeric(cy[1L, 2L])
    )
  }) %>%
  dplyr::ungroup()

fmri3_pupil_qc_base <- fmri3_pupil_data %>%
  dplyr::left_join(fmri3_gaze_ci_bounds, by = "subject") %>%
  dplyr::mutate(
    gaze_region_01 = dplyr::if_else(
      is.na(pupil_x_preproc_norm) | is.na(pupil_y_preproc_norm),
      NA_character_,
      dplyr::if_else(
        pupil_x_preproc_norm < 0 | pupil_x_preproc_norm > 1 |
          pupil_y_preproc_norm < 0 | pupil_y_preproc_norm > 1,
        "gaze outside [0, 1] (x or y)",
        "gaze inside [0, 1]"
      )
    ),
    gaze_vs_mean_ci = dplyr::case_when(
      is.na(xlo) | is.na(xhi) | is.na(ylo) | is.na(yhi) ~ NA_character_,
      is.na(pupil_x_preproc_norm) | is.na(pupil_y_preproc_norm) ~ NA_character_,
      pupil_x_preproc_norm < xlo | pupil_x_preproc_norm > xhi |
        pupil_y_preproc_norm < ylo | pupil_y_preproc_norm > yhi ~
        "gaze outside 95% CI box (mean x & y)",
      TRUE ~ "gaze inside 95% CI box (mean x & y)"
    )
  )

fmri3_pupil_qc_ci <- fmri3_pupil_qc_base %>%
  dplyr::filter(!is.na(pupilDiameter_scaled), !is.na(gaze_vs_mean_ci))

ggplot(fmri3_pupil_qc_ci, aes(x = pupilDiameter_scaled, fill = gaze_vs_mean_ci)) +
  geom_density(alpha = 0.4, linewidth = 0.35, color = "gray20", na.rm = TRUE) +
  facet_wrap(vars(subject), scales = "free", ncol = 6) +
  theme_classic() +
  theme(legend.position = "bottom") +
  scale_fill_manual(
    values = c(
      "gaze inside 95% CI box (mean x & y)" = "gray65",
      "gaze outside 95% CI box (mean x & y)" = "darkorange2"
    )
  ) +
  labs(
    title = "fMRI study 3 — pupil by gaze vs per-subject 95% CI rectangle (mean x, mean y)",
    subtitle = "Split rule uses gaze only (confint on lm intercept for each axis); curves are pupilDiameter_scaled",
    x = "z-scored pupil diameter",
    y = "density",
    fill = NULL
  )

ggplot(fmri3_pupil_qc_ci, aes(x = pupilDiameter_scaled, fill = gaze_vs_mean_ci)) +
  geom_density(alpha = 0.4, linewidth = 0.35, color = "gray20", na.rm = TRUE) +
  theme_classic() +
  theme(legend.position = "bottom") +
  scale_fill_manual(
    values = c(
      "gaze inside 95% CI box (mean x & y)" = "gray65",
      "gaze outside 95% CI box (mean x & y)" = "darkorange2"
    )
  ) +
  labs(
    title = "fMRI study 3 — same gaze–CI split, all subjects pooled",
    x = "z-scored pupil diameter",
    y = "density",
    fill = NULL
  )
```

# Compare original vs gaze-regressed pupil signals and their associations with arousal 

### VR study 1 (vrmid1) — example participant timecourse overlay

```{r}
example_sub <- vrmid1_pupil_data %>%
  group_by(Subject) %>%
  summarise(n_arousal = sum(!is.na(arousal)),
            n_both_signal = sum(!is.na(pupil_Avg_scaled) & !is.na(pupil_Avg_xyvar_scaled)),
            .groups = "drop") %>%
  filter(n_arousal > 20, n_both_signal > 500) %>%
  arrange(desc(n_arousal), desc(n_both_signal)) %>%
  slice(2) %>%
  pull(Subject)

example_df <- vrmid1_pupil_data %>%
  filter(Subject == example_sub,
         sample_in_trial_t >= 0,
         Time_sec >= 0, trial< 5) %>%
  select(Subject, trial, sample_in_trial_t, arousal_start, Time,
         pupil_Avg_scaled, pupil_Avg_xyvar_scaled) %>%
  pivot_longer(cols = c(pupil_Avg_scaled, pupil_Avg_xyvar_scaled),
               names_to = "signal",
               values_to = "pupil_value")

ggplot(example_df,
       aes(x = sample_in_trial_t, y = pupil_value, color = signal)) +
  geom_line(alpha = 0.8, linewidth = 0.4) +
  scale_color_manual(values = c("pupil_Avg_scaled" = "steelblue4",
                                "pupil_Avg_xyvar_scaled" = "firebrick3")) +
  theme_classic() +
  labs(title = paste0("VR study 1 — example participant: ", example_sub),
       x = "Sample index (continuous)",
       y = "Scaled pupil",
       color = "Signal")+
  facet_wrap(~trial)
```

### fMRI study 3 (fmri3) — example participant timecourse overlay

```{r}
example_sub_fmri <- fmri3_pupil_data %>%
  group_by(subject) %>%
  summarise(n_arousal = sum(!is.na(arousal)),
            n_both_signal = sum(!is.na(pupilDiameter_scaled) & !is.na(pupilDiameter_xyvar_scaled)),
            .groups = "drop") %>%
  filter(n_arousal > 20, n_both_signal > 500) %>%
  arrange(desc(n_arousal), desc(n_both_signal)) %>%
  slice(1) %>%
  pull(subject)

example_df_fmri <- fmri3_pupil_data %>%
  filter(subject == example_sub_fmri,
         sample_in_trial_t >= 0,
         Time_sec >= 0, trial<5) %>%
  select(subject, trial, sample_in_trial_t, times, Time_sec,
         pupilDiameter_scaled, pupilDiameter_xyvar_scaled) %>%
  pivot_longer(cols = c(pupilDiameter_scaled, pupilDiameter_xyvar_scaled),
               names_to = "signal",
               values_to = "pupil_value")

ggplot(example_df_fmri,
       aes(x = sample_in_trial_t, y = pupil_value, color = signal)) +
  geom_line(alpha = 0.8, linewidth = 0.4) +
  scale_color_manual(values = c("pupilDiameter_scaled" = "steelblue4",
                                "pupilDiameter_xyvar_scaled" = "firebrick3")) +
  theme_classic() +
  labs(title = paste0("fMRI study 3 — example participant: ", example_sub_fmri),
       x = "Sample index (continuous)",
       y = "Scaled pupil",
       color = "Signal")+
  facet_wrap(~trial)
```

## variance explained by the regression model
```{r}
vrmid1_xyvar_fit_summary<-read_csv("~/Desktop/VRMID-analysis/mid-pupil/data/vrmid1/derivatives/pupil_xyvar_fit_summary.csv")
fmri3_xyvar_fit_summary<-read_csv("~/Desktop/VRMID-analysis/mid-pupil/data/fmri3//derivatives/pupil_xyvar_fit_summary.csv")

summary(vrmid1_xyvar_fit_summary$adj_r2)*100
confint(vrmid1_xyvar_fit_summary$adj_r2)*100

summary(fmri3_xyvar_fit_summary$adj_r2)*100
confint(fmri3_xyvar_fit_summary$adj_r2)*100
```

## LMER comparison by study (parallel to s4a style)

### anticipation
```{r}
# lmerTest::anova() Pr(>F) for fixed effects, concatenated in same model order as r.squaredGLMM rows
collect_anova_p <- function(...) {
  vals <- numeric(0)
  for (m in list(...)) {
    vals <- c(vals, as.numeric(stats::na.omit(anova(m)[["Pr(>F)"]])))
  }
  vals
}

# vrmid1
vrmid1_xy_ant <- vrmid1_pupil_data %>%
  filter(
    probe == "anti",
    sample_in_trial_t <= vrmid1_ant_window[2],
    sample_in_trial_t > vrmid1_ant_window[1]
  ) %>%
  group_by(Subject, trial) %>%
  summarise(mean_pupil_xyvar = mean(pupil_Avg_xyvar_scaled, na.rm = TRUE), 
            mean_pupil_xyvar_baseline = mean(pupil_Avg_xyvar_baseline, na.rm = TRUE),
            mean_pupil_xyvar_bc = mean(pupil_Avg_xyvar_bc_scaled, na.rm = TRUE), .groups = "drop")

da <- vrmid1_data_antprobe  %>%
  filter(
    !is.na(arousal_scaled),
    !is.na(mean_pupil_nobc_ant),
    !is.na(mean_pupil_baseline_ant),
    !is.na(mean_pupil_bc_ant)
  )%>%
  select(Subject, trial, condition, arousal_scaled, mean_pupil_nobc_ant) %>%
  rename(mean_pupil_avg = mean_pupil_nobc_ant) %>%
  left_join(vrmid1_xy_ant, by = c("Subject", "trial")) %>%
  filter(!is.na(arousal_scaled), !is.na(mean_pupil_avg), !is.na(mean_pupil_xyvar))

summary(avg <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_avg) + (1 | Subject) + (1 | condition), da))

summary(xy_tp <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_xyvar) + (1 | Subject) + (1 | condition), da))

summary(xy_t_p <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_xyvar_baseline) + scale(mean_pupil_xyvar_bc) + (1 | Subject) + (1 | condition), da))

summary(xy_t <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_xyvar_baseline) + (1 | Subject) + (1 | condition), da))
summary(xy_p <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_xyvar_bc) + (1 | Subject) + (1 | condition), da))

rbind(r.squaredGLMM(avg), #should be 14.11
r.squaredGLMM(xy_t),
r.squaredGLMM(xy_p),
r.squaredGLMM(xy_tp),
r.squaredGLMM(xy_t_p))*100

data.frame(
  model = c("avg", "xy_t", "xy_p", "xy_tp", "xy_t_p_baseline", "xy_t_p_bc"),
  `Pr(>F)` = collect_anova_p(avg, xy_t, xy_p, xy_tp, xy_t_p),
  row.names = NULL,
  check.names = FALSE
)
```

```{r}
# fmri3
fmri3_xy_ant <- fmri3_pupil_data %>%
  filter(
    probe == 1,
    sample_in_trial_t <= fmri3_ant_window[2],
    sample_in_trial_t > fmri3_ant_window[1]
  ) %>%
  group_by(subject, trial) %>%
  summarise(
    mean_pupil_xyvar = mean(pupilDiameter_xyvar_scaled, na.rm = TRUE),
    mean_pupil_xyvar_baseline = mean(pupilDiameter_xyvar_baseline, na.rm = TRUE),
    mean_pupil_xyvar_bc = mean(pupilDiameter_xyvar_bc_scaled, na.rm = TRUE),
    .groups = "drop"
  )

da <- fmri3_data_antprobe %>%
  filter(
    !is.na(arousal_scaled),
    !is.na(mean_pupil_nobc_scaled_ant),
    !is.na(mean_pupil_baseline_scaled),
    !is.na(mean_pupil_bc_scaled_ant)
  ) %>%
  select(subject, trial, cue_size, arousal_scaled, mean_pupil_nobc_scaled_ant) %>%
  rename(mean_pupil_avg = mean_pupil_nobc_scaled_ant) %>%
  left_join(fmri3_xy_ant, by = c("subject", "trial")) %>%
  filter(!is.na(arousal_scaled), !is.na(mean_pupil_avg), !is.na(mean_pupil_xyvar))

summary(avg <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_avg) + (1 | subject) + (1 | cue_size), da))

summary(xy_tp <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_xyvar) + (1 | subject) + (1 | cue_size), da))

summary(xy_t_p <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_xyvar_baseline) + scale(mean_pupil_xyvar_bc) + (1 | subject) + (1 | cue_size), da))

summary(xy_t <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_xyvar_baseline) + (1 | subject) + (1 | cue_size), da))
summary(xy_p <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_xyvar_bc) + (1 | subject) + (1 | cue_size), da))

rbind(r.squaredGLMM(avg),
      r.squaredGLMM(xy_t),
      r.squaredGLMM(xy_p),
      r.squaredGLMM(xy_tp),
      r.squaredGLMM(xy_t_p)) * 100

data.frame(
  model = c("avg", "xy_t", "xy_p", "xy_tp", "xy_t_p_baseline", "xy_t_p_bc"),
  `Pr(>F)` = collect_anova_p(avg, xy_t, xy_p, xy_tp, xy_t_p),
  row.names = NULL,
  check.names = FALSE
)
```

### outcome
```{r}
# vrmid1
vrmid1_xy_out <- vrmid1_pupil_data %>%
  filter(
    probe == "out",
    sample_in_trial_t <= vrmid1_outprobe_out_window[2],
    sample_in_trial_t > vrmid1_outprobe_out_window[1]
  ) %>%
  group_by(Subject, trial) %>%
  summarise(
    mean_pupil_xyvar = mean(pupil_Avg_xyvar_scaled, na.rm = TRUE),
    mean_pupil_xyvar_baseline = mean(pupil_Avg_xyvar_baseline, na.rm = TRUE),
    mean_pupil_xyvar_bc = mean(pupil_Avg_xyvar_bc_scaled, na.rm = TRUE),
    .groups = "drop"
  )

do <- vrmid1_data_outprobe %>%
  filter(
    !is.na(arousal_scaled),
    !is.na(mean_pupil_nobc_out),
    !is.na(mean_pupil_baseline_out),
    !is.na(mean_pupil_bc_out)
  ) %>%
  select(Subject, trial, condition, arousal_scaled, mean_pupil_nobc_out) %>%
  rename(mean_pupil_avg = mean_pupil_nobc_out) %>%
  left_join(vrmid1_xy_out, by = c("Subject", "trial")) %>%
  filter(!is.na(arousal_scaled), !is.na(mean_pupil_avg), !is.na(mean_pupil_xyvar))

summary(avg <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_avg) + (1 | Subject) + (1 | condition), do))

summary(xy_tp <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_xyvar) + (1 | Subject) + (1 | condition), do))

summary(xy_t_p <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_xyvar_baseline) + scale(mean_pupil_xyvar_bc) + (1 | Subject) + (1 | condition), do))

summary(xy_t <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_xyvar_baseline) + (1 | Subject) + (1 | condition), do))
summary(xy_p <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_xyvar_bc) + (1 | Subject) + (1 | condition), do))

rbind(r.squaredGLMM(avg),
      r.squaredGLMM(xy_t),
      r.squaredGLMM(xy_p),
      r.squaredGLMM(xy_tp),
      r.squaredGLMM(xy_t_p)) * 100

data.frame(
  model = c("avg", "xy_t", "xy_p", "xy_tp", "xy_t_p_baseline", "xy_t_p_bc"),
  `Pr(>F)` = collect_anova_p(avg, xy_t, xy_p, xy_tp, xy_t_p),
  row.names = NULL,
  check.names = FALSE
)
```

```{r}
# fmri3
fmri3_xy_out <- fmri3_pupil_data %>%
  filter(
    probe == 2,
    sample_in_trial_t <= fmri3_outprobe_out_window[2],
    sample_in_trial_t > fmri3_outprobe_out_window[1]
  ) %>%
  group_by(subject, trial) %>%
  summarise(
    mean_pupil_xyvar = mean(pupilDiameter_xyvar_scaled, na.rm = TRUE),
    mean_pupil_xyvar_baseline = mean(pupilDiameter_xyvar_baseline, na.rm = TRUE),
    mean_pupil_xyvar_bc = mean(pupilDiameter_xyvar_bc_scaled, na.rm = TRUE),
    .groups = "drop"
  )

do <- fmri3_data_outprobe %>%
  filter(
    !is.na(arousal_scaled),
    !is.na(mean_pupil_nobc_scaled_out),
    !is.na(mean_pupil_baseline_scaled),
    !is.na(mean_pupil_bc_scaled_out)
  ) %>%
  select(subject, trial, cue_size, arousal_scaled, mean_pupil_nobc_scaled_out) %>%
  rename(mean_pupil_avg = mean_pupil_nobc_scaled_out) %>%
  left_join(fmri3_xy_out, by = c("subject", "trial")) %>%
  filter(!is.na(arousal_scaled), !is.na(mean_pupil_avg), !is.na(mean_pupil_xyvar))

summary(avg <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_avg) + (1 | subject) + (1 | cue_size), do))

summary(xy_tp <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_xyvar) + (1 | subject) + (1 | cue_size), do))

summary(xy_t_p <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_xyvar_baseline) + scale(mean_pupil_xyvar_bc) + (1 | subject) + (1 | cue_size), do))

summary(xy_t <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_xyvar_baseline) + (1 | subject) + (1 | cue_size), do))
summary(xy_p <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_xyvar_bc) + (1 | subject) + (1 | cue_size), do))

rbind(r.squaredGLMM(avg),
      r.squaredGLMM(xy_t),
      r.squaredGLMM(xy_p),
      r.squaredGLMM(xy_tp),
      r.squaredGLMM(xy_t_p)) * 100

data.frame(
  model = c("avg", "xy_t", "xy_p", "xy_tp", "xy_t_p_baseline", "xy_t_p_bc"),
  `Pr(>F)` = collect_anova_p(avg, xy_t, xy_p, xy_tp, xy_t_p),
  row.names = NULL,
  check.names = FALSE
)
```

### both probes
```{r}
# vrmid1
vrmid1_xy_both <- bind_rows(
  vrmid1_xy_ant %>% mutate(probe_model = "anti"),
  vrmid1_xy_out %>% mutate(probe_model = "out")
) %>% mutate(probe_model = factor(probe_model, levels = c("anti", "out")))

db <- vrmid1_data_2probes %>%
  filter(
    !is.na(arousal_scaled),
    !is.na(mean_pupil_nobc),
    !is.na(mean_pupil_baseline),
    !is.na(mean_pupil_bc)
  ) %>%
  select(Subject, trial, probe, condition, arousal_scaled, mean_pupil_nobc) %>%
  mutate(probe_model = factor(probe, levels = c("anti", "out"))) %>%
  rename(mean_pupil_avg = mean_pupil_nobc) %>%
  left_join(vrmid1_xy_both, by = c("Subject", "trial", "probe_model")) %>%
  filter(!is.na(arousal_scaled), !is.na(mean_pupil_avg), !is.na(mean_pupil_xyvar))

summary(avg <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_avg) + (1 | Subject) + (1 | condition) + (1+scale(mean_pupil_avg)| probe_model), db))

summary(xy_tp <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_xyvar) + (1 | Subject) + (1 | condition) + (1+scale(mean_pupil_xyvar)  | probe_model), db))

summary(xy_t_p <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_xyvar_baseline) + scale(mean_pupil_xyvar_bc) + (1 | Subject) + (1 | condition) + (1+scale(mean_pupil_xyvar_baseline) + scale(mean_pupil_xyvar_bc) | probe_model), db))

summary(xy_t <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_xyvar_baseline) + (1 | Subject) + (1 | condition) + (1+ scale(mean_pupil_xyvar_baseline) | probe_model), db))

summary(xy_p <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_xyvar_bc) + (1 | Subject) + (1 | condition) + (1 +scale(mean_pupil_xyvar_bc) | probe_model), db))

round(rbind(r.squaredGLMM(avg),
      r.squaredGLMM(xy_t),
      r.squaredGLMM(xy_p),
      r.squaredGLMM(xy_tp),
      r.squaredGLMM(xy_t_p)) * 100,2)

data.frame(
  model = c("avg", "xy_t", "xy_p", "xy_tp", "xy_t_p_baseline", "xy_t_p_bc"),
  `Pr(>F)` = collect_anova_p(avg, xy_t, xy_p, xy_tp, xy_t_p),
  row.names = NULL,
  check.names = FALSE
)
```

```{r}
# fmri3
fmri3_xy_both <- bind_rows(
  fmri3_xy_ant %>% mutate(probe_model = "anti"),
  fmri3_xy_out %>% mutate(probe_model = "out")
) %>% mutate(probe_model = factor(probe_model, levels = c("anti", "out")))

db <- fmri3_data_2probes %>%
  filter(
    !is.na(arousal_scaled),
    !is.na(mean_pupil_nobc),
    !is.na(mean_pupil_baseline),
    !is.na(mean_pupil_bc)
  ) %>%
  select(subject, trial, probe, cue_size, arousal_scaled, mean_pupil_nobc) %>%
  mutate(probe_model = factor(probe, levels = c(1, 2), labels = c("anti", "out"))) %>%
  rename(mean_pupil_avg = mean_pupil_nobc) %>%
  left_join(fmri3_xy_both, by = c("subject", "trial", "probe_model")) %>%
  filter(!is.na(arousal_scaled), !is.na(mean_pupil_avg), !is.na(mean_pupil_xyvar))

summary(avg <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_avg) + (1 | subject) + (1 | cue_size) + (1 | probe_model), db))

summary(xy_tp <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_xyvar) + (1 | subject) + (1 | cue_size) + (1 | probe_model), db))

summary(xy_t_p <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_xyvar_baseline) + scale(mean_pupil_xyvar_bc) + (1 | subject) + (1 | cue_size) + (1 | probe_model), db))

summary(xy_t <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_xyvar_baseline) + (1 | subject) + (1 | cue_size) + (1 | probe_model), db))
summary(xy_p <- lmer(scale(arousal_scaled) ~ scale(mean_pupil_xyvar_bc) + (1 | subject) + (1 | cue_size) + (1 | probe_model), db))

rbind(r.squaredGLMM(avg),
      r.squaredGLMM(xy_t),
      r.squaredGLMM(xy_p),
      r.squaredGLMM(xy_tp),
      r.squaredGLMM(xy_t_p)) * 100

data.frame(
  model = c("avg", "xy_t", "xy_p", "xy_tp", "xy_t_p_baseline", "xy_t_p_bc"),
  `Pr(>F)` = collect_anova_p(avg, xy_t, xy_p, xy_tp, xy_t_p),
  row.names = NULL,
  check.names = FALSE
)
```

## pool the effect sizes and make summary plots
```{r}
# trial-level pooled data (anticipation)
data_antprobe <- bind_rows(
  vrmid1_data_antprobe %>%
    select(Subject, trial, condition, arousal_scaled, mean_pupil_nobc_ant) %>%
    rename(mean_pupil_avg = mean_pupil_nobc_ant) %>%
    left_join(vrmid1_xy_ant, by = c("Subject", "trial")) %>%
    mutate(study = "VRStudy"),
  fmri3_data_antprobe %>%
    select(subject, trial, cue_size, arousal_scaled, mean_pupil_nobc_scaled_ant) %>%
    rename(mean_pupil_avg = mean_pupil_nobc_scaled_ant) %>%
    left_join(fmri3_xy_ant, by = c("subject", "trial")) %>%
    rename(Subject = subject, condition = cue_size) %>%
    mutate(study = "FMRIStudy")
) %>%
  filter(!is.na(arousal_scaled), !is.na(mean_pupil_avg), !is.na(mean_pupil_xyvar)) %>%
  ungroup()

# trial-level pooled data (outcome)
data_outprobe <- bind_rows(
  vrmid1_data_outprobe %>%
    select(Subject, trial, condition, arousal_scaled, mean_pupil_nobc_out) %>%
    rename(mean_pupil_avg = mean_pupil_nobc_out) %>%
    left_join(vrmid1_xy_out, by = c("Subject", "trial")) %>%
    mutate(study = "VRStudy"),
  fmri3_data_outprobe %>%
    select(subject, trial, cue_size, arousal_scaled, mean_pupil_nobc_scaled_out) %>%
    rename(mean_pupil_avg = mean_pupil_nobc_scaled_out) %>%
    left_join(fmri3_xy_out, by = c("subject", "trial")) %>%
    rename(Subject = subject, condition = cue_size) %>%
    mutate(study = "FMRIStudy")
) %>%
  filter(!is.na(arousal_scaled), !is.na(mean_pupil_avg), !is.na(mean_pupil_xyvar)) %>%
  ungroup()

plot_dat <- bind_rows(
  data_antprobe %>% mutate(probe = "Anticipation"),
  data_outprobe %>% mutate(probe = "Outcome")
) %>%
  mutate(
    study = recode(study, VRStudy = "VR", FMRIStudy = "fMRI"),
    study = factor(study, levels = c("VR", "fMRI"))
  ) %>%
  pivot_longer(
    cols = c(mean_pupil_avg, mean_pupil_xyvar),
    names_to = "signal",
    values_to = "pupil_value"
  ) %>%
  mutate(
    signal = recode(signal,
                    mean_pupil_avg = "Original",
                    mean_pupil_xyvar = "XYvar"),
    signal = factor(signal, levels = c("Original", "XYvar")),
    probe = factor(probe, levels = c("Anticipation", "Outcome"))
  )

ggplot(plot_dat, aes(x = pupil_value, y = arousal_scaled, color = signal)) +
  geom_point(alpha = 0.22, size = 0.5) +
  geom_smooth(method = "lm", se = TRUE, linewidth = 1) +
  facet_grid(probe ~ study, scales = "free_x") +
  scale_color_manual(values = c("Original" = "steelblue4", "XYvar" = "firebrick3")) +
  theme_classic() +
  labs(
    x = "z-scored pupil size",
    y = "z-scored arousal rating",
    color = "Signal"
  )
# ggsave("~/Desktop/VRMID-analysis/mid-pupil/figures/fig4c_pooled_effects_xyvar.tiff", dpi = 300, height = 6, width = 8)
ggsave("~/Desktop/VRMID-analysis/mid-pupil/figures/fig4c_pooled_effects_xyvar.png", dpi = 300, height = 6, width = 8)
```

```{r}
get_model_stats <- function(dat, predictor, study_label, probe_label) {
  if (study_label == "VR") {
    fit <- lmer(
      as.formula(paste0("scale(arousal_scaled) ~ scale(", predictor, ") + (1|Subject) + (1|condition)")),
      dat
    )
  } else {
    fit <- lmer(
      as.formula(paste0("scale(arousal_scaled) ~ scale(", predictor, ") + (1|subject) + (1|cue_size)")),
      dat
    )
  }

  cf <- summary(fit)$coefficient
  r2 <- r.squaredGLMM(fit)

  data.frame(
    probe = probe_label,
    study = study_label,
    signal = ifelse(predictor == "mean_pupil_avg", "Original", "XYvar"),
    beta = unname(cf[2, "Estimate"]),
    p_value = unname(cf[2, "Pr(>|t|)"]),
    R2m = unname(r2[1]),
    R2c = unname(r2[2])
  )
}

vr_ant <- data_antprobe %>% filter(study == "VRStudy")
fmri_ant <- data_antprobe %>% filter(study == "FMRIStudy") %>% rename(subject = Subject, cue_size = condition)
vr_out <- data_outprobe %>% filter(study == "VRStudy")
fmri_out <- data_outprobe %>% filter(study == "FMRIStudy") %>% rename(subject = Subject, cue_size = condition)

model_table <- bind_rows(
  get_model_stats(vr_ant, "mean_pupil_avg", "VR", "Anticipation"),
  get_model_stats(vr_ant, "mean_pupil_xyvar", "VR", "Anticipation"),
  get_model_stats(fmri_ant, "mean_pupil_avg", "fMRI", "Anticipation"),
  get_model_stats(fmri_ant, "mean_pupil_xyvar", "fMRI", "Anticipation"),
  get_model_stats(vr_out, "mean_pupil_avg", "VR", "Outcome"),
  get_model_stats(vr_out, "mean_pupil_xyvar", "VR", "Outcome"),
  get_model_stats(fmri_out, "mean_pupil_avg", "fMRI", "Outcome"),
  get_model_stats(fmri_out, "mean_pupil_xyvar", "fMRI", "Outcome")
) %>%
  mutate(
    p_value = signif(p_value, 3),
    beta = round(beta, 3),
    R2m = round(R2m, 3),
    R2c = round(R2c, 3)
  ) %>%
  arrange(probe, study, signal)

model_table %>%
  kable() %>%
  kable_styling()
```
