---
title: "tonic_phasic_behavior"
output: html_document
date: "2025-12-27"
---

```{r setup, include=FALSE}
source("../helper/save_figure.R")
```

## fatigue: visualise tonic activity over time
```{r}
vrmid1_pupil_data_tonic <- vrmid1_pupil_data%>%
  filter(Time_sec >= vrmid1_ant_window[1], Time_sec <= vrmid1_ant_window[2])%>% 
  select(Subject,probe,condition,trial,pupil_Avg_baseline_scaled,pupil_Avg_bc_scaled,pupil_Avg_scaled,
         last_ITI,arousal_scaled,valence_scaled,reaction_outcome)%>%
  group_by(Subject,trial,probe,condition,
         arousal_scaled,valence_scaled,reaction_outcome)%>%
  summarise(pupil_Avg_baseline_scaled = mean(pupil_Avg_baseline_scaled,na.rm = T),
                   pupil_Avg_bc_scaled = mean(pupil_Avg_bc_scaled,na.rm=T),
            pupil_Avg_scaled = mean(pupil_Avg_scaled, na.rm = T)) %>% 
  mutate(hit = (reaction_outcome == "Hit"))%>%
  ungroup() %>% 
  group_by(Subject) %>% 
  mutate(half = ifelse(trial >= 48,"second","first"),
         hit = zoo::rollmean(hit, k = 5, align = "right", fill = NA)
  )

vrmid1_pupil_data_phasicarousal <- vrmid1_pupil_data%>%
  mutate(half = ifelse(trial >= 48,"second","first"))%>%
  select(Subject,probe,trial,half,
         last_ITI,arousal_scaled,valence_scaled,
         trial_type,reaction_outcome)%>%
  group_by(Subject,trial,trial_type,
         arousal_scaled,valence_scaled)%>%
  mutate(rowid = row_number(),
         hit = (reaction_outcome == "Hit")) %>% 
  filter(rowid == 1) %>% 
  ungroup() %>% 
  group_by(Subject,half) %>% 
  mutate(hit_rate = mean(hit)) %>% 
  group_by(Subject,half,trial_type,hit_rate)%>%
  summarise(arousal_scaled = mean(arousal_scaled,na.rm = T)) %>% 
  pivot_wider(names_from = trial_type, values_from = arousal_scaled) %>% 
  mutate(plus5_plus0 = `+$5` - `+$0`,
         minus5_minus0 = `-$5` - `-$0`,
         five_vs_zero = (plus5_plus0+minus5_minus0)/2)
  
summary(l1<-lmer(scale(pupil_Avg_baseline_scaled) ~ scale(trial)+scale(hit) + (1+scale(trial)+scale(hit)|Subject),vrmid1_pupil_data_tonic))

mytext=summary(l1)$coefficients

mytext = ifelse(mytext[2,5] >= 0.05, "n.s.",
                ifelse(mytext[2,5] >= 0.01, "*",
                       ifelse(mytext[2,5] >= 0.001, "**","***")))

# Extract random effects (BLUPs) for each participant
# Extract fixed and random effects from model
fixed_eff  <- fixef(l1)["scale(trial)"]
rand_eff   <- ranef(l1)$Subject[,"scale(trial)"]

# Combine into dataframe
df_slopes <- data.frame(Subject = rownames(ranef(l1)$Subject),
                        slope_trial = fixed_eff + rand_eff)

# Prepare trial values (use your observed range)
trial_seq <- 1:96

# Build dataframe of all predicted lines
df_lines <- do.call(rbind, lapply(unique(df_slopes$Subject), function(subj){
  intercept <- fixef(l1)[1] + ranef(l1)$Subject[subj,"(Intercept)"]
  slope     <- df_slopes[df_slopes$Subject == subj, "slope_trial"]
  
  data.frame(
    Subject = subj,
    trial   = trial_seq,
    pred    = intercept + slope * scale(trial_seq))
}))

df_lines2 <- data.frame(
    trial   = trial_seq,
    pred    = fixef(l1)[1] + fixed_eff * scale(trial_seq))

pt11 <- ggplot(data = df_lines) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  # add model-predicted lines
  geom_line(
            aes(x = trial, y = pred, group = Subject),
            color = "grey", alpha = 0.4, size = 0.4) +
  stat_summary(data = df_lines2,aes(x = trial, y = pred, group=1),
               size =1, geom = "line")+
  labs(y = "z-scored pupil",
       subtitle = "VR study",
       title = "Tonic pupil") +
  annotate("text", x = 48, y = 1, label = mytext)+
  scale_x_continuous(breaks = c(1,24,48,72,96))

summary(l1<-lmer(scale(pupil_Avg_bc_scaled) ~ scale(trial)+scale(hit) + (1+scale(trial)+scale(hit)|Subject),vrmid1_pupil_data_tonic))

mytext=summary(l1)$coefficients

mytext = ifelse(mytext[2,5] >= 0.05, "n.s.",
                ifelse(mytext[2,5] >= 0.01, "*",
                       ifelse(mytext[2,5] >= 0.001, "**","***")))

# Extract random effects (BLUPs) for each participant
# Extract fixed and random effects from model
fixed_eff  <- fixef(l1)["scale(trial)"]
rand_eff   <- ranef(l1)$Subject[,"scale(trial)"]

# Combine into dataframe
df_slopes <- data.frame(Subject = rownames(ranef(l1)$Subject),
                        slope_trial = fixed_eff + rand_eff)

# Prepare trial values (use your observed range)
trial_seq <- 1:96

# Build dataframe of all predicted lines
df_lines <- do.call(rbind, lapply(unique(df_slopes$Subject), function(subj){
  intercept <- fixef(l1)[1] + ranef(l1)$Subject[subj,"(Intercept)"]
  slope     <- df_slopes[df_slopes$Subject == subj, "slope_trial"]
  
  data.frame(
    Subject = subj,
    trial   = trial_seq,
    pred    = intercept + slope * scale(trial_seq))
}))


df_lines2 <- data.frame(
    trial   = trial_seq,
    pred    = fixef(l1)[1] + fixed_eff * scale(trial_seq))

pt12 <- ggplot(data = df_lines) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  # add model-predicted lines
  geom_line(aes(x = trial, y = pred, group = Subject),
            color = "grey", alpha = 0.4, size = 0.4) +
  stat_summary(data = df_lines2,aes(x = trial, y = pred, group=1),
               size =1, geom = "line")+
  labs(y = "z-scored pupil",
       subtitle = "VR study",
       title = "Corrected phasic pupil") +
  annotate("text", x = 48, y = 1, label = mytext)+
  scale_x_continuous(breaks = c(1,24,48,72,96))

summary(l1<-lmer(scale(arousal_scaled) ~ scale(trial)+scale(hit) + (1+scale(trial)+scale(hit)|Subject),vrmid1_pupil_data_tonic))

mytext=summary(l1)$coefficients

mytext = ifelse(mytext[2,5] >= 0.05, "n.s.",
                ifelse(mytext[2,5] >= 0.01, "*",
                       ifelse(mytext[2,5] >= 0.001, "**","***")))

# Extract random effects (BLUPs) for each participant
# Extract fixed and random effects from model
fixed_eff  <- fixef(l1)["scale(trial)"]
rand_eff   <- ranef(l1)$Subject[,"scale(trial)"]

# Combine into dataframe
df_slopes <- data.frame(Subject = rownames(ranef(l1)$Subject),
                        slope_trial = fixed_eff + rand_eff)

# Prepare trial values (use your observed range)
trial_seq <- 1:96

# Build dataframe of all predicted lines
df_lines <- do.call(rbind, lapply(unique(df_slopes$Subject), function(subj){
  intercept <- fixef(l1)[1] + ranef(l1)$Subject[subj,"(Intercept)"]
  slope     <- df_slopes[df_slopes$Subject == subj, "slope_trial"]
  
  data.frame(
    Subject = subj,
    trial   = trial_seq,
    pred    = intercept + slope * scale(trial_seq))
}))

df_lines2 <- data.frame(
    trial   = trial_seq,
    pred    = fixef(l1)[1] + fixed_eff * scale(trial_seq))

pt13 <- ggplot(data = df_lines) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  # add model-predicted lines
  geom_line(
            aes(x = trial, y = pred, group = Subject),
            color = "grey", alpha = 0.4, size = 0.4) +
  stat_summary(data = df_lines2,aes(x = trial, y = pred, group=1),
               size =1, geom = "line")+
  labs(y = "z-scored pupil",
       title = "VR Study",
       subtitle = "Mean reported arousal") +
  annotate("text", x = 48, y = 0.5, label = mytext)+
  scale_x_continuous(breaks = c(1,24,48,72,96))

summary(l1<-lmer(scale(valence_scaled) ~ scale(trial)+scale(hit) + (1+scale(trial)+scale(hit)|Subject),vrmid1_pupil_data_tonic))

mytext=summary(l1)$coefficients

mytext = ifelse(mytext[2,5] >= 0.05, "n.s.",
                ifelse(mytext[2,5] >= 0.01, "*",
                       ifelse(mytext[2,5] >= 0.001, "**","***")))

# Extract random effects (BLUPs) for each participant
# Extract fixed and random effects from model
fixed_eff  <- fixef(l1)["scale(trial)"]
rand_eff   <- ranef(l1)$Subject[,"scale(trial)"]

# Combine into dataframe
df_slopes <- data.frame(Subject = rownames(ranef(l1)$Subject),
                        slope_trial = fixed_eff + rand_eff)

# Prepare trial values (use your observed range)
trial_seq <- 1:96

# Build dataframe of all predicted lines
df_lines <- do.call(rbind, lapply(unique(df_slopes$Subject), function(subj){
  intercept <- fixef(l1)[1] + ranef(l1)$Subject[subj,"(Intercept)"]
  slope     <- df_slopes[df_slopes$Subject == subj, "slope_trial"]
  
  data.frame(
    Subject = subj,
    trial   = trial_seq,
    pred    = intercept + slope * scale(trial_seq))
}))

df_lines2 <- data.frame(
    trial   = trial_seq,
    pred    = fixef(l1)[1] + fixed_eff * scale(trial_seq))

pt14 <- ggplot(data = df_lines) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  # add model-predicted lines
  geom_line(
            aes(x = trial, y = pred, group = Subject),
            color = "grey", alpha = 0.4, size = 0.4) +
  stat_summary(data = df_lines2,aes(x = trial, y = pred, group=1),
               size =1, geom = "line")+
  labs(y = "z-scored pupil",
       title = "VR Study",
       subtitle = "Mean reported valence") +
  annotate("text", x = 48, y = 0.5, label = mytext)+
  scale_x_continuous(breaks = c(1,24,48,72,96))

summary(lmer(scale(five_vs_zero) ~ half + scale(hit_rate) +  (1|Subject),
             vrmid1_pupil_data_phasicarousal))
mytext=summary(lmer(scale(five_vs_zero) ~ half +hit_rate +  (1|Subject),vrmid1_pupil_data_phasicarousal))$coefficients
mytext = ifelse(mytext[2,5] >= 0.05, "n.s.",
                ifelse(mytext[2,5] >= 0.01, "*",
                       ifelse(mytext[2,5] >= 0.001, "**","***")))
pt15 <- ggplot(vrmid1_pupil_data_phasicarousal)+
  geom_hline(yintercept = 0, linetype = 'dashed')+
  stat_summary(aes(group = Subject, x = half, y = five_vs_zero),geom = "line",size = 0.3, alpha = 0.3,
            color = "grey")+
  stat_summary(aes(x = half, y = five_vs_zero),fun.data = "mean_cl_boot",geom = "pointrange",
               size = 0.2)+
  labs(y = "arousal ±$5-$0",
       subtitle = "arousal ±$5 minus ±$0",
       title = "VR Study")+
    annotate("text",x = 1.5, y = 1,label = mytext)+
  theme(plot.subtitle = element_text(size = 10))

fmri3_pupil_data_tonic <- fmri3_pupil_data%>%
  filter(Time_sec >= fmri3_ant_window[1], Time_sec <= fmri3_ant_window[2])%>% 
  select(subject,probe,cue_size,trial,pupilDiameter_baseline_scaled,pupilDiameter_bc_scaled,
         pupilDiameter_scaled,
         last_iti,arousal_scaled,valence_scaled,hit)%>%
  group_by(subject,trial,probe,cue_size,
         arousal_scaled,valence_scaled,hit,)%>%
  filter(last_iti != 0) %>% 
  summarise(pupilDiameter_baseline_scaled = mean(pupilDiameter_baseline_scaled,na.rm = T),
                   pupilDiameter_bc_scaled = mean(pupilDiameter_bc_scaled,na.rm=T),
            pupilDiameter_scaled = mean(pupilDiameter_scaled, na.rm = T)) %>% 
  ungroup()%>%
  mutate(half = ifelse(trial >= 48,"second","first"),
         hit = zoo::rollmean(as.numeric(hit=="Hit"), k = 5, align = "right", fill = NA))

fmri3_pupil_data_phasicarousal <- fmri3_pupil_data%>% 
   filter(!subject %in% c("tc240311","st240312"))%>%
  filter(rating_type == 1) %>%
  group_by(subject,trial,cue_value,
         arousal_scaled,valence_scaled,hit)%>%
  mutate(rowid = row_number()) %>% 
  filter(rowid == 1) %>% 
  group_by(subject)%>%
  mutate(trial = row_number()) %>% 
  mutate(half = ifelse(trial >= 24,"second","first"))%>%
  group_by(subject,half) %>% 
  mutate(hit_rate = mean(hit=="Hit")) %>% 
  group_by(subject,half,cue_value,hit_rate)%>%
  summarise(arousal_scaled = mean(arousal_scaled,na.rm = T)) %>%
  pivot_wider(names_from = cue_value, values_from = arousal_scaled) %>% 
  mutate(plus5_plus0 = `+$5` - `+$0`,
         minus5_minus0 = `-$5` - `-$0`,
         five_vs_zero = (plus5_plus0+minus5_minus0)/2)

summary(l3<-lmer(scale(pupilDiameter_baseline_scaled) ~ scale(trial)+scale(hit) + (1+scale(trial)+scale(hit)|subject),fmri3_pupil_data_tonic))

mytext=summary(l3)$coefficients

mytext = ifelse(mytext[2,5] >= 0.05, "n.s.",
                ifelse(mytext[2,5] >= 0.01, "*",
                       ifelse(mytext[2,5] >= 0.001, "**","***")))

# Extract random effects (BLUPs) for each participant
# Extract fixed and random effects from model
fixed_eff  <- fixef(l3)["scale(trial)"]
rand_eff   <- ranef(l3)$subject[,"scale(trial)"]

# Combine into dataframe
df_slopes <- data.frame(subject = rownames(ranef(l3)$subject),
                        slope_trial = fixed_eff + rand_eff)

# Prepare trial values (use your observed range)
trial_seq <- 1:96

# Build dataframe of all predicted lines
df_lines <- do.call(rbind, lapply(unique(df_slopes$subject), function(subj){
  intercept <- fixef(l3)[1] + ranef(l3)$subject[subj,"(Intercept)"]
  slope     <- df_slopes[df_slopes$subject == subj, "slope_trial"]
  
  data.frame(
    subject = subj,
    trial   = trial_seq,
    pred    = intercept + slope * scale(trial_seq))
}))


df_lines2 <- data.frame(
    trial   = trial_seq,
    pred    = fixef(l3)[1] + fixed_eff * scale(trial_seq))

pt31 <- ggplot(data = df_lines) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  # add model-predicted lines
  geom_line(
            aes(x = trial, y = pred, group = subject),
            color = "grey", alpha = 0.4, size = 0.4) +
  stat_summary(data = df_lines2,aes(x = trial, y = pred, group=1),
               size =1, geom = "line")+
  labs(y = "z-scored pupil",
       subtitle = "FMRI Study",
       # subtitle = "Tonic pupil"
       ) +
  annotate("text", x = 48, y = 1, label = mytext)+
  scale_x_continuous(breaks = c(1,24,48,72,96))

summary(l3<-lmer(scale(pupilDiameter_bc_scaled) ~ scale(trial)+scale(hit) + (1+scale(trial)+scale(hit)|subject),fmri3_pupil_data_tonic))

mytext=summary(l3)$coefficients

mytext = ifelse(mytext[2,5] >= 0.05, "n.s.",
                ifelse(mytext[2,5] >= 0.01, "*",
                       ifelse(mytext[2,5] >= 0.001, "**","***")))

# Extract random effects (BLUPs) for each participant
# Extract fixed and random effects from model
fixed_eff  <- fixef(l3)["scale(trial)"]
rand_eff   <- ranef(l3)$subject[,"scale(trial)"]

# Combine into dataframe
df_slopes <- data.frame(subject = rownames(ranef(l3)$subject),
                        slope_trial = fixed_eff + rand_eff)

# Prepare trial values (use your observed range)
trial_seq <- 1:96

# Build dataframe of all predicted lines
df_lines <- do.call(rbind, lapply(unique(df_slopes$subject), function(subj){
  intercept <- fixef(l3)[1] + ranef(l3)$subject[subj,"(Intercept)"]
  slope     <- df_slopes[df_slopes$subject == subj, "slope_trial"]
  
  data.frame(
    subject = subj,
    trial   = trial_seq,
    pred    = intercept + slope * scale(trial_seq))
}))


df_lines2 <- data.frame(
    trial   = trial_seq,
    pred    = fixef(l3)[1] + fixed_eff * scale(trial_seq))

pt32 <- ggplot(data = df_lines) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  # add model-predicted lines
  geom_line(
            aes(x = trial, y = pred, group = subject),
            color = "grey", alpha = 0.4, size = 0.4) +
  stat_summary(data = df_lines2,aes(x = trial, y = pred, group=1),
               size =1, geom = "line")+
  labs(y = "z-scored pupil",
       subtitle = "FMRI Study",
       # subtitle = "Corrected phasic pupil"
       ) +
  annotate("text", x = 48, y = 1, label = mytext)+
  scale_x_continuous(breaks = c(1,24,48,72,96))

summary(l3<-lmer(scale(arousal_scaled) ~ scale(trial)+scale(hit) + (1+scale(trial)+scale(hit)|subject),fmri3_pupil_data_tonic))

mytext=summary(l3)$coefficients

mytext = ifelse(mytext[2,5] >= 0.05, "n.s.",
                ifelse(mytext[2,5] >= 0.01, "*",
                       ifelse(mytext[2,5] >= 0.001, "**","***")))

# Extract random effects (BLUPs) for each participant
# Extract fixed and random effects from model
fixed_eff  <- fixef(l3)["scale(trial)"]
rand_eff   <- ranef(l3)$subject[,"scale(trial)"]

# Combine into dataframe
df_slopes <- data.frame(subject = rownames(ranef(l3)$subject),
                        slope_trial = fixed_eff + rand_eff)

# Prepare trial values (use your observed range)
trial_seq <- 1:96

# Build dataframe of all predicted lines
df_lines <- do.call(rbind, lapply(unique(df_slopes$subject), function(subj){
  intercept <- fixef(l3)[1] + ranef(l3)$subject[subj,"(Intercept)"]
  slope     <- df_slopes[df_slopes$subject == subj, "slope_trial"]
  
  data.frame(
    subject = subj,
    trial   = trial_seq,
    pred    = intercept + slope * scale(trial_seq))
}))


df_lines2 <- data.frame(
    trial   = trial_seq,
    pred    = fixef(l3)[1] + fixed_eff * scale(trial_seq))

pt33 <- ggplot(data = df_lines) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  # add model-predicted lines
  geom_line(
            aes(x = trial, y = pred, group = subject),
            color = "grey", alpha = 0.4, size = 0.4) +
  stat_summary(data = df_lines2,aes(x = trial, y = pred, group=1),
               size =1, geom = "line")+
  labs(y = "z-scored pupil",
       title = "FMRI Study",
       subtitle = "Mean reported arousal") +
  annotate("text", x = 48, y = 1, label = mytext)+
  scale_x_continuous(breaks = c(1,24,48,72,96))

summary(l3<-lmer(scale(valence_scaled) ~ scale(trial)+scale(hit) + (1+scale(trial)+scale(hit)|subject),fmri3_pupil_data_tonic))

mytext=summary(l3)$coefficients

mytext = ifelse(mytext[2,5] >= 0.05, "n.s.",
                ifelse(mytext[2,5] >= 0.01, "*",
                       ifelse(mytext[2,5] >= 0.001, "**","***")))

# Extract random effects (BLUPs) for each participant
# Extract fixed and random effects from model
fixed_eff  <- fixef(l3)["scale(trial)"]
rand_eff   <- ranef(l3)$subject[,"scale(trial)"]

# Combine into dataframe
df_slopes <- data.frame(subject = rownames(ranef(l3)$subject),
                        slope_trial = fixed_eff + rand_eff)

# Prepare trial values (use your observed range)
trial_seq <- 1:96

# Build dataframe of all predicted lines
df_lines <- do.call(rbind, lapply(unique(df_slopes$subject), function(subj){
  intercept <- fixef(l3)[1] + ranef(l3)$subject[subj,"(Intercept)"]
  slope     <- df_slopes[df_slopes$subject == subj, "slope_trial"]
  
  data.frame(
    subject = subj,
    trial   = trial_seq,
    pred    = intercept + slope * scale(trial_seq))
}))


df_lines2 <- data.frame(
    trial   = trial_seq,
    pred    = fixef(l3)[1] + fixed_eff * scale(trial_seq))

pt34 <- ggplot(data = df_lines) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  # add model-predicted lines
  geom_line(
            aes(x = trial, y = pred, group = subject),
            color = "grey", alpha = 0.4, size = 0.4) +
  stat_summary(data = df_lines2,aes(x = trial, y = pred, group=1),
               size =1, geom = "line")+
  labs(y = "z-scored pupil",
       title = "FMRI Study",
       subtitle = "Mean reported valence") +
  annotate("text", x = 48, y = 1, label = mytext)+
  scale_x_continuous(breaks = c(1,24,48,72,96))

summary(lmer(scale(five_vs_zero) ~ half + scale(hit_rate) +  (1|subject),
             fmri3_pupil_data_phasicarousal))
mytext=summary(lmer(five_vs_zero ~ half + hit_rate + (1|subject),fmri3_pupil_data_phasicarousal))$coefficients
mytext = ifelse(mytext[2,5] >= 0.05/4, "n.s.",
                ifelse(mytext[2,5] >= 0.01/4, "*",
                       ifelse(mytext[2,5] >= 0.001/4, "**","***")))
pt35 <- ggplot(fmri3_pupil_data_phasicarousal)+
  geom_hline(yintercept = 0, linetype = 'dashed')+
  stat_summary(aes(group = subject, x = half, y = five_vs_zero),geom = "line",size = 0.3, alpha = 0.3,
            color = "grey")+
  stat_summary(aes(x = half, y = five_vs_zero),fun.data = "mean_cl_boot",geom = "pointrange",
               size = 0.2)+
  labs(y = "arousal ±$5-±$0",
       subtitle = "arousal ±$5 minus ±$0",
       title = "FMRI Study")+
    annotate("text",x = 1.5, y = 0.4,label = mytext)+
   theme(plot.subtitle = element_text(size = 10))
  # annotate("text",x = 1.5, y = 0.4,label = paste0("t = ", round(mytext[2,4],2),", p = ",round(mytext[2,5],2)))
```

## were tonic and phasic both related to previous arousal?
### The original version
```{r}
vrmid1_pupil_data_tonic_history <- vrmid1_pupil_data_tonic %>% 
  group_by(Subject) %>%
  mutate(    # Generate recent average win percentages for windows 1 to 20
    map_dfc(0:9, function(k) {
      col <- lag(arousal_scaled, k)
      setNames(data.frame(col), paste0("arousal_scaled_lag", k))
    }))

vrmid1_pupil_data_tonic_history <- vrmid1_pupil_data_tonic_history %>%
  pivot_longer(arousal_scaled_lag0:arousal_scaled_lag9,
               names_to = "lag", values_to = "arousal",
               names_prefix = "arousal_scaled_lag")

dftemp1 <- NULL

for (l in 0:9){
  l1<-summary(lmer(arousal ~ pupil_Avg_baseline_scaled + (1|Subject) + (1|probe) + (1|condition),
               vrmid1_pupil_data_tonic_history %>% filter(lag == l)))
  l2<-summary(lmer(arousal ~ pupil_Avg_bc_scaled + (1|Subject)+ (1|probe) + (1|condition),
               vrmid1_pupil_data_tonic_history %>% filter(lag == l)))
  l3<-summary(lmer(arousal ~ pupil_Avg_scaled + (1|Subject)+ (1|probe) + (1|condition),
               vrmid1_pupil_data_tonic_history %>% filter(lag == l)))
  dftemp1 <- rbind(dftemp1,
                  rbind(l1$coefficients[2,],
                        l2$coefficients[2,],
                        l3$coefficients[2,]))
}
  
dftemp1 <- as.data.frame(dftemp1)
dftemp1$lag <- rep(0:9,each=3)
dftemp1$measure <- rep(c("tonic","corrected phasic","total evoked response"),10)
dftemp1 <- dftemp1 %>% 
  mutate(p_corrected = `Pr(>|t|)`*10,
         shape = ifelse(`Pr(>|t|)` < .05/10, 19, 1))  # numeric alpha

p1 <- ggplot(dftemp1 %>% filter(measure != "total evoked response"), aes(x = lag, y = Estimate, color = measure,shape = shape)) +
  annotate("rect", xmin = -0.5, ymin = -0.1, xmax = 0.5, ymax = 0.3, alpha = 0.1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`),
                width = 0.1) +
  labs(x = "arousal rating __ trials ago",
       y = "std. beta",
       title = "VR Study",
       color = NULL) +
  theme(legend.position = "top") +
  scale_color_manual(values = c("red4", "steelblue")) +
  scale_shape_identity()+
  guides(color = guide_legend(nrow = 2))+
  scale_x_reverse(breaks = 0:9)

fmri3_pupil_data_tonic_history <- fmri3_pupil_data_tonic %>% 
  group_by(subject) %>%
  mutate(    # Generate recent average win percentages for windows 1 to 20
    map_dfc(0:9, function(k) {
      col <- lag(arousal_scaled, k)
      setNames(data.frame(col), paste0("arousal_scaled_lag", k))
    }))

fmri3_pupil_data_tonic_history <- fmri3_pupil_data_tonic_history %>%
  pivot_longer(arousal_scaled_lag0:arousal_scaled_lag9,
               names_to = "lag", values_to = "arousal",
               names_prefix = "arousal_scaled_lag")


dftemp3 <- NULL

for (l in 0:9){
  l1<-summary(lmer(arousal ~ pupilDiameter_baseline_scaled + (1|subject)+ (1|probe) + (1|cue_size),
               fmri3_pupil_data_tonic_history %>% filter(lag == l)))
  l2<-summary(lmer(arousal ~ pupilDiameter_bc_scaled + (1|subject)+ (1|probe)+ (1|cue_size),
               fmri3_pupil_data_tonic_history %>% filter(lag == l)))
  l3<-summary(lmer(arousal ~ pupilDiameter_scaled + (1|subject)+ (1|probe)+ (1|cue_size),
               fmri3_pupil_data_tonic_history %>% filter(lag == l)))
  dftemp3 <- rbind(dftemp3,
                  rbind(l1$coefficients[2,],
                        l2$coefficients[2,],
                        l3$coefficients[2,]))
}
  
dftemp3 <- as.data.frame(dftemp3)
dftemp3$lag <- rep(0:9,each=3)
dftemp3$measure <- rep(c("tonic","corrected phasic","total evoked response"),10)
dftemp3 <- dftemp3  %>% 
  mutate(p_corrected = `Pr(>|t|)`*10,
         shape = ifelse(`Pr(>|t|)` < .05/10, 19, 1))  # numeric alpha

p3 <- ggplot(dftemp3%>% filter(measure != "total evoked response"), aes(x = lag, y = Estimate, color = measure,shape=shape)) +
  annotate("rect", xmin = -0.5, ymin = -0.1, xmax = 0.5, ymax = 0.4, alpha = 0.1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`),
                width = 0.1) +
  scale_x_continuous(breaks = 0:9) +
  labs(x = "arousal rating __ trials ago",
       y = "std. beta",
       title = "FMRI study") +
  theme(legend.position = "none") +
  scale_color_manual(values = c("red4", "steelblue")) +
  scale_shape_identity()+   # use alpha directly
  scale_x_reverse(breaks = 0:9)

p1+p3
```

### The version with residualized arousal rating
```{r}
# Step 1: Create lagged arousal columns
vrmid1_pupil_data_tonic_history <- vrmid1_pupil_data_tonic %>% 
  group_by(Subject) %>%
  mutate(map_dfc(0:4, function(k) {
    col <- lag(arousal_scaled, k)
    setNames(data.frame(col), paste0("arousal_scaled_lag", k))
  }))

# Step 2: Residualize each lag wrt closer lags (fixing NA alignment issue)
for (k in 0:4) {
  if (k == 0){
    vrmid1_pupil_data_tonic_history[[paste0("arousal_scaled_lag", k, "_resid")]] <- vrmid1_pupil_data_tonic_history$arousal_scaled_lag0
  } else {
    formula_str <- paste0("arousal_scaled_lag", k, " ~ ", 
                        paste0("arousal_scaled_lag", 0:(k-1), collapse = " + "))
  
  # Identify rows with complete data for this model
  rows_complete <- complete.cases(vrmid1_pupil_data_tonic_history[, paste0("arousal_scaled_lag", 0:k)])
  
  # Fit model only on those rows
  model <- lm(as.formula(formula_str),
              data = vrmid1_pupil_data_tonic_history[rows_complete, ])
  
  # Initialize full-length residual vector with NAs
  resid_full <- rep(NA, nrow(vrmid1_pupil_data_tonic_history))
  
  # Fill in residuals where model was estimated
  resid_full[rows_complete] <- resid(model)
  
  # Store residuals in data frame
  vrmid1_pupil_data_tonic_history[[paste0("arousal_scaled_lag", k, "_resid")]] <- resid_full
  }
}

# Step 3: Reshape to long format (for residualized variables)
vrmid1_pupil_data_tonic_history_long <- vrmid1_pupil_data_tonic_history %>%
  pivot_longer(cols = matches("arousal_scaled_lag[0-9]_resid"),
               names_to = "lag", values_to = "arousal_resid",
               names_pattern = "arousal_scaled_lag([0-9])_resid") %>%
  mutate(lag = as.numeric(lag))

# Step 4: Fit mixed models for each lag
dftemp1 <- NULL

for (l in 0:4){  # start at 1 because lag0 residual is undefined
  df_subset <- vrmid1_pupil_data_tonic_history_long %>% filter(lag == l)
  
  l1 <- summary(lmer(arousal_resid ~ pupil_Avg_baseline_scaled + (1|Subject) + (1|probe)
                     +(1|condition), df_subset))
  l2 <- summary(lmer(arousal_resid ~ pupil_Avg_bc_scaled + (1|Subject) + (1|probe)
                     +(1|condition), df_subset))
  l3 <- summary(lmer(arousal_resid ~ pupil_Avg_scaled + (1|Subject) + (1|probe)
                     +(1|condition), df_subset))
  
  dftemp1 <- rbind(
    dftemp1,
    rbind(l1$coefficients[2,],
          l2$coefficients[2,],
          l3$coefficients[2,])
  )
}

dftemp1 <- as.data.frame(dftemp1)
dftemp1$lag <- rep(0:4,each=3)
dftemp1$measure <- rep(c("tonic","corrected phasic","total evoked response"),5)
dftemp1 <- dftemp1  %>% 
  mutate(p_corrected = `Pr(>|t|)`*5,
         shape = ifelse(`Pr(>|t|)` < .05/5, 19, 1))  # numeric alpha

p1 <- ggplot(dftemp1 %>% filter(measure != "total evoked response"), aes(x = lag, y = Estimate, color = measure,shape = shape)) +
  annotate("rect", xmin = -0.5, ymin = -0.1, xmax = 0.5, ymax = 0.3, alpha = 0.1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`),
                width = 0.1) +
  labs(x = "arousal rating __ trials ago",
       y = "std. beta",
       title = "VR Study",
       color = NULL) +
  theme(legend.position = "top") +
  scale_color_manual(values = c("red4", "steelblue")) +
  scale_shape_identity()+
  guides(color = guide_legend(nrow = 2))+
  scale_x_reverse(breaks = 0:4)

fmri3_pupil_data_tonic_history <- fmri3_pupil_data_tonic %>% 
  group_by(subject) %>%
  mutate(map_dfc(0:4, function(k) {
    col <- lag(arousal_scaled, k)
    setNames(data.frame(col), paste0("arousal_scaled_lag", k))
  }))

for (k in 0:4) {
  if (k == 0){
    fmri3_pupil_data_tonic_history[[paste0("arousal_scaled_lag", k, "_resid")]] <- fmri3_pupil_data_tonic_history$arousal_scaled_lag0
  } else {
    formula_str <- paste0("arousal_scaled_lag", k, " ~ ", 
                        paste0("arousal_scaled_lag", 0:(k-1), collapse = " + "))
  
  # Identify rows with complete data for this model
  rows_complete <- complete.cases(fmri3_pupil_data_tonic_history[, paste0("arousal_scaled_lag", 0:k)])
  
  # Fit model only on those rows
  model <- lm(as.formula(formula_str),
              data = fmri3_pupil_data_tonic_history[rows_complete, ])
  
  # Initialize full-length residual vector with NAs
  resid_full <- rep(NA, nrow(fmri3_pupil_data_tonic_history))
  
  # Fill in residuals where model was estimated
  resid_full[rows_complete] <- resid(model)
  
  # Store residuals in data frame
  fmri3_pupil_data_tonic_history[[paste0("arousal_scaled_lag", k, "_resid")]] <- resid_full
  }
}

fmri3_pupil_data_tonic_history_long <- fmri3_pupil_data_tonic_history %>%
  pivot_longer(cols = matches("arousal_scaled_lag[0-9]_resid"),
               names_to = "lag", values_to = "arousal_resid",
               names_pattern = "arousal_scaled_lag([0-9])_resid") %>%
  mutate(lag = as.numeric(lag))

dftemp3 <- NULL

for (l in 0:4){  # start at 1 because lag0 residual is undefined
  df_subset <- fmri3_pupil_data_tonic_history_long %>% filter(lag == l)
  
  l1 <- summary(lmer(arousal_resid ~ pupilDiameter_baseline_scaled + (1|subject) + (1|probe)
                     +(1|cue_size), df_subset))
  l2 <- summary(lmer(arousal_resid ~ pupilDiameter_bc_scaled + (1|subject) + (1|probe)
                     +(1|cue_size), df_subset))
  l3 <- summary(lmer(arousal_resid ~ pupilDiameter_scaled + (1|subject) + (1|probe)
                     +(1|cue_size), df_subset))
  
  dftemp3 <- rbind(
    dftemp3,
    rbind(l1$coefficients[2,],
          l2$coefficients[2,],
          l3$coefficients[2,])
  )
}

dftemp3 <- as.data.frame(dftemp3)
dftemp3$lag <- rep(0:4,each=3)
dftemp3$measure <- rep(c("tonic","corrected phasic","total evoked response"),5)
dftemp3 <- dftemp3  %>% 
  mutate(p_corrected = `Pr(>|t|)`,
         shape = ifelse(`Pr(>|t|)` < .05, 19, 1))  # numeric alpha

p3 <- ggplot(dftemp3 %>% filter(measure != "total evoked response"), aes(x = lag, y = Estimate, color = measure,shape = shape)) +
  annotate("rect", xmin = -0.5, ymin = -0.1, xmax = 0.5, ymax = 0.3, alpha = 0.1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`),
                width = 0.1) +
  labs(x = "arousal rating __ trials ago",
       y = "std. beta",
       title = "FMRI Study",
       color = NULL) +
  theme(legend.position = "top") +
  scale_color_manual(values = c("red4", "steelblue")) +
  scale_shape_identity()+
  guides(color = guide_legend(nrow = 2))+
  scale_x_reverse(breaks = 0:4)
```

### The version with rolling mean
```{r}
vrmid1_pupil_data_tonic_history <- vrmid1_pupil_data_tonic %>% 
  group_by(Subject) %>%
  mutate(
    map_dfc(0:9, function(k) {
      mean_lag <- map_dbl(seq_len(n()), function(i) {
        if (i <= (k+1) - 1) {
          NA  # Not enough previous data points
        } else {
          mean(arousal_scaled[(i - (k+1) + 1):i], na.rm = TRUE)
        }
      })
      setNames(data.frame(mean_lag), paste0("arousal_scaled_lag", k))
    })
  )

vrmid1_pupil_data_tonic_history <- vrmid1_pupil_data_tonic_history %>%
  pivot_longer(arousal_scaled_lag0:arousal_scaled_lag9,
               names_to = "lag", values_to = "arousal",
               names_prefix = "arousal_scaled_lag")

dftemp1 <- NULL

for (l in 0:9){
  l1<-summary(lmer(arousal ~ pupil_Avg_baseline_scaled + (1|Subject) + (1|probe)
                   +(1|condition),
               vrmid1_pupil_data_tonic_history %>% filter(lag == l)))
  l2<-summary(lmer(arousal ~ pupil_Avg_bc_scaled + (1|Subject)+ (1|probe)
                   +(1|condition),
               vrmid1_pupil_data_tonic_history %>% filter(lag == l)))
  l3<-summary(lmer(arousal ~ pupil_Avg_scaled + (1|Subject)+ (1|probe)
                   +(1|condition),
               vrmid1_pupil_data_tonic_history %>% filter(lag == l)))
  dftemp1 <- rbind(dftemp1,
                  rbind(l1$coefficients[2,],
                        l2$coefficients[2,],
                        l3$coefficients[2,]))
}
  
dftemp1 <- as.data.frame(dftemp1)
dftemp1$lag <- rep(0:9,each=3)
dftemp1$measure <- rep(c("tonic","corrected phasic","total evoked response"),10)
dftemp1 <- dftemp1 %>% 
  mutate(p_corrected = `Pr(>|t|)`*10,
         shape = ifelse(`Pr(>|t|)` < .05/10, 19, 1))  # numeric alpha

p1 <- ggplot(dftemp1 %>% filter(measure != "total evoked response"), aes(x = lag, y = Estimate, color = measure,shape = shape)) +
  annotate("rect", xmin = -0.5, ymin = -0.1, xmax = 0.5, ymax = 0.3, alpha = 0.1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`),
                width = 0.1) +
  labs(x = "Rolling window size",
       y = "std. beta",
       title = "VR Study",
       color = NULL) +
  theme(legend.position = "top") +
  scale_color_manual(values = c("red4", "steelblue")) +
  scale_shape_identity()+
  guides(color = guide_legend(nrow = 2))+
  scale_x_reverse(breaks = 0:9)

fmri3_pupil_data_tonic_history <- fmri3_pupil_data_tonic %>% 
  group_by(subject) %>%
  mutate(
    map_dfc(0:9, function(k) {
      mean_lag <- map_dbl(seq_len(n()), function(i) {
        if (i <= (k+1) - 1) {
          NA  # Not enough previous data points
        } else {
          mean(arousal_scaled[(i - (k+1) + 1):i], na.rm = TRUE)
        }
      })
      setNames(data.frame(mean_lag), paste0("arousal_scaled_lag", k))
    })
  )

fmri3_pupil_data_tonic_history <- fmri3_pupil_data_tonic_history %>%
  pivot_longer(arousal_scaled_lag0:arousal_scaled_lag9,
               names_to = "lag", values_to = "arousal",
               names_prefix = "arousal_scaled_lag")


dftemp3 <- NULL

for (l in 0:9){
  l1<-summary(lmer(arousal ~ pupilDiameter_baseline_scaled + (1|subject)+ (1|probe)
                   +(1|cue_size),
               fmri3_pupil_data_tonic_history %>% filter(lag == l)))
  l2<-summary(lmer(arousal ~ pupilDiameter_bc_scaled + (1|subject)+ (1|probe)
                   +(1|cue_size),
               fmri3_pupil_data_tonic_history %>% filter(lag == l)))
  l3<-summary(lmer(arousal ~ pupilDiameter_scaled + (1|subject)+ (1|probe)
                   +(1|cue_size),
               fmri3_pupil_data_tonic_history %>% filter(lag == l)))
  dftemp3 <- rbind(dftemp3,
                  rbind(l1$coefficients[2,],
                        l2$coefficients[2,],
                        l3$coefficients[2,]))
}
  
dftemp3 <- as.data.frame(dftemp3)
dftemp3$lag <- rep(0:9,each=3)
dftemp3$measure <- rep(c("tonic","corrected phasic","total evoked response"),10)
dftemp3 <- dftemp3  %>% 
  mutate(p_corrected = `Pr(>|t|)`*10,
         shape = ifelse(`Pr(>|t|)` < .05/10, 19, 1))  # numeric alpha

p3 <- ggplot(dftemp3%>% filter(measure != "total evoked response"), aes(x = lag, y = Estimate, color = measure,shape=shape)) +
  annotate("rect", xmin = -0.5, ymin = -0.1, xmax = 0.5, ymax = 0.4, alpha = 0.1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`),
                width = 0.1) +
  labs(x = "Rolling window size",
       y = "std. beta",
       title = "FMRI study") +
  theme(legend.position = "none") +
  scale_color_manual(values = c("red4", "steelblue")) +
  scale_shape_identity()+   # use alpha directly
  scale_x_reverse(breaks = 0:9)

p1+p3+
  plot_layout(nrow = 1)
```



## do the reverse: were arousal related to previous tonic / phasic?

### the original version
```{r}
vrmid1_pupil_data_arousal_history <- vrmid1_pupil_data_tonic %>%
  group_by(Subject) %>%
  mutate(
    map_dfc(0:9, function(k) {
      col <- lag(pupil_Avg_baseline_scaled, k)
      setNames(data.frame(col), paste0("pupil_Avg_baseline_scaled_lag", k))
    }),
    map_dfc(0:9, function(k) {
      col <- lag(pupil_Avg_bc_scaled, k)
      setNames(data.frame(col), paste0("pupil_Avg_bc_scaled_lag", k))
    }),
    map_dfc(0:9, function(k) {
      col <- lag(pupil_Avg_scaled, k)
      setNames(data.frame(col), paste0("pupil_Avg_scaled_lag", k))
    }))

vrmid1_pupil_data_arousal_history <- vrmid1_pupil_data_arousal_history %>%
  pivot_longer(pupil_Avg_baseline_scaled_lag0:pupil_Avg_scaled_lag9,
               names_to = c("measure","lag"),names_pattern = "(.*)_lag(\\d+)", values_to = "pupil_size",
               names_prefix = "pupil_lag")

dftemp4 <- NULL

for (l in 0:9){
  l1<-summary(lmer(arousal_scaled ~ pupil_size + (1|Subject) + (1|probe) + (1|condition),
               vrmid1_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupil_Avg_baseline_scaled")))
  l2<-summary(lmer(arousal_scaled ~ pupil_size + (1|Subject) + (1|probe) + (1|condition),
               vrmid1_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupil_Avg_bc_scaled")))
  l3<-summary(lmer(arousal_scaled ~ pupil_size + (1|Subject) + (1|probe) + (1|condition),
               vrmid1_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupil_Avg_scaled")))
  dftemp4 <- rbind(dftemp4,
                  rbind(l1$coefficients[2,],
                        l2$coefficients[2,],
                        l3$coefficients[2,]))
}

dftemp4 <- as.data.frame(dftemp4)
dftemp4$lag <- rep(0:9,each=3)
dftemp4$measure <- rep(c("tonic","corrected phasic","total evoked response"),10)
dftemp4 <- dftemp4 %>%
  group_by(measure) %>% 
  mutate(p_corrected = p.adjust(`Pr(>|t|)`, method = "fdr")) %>%
  mutate(shape = ifelse(p_corrected < .05, 19, 1))

p4 <- ggplot(dftemp4%>% filter(measure != "total evoked response"), aes(x = lag, y = Estimate, color = measure,shape=shape)) +
  annotate("rect", xmin = -0.5, ymin = -0.1, xmax = 0.5, ymax = 0.4, alpha = 0.1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`),
                width = 0.1) +
  labs(x = "Pupil size __ trials ago",
       y = "std. beta",
       title = "VR Study") +
  theme(legend.position = "top") +
  scale_color_manual(values = c("red4", "steelblue")) +
  scale_shape_identity()+   # use alpha directly
  scale_x_reverse(breaks = 0:9)

p4

fmri3_pupil_data_arousal_history <- fmri3_pupil_data_tonic %>%
  group_by(subject)  %>%
  mutate(
    map_dfc(0:9, function(k) {
      col <- lag(pupilDiameter_baseline_scaled, k)
      setNames(data.frame(col), paste0("pupilDiameter_baseline_scaled_lag", k))
    }),
    map_dfc(0:9, function(k) {
      col <- lag(pupilDiameter_bc_scaled, k)
      setNames(data.frame(col), paste0("pupilDiameter_bc_scaled_lag", k))
    }),
    map_dfc(0:9, function(k) {
      col <- lag(pupilDiameter_scaled, k)
      setNames(data.frame(col), paste0("pupilDiameter_scaled_lag", k))
    }))


fmri3_pupil_data_arousal_history <- fmri3_pupil_data_arousal_history %>%
  pivot_longer(pupilDiameter_baseline_scaled_lag0:pupilDiameter_scaled_lag9,
               names_to = c("measure","lag"),names_pattern = "(.*)_lag(\\d+)", values_to = "pupil_size",
               names_prefix = "pupil_lag")

dftemp6 <- NULL

for (l in 0:9){
  l1<-summary(lmer(arousal_scaled ~ pupil_size + (1|subject) + (1|probe) + (1|cue_size),
               fmri3_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupilDiameter_baseline_scaled")))
  l2<-summary(lmer(arousal_scaled ~ pupil_size + (1|subject) + (1|probe)+ (1|cue_size),
               fmri3_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupilDiameter_bc_scaled")))
  l3<-summary(lmer(arousal_scaled ~ pupil_size + (1|subject) + (1|probe)+ (1|cue_size),
               fmri3_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupilDiameter_scaled")))
  dftemp6 <- rbind(dftemp6,
                  rbind(l1$coefficients[2,],
                        l2$coefficients[2,],
                        l3$coefficients[2,]))
}

dftemp6 <- as.data.frame(dftemp6)
dftemp6$lag <- rep(0:9,each=3)
dftemp6$measure <- rep(c("tonic","corrected phasic","total evoked response"),10)
dftemp6 <- dftemp6  %>%
  group_by(measure) %>% 
  mutate(p_corrected = p.adjust(`Pr(>|t|)`, method = "fdr")) %>%
  mutate(shape = ifelse(p_corrected < .05, 19, 1))

p6 <- ggplot(dftemp6%>% filter(measure != "total evoked response"), aes(x = lag, y = Estimate, color = measure,shape=shape)) +
  annotate("rect", xmin = -0.5, ymin = -0.1, xmax = 0.5, ymax = 0.4, alpha = 0.1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`),
                width = 0.1) +
  labs(x = "Pupil size __ trials ago",
       y = "std. beta",
       title = "FMRI Study") +
  theme(legend.position = "none") +
  scale_color_manual(values = c("red4", "steelblue")) +
  scale_shape_identity()+   # use alpha directly
  scale_x_reverse(breaks = 0:9)

p4+p6
```

### the version with residualized pupil size
```{r}
vrmid1_pupil_data_arousal_history <- vrmid1_pupil_data_tonic %>%
  group_by(Subject) %>%
  mutate(
    map_dfc(0:9, function(k) {
      col <- lag(pupil_Avg_baseline_scaled, k)
      setNames(data.frame(col), paste0("pupil_Avg_baseline_scaled_lag", k))
    }),
    map_dfc(0:9, function(k) {
      col <- lag(pupil_Avg_bc_scaled, k)
      setNames(data.frame(col), paste0("pupil_Avg_bc_scaled_lag", k))
    }),
    map_dfc(0:9, function(k) {
      col <- lag(pupil_Avg_scaled, k)
      setNames(data.frame(col), paste0("pupil_Avg_scaled_lag", k))
    }))

# Step 2: Residualize each lag wrt closer lags (fixing NA alignment issue)
# Step 2: Residualize each pupil variable's lags wrt closer lags (fixing NA alignment issue)

for (var in c("pupil_Avg_baseline_scaled", "pupil_Avg_bc_scaled", "pupil_Avg_scaled")) {
  for (k in 0:9) {
    if (k == 0) {
      vrmid1_pupil_data_arousal_history[[paste0(var, "_lag", k, "_resid")]] <- 
        vrmid1_pupil_data_arousal_history[[paste0(var, "_lag0")]]
    } else {
      formula_str <- paste0(var, "_lag", k, " ~ ", 
                            paste0(var, "_lag", 0:(k-1), collapse = " + "))
      
      # Identify rows with complete data for this model
      rows_complete <- complete.cases(vrmid1_pupil_data_arousal_history[, paste0(var, "_lag", 0:k)])
      
      # Fit model only on those rows
      model <- lm(as.formula(formula_str),
                  data = vrmid1_pupil_data_arousal_history[rows_complete, ])
      
      # Initialize full-length residual vector with NAs
      resid_full <- rep(NA, nrow(vrmid1_pupil_data_arousal_history))
      
      # Fill in residuals where model was estimated
      resid_full[rows_complete] <- resid(model)
      
      # Store residuals in data frame
      vrmid1_pupil_data_arousal_history[[paste0(var, "_lag", k, "_resid")]] <- resid_full
    }
  }
}

vrmid1_pupil_data_arousal_history <- vrmid1_pupil_data_arousal_history %>%
  pivot_longer(pupil_Avg_baseline_scaled_lag0_resid:pupil_Avg_scaled_lag9_resid,
               names_to = c("measure","lag"),names_pattern = "(.*)_lag(\\d+)", values_to = "pupil_size",
               names_prefix = "pupil_lag")

dftemp4 <- NULL

for (l in 0:9){
  l1<-summary(lmer(arousal_scaled ~ pupil_size + (1|Subject) + (1|probe) + (1|condition),
               vrmid1_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupil_Avg_baseline_scaled")))
  l2<-summary(lmer(arousal_scaled ~ pupil_size + (1|Subject) + (1|probe) + (1|condition),
               vrmid1_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupil_Avg_bc_scaled")))
  l3<-summary(lmer(arousal_scaled ~ pupil_size + (1|Subject) + (1|probe) + (1|condition),
               vrmid1_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupil_Avg_scaled")))
  dftemp4 <- rbind(dftemp4,
                  rbind(l1$coefficients[2,],
                        l2$coefficients[2,],
                        l3$coefficients[2,]))
}

dftemp4 <- as.data.frame(dftemp4)
dftemp4$lag <- rep(0:9,each=3)
dftemp4$measure <- rep(c("tonic","corrected phasic","total evoked response"),10)
dftemp4 <- dftemp4 %>%
  group_by(measure) %>% 
  mutate(p_corrected = p.adjust(`Pr(>|t|)`, method = "fdr")) %>%
  mutate(shape = ifelse(p_corrected < .05, 19, 1))

p4 <- ggplot(dftemp4%>% filter(measure != "total evoked response"), aes(x = lag, y = Estimate, color = measure,shape=shape)) +
  annotate("rect", xmin = -0.5, ymin = -0.1, xmax = 0.5, ymax = 0.4, alpha = 0.1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`),
                width = 0.1) +
  labs(x = "Pupil size __ trials ago",
       y = "std. beta",
       title = "VR Study") +
  theme(legend.position = "none") +
  scale_color_manual(values = c("red4", "steelblue")) +
  scale_shape_identity()+   # use alpha directly
  scale_x_reverse(breaks = 0:9)

p4

fmri3_pupil_data_arousal_history <- fmri3_pupil_data_tonic %>%
  group_by(subject)  %>%
  mutate(
    map_dfc(0:9, function(k) {
      col <- lag(pupilDiameter_baseline_scaled, k)
      setNames(data.frame(col), paste0("pupilDiameter_baseline_scaled_lag", k))
    }),
    map_dfc(0:9, function(k) {
      col <- lag(pupilDiameter_bc_scaled, k)
      setNames(data.frame(col), paste0("pupilDiameter_bc_scaled_lag", k))
    }),
    map_dfc(0:9, function(k) {
      col <- lag(pupilDiameter_scaled, k)
      setNames(data.frame(col), paste0("pupilDiameter_scaled_lag", k))
    }))

for (var in c("pupilDiameter_baseline_scaled", "pupilDiameter_bc_scaled", "pupilDiameter_scaled")) {
  for (k in 0:9) {
    if (k == 0) {
      fmri3_pupil_data_arousal_history[[paste0(var, "_lag", k, "_resid")]] <- 
        fmri3_pupil_data_arousal_history[[paste0(var, "_lag0")]]
    } else {
      formula_str <- paste0(var, "_lag", k, " ~ ", 
                            paste0(var, "_lag", 0:(k-1), collapse = " + "))
      
      # Identify rows with complete data for this model
      rows_complete <- complete.cases(fmri3_pupil_data_arousal_history[, paste0(var, "_lag", 0:k)])
      
      # Fit model only on those rows
      model <- lm(as.formula(formula_str),
                  data = fmri3_pupil_data_arousal_history[rows_complete, ])
      
      # Initialize full-length residual vector with NAs
      resid_full <- rep(NA, nrow(fmri3_pupil_data_arousal_history))
      
      # Fill in residuals where model was estimated
      resid_full[rows_complete] <- resid(model)
      
      # Store residuals in data frame
      fmri3_pupil_data_arousal_history[[paste0(var, "_lag", k, "_resid")]] <- resid_full
    }
  }
}

fmri3_pupil_data_arousal_history <- fmri3_pupil_data_arousal_history %>%
  pivot_longer(pupilDiameter_baseline_scaled_lag0_resid:pupilDiameter_scaled_lag9_resid,
               names_to = c("measure","lag"),names_pattern = "(.*)_lag(\\d+)", values_to = "pupil_size",
               names_prefix = "pupil_lag")

dftemp6 <- NULL

for (l in 0:9){
  l1<-summary(lmer(arousal_scaled ~ pupil_size + (1|subject) + (1|probe)+(1|cue_size),
               fmri3_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupilDiameter_baseline_scaled")))
  l2<-summary(lmer(arousal_scaled ~ pupil_size + (1|subject) + (1|probe)+(1|cue_size),
               fmri3_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupilDiameter_bc_scaled")))
  l3<-summary(lmer(arousal_scaled ~ pupil_size + (1|subject) + (1|probe)+(1|cue_size),
               fmri3_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupilDiameter_scaled")))
  dftemp6 <- rbind(dftemp6,
                  rbind(l1$coefficients[2,],
                        l2$coefficients[2,],
                        l3$coefficients[2,]))
}

dftemp6 <- as.data.frame(dftemp6)
dftemp6$lag <- rep(0:9,each=3)
dftemp6$measure <- rep(c("tonic","corrected phasic","total evoked response"),10)
dftemp6 <- dftemp6  %>%
  group_by(measure) %>% 
  mutate(p_corrected = p.adjust(`Pr(>|t|)`, method = "fdr")) %>%
  mutate(shape = ifelse(p_corrected < .05, 19, 1))

p6 <- ggplot(dftemp6%>% filter(measure != "total evoked response"), aes(x = lag, y = Estimate, color = measure,shape=shape)) +
  annotate("rect", xmin = -0.5, ymin = -0.1, xmax = 0.5, ymax = 0.4, alpha = 0.1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`),
                width = 0.1) +
  labs(x = "Pupil size __ trials ago",
       y = "std. beta",
       title = "FMRI Study") +
  theme(legend.position = "none") +
  scale_color_manual(values = c("red4", "steelblue")) +
  scale_shape_identity()+   # use alpha directly
  scale_x_reverse(breaks = 0:9)

p4+p6
```

### the rolling mean version of arousal ~pupil
```{r}
vrmid1_pupil_data_arousal_history <- vrmid1_pupil_data_tonic %>%
  group_by(Subject) %>%
  mutate(
    map_dfc(0:9, function(k) {
      mean_lag <- map_dbl(seq_len(n()), function(i) {
        if (i <= (k+1) - 1) {
          NA  # Not enough previous data points
        } else {
          mean(pupil_Avg_baseline_scaled[(i - (k+1) + 1):i], na.rm = TRUE)
        }})
      setNames(data.frame(mean_lag), paste0("pupil_Avg_baseline_scaled_lag", k))
    }),
    map_dfc(0:9, function(k) {
      mean_lag <- map_dbl(seq_len(n()), function(i) {
        if (i <= (k+1) - 1) {
          NA  # Not enough previous data points
        } else {
          mean(pupil_Avg_bc_scaled[(i - (k+1) + 1):i], na.rm = TRUE)
        }})
      setNames(data.frame(mean_lag), paste0("pupil_Avg_bc_scaled_lag", k))
    }),
    map_dfc(0:9, function(k) {
      mean_lag <- map_dbl(seq_len(n()), function(i) {
        if (i <= (k+1) - 1) {
          NA  # Not enough previous data points
        } else {
          mean(pupil_Avg_scaled[(i - (k+1) + 1):i], na.rm = TRUE)
        }})
      setNames(data.frame(mean_lag), paste0("pupil_Avg_scaled_lag", k))
    }))

vrmid1_pupil_data_arousal_history <- vrmid1_pupil_data_arousal_history %>%
  pivot_longer(pupil_Avg_baseline_scaled_lag0:pupil_Avg_scaled_lag9,
               names_to = c("measure","lag"),names_pattern = "(.*)_lag(\\d+)", values_to = "pupil_size",
               names_prefix = "pupil_lag")

dftemp4 <- NULL

for (l in 0:9){
  l1<-summary(lmer(arousal_scaled ~ pupil_size + (1|Subject) + (1|probe)+(1|condition),
               vrmid1_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupil_Avg_baseline_scaled")))
  l2<-summary(lmer(arousal_scaled ~ pupil_size + (1|Subject) + (1|probe)+(1|condition),
               vrmid1_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupil_Avg_bc_scaled")))
  l3<-summary(lmer(arousal_scaled ~ pupil_size + (1|Subject) + (1|probe)+(1|condition),
               vrmid1_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupil_Avg_scaled")))
  dftemp4 <- rbind(dftemp4,
                  rbind(l1$coefficients[2,],
                        l2$coefficients[2,],
                        l3$coefficients[2,]))
}

dftemp4 <- as.data.frame(dftemp4)
dftemp4$lag <- rep(0:9,each=3)
dftemp4$measure <- rep(c("tonic","corrected phasic","total evoked response"),10)
dftemp4 <- dftemp4 %>%
  group_by(measure) %>% 
  mutate(p_corrected = p.adjust(`Pr(>|t|)`, method = "fdr")) %>%
  mutate(shape = ifelse(p_corrected < .05, 19, 1))

p4 <- ggplot(dftemp4%>% filter(measure != "total evoked response"), aes(x = lag, y = Estimate, color = measure,shape=shape)) +
  annotate("rect", xmin = -0.5, ymin = -0.1, xmax = 0.5, ymax = 0.4, alpha = 0.1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`),
                width = 0.1) +
  labs(x = "Rolling window size",
       y = "std. beta",
       title = "VR Study") +
  theme(legend.position = "none") +
  scale_color_manual(values = c("red4", "steelblue")) +
  scale_shape_identity()+   # use alpha directly
  scale_x_reverse(breaks = 0:9, labels = 1:10)

fmri3_pupil_data_arousal_history <- fmri3_pupil_data_tonic %>%
  group_by(subject) %>%
  mutate(
    map_dfc(0:9, function(k) {
      mean_lag <- map_dbl(seq_len(n()), function(i) {
        if (i <= (k+1) - 1) {
          NA  # Not enough previous data points
        } else {
          mean(pupilDiameter_baseline_scaled[(i - (k+1) + 1):i], na.rm = TRUE)
        }})
      setNames(data.frame(mean_lag), paste0("pupilDiameter_baseline_scaled_lag", k))
    }),
    map_dfc(0:9, function(k) {
      mean_lag <- map_dbl(seq_len(n()), function(i) {
        if (i <= (k+1) - 1) {
          NA  # Not enough previous data points
        } else {
          mean(pupilDiameter_bc_scaled[(i - (k+1) + 1):i], na.rm = TRUE)
        }})
      setNames(data.frame(mean_lag), paste0("pupilDiameter_bc_scaled_lag", k))
    }),
    map_dfc(0:9, function(k) {
      mean_lag <- map_dbl(seq_len(n()), function(i) {
        if (i <= (k+1) - 1) {
          NA  # Not enough previous data points
        } else {
          mean(pupilDiameter_scaled[(i - (k+1) + 1):i], na.rm = TRUE)
        }})
      setNames(data.frame(mean_lag), paste0("pupilDiameter_scaled_lag", k))
    }))


fmri3_pupil_data_arousal_history <- fmri3_pupil_data_arousal_history %>%
  pivot_longer(pupilDiameter_baseline_scaled_lag0:pupilDiameter_scaled_lag9,
               names_to = c("measure","lag"),names_pattern = "(.*)_lag(\\d+)", values_to = "pupil_size",
               names_prefix = "pupil_lag")

dftemp6 <- NULL

for (l in 0:9){
  l1<-summary(lmer(arousal_scaled ~ pupil_size + (1|subject) + (1|probe)+(1|cue_size),
               fmri3_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupilDiameter_baseline_scaled")))
  l2<-summary(lmer(arousal_scaled ~ pupil_size + (1|subject) + (1|probe)+(1|cue_size),
               fmri3_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupilDiameter_bc_scaled")))
  l3<-summary(lmer(arousal_scaled ~ pupil_size + (1|subject) + (1|probe)+(1|cue_size),
               fmri3_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupilDiameter_scaled")))
  dftemp6 <- rbind(dftemp6,
                  rbind(l1$coefficients[2,],
                        l2$coefficients[2,],
                        l3$coefficients[2,]))
}

dftemp6 <- as.data.frame(dftemp6)
dftemp6$lag <- rep(0:9,each=3)
dftemp6$measure <- rep(c("tonic","corrected phasic","total evoked response"),10)
dftemp6 <- dftemp6  %>%
  group_by(measure) %>% 
  mutate(p_corrected = p.adjust(`Pr(>|t|)`, method = "fdr")) %>%
  mutate(shape = ifelse(p_corrected < .05, 19, 1))

p6 <- ggplot(dftemp6%>% filter(measure != "total evoked response"), aes(x = lag, y = Estimate, color = measure,shape=shape)) +
  annotate("rect", xmin = -0.5, ymin = -0.1, xmax = 0.5, ymax = 0.4, alpha = 0.1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`),
                width = 0.1) +
  labs(x = "Rolling window size",
       y = "std. beta",
       title = "FMRI Study") +
  theme(legend.position = "none") +
  scale_color_manual(values = c("red4", "steelblue")) +
  scale_shape_identity()+   # use alpha directly
  scale_x_reverse(breaks = 0:9, labels = 1:10)

p4+p6
```


## rt / hit rate should be predicted by arousal and pupil dilation
```{r}
vrmid1_data_rt <- vrmid1_pupil_data%>%
  filter(sample_in_trial_t <= vrmid1_ant_window[2] & sample_in_trial_t > vrmid1_ant_window[1]) %>% 
  group_by(probe,Subject,trial,reaction_outcome,trial_type,PosA_scaled,NegA_scaled,
           arousal,valence,last_ITI,
           arousal_scaled,valence_scaled,
           condition,reaction_time)%>%
  summarise(mean_pupil_bc = mean(pupil_Avg_bc_scaled, na.rm = T),
            mean_pupil_nobc = mean(pupil_Avg_scaled, na.rm = T),
            mean_pupil_baseline = mean(pupil_Avg_baseline_scaled, na.rm = T))%>%
  filter(abs(mean_pupil_bc) < 4,
         abs(mean_pupil_nobc) < 4,
         abs(mean_pupil_baseline) < 4)  %>% 
  group_by(Subject)%>%
  mutate(log_rt = log(reaction_time),
         log_rt = as.numeric(scale(log_rt)),
         hit = ifelse(reaction_outcome == "Hit",1,0)) 

fmri3_data_rt <- fmri3_pupil_data%>%
  filter(sample_in_trial_t <= fmri3_ant_window[2] & sample_in_trial_t > fmri3_ant_window[1]) %>% 
  group_by(probe,subject,trial,hit,cue_value,
           arousal,valence,last_iti,
           arousal_scaled,valence_scaled,
           cue_size,rt)%>%
  summarise(mean_pupil_bc = mean(pupilDiameter_bc_scaled, na.rm = T),
            mean_pupil_nobc = mean(pupilDiameter_scaled, na.rm = T),
            mean_pupil_baseline = mean(pupilDiameter_baseline_scaled, na.rm = T))%>%
  filter(abs(mean_pupil_bc) < 4,
         abs(mean_pupil_nobc) < 4,
         abs(mean_pupil_baseline) < 4)  %>% 
  group_by(subject)%>%
  mutate(log_rt = log(rt),
         log_rt = as.numeric(scale(log_rt)),
         hit_bin = ifelse(hit == "Hit",1,0)) 
```

### hit
```{r}
hit_reg_coef <- as.data.frame(
  Reduce(rbind,list(
  summary(glmer(hit ~ scale(mean_pupil_bc) + scale(mean_pupil_baseline)+ (1|probe)+ (1|Subject),
                family = "binomial",
                vrmid1_data_rt))$coefficients,
summary(glmer(hit ~  scale(arousal_scaled) + (1|Subject),
               family = "binomial",
              vrmid1_data_rt %>% filter(probe == "anti")))$coefficients,

summary(glmer(hit_bin ~ scale(mean_pupil_bc) + scale(mean_pupil_baseline)  + (1|probe) + (1|subject),
               family = "binomial",
              fmri3_data_rt))$coefficients,
summary(glmer(hit_bin ~ scale(arousal_scaled) + (1|subject),
              family = "binomial",
              fmri3_data_rt %>% filter(probe == 1)))$coefficients))
) %>% 
  rownames_to_column() %>% 
  filter(!grepl("Intercept",rowname))

hit_reg_coef$study <- c("VRstudy","VRstudy","VRstudy","FMRIstudy","FMRIstudy","FMRIstudy")
hit_reg_coef$predictor <- rep(c("phasic_pupil","tonic_pupil","arousal"),2)

hit_reg_coef<-hit_reg_coef %>% 
  mutate(sig = ifelse(`Pr(>|z|)` >= .05, "n.s.",
                      ifelse(`Pr(>|z|)` >= .01, "*",
                             ifelse(`Pr(>|z|)` >= .005,"**","***"))))

hit_reg_coef$predictor <- factor(hit_reg_coef$predictor, levels = c("phasic_pupil","tonic_pupil","arousal"),
                                labels = c("corrected phasic pupil","tonic pupil","subjective arousal"))
hit_reg_coef$study <- factor(hit_reg_coef$study, levels = c("VRstudy","FMRIstudy"),
                                labels = c("VR study","FMRI study"))
pp1<-ggplot(hit_reg_coef %>% filter(predictor != "subjective arousal"), aes(x = study, y = Estimate,
                        color = study))+
  geom_hline(yintercept = 0, linetype = "dashed")+
  geom_text(aes(x = study, y = Estimate+0.1,
                        color = study, label = sig))+
  geom_errorbar(aes(x = study, y = Estimate,ymin = Estimate-`Std. Error`,
                    ymax = Estimate+`Std. Error`,
                        color = study), width = 0.1)+
  geom_point(size = 3, shape = 5)+
  theme_bw()+
  facet_wrap(~predictor)+
  scale_color_brewer(palette = "Dark2")+
  theme(legend.position = "none",
        panel.grid = element_blank())+
  labs(y = "std. beta",
       x = "",
       title = "hit rate ~ tonic + phasic")
```

### rt
```{r}
rt_reg_coef <- as.data.frame(
  Reduce(rbind,list(
  summary(lmer(scale(log_rt) ~ scale(mean_pupil_bc) + scale(mean_pupil_baseline)+ (1|probe)+ (1|Subject),vrmid1_data_rt %>% filter(hit == 1)))$coefficients,
summary(lmer(scale(log_rt) ~ scale(arousal_scaled) + (1|Subject),vrmid1_data_rt %>% filter(hit == 1, probe == "anti")))$coefficients,

summary(lmer(scale(log_rt) ~ scale(mean_pupil_bc) + scale(mean_pupil_baseline)  + (1|probe) + (1|subject),fmri3_data_rt%>% filter(hit == "Hit")))$coefficients,
summary(lmer(scale(log_rt) ~ scale(arousal_scaled) + (1|subject),fmri3_data_rt %>% filter(hit == "Hit", probe == 1)))$coefficients))
) %>% 
  rownames_to_column() %>% 
  filter(!grepl("Intercept",rowname))

rt_reg_coef$study <- c("VRstudy","VRstudy","VRstudy","FMRIstudy","FMRIstudy","FMRIstudy")
rt_reg_coef$predictor <- rep(c("phasic_pupil","tonic_pupil","arousal"),2)

rt_reg_coef<-rt_reg_coef %>% 
  mutate(sig = ifelse(`Pr(>|t|)` >= .05, "n.s.",
                      ifelse(`Pr(>|t|)` >= .01, "*",
                             ifelse(`Pr(>|t|)` >= .005,"**","***"))))

rt_reg_coef$predictor <- factor(rt_reg_coef$predictor, levels = c("phasic_pupil","tonic_pupil","arousal"),
                                labels = c("corrected phasic pupil","tonic pupil","subjective arousal"))
rt_reg_coef$study <- factor(rt_reg_coef$study, levels = c("VRstudy","FMRIstudy"),
                                labels = c("VR study","FMRI study"))
pp2<-ggplot(rt_reg_coef %>% filter(predictor != "subjective arousal"), aes(x = study, y = Estimate,
                        color = study))+
  geom_hline(yintercept = 0, linetype = "dashed")+
  geom_text(aes(x = study, y = Estimate+0.05,
                        color = study, label = sig))+
  geom_errorbar(aes(x = study, y = Estimate,ymin = Estimate-`Std. Error`,
                    ymax = Estimate+`Std. Error`,
                        color = study), width = 0.1)+
  geom_point(size = 3, shape = 5)+
  theme_bw()+
  facet_wrap(~predictor)+
  scale_color_brewer(palette = "Dark2")+
  theme(legend.position = "none",
        panel.grid = element_blank())+
  labs(y = "std. beta",
       x = "",
       title = "rt ~ tonic + phasic")
pp1+pp2
save_figure("s6_pupil_rt_correlation", dpi = 300, height = 3, width = 8)
```


### get autocorrelation of phasic, tonic and arousal
```{r}
acf_results_vrmid1 <- vrmid1_pupil_data_tonic %>%
  group_by(Subject) %>% 
  summarise(across(
    c(arousal_scaled, valence_scaled, pupil_Avg_baseline_scaled,
      pupil_Avg_bc_scaled, pupil_Avg_scaled),
    ~ acf(na.omit(.x), plot = FALSE)$acf[2],
    .names = "{.col}"
  )) %>% 
  pivot_longer(arousal_scaled:pupil_Avg_scaled, names_to = "variable",values_to = "AR")

acf_results_vrmid1$variable <- factor(acf_results_vrmid1$variable,
                                     levels = c("arousal_scaled","valence_scaled",
                                                "pupil_Avg_baseline_scaled",
                                                "pupil_Avg_bc_scaled","pupil_Avg_scaled"),
                                     labels = c("arousal","valence","tonic","corrected phasic",
                                                "total evoked response"))

t.test(acf_results_vrmid1$AR[acf_results_vrmid1$variable == "corrected phasic"])
t.test(acf_results_vrmid1$AR[acf_results_vrmid1$variable == "tonic"],
       acf_results_vrmid1$AR[acf_results_vrmid1$variable == "corrected phasic"],paired = T)

lar1 <- lmer(AR~variable + (1|Subject),acf_results_vrmid1)
cld_results <- multcomp::cld(emmeans(lar1, ~ variable), Letters = letters, adjust = "tukey")

cld_df <- as.data.frame(cld_results)

par1<-ggplot() +
  geom_violin(data=acf_results_vrmid1, aes(x = variable, y = AR),
              fill = "gray40", color = NA, width = 0.8) +
  # individual data points
  geom_jitter(data=acf_results_vrmid1, aes(x = variable, y = AR),
              width = 0.15, size = 0.4,color = "black") +
  # mean and CI
  geom_point(data=cld_df,aes(x = variable, y = emmean),
             size = 1,color = "#2E86AB") +
  geom_errorbar(data=cld_df,aes(x = variable, ymin = emmean - SE, ymax = emmean + SE),  color = "#2E86AB", linewidth = 0.8,width = 0.2) +
  labs(
    x = NULL,
    y = "Autocorrelation (lag 1)",
    subtitle = "VR Study")+
  ylim(-0.5,1)+
  coord_flip()+
  # add semi-transparent white squares behind "valence" and "total evoked response"
  annotate("rect",
           xmin = 1.5, xmax = 2.5,  # for "valence"
           ymin = -Inf, ymax = Inf,
           fill = "white", alpha = 0.6) +
  annotate("rect",
           xmin = 4.5, xmax = 5.5,  # for "total evoked response"
           ymin = -Inf, ymax = Inf,
           fill = "white", alpha = 0.6)+
  annotate("rect",
           xmin = 0.5, xmax = 1.5,  # for "arousal"
           ymin = -Inf, ymax = Inf,
           fill = "white", alpha = 0.6)+
  geom_hline(yintercept = 0)+
    geom_text(data=cld_df,aes(x = variable, label = .group, y = 0.9), vjust=0.5) 


acf_results_fmri3 <- fmri3_pupil_data_tonic %>%
  group_by(subject) %>% 
  summarise(across(
    c(arousal_scaled, valence_scaled, pupilDiameter_baseline_scaled,
      pupilDiameter_bc_scaled, pupilDiameter_scaled),
    ~ acf(na.omit(.x), plot = FALSE)$acf[2],
    .names = "{.col}"
  )) %>% 
  pivot_longer(arousal_scaled:pupilDiameter_scaled, names_to = "variable",values_to = "AR")

acf_results_fmri3$variable <- factor(acf_results_fmri3$variable,
                                     levels = c("arousal_scaled","valence_scaled",
                                                "pupilDiameter_baseline_scaled",
                                                "pupilDiameter_bc_scaled","pupilDiameter_scaled"),
                                     labels = c("arousal","valence","tonic","corrected phasic",
                                                "total evoked response"))

t.test(acf_results_fmri3$AR[acf_results_fmri3$variable == "corrected phasic"])
t.test(acf_results_fmri3$AR[acf_results_fmri3$variable == "tonic"],
       acf_results_fmri3$AR[acf_results_fmri3$variable == "corrected phasic"],paired = T)

lar3 <- lmer(AR~variable + (1|subject),acf_results_fmri3)
cld_results <- multcomp::cld(emmeans(lar3, ~ variable), Letters = letters, adjust = "tukey")

cld_df <- as.data.frame(cld_results)

par3<-ggplot() +
  geom_violin(data=acf_results_fmri3, aes(x = variable, y = AR),
              fill = "gray40", color = NA, width = 0.8) +
  # individual data points
  geom_jitter(data=acf_results_fmri3, aes(x = variable, y = AR),
              width = 0.15, size = 0.4,color = "black") +
  # mean and CI
  geom_point(data=cld_df,aes(x = variable, y = emmean),
             size = 1,color = "#2E86AB") +
  geom_errorbar(data=cld_df,aes(x = variable, ymin = emmean - SE, ymax = emmean + SE),  color = "#2E86AB", linewidth = 0.8,width = 0.2) +
  labs(
    x = NULL,
    y = "Autocorrelation (lag 1)",
    subtitle = "FMRI Study")+
  ylim(-0.5,1)+
  coord_flip()+
  # add semi-transparent white squares behind "valence" and "total evoked response"
  annotate("rect",
           xmin = 1.5, xmax = 2.5,  # for "valence"
           ymin = -Inf, ymax = Inf,
           fill = "white", alpha = 0.6) +
  annotate("rect",
           xmin = 4.5, xmax = 5.5,  # for "total evoked response"
           ymin = -Inf, ymax = Inf,
           fill = "white", alpha = 0.6)+
  annotate("rect",
           xmin = 0.5, xmax = 1.5,  # for "arousal"
           ymin = -Inf, ymax = Inf,
           fill = "white", alpha = 0.6)+
  geom_hline(yintercept = 0)+
    geom_text(data=cld_df,aes(x = variable, label = .group, y = 0.9), vjust=0.5) 

par1+par3

save_figure("s6_arousal_rating_correlation", dpi = 300, height = 3, width = 9)
```

```{r}
(pt12|pt32|pt11|pt31)/
(par1+par3)
  # plot_annotation(tag_levels = "a")

save_figure("s6_tonic_phasic_behavior", dpi = 300, height = 6, width = 12)

fig5 <- image_read(mid_pupil_figure_path("s6_tonic_phasic_behavior", "png"))
fig5 <- image_annotate(fig5, "A", size = 55, location = "+250+00", color = "black", gravity = "northwest")
fig5 <- image_annotate(fig5, "B", size = 55, location = "+2000+00", color = "black", gravity = "northwest")
fig5 <- image_annotate(fig5, "C", size = 55, location = "+250+950", color = "black", gravity = "northwest")
# fig5 <- image_annotate(fig5, "D", size = 55, location = "+1600+950", color = "black", gravity = "northwest")
save_figure_image("s6_tonic_phasic_behavior", fig5)
magick::image_write(fig5, mid_pupil_figure_path("s6_tonic_phasic_behavior", "jpeg"))
```

```{r}
pp<-ggplot(hit_reg_coef %>% filter(predictor == "subjective arousal"), aes(x = study, y = Estimate,
                        color = study))+
  geom_hline(yintercept = 0, linetype = "dashed")+
  geom_text(aes(x = study, y = Estimate+`Std. Error`+0.01,
                        color = study, label = sig))+
  geom_errorbar(aes(x = study, y = Estimate,ymin = Estimate-`Std. Error`,
                    ymax = Estimate+`Std. Error`,
                        color = study), width = 0.1)+
  geom_point(size = 3, shape = 5)+
  theme_bw()+
  facet_wrap(~predictor)+
  scale_color_brewer(palette = "Dark2")+
  theme(legend.position = "none",
        panel.grid = element_blank())+
  labs(y = "std. beta",
       x = "",
       title = "hit ~ arousal")+
ggplot(rt_reg_coef %>% filter(predictor == "subjective arousal"), aes(x = study, y = Estimate,
                        color = study))+
  geom_hline(yintercept = 0, linetype = "dashed")+
  geom_text(aes(x = study, y = Estimate+`Std. Error`+0.01,
                        color = study, label = sig))+
  geom_errorbar(aes(x = study, y = Estimate,ymin = Estimate-`Std. Error`,
                    ymax = Estimate+`Std. Error`,
                        color = study), width = 0.1)+
  geom_point(size = 3, shape = 5)+
  theme_bw()+
  facet_wrap(~predictor)+
  scale_color_brewer(palette = "Dark2")+
  theme(legend.position = "none",
        panel.grid = element_blank())+
  labs(y = "std. beta",
       x = "",
       title = "rt ~ arousal")

(pt13+pt33)/(pt15+pt35)/pp+
  plot_layout(nrow = 3)+
  plot_annotation(title = "Self-reported arousal",
                  tag_levels = "A")


save_figure("s6_tonic_phasic_behavior_by_study", dpi = 300, height = 9, width = 5)
```

