---
title: "analyses_for_natalie_thesis"
output: html_document
date: "2024-10-21"
---

This code compares the FMRI Study 1 and a separate sample (here we call FMRI validation).
## define the time windows of interest
```{r}
fmri4_ant_window = c(2,4)+1.5
fmri4_antprobe_out_window = c(16,18)+1.5
fmri4_outprobe_out_window = c(6,8)+1.5
```

# read in pupil data

## fmri4
```{r}
fmri4_pupil_data <- read_csv("~/Desktop/midaffemo2/analyses/pupil/derivatives/pupillometry_baselineCorrected.csv") %>% 
  mutate(cue_value = factor(trialtype, levels = 1:6, labels = c("-$0","-$1","-$5","+$0","+$1","+$5"))) %>% 
  filter(!is.na(subject)) %>% 
  ungroup()

fmri4_bad_participants <- read_delim("~/Desktop/midaffemo2/analyses/pupil/subject_to_drop_pupil.txt", col_names = F, delim = " ")

fmri4_pupil_data <- fmri4_pupil_data %>% 
  filter(!sub_id %in% fmri4_bad_participants) %>% 
  filter(!subject %in% c("cc250121","kv250109","ha250127"))#these are manual exclusions based on data collection notes


fmri4_subjects <- unique(fmri4_pupil_data$subject)
fmri4_subject_n<-length(fmri4_subjects)
fmri4_subject_n

fmri4_pupil_data$cue_value <- factor(fmri4_pupil_data$cue_value,
                                levels = c("-$5","-$1","-$0","+$0","+$1","+$5"))

df.beh.fmri4 <- read_csv("~/Desktop/midaffemo2/analyses/pupil/derivatives/beh.csv")

## loop through each row, get (1) V/A at each time point and (2) ending location
df.beh.all <- df.beh.fmri4 %>% 
  # Replace square brackets and split the strings by ';'
  mutate_at(vars(vrating,arating,sampling_t), ~gsub("\\[|\\]", "", .x)) %>%
  separate_rows(c(vrating,arating,sampling_t), sep = ";") %>%
  # Optionally convert `vrating` to numeric
  mutate_at(vars(vrating,arating,sampling_t),~ as.numeric(.x))

df.beh.fmri4 <- df.beh.all %>% 
  ungroup() %>% 
  filter(!is.na(sampling_t)) %>% 
  group_by(subject, trial) %>% 
  mutate(rowid = row_number()) %>% 
  filter(rowid == max(rowid)) %>% 
  group_by(subject) %>% 
  mutate(arousal_scaled = as.numeric(scale(arating)),
         valence_scaled = as.numeric(scale(vrating)))

fmri4_pupil_data <- fmri4_pupil_data %>% 
  select(-vrating,-arating,-arousal_scaled,-valence_scaled) %>% 
  left_join(df.beh.fmri4 %>% select(subject,trial,arating,vrating,arousal_scaled,valence_scaled),
            by = c("trial","subject"))

fmri4_pupil_data<-fmri4_pupil_data %>% 
  filter(abs(pupilDiameter_scaled)<5) %>% 
  group_by(subject, trial, Time_sec) %>% 
  mutate(sample_in_sec = row_number())

fmri4_pupil_data$cue_size <- factor(fmri4_pupil_data$cue_size,levels = c(1,2),labels = c("small","large")) #note that this is different from midaffemo1
```

# read in demographics
```{r}
fmri4_subject_n
```

# compare study 3 and study 4 arousal ratings
```{r}
df.beh.fmri4 <- df.beh.fmri4 %>% 
  mutate(cue_value = factor(trialtype, levels = 1:6, labels = c("-$0","-$1","-$5","+$0","+$1","+$5"))) %>% 
  mutate(cue_value = factor(cue_value,
                                levels = c("-$5","-$1","-$0","+$0","+$1","+$5")))

df.beh.fmri3 %>% 
  group_by(subject) %>% 
  summarise(mean_arousal = mean(arating,na.rm = T)) %>% 
  ungroup() %>% 
  summarise(mean_arousal = mean(mean_arousal,na.rm = T))/5

df.beh.fmri4 %>% 
  group_by(subject) %>% 
  summarise(mean_arousal = mean(arating,na.rm = T)) %>% 
  ungroup() %>% 
  summarise(mean_arousal = mean(mean_arousal,na.rm = T))

d1<-df.beh.fmri3 %>% 
    group_by(subject, cue_value) %>% 
    summarise(arating = mean(arating,na.rm = T)) %>% 
    group_by(cue_value) %>% 
    summarise(mean_arousal = mean(arating,na.rm = T)/5,
              se_arousal=sd(arating,na.rm = T)/5/sqrt(n()))
d2<-df.beh.fmri4 %>% 
    group_by(subject, cue_value) %>% 
    summarise(arating = mean(arating,na.rm = T))%>% 
    group_by(cue_value) %>% 
    summarise(mean_arousal = mean(arating,na.rm = T),
              se_arousal=sd(arating,na.rm = T)/sqrt(n()))

ggplot()+
  geom_line(data = d1,
              aes(x = cue_value, y = mean_arousal, group = 1), linewidth = 1)+
    geom_errorbar(data = d1,
              aes(x = cue_value, ymin = mean_arousal-se_arousal,
                  ymax = mean_arousal+se_arousal, group = 1), linewidth = 1,
              width = 0.1)+
  geom_line(data = d2,
              aes(x = cue_value, y = mean_arousal, group = 1), color = "#FF34B3", linewidth = 1)+
      geom_errorbar(data = d2,
              aes(x = cue_value, ymin = mean_arousal-se_arousal,
                  ymax = mean_arousal+se_arousal, group = 1), linewidth = 1,color = "#FF34B3",
              width = 0.1)+
  annotate("text",x=2,y = 0.8, label = "FMRI study")+
  annotate("text",x=2,y = 0.66, label = "Validation sample",color = "#FF34B3")

ggsave("~/Desktop/VRMID-analysis/mid-pupil/figures/validation_fig1.png",dpi = 300, height = 3, width = 4)
```


# plot example time courses

## entire timeline (1 line)
```{r}
fmri3_summary_nobc <- fmri3_pupil_data%>%
  ungroup()%>%
  group_by(sample_in_trial_t,probe)%>%
  summarise(mean = mean(pupilDiameter_scaled, na.rm = T),
            lower = mean(pupilDiameter_scaled, na.rm = T) - qt(0.975, df = n() - 1) * sd(pupilDiameter_scaled, na.rm = T) / sqrt(n()),
            upper = mean(pupilDiameter_scaled, na.rm = T) + qt(0.975, df = n() - 1) * sd(pupilDiameter_scaled, na.rm = T) / sqrt(n()))

fmri4_summary_nobc <- fmri4_pupil_data%>%
  ungroup()%>%
  group_by(sample_in_trial_t,probe)%>%
  summarise(mean = mean(pupilDiameter_scaled, na.rm = T),
            lower = mean(pupilDiameter_scaled, na.rm = T) - qt(0.975, df = n() - 1) * sd(pupilDiameter_scaled, na.rm = T) / sqrt(n()),
            upper = mean(pupilDiameter_scaled, na.rm = T) + qt(0.975, df = n() - 1) * sd(pupilDiameter_scaled, na.rm = T) / sqrt(n()))


```

```{r}
ggplot()+
    geom_vline(xintercept = c(0,2,4,12,14,16,18), size = 1, color = "grey")+
    geom_hline(yintercept = 0, linetype = "dashed",color = "grey")+
  geom_line(data = fmri3_summary_nobc%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == 1), aes(x = sample_in_trial_t,
                       y = mean),size=1)+
  geom_ribbon(data = fmri3_summary_nobc%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == 1),aes(x = sample_in_trial_t,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2)+
   geom_line(data = fmri4_summary_nobc%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == 1), aes(x = sample_in_trial_t,
                       y = mean),size=1, color = "#FF34B3")+
  geom_ribbon(data = fmri4_summary_nobc%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == 1),aes(x = sample_in_trial_t,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2, fill = "#FF34B3")+
  annotate("text", x = 1,y = 0.7, label = "C",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 3,y = 0.7, label = "F",
          color = "black",size = unit(4,"pt"))+
    annotate("text", x = 13,y = 0.7, label = "F",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 15,y = 0.7, label = "T",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 17,y = 0.7, label = "O",
          color = "black",size = unit(4,"pt"))+
    annotate("text", x = 8,y = 0.7, label = "R",
          color = "black",size = unit(4,"pt"))+
  labs(title = "",
       subtitle = "anticipation probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  ylim(-1.3,1)+


ggplot()+
    geom_vline(xintercept = c(0,2,4,6,8,16), size = 1, color = "grey")+
  geom_hline(yintercept = 0, linetype = "dashed",color = "grey")+
  geom_line(data=fmri3_summary_nobc%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == 2), aes(x = sample_in_trial_t,
                       y = mean),size = 1)+
  geom_ribbon(data=fmri3_summary_nobc%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == 2),aes(x = sample_in_trial_t,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2)+
   geom_line(data=fmri4_summary_nobc%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == 2), aes(x = sample_in_trial_t,
                       y = mean),size = 1, color = "#FF34B3")+
  geom_ribbon(data=fmri4_summary_nobc%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == 2),aes(x = sample_in_trial_t,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2, fill = "#FF34B3")+
  scale_color_manual(values = purpleOrange_palette6)+
  scale_fill_manual(values = purpleOrange_palette6)+
  annotate("text", x = 1,y = 0.7, label = "C",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 3,y = 0.7, label = "F",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 5,y = 0.7, label = "T",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 7,y = 0.7, label = "O",
          color = "black",size = unit(4,"pt"))+
    annotate("text", x = 12,y = 0.7, label = "R",
          color = "black",size = unit(4,"pt"))+
  labs(subtitle = "outcome probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  ylim(-1.3,1)

ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/validation_fig2.png"),dpi = 300, height = 3, width = 9)

```

```{r}
#get the range of pupil values
range(fmri3_summary_nobc$mean,na.rm = T)
max(fmri3_summary_nobc$mean,na.rm = T)-min(fmri3_summary_nobc$mean,na.rm = T)

range(fmri4_summary_nobc$mean,na.rm = T)
max(fmri4_summary_nobc$mean,na.rm = T)-min(fmri4_summary_nobc$mean,na.rm = T)
```

## entire timeline by cue size (2 lines)
```{r}
fmri3_summary_nobc2 <- fmri3_pupil_data%>%
  ungroup()%>%
  group_by(sample_in_trial_t,probe,cue_size)%>%
  summarise(mean = mean(pupilDiameter_scaled, na.rm = T),
            lower = mean(pupilDiameter_scaled, na.rm = T) - qt(0.975, df = n() - 1) * sd(pupilDiameter_scaled, na.rm = T) / sqrt(n()),
            upper = mean(pupilDiameter_scaled, na.rm = T) + qt(0.975, df = n() - 1) * sd(pupilDiameter_scaled, na.rm = T) / sqrt(n()))

p3a<-ggplot(fmri3_summary_nobc2%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == 1), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,2,4,12,14,16,18), size = 1, color = "grey")+
  geom_line(aes(color = cue_size),size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t,
                  ymin = lower, 
                  ymax = upper,
                  color = cue_size), 
              alpha = 0.2)+
  annotate("text", x = 1,y = 0.7, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 3,y = 0.7, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 13,y = 0.7, label = "fix2",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 15,y = 0.7, label = "target",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 17,y = 0.7, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 8,y = 0.7, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  scale_color_manual(values = c("#E78AC3FF","#66C2A5FF"))+
  scale_fill_manual(values = c("#E78AC3FF","#66C2A5FF"))+
  labs(title = "FMRI Study",
       subtitle = "anticipation probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  ylim(-2,1)

p3b<-ggplot(fmri3_summary_nobc2%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == 2), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,2,4,6,8,16), size = 1, color = "grey")+
  geom_line(aes(color = cue_size),size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t,
                  ymin = lower, 
                  ymax = upper,
                  color = cue_size), 
              alpha = 0.2)+
  annotate("text", x = 1,y = 0.7, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 3,y = 0.7, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 0.7, label = "target",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 7,y = 0.7, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 12,y = 0.7, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "FMRI Study",
       subtitle = "outcome probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  scale_color_manual(values = c("#E78AC3FF","#66C2A5FF"))+
  scale_fill_manual(values = c("#E78AC3FF","#66C2A5FF"))+
  ylim(-2,1)

fmri4_summary_nobc2 <- fmri4_pupil_data%>%
  ungroup()%>%
  mutate(cue_size= as.factor(cue_size)) %>% 
  group_by(sample_in_trial_t,probe,cue_size)%>%
  summarise(mean = mean(pupilDiameter_scaled, na.rm = T),
            lower = mean(pupilDiameter_scaled, na.rm = T) - qt(0.975, df = n() - 1) * sd(pupilDiameter_scaled, na.rm = T) / sqrt(n()),
            upper = mean(pupilDiameter_scaled, na.rm = T) + qt(0.975, df = n() - 1) * sd(pupilDiameter_scaled, na.rm = T) / sqrt(n()))

p4a<-ggplot(fmri4_summary_nobc2%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == 1), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,2,4,12,14,16,18), size = 1, color = "grey")+
  geom_line(aes(color = cue_size),size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t,
                  ymin = lower, 
                  ymax = upper,
                  color = cue_size), 
              alpha = 0.2)+
  annotate("text", x = 1,y = 0.7, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 3,y = 0.7, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 13,y = 0.7, label = "fix2",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 15,y = 0.7, label = "target",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 17,y = 0.7, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 8,y = 0.7, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "Validation Sample",
       subtitle = "anticipation probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  ylim(-2,1)+
  theme(legend.position = "none")+
  scale_color_manual(values = c( "#E78AC3FF","#66C2A5FF"))+
  scale_fill_manual(values = c( "#E78AC3FF","#66C2A5FF"))

p4b<-ggplot(fmri4_summary_nobc2%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == 2), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,2,4,6,8,16), size = 1, color = "grey")+
  geom_line(aes(color = cue_size),size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t,
                  ymin = lower, 
                  ymax = upper,
                  color = cue_size), 
              alpha = 0.2)+
  annotate("text", x = 1,y = 0.7, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 3,y = 0.7, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 0.7, label = "target",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 7,y = 0.7, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 12,y = 0.7, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "Validation Sample",
       subtitle = "outcome probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  ylim(-2,1)+
  theme(legend.position = "none")+
  scale_color_manual(values = c( "#E78AC3FF","#66C2A5FF"))+
  scale_fill_manual(values = c( "#E78AC3FF","#66C2A5FF"))

p3a+p4a+p3b+p4b

ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/validation_fig3.png"),dpi = 300, height = 5, width = 6)
```


# pre-selected time window predicting affect

# calculate df
```{r}
fmri4_data_antprobe <-  fmri4_pupil_data%>%
  mutate(pupil_window = ifelse(sample_in_trial_t <= fmri4_antprobe_out_window[2] & 
                                 sample_in_trial_t > fmri4_antprobe_out_window[1],
                               "out",
                               ifelse(sample_in_trial_t <= fmri4_ant_window[2] & 
                                        sample_in_trial_t > fmri4_ant_window[1],
                                      "ant",NA)))%>%
  filter(probe == 1, pupil_window %in% c("out","ant"))%>%
  ungroup()%>%
  group_by(subject) %>% 
  group_by(probe,subject,trial,hit,cue_value,
           pupil_window,
           arousal_scaled,valence_scaled,cue_size,rt,iti,last_iti)%>%
  summarise(mean_pupil_bc_scaled = mean(pupilDiameter_bc_scaled, na.rm = T),
            mean_pupil_nobc_scaled= mean(pupilDiameter_scaled, na.rm = T),
            mean_pupil_baseline_scaled = mean(pupilDiameter_baseline_scaled, na.rm = T))%>%
  pivot_wider(values_from = mean_pupil_bc_scaled:mean_pupil_nobc_scaled, names_from = pupil_window)%>%
  ungroup()%>%
  group_by(subject)%>%
  mutate(log_rt = log(rt),
         log_rt = as.numeric(scale(log_rt)))

fmri4_data_outprobe <-  fmri4_pupil_data%>%
  mutate(pupil_window = ifelse(probe == 2 & sample_in_trial_t <= fmri4_outprobe_out_window[2] 
                               & sample_in_trial_t > fmri4_outprobe_out_window[1],
                               "out",
                               ifelse(probe == 2 &  sample_in_trial_t <= fmri4_ant_window[2] 
                                      & sample_in_trial_t > fmri4_ant_window[1],
                                      "ant",NA)))%>%
  filter(probe == 2, pupil_window %in% c("out","ant"))%>%
  ungroup()%>%
  group_by(subject) %>% 
  group_by(probe,subject,trial,hit,cue_value,
           pupil_window,
           arousal_scaled,valence_scaled,cue_size,rt,iti,last_iti)%>%
  summarise(mean_pupil_bc_scaled = mean(pupilDiameter_bc_scaled, na.rm = T),
            mean_pupil_nobc_scaled= mean(pupilDiameter_scaled, na.rm = T),
            mean_pupil_baseline_scaled = mean(pupilDiameter_baseline_scaled, na.rm = T))%>%
  pivot_wider(values_from = mean_pupil_bc_scaled:mean_pupil_nobc_scaled, names_from = pupil_window)%>%
  ungroup()%>%
  group_by(subject)%>%
  mutate(log_rt = log(rt),
         log_rt = as.numeric(scale(log_rt)))
```

# pupil by cue value and hit
```{r}

pupil_avg_ant <- rbind(fmri4_data_antprobe %>% 
                         select(subject,probe,cue_value,mean_pupil_nobc_scaled_ant,mean_pupil_nobc_scaled_out),
                       fmri4_data_outprobe %>% 
                         select(subject,probe,cue_value,mean_pupil_nobc_scaled_ant,mean_pupil_nobc_scaled_out))%>%
  ungroup()%>%
    group_by(subject,cue_value,probe)%>%
  summarise(mean_pupil_nobc_scaled_ant = mean(mean_pupil_nobc_scaled_ant, na.rm = T)) %>% 
  group_by(cue_value)%>%
  summarise(pupil_mean = mean(mean_pupil_nobc_scaled_ant, na.rm = T),
            pupil_sd = sd(mean_pupil_nobc_scaled_ant, na.rm = T)/sqrt(n()))%>%
  select(cue_value,pupil_mean,pupil_sd) %>% 
  mutate(probe = "anticipation")

pupil_avg_out <- rbind(fmri4_data_antprobe %>% 
                         select(subject,probe,hit,cue_value,mean_pupil_nobc_scaled_ant,mean_pupil_nobc_scaled_out),
                       fmri4_data_outprobe %>% 
                         select(subject,probe,hit,cue_value,mean_pupil_nobc_scaled_ant,mean_pupil_nobc_scaled_out))%>%
  ungroup()%>%
      group_by(subject,cue_value,probe,hit)%>%
  summarise(mean_pupil_nobc_scaled_out = mean(mean_pupil_nobc_scaled_out, na.rm = T)) %>% 
  # filter(probe == "out") %>% 
  group_by(cue_value,hit)%>%
  summarise(pupil_mean = mean(mean_pupil_nobc_scaled_out, na.rm = T),
            pupil_sd = sd(mean_pupil_nobc_scaled_out, na.rm = T)/sqrt(n()))%>%
  select(cue_value,hit,pupil_mean,pupil_sd) %>% 
  mutate(probe = ifelse(hit == 1,"outcome-hit","outcome-miss"))

p4a<-ggplot()+
  geom_point(data = pupil_avg_ant, aes(x = cue_value, y = pupil_mean,color = cue_value, shape = probe),
             size = 2)+
  geom_errorbar(data = pupil_avg_ant,aes(ymin=pupil_mean-pupil_sd, ymax=pupil_mean+pupil_sd,
                    x=cue_value,color = cue_value), width=.5)+
  scale_color_manual(values = redOrange_palette6)+
  labs(y = "pupil zscore",
       title = "Validation Sample",
       subtitle = "anticipatory period",
       x = "")+
  theme(legend.position = "none")
  
p4b<-ggplot()+ 
  geom_point(data = pupil_avg_out, aes(x = cue_value, y = pupil_mean,color = cue_value, shape = probe),
             size = 2)+
  geom_errorbar(data = pupil_avg_out,aes(ymin=pupil_mean-pupil_sd, ymax=pupil_mean+pupil_sd,
                    x=cue_value,color = cue_value), width=.5)+
  scale_color_manual(values = redOrange_palette6)+
      scale_shape_manual(values = c("outcome-hit" = 17, "outcome-miss" = 15)) +
  # scale_linetype_manual(values = c("outcome-hit" = "dashed", "outcome-miss" = "dotdash"))+
  labs(y = "pupil zscore",
       title = "Validation Sample",
       subtitle = "outcome period",
       x = "")+
  theme(legend.position = "none")


p4a+p4b
```

### by cue size, cue value and hit
```{r}
# fmri 3 - when not controlling for luminance
pupil_avg_ant_pre <- rbind(fmri3_data_antprobe %>% 
                         select(subject,probe,cue_value,cue_size,
                                mean_pupil_nobc_scaled_ant,mean_pupil_nobc_scaled_out),
                       fmri3_data_outprobe %>% 
                         select(subject,probe,cue_value,cue_size,
                                mean_pupil_nobc_scaled_ant,mean_pupil_nobc_scaled_out))%>%
  ungroup()%>%
    group_by(subject,cue_value,cue_size,probe)%>%
  summarise(mean_pupil_nobc_scaled_ant = mean(mean_pupil_nobc_scaled_ant, na.rm = T)) %>% 
  group_by(cue_value,cue_size)%>%
  summarise(pupil_mean = mean(mean_pupil_nobc_scaled_ant, na.rm = T),
            pupil_sd = sd(mean_pupil_nobc_scaled_ant, na.rm = T)/sqrt(n()))%>%
  select(cue_value,cue_size,pupil_mean,pupil_sd) %>% 
  mutate(probe = "anticipation")

pupil_avg_out_pre <- rbind(fmri3_data_antprobe %>% 
                         select(subject,probe,cue_value,cue_size,hit,
                                mean_pupil_nobc_scaled_ant,mean_pupil_nobc_scaled_out),
                       fmri3_data_outprobe %>% 
                         select(subject,probe,cue_value,cue_size,hit,
                                mean_pupil_nobc_scaled_ant,mean_pupil_nobc_scaled_out))%>%
  ungroup()%>%
      group_by(subject,cue_value,cue_size,probe,hit)%>%
  summarise(mean_pupil_nobc_scaled_out = mean(mean_pupil_nobc_scaled_out, na.rm = T)) %>% 
  # filter(probe == "out") %>% 
  group_by(cue_value,hit,cue_size)%>%
  summarise(pupil_mean = mean(mean_pupil_nobc_scaled_out, na.rm = T),
            pupil_sd = sd(mean_pupil_nobc_scaled_out, na.rm = T)/sqrt(n()))%>%
  select(cue_value,cue_size,hit,pupil_mean,pupil_sd) %>% 
  mutate(probe = ifelse(hit == 1,"outcome-hit","outcome-miss"))


# study 3 - when controlling for luminance
pupil_avg_ant_post <-rbind(fmri3_data_antprobe %>% 
                         select(subject,probe,cue_value,cue_size,
                                mean_pupil_nobc_scaled_residual_conv_ant,mean_pupil_nobc_scaled_residual_conv_out),
                       fmri3_data_outprobe %>% 
                         select(subject,probe,cue_value,cue_size,
                                mean_pupil_nobc_scaled_residual_conv_ant,mean_pupil_nobc_scaled_residual_conv_out))%>%
                         select(subject,probe,cue_value,cue_size,
                                mean_pupil_nobc_scaled_residual_conv_ant,
                                mean_pupil_nobc_scaled_residual_conv_out)%>%
  ungroup()%>%
    group_by(subject,cue_value,cue_size,probe)%>%
  summarise(mean_pupil_nobc_scaled_ant = mean(mean_pupil_nobc_scaled_residual_conv_ant, na.rm = T)) %>% 
  group_by(cue_value,cue_size)%>%
  summarise(pupil_mean = mean(mean_pupil_nobc_scaled_ant, na.rm = T),
            pupil_sd = sd(mean_pupil_nobc_scaled_ant, na.rm = T)/sqrt(n()))%>%
  select(cue_value,cue_size,pupil_mean,pupil_sd) %>% 
  mutate(probe = "anticipation")

  
ggplot()+
  geom_point(data = pupil_avg_ant_pre, aes(x = cue_value, y = pupil_mean, color = cue_size))+
  geom_errorbar(data = pupil_avg_ant_pre,aes(ymin=pupil_mean-pupil_sd, ymax=pupil_mean+pupil_sd,
                    x=cue_value,color = cue_size), width=.5)+
  labs(y = "pupil zscore",
       title = "before controlling for luminance",
       subtitle = "anticipatory period",
       x = "")+
  ylim(-0.35,0.45)

ggplot()+ 
  geom_point(data = pupil_avg_out_post, aes(x = cue_value, y = pupil_mean,color = cue_size, shape = probe),
             size = 2)+
  geom_errorbar(data = pupil_avg_out_post,aes(ymin=pupil_mean-pupil_sd, ymax=pupil_mean+pupil_sd,
                    x=cue_value,color = cue_size), width=.5)+
      scale_shape_manual(values = c("outcome-hit" = 17, "outcome-miss" = 15)) +
  # scale_linetype_manual(values = c("outcome-hit" = "dashed", "outcome-miss" = "dotdash"))+
  labs(y = "pupil zscore",
       title = "FMRI Study",
       subtitle = "outcome period",
       x = "")+
  facet_wrap(~hit)
```

```{r}
# study 4
pupil_avg_ant <-  rbind(fmri4_data_antprobe %>% 
                         select(subject,probe,cue_value,cue_size,
                                mean_pupil_nobc_scaled_ant,mean_pupil_nobc_scaled_out),
                       fmri4_data_outprobe %>% 
                         select(subject,probe,cue_value,cue_size,
                                mean_pupil_nobc_scaled_ant,mean_pupil_nobc_scaled_out))%>%
                         select(subject,probe,cue_value,cue_size,
                                mean_pupil_nobc_scaled_ant,
                                mean_pupil_nobc_scaled_out)%>%
  ungroup()%>%
    group_by(subject,cue_value,cue_size,probe)%>%
  summarise(mean_pupil_nobc_scaled_ant = mean(mean_pupil_nobc_scaled_ant, na.rm = T)) %>% 
  group_by(cue_value,cue_size)%>%
  summarise(pupil_mean = mean(mean_pupil_nobc_scaled_ant, na.rm = T),
            pupil_sd = sd(mean_pupil_nobc_scaled_ant, na.rm = T)/sqrt(n()))%>%
  select(cue_value,cue_size,pupil_mean,pupil_sd) %>% 
  mutate(probe = "anticipation")

pupil_avg_out <- rbind(fmri4_data_antprobe %>% 
                         select(subject,probe,cue_value,cue_size,hit,
                                mean_pupil_nobc_scaled_ant,mean_pupil_nobc_scaled_out),
                       fmri4_data_outprobe %>% 
                         select(subject,probe,cue_value,cue_size,hit,
                                mean_pupil_nobc_scaled_ant,mean_pupil_nobc_scaled_out))%>%
                         select(subject,probe,hit,cue_size,cue_value,
                                mean_pupil_nobc_scaled_ant,
                                mean_pupil_nobc_scaled_out)%>%
  ungroup()%>%
      group_by(subject,cue_value,cue_size,probe,hit)%>%
  summarise(mean_pupil_nobc_scaled_out = mean(mean_pupil_nobc_scaled_out, na.rm = T)) %>% 
  # filter(probe == "out") %>% 
  group_by(cue_value,hit,cue_size)%>%
  summarise(pupil_mean = mean(mean_pupil_nobc_scaled_out, na.rm = T),
            pupil_sd = sd(mean_pupil_nobc_scaled_out, na.rm = T)/sqrt(n()))%>%
  select(cue_value,cue_size,hit,pupil_mean,pupil_sd) %>% 
  mutate(probe = ifelse(hit == 1,"outcome-hit","outcome-miss"))

ggplot()+
  geom_point(data = pupil_avg_ant, aes(x = cue_value, y = pupil_mean, color = as.factor(cue_size)))+
  geom_errorbar(data = pupil_avg_ant,aes(ymin=pupil_mean-pupil_sd, ymax=pupil_mean+pupil_sd,
                    x=cue_value,color = as.factor(cue_size)), width=.5)+
  labs(y = "pupil zscore",
       title = "Validation Sample",
       subtitle = "anticipatory period",
       x = "")+
  theme(legend.position = "none")
  
ggplot()+ 
  geom_point(data = pupil_avg_out, aes(x = cue_value, y = pupil_mean,color = as.factor(cue_size), shape = probe),
             size = 2)+
  geom_errorbar(data = pupil_avg_out,aes(ymin=pupil_mean-pupil_sd, ymax=pupil_mean+pupil_sd,
                    x=cue_value,color = as.factor(cue_size)), width=.5)+
      scale_shape_manual(values = c("outcome-hit" = 17, "outcome-miss" = 15)) +
  # scale_linetype_manual(values = c("outcome-hit" = "dashed", "outcome-miss" = "dotdash"))+
  labs(y = "pupil zscore",
       title = "Validation Sample",
       subtitle = "outcome period",
       x = "")+
  facet_wrap(~hit)


pupil_avg_ant <-  rbind(fmri4_data_antprobe %>% 
                         select(subject,probe,cue_value,cue_size,
                                mean_pupil_nobc_scaled_ant,mean_pupil_nobc_scaled_out),
                       fmri4_data_outprobe %>% 
                         select(subject,probe,cue_value,cue_size,
                                mean_pupil_nobc_scaled_ant,mean_pupil_nobc_scaled_out))%>%
                         select(subject,probe,cue_value,cue_size,
                                mean_pupil_nobc_scaled_ant,
                                mean_pupil_nobc_scaled_out)%>%
  ungroup()%>%
    group_by(subject,cue_value,probe)%>%
  summarise(mean_pupil_nobc_scaled_ant = mean(mean_pupil_nobc_scaled_ant, na.rm = T)) %>% 
  group_by(cue_value)%>%
  summarise(pupil_mean = mean(mean_pupil_nobc_scaled_ant, na.rm = T),
            pupil_sd = sd(mean_pupil_nobc_scaled_ant, na.rm = T)/sqrt(n()))%>%
  select(cue_value,pupil_mean,pupil_sd) %>% 
  mutate(probe = "anticipation")

ggplot()+
  geom_point(data = pupil_avg_ant, aes(x = cue_value, y = pupil_mean))+
  geom_errorbar(data = pupil_avg_ant,aes(ymin=pupil_mean-pupil_sd, ymax=pupil_mean+pupil_sd,
                    x=cue_value), width=.5)+
  labs(y = "pupil zscore",
       title = "Validation Sample",
       subtitle = "anticipatory period",
       x = "")+
  theme(legend.position = "none")
```

## does pupil explain additional variance?
### anticipation
```{r}
summary(l1<-lmer(arousal_scaled ~ cue_value + mean_pupil_nobc_scaled_ant + (1|subject)+ (1|cue_size),fmri4_data_antprobe))
round(anova(l1),2)
```
### outcome
```{r}
summary(l1<-lmer(arousal_scaled ~ mean_pupil_nobc_scaled_out + cue_value * hit + (1|subject)+ (1|cue_size),fmri4_data_outprobe))
round(anova(l1),2)
```

## calculate separate effect sizes for each study

### anticipation
```{r}
## combined (the best)
summary(l3a<-lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc_scaled_ant) +(1|subject) + (1|cue_size),
              fmri3_data_antprobe))

## combined (the best)
summary(l4a<-lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc_scaled_ant) +(1|subject) + (1|cue_size),
              fmri4_data_antprobe))
```

### outcome
```{r}
## combined (the best)
summary(l3b<-lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc_scaled_out) +(1|subject) + (1|cue_size),
              fmri3_data_outprobe))

## combined (the best)
summary(l4b<-lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc_scaled_out) +(1|subject) + (1|cue_size),
              fmri4_data_outprobe))
```


```{r}
# Extract predicted data
p3a_data <- plot_model(l3a, type = "pred", terms = "mean_pupil_nobc_scaled_ant", show.data = TRUE)$data
p4a_data <- plot_model(l4a, type = "pred", terms = "mean_pupil_nobc_scaled_ant", show.data = TRUE)$data

# Add a study identifier
p3a_data$study <- "FMRI Study"
p4a_data$study <- "Validation Sample"

# Combine the data
combined_data <- rbind(p3a_data, p4a_data)

p_combined1 <- ggplot(combined_data, aes(x = x, y = predicted, color = study, fill = study)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, linetype = 0) +
  # geom_point(alpha = 0.3, size = 0.5, inherit.aes = FALSE) +
  labs(
    x = "uncorrected phasic pupil",
    y = "arousal zscore",
    title = "Anticipation probe",
  ) +
  scale_color_manual(values = c("FMRI Study" = "black", "Validation Sample" = "#FF34B3")) +
  scale_fill_manual(values = c("FMRI Study" = "black", "Validation Sample" = "#FF34B3"))+
  theme(legend.position = "left")


# Extract predicted data
p3c_data <- plot_model(l3b, type = "pred", terms = "mean_pupil_nobc_scaled_out", show.data = TRUE)$data
p4c_data <- plot_model(l4b, type = "pred", terms = "mean_pupil_nobc_scaled_out", show.data = TRUE)$data

# Add a study identifier
p3c_data$study <- "FMRI Study"
p4c_data$study <- "Validation Sample"

# Combine the data
combined_data <- rbind(p3c_data, p4c_data)

p_combined2 <- ggplot(combined_data, aes(x = x, y = predicted, color = study, fill = study)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2, linetype = 0) +
  # geom_point(alpha = 0.3, size = 0.5, inherit.aes = FALSE) +
  labs(
    x = "uncorrected phasic pupil",
    y = "arousal zscore",
    title = "Outcome probe",
  ) +
  scale_color_manual(values = c("FMRI Study" = "black", "Validation Sample" = "#FF34B3")) +
  scale_fill_manual(values = c("FMRI Study" = "black", "Validation Sample" = "#FF34B3"))+
  theme(legend.position = "none")

p_combined1+p_combined2
ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/validation_fig4.png"),dpi = 300, height = 3, width = 7)
```

## compare rt
```{r}
fmri3_data_rt <- fmri3_pupil_data%>%
  filter(sample_in_trial_t <= fmri3_ant_window[2] & sample_in_trial_t > fmri3_ant_window[1]) %>% 
  group_by(probe,subject,trial,hit,cue_value,
           arousal,valence,last_iti,
           arousal_scaled,valence_scaled,
           cue_size,rt)%>%
  summarise(mean_pupil_bc = mean(pupilDiameter_bc_scaled, na.rm = T),
            mean_pupil_nobc = mean(pupilDiameter_scaled, na.rm = T),
            mean_pupil_baseline = mean(pupilDiameter_baseline_scaled, na.rm = T))%>%
  filter(abs(mean_pupil_bc) < 4,
         abs(mean_pupil_nobc) < 4,
         abs(mean_pupil_baseline) < 4)  %>% 
  group_by(subject)%>%
  mutate(log_rt = log(rt),
         log_rt = as.numeric(scale(log_rt))) 

fmri4_data_rt <- fmri4_pupil_data%>%
  filter(sample_in_trial_t <= fmri4_ant_window[2] & sample_in_trial_t > fmri4_ant_window[1]) %>% 
  group_by(probe,subject,trial,hit,cue_value,
           last_iti,
           arousal_scaled,valence_scaled,
           cue_size,rt)%>%
  summarise(mean_pupil_bc = mean(pupilDiameter_bc_scaled, na.rm = T),
            mean_pupil_nobc = mean(pupilDiameter_scaled, na.rm = T),
            mean_pupil_baseline = mean(pupilDiameter_baseline_scaled, na.rm = T))%>%
  filter(abs(mean_pupil_bc) < 4,
         abs(mean_pupil_nobc) < 4,
         abs(mean_pupil_baseline) < 4)  %>% 
  group_by(subject)%>%
  mutate(log_rt = log(rt),
         log_rt = as.numeric(scale(log_rt))) 

fmri3_data_rt %>% 
  filter(hit == 1) %>% 
  group_by(subject,probe) %>% 
  summarise(rt = mean(rt)) %>% 
  ungroup() %>% 
  group_by(probe) %>% 
  summarise(rt = mean(rt))

fmri4_data_rt %>% 
  filter(rt != -1) %>% 
  group_by(subject,probe) %>% 
  summarise(rt = mean(rt)) %>% 
  ungroup() %>% 
  group_by(probe) %>% 
  summarise(rt = mean(rt))

rt_comp <- rbind(fmri3_data_rt%>% 
  filter(hit == 1) %>% 
  mutate(study = "FMRI Study"),
                 fmri4_data_rt%>% 
  filter(hit == 1)%>% 
  mutate(study = "Validation Sample")) %>% 
  mutate(probe = ifelse(probe == 1, "anticipation probe","outcome probe"))

ggplot(rt_comp, aes(x = study, y = rt, color = study))+
  geom_jitter(size = 0.1, width = 0.2, alpha = 0.1)+
  stat_summary(size = 0.4)+
  facet_wrap(~probe)+
  scale_color_manual(values = c("FMRI Study" = "black", "Validation Sample" = "#FF34B3"))

ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/validation_fig5.png"),dpi = 300, height = 3, width = 7)
```


# time course correlation
## get the correlation time series
```{r warning = F, message=F}
fmri3_regression_coefs_ant_nobc<-read_csv("../../data/fmri3/derivatives/fmri3_regression_coefs_ant_nobc.csv")
fmri3_regression_coefs_out_nobc<-read_csv("../../data/fmri3/derivatives/fmri3_regression_coefs_out_bc.csv")
```

```{r warning = F, message=F}
fmri4_regression_coefs_ant_nobc <- {}

for (t in 1:20) {
  coefs <- {}
  print(t)
  for (s in 1:200){
  df_ant_temp <- fmri4_pupil_data%>%
  filter(probe == 1,Time_sec == t, sample_in_sec == s)
  lm_ant_temp <- lmer(scale(arousal_scaled) ~ scale(pupilDiameter_scaled) + (1|subject) + (1|cue_size),df_ant_temp)
  lm_out <- c(summary(lm_ant_temp)$coefficient[2,],'r2m' = r.squaredGLMM(lm_ant_temp)[1])
  coefs <- rbind(coefs,lm_out)
  }
  coefs <- as.data.frame(coefs)%>%
    mutate(sample_in_sec = row_number(),
           Time_sec = t)
  rownames(coefs) <- NULL
  fmri4_regression_coefs_ant_nobc <- rbind(fmri4_regression_coefs_ant_nobc,coefs)
}

fmri4_regression_coefs_ant_nobc <- fmri4_regression_coefs_ant_nobc%>%
  mutate(sample_point = row_number())%>%
    rename(p_val = `Pr(>|t|)`) %>% 
  mutate(p_val_fdr = p.adjust(p_val, method = "fdr")) #applies the Benjamini–Hochberg correction

write.csv(fmri4_regression_coefs_ant_nobc, "../../data/fmri4/derivatives/fmri4_regression_coefs_ant_nobc.csv")

fmri4_regression_coefs_out_nobc <- {}

for (t in 1:20) {
  coefs <- {}
  print(t)
  for (s in 1:200){
  df_out_temp <- fmri4_pupil_data%>%
  filter(probe == 2,Time_sec == t, sample_in_sec == s)
  lm_out_temp <-  lmer(scale(arousal_scaled) ~ scale(pupilDiameter_scaled) + (1|subject) + (1|cue_size),df_out_temp)
  lm_out <- summary(lm_out_temp)$coefficient[2,]
  coefs <- rbind(coefs,lm_out)
  }
  coefs <- as.data.frame(coefs)%>%
    mutate(sample_in_sec = row_number(),
           Time_sec = t)
  rownames(coefs) <- NULL
  fmri4_regression_coefs_out_nobc <- rbind(fmri4_regression_coefs_out_nobc,coefs)
}

fmri4_regression_coefs_out_nobc <- fmri4_regression_coefs_out_nobc%>%
  mutate(sample_point = row_number())%>%
    rename(p_val = `Pr(>|t|)`) %>% 
  mutate(p_val_fdr = p.adjust(p_val, method = "fdr")) #applies the Benjamini–Hochberg correction

write.csv(fmri4_regression_coefs_out_nobc, "../../data/fmri4/derivatives/fmri4_regression_coefs_out_nobc.csv")
```

```{r}
min_cluster_length <- 1 * 200  # 0.5s * 200 samples/sec = 100 samples
merge_gap <- 0.3 * 200          # 0.1s * 200 samples/sec = 20 samples
fmri4_regression_coefs_ant_nobc  <- mark_clusters(fmri4_regression_coefs_ant_nobc,  p_thresh, min_cluster_length,merge_gap)
fmri4_regression_coefs_out_nobc  <- mark_clusters(fmri4_regression_coefs_out_nobc,  p_thresh, min_cluster_length,merge_gap)
```

```{r}
p3a<-ggplot(fmri3_regression_coefs_ant_nobc, aes(x = sample_point,y = Estimate))+
  geom_vline(xintercept = c(0,2,4,12,14,16,18)*200, size = 1, color = "grey")+
  geom_vline(xintercept = c(826,3291), size = 1, color = "orange", linetype = "dashed")+
  geom_point(aes(x = sample_point, y = sig_cluster-1),
             size = 0.1)+
     geom_ribbon(aes(x = sample_point, y = Estimate, ymin = Estimate - `Std. Error`,
                  ymax = Estimate + `Std. Error`),alpha = 0.1,
             size = 0.1)+
  annotate("text", x = 1*200,y = 0.1, label = "C",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 3*200,y = 0.1, label = "F",
          color = "black",size = unit(4,"pt"))+
    annotate("text", x = 13*200,y = 0.1, label = "F",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 15*200,y = 0.1, label = "T",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 17*200,y = 0.1, label = "O",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 8*200,y = 0.1, label = "R",
          color = "black",size = unit(4,"pt"))+
  geom_line(aes(color = Estimate),
             size = 1)+
  scale_x_continuous(breaks = seq(0,200*20,5*200), labels =  seq(0,20,5))+
  labs(x = "time (sec)",
       y =  "",
       title = "FMRI study",
       subtitle = "anticipation probe")+
  scale_color_viridis_c(limits=axis_range)+
  theme_blank()+
  ylim(axis_range)+
  theme(legend.position = "none")

p3b<-ggplot(fmri3_regression_coefs_out_nobc %>% filter(sample_point <= 18*200), aes(x = sample_point,y = Estimate))+
  geom_vline(xintercept = c(0,2,4,6,8,16)*200, size = 1, color = "grey")+
  geom_vline(xintercept = c(1294), size = 1, color = "orange", linetype = "dashed")+
  geom_point(aes(x = sample_point, y = sig_cluster-1),
             size = 0.1)+
   geom_ribbon(aes(x = sample_point, y = Estimate, ymin = Estimate - `Std. Error`,
                  ymax = Estimate + `Std. Error`),alpha = 0.1,
             size = 0.1)+
  annotate("text", x = 1*200,y = 0.02, label = "C",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 3*200,y =0.02, label = "F",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 5*200,y = 0.02, label = "T",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 7*200,y = 0.02, label = "O",
          color = "black",size = unit(4,"pt"))+
    annotate("text", x = 12*200,y = 0.02, label = "R",
          color = "black",size = unit(4,"pt"))+
    geom_line(aes(color = Estimate),
             size = 1)+
 scale_x_continuous(breaks = seq(0,200*20,5*200), labels =  seq(0,20,5))+
  labs(x = "time (sec)",
       y =  "",
       title = "FMRI study",
       subtitle = "outcome probe")+
  scale_color_viridis_c(limits=axis_range)+
  theme_blank()+
  ylim(axis_range)+
  theme(legend.position = "none")

p4a<-ggplot(fmri4_regression_coefs_ant_nobc, aes(x = sample_point,y = Estimate))+
  geom_vline(xintercept = c(0,2,4,12,14,16,18)*200, size = 1, color = "grey")+
  geom_vline(xintercept = c(775), size = 1, color = "orange", linetype = "dashed")+
  geom_point(aes(x = sample_point, y = sig_cluster-1),
             size = 0.1)+
     geom_ribbon(aes(x = sample_point, y = Estimate, ymin = Estimate - `Std. Error`,
                  ymax = Estimate + `Std. Error`),alpha = 0.1,
             size = 0.1)+
  annotate("text", x = 1*200,y = 0.1, label = "C",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 3*200,y = 0.1, label = "F",
          color = "black",size = unit(4,"pt"))+
    annotate("text", x = 13*200,y = 0.1, label = "F",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 15*200,y = 0.1, label = "T",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 17*200,y = 0.1, label = "O",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 8*200,y = 0.1, label = "R",
          color = "black",size = unit(4,"pt"))+
  geom_line(aes(color = Estimate),
             size = 1)+
  scale_x_continuous(breaks = seq(0,200*20,5*200), labels =  seq(0,20,5))+
  labs(x = "time (sec)",
       y =  "",
       title = "Validation Sample",
       subtitle = "anticipation probe")+
  scale_color_viridis_c(limits=axis_range)+
  theme_blank()+
  ylim(axis_range)+
  theme(legend.position = "none")

p4b<-ggplot(fmri4_regression_coefs_out_nobc %>% filter(sample_point <= 18*200), aes(x = sample_point,y = Estimate))+
  geom_vline(xintercept = c(0,2,4,6,8,16)*200, size = 1, color = "grey")+
  geom_vline(xintercept = c(1328), size = 1, color = "orange", linetype = "dashed")+
  geom_point(aes(x = sample_point, y = sig_cluster-1),
             size = 0.1)+
   geom_ribbon(aes(x = sample_point, y = Estimate, ymin = Estimate - `Std. Error`,
                  ymax = Estimate + `Std. Error`),alpha = 0.1,
             size = 0.1)+
  annotate("text", x = 1*200,y = 0.02, label = "C",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 3*200,y =0.02, label = "F",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 5*200,y = 0.02, label = "T",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 7*200,y = 0.02, label = "O",
          color = "black",size = unit(4,"pt"))+
    annotate("text", x = 12*200,y = 0.02, label = "R",
          color = "black",size = unit(4,"pt"))+
    geom_line(aes(color = Estimate),
             size = 1)+
 scale_x_continuous(breaks = seq(0,200*20,5*200), labels =  seq(0,20,5))+
  labs(x = "time (sec)",
       y =  "",
       title = "Validation Sample",
       subtitle = "outcome probe")+
  scale_color_viridis_c(limits=axis_range)+
  theme_blank()+
  ylim(axis_range)+
  theme(legend.position = "none")
```

```{r}
p3a+p3b+p4a+p4b
ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/validation_fig6.png"),dpi = 300, height = 7, width = 7)
```


