---
title: "pooled_analyses"
output: html_document
date: "2024-10-21"
---


```{r setup, include=FALSE}
source("~/Desktop/VRMID-analysis/mid-pupil/analyses/load_libraries.R")
knitr::opts_chunk$set(echo = TRUE)
theme_set(theme_blank() + #set the theme 
            theme(text = element_text(family = "Helvetica",size = 12))) #set the default text size
redOrange_palette6 = c("red","salmon","darkred","goldenrod3","orange","gold")
redOrange_palette2 = c("tomato4","gold")
emotions_palette6 = c( "Angry"="red", "Anxious"="orange","Excited"="gold", "Happy"="green3","Calm"="skyblue3","Sad"="purple")
emotions_palette2 = c("orangered","pink1")
emotions_palette2b = c("orange","red")
```

```{r}
rm(list = ls())
```


# read in pupil data

## vrmid1
```{r}
vrmid1_pupil_data <- read_csv("~/Desktop/VRMID-analysis/mid-pupil/data/vrmid1/derivatives/pupillometry_lowpass_baselineCorrected.csv")%>%
  group_by(Subject)%>%
  mutate(arousal_scaled = as.numeric(scale(arousal)),
         valence_scaled = as.numeric(scale(valence)))%>%
  ungroup()

vrmid1_pupil_data <- vrmid1_pupil_data %>%
  rename_with(~ str_replace(., "_scale$", "_scaled"))

vrmid1_bad_participants <- read_delim("../../data/vrmid1/subjects_list/subject_to_drop_pupil.txt", col_names = F, delim = " ")

vrmid1_pupil_data <- vrmid1_pupil_data %>% 
  filter(!Subject %in% c("cn221206","vx220916"), #manual bad participants
         !Subject %in% vrmid1_bad_participants) 

vrmid1_subjects <- unique(vrmid1_pupil_data$Subject)
vrmid1_subject_n<-length(vrmid1_subjects)
vrmid1_subject_n

for (i in 1:vrmid1_subject_n){
  ggplot(vrmid1_pupil_data %>% filter(Subject == vrmid1_subjects[i]), aes(x = sample_in_trial_t, y = pupil_Avg_scaled))+
    geom_line()+
    facet_wrap(~trial)+
    labs(title = i)

  ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/vrmid1/examine_data/trial_figs/",vrmid1_subjects[i],".png"),dpi = 300, height = 7, width = 14)
}

vrmid1_pupil_data$trial_type <- factor(vrmid1_pupil_data$trial_type, levels = c("-$5","-$1","-$0","+$0","+$1","+$5"))

vrmid1_pupil_data <- vrmid1_pupil_data%>%
  mutate(sample_in_trial_t = round(sample_in_trial_t,4))

vrmid1_pupil_data<-vrmid1_pupil_data %>% 
  filter(abs(pupil_Avg_scaled)<5)


vrmid1_beh_data <- vrmid1_pupil_data %>% 
  ungroup() %>% 
  group_by(Subject,trial,probe,trial_type) %>% 
  slice(1) %>% 
  select(Subject,trial,probe,trial_type,reaction_outcome,reaction_time)
```

## fmri3
<!-- ### first, run the code below to regress out the luminance component -->
<!-- ```{r eval = F, echo = F} -->
<!-- fmri3_pupil_data <- read_csv("~/Desktop/VRMID-analysis/mid-pupil/data/fmri3/derivatives/pupillometry_baselineCorrected.csv") %>%  -->
<!--   mutate(cue_value = factor(trialtype, levels = 1:6, labels = c("-$0","-$1","-$5","+$0","+$1","+$5"))) %>%  -->
<!--   filter(!is.na(subject)) %>%  -->
<!--   ungroup()  -->

<!-- fmri3_bad_participants <- read_delim("../../data/fmri3/subjects_list/subject_to_drop_pupil.txt", col_names = F, delim = " ") -->

<!-- fmri3_pupil_data <- fmri3_pupil_data %>%  -->
<!--   filter(!sub_id %in% fmri3_bad_participants) %>%  -->
<!--   filter(!subject %in% c("sk240301","hc240324","js240311","jy240308","tc240311","el240312"))#these are manual exclusions based on data collection notes -->

<!-- # # ## run the code for binding luminance data to fmri3 -->
<!-- source("../step1_preprocessing/fmri3/bind_luminance_fmri3.R", local = TRUE) -->
<!-- source("../step1_preprocessing/fmri3/convolve_luminance_fmri3.R", local = TRUE) -->
<!-- ``` -->

```{r}
fmri3_pupil_data <- read_csv("~/Desktop/VRMID-analysis/mid-pupil/data/fmri3/derivatives/pupillometry_baselineCorrected_with_luminance_convolved.csv") %>% 
  mutate(cue_value = factor(trialtype, levels = 1:6, labels = c("-$0","-$1","-$5","+$0","+$1","+$5"))) %>% 
  filter(!is.na(subject)) %>% 
  ungroup() 

fmri3_subjects <- unique(fmri3_pupil_data$subject)
fmri3_subject_n<-length(fmri3_subjects)
fmri3_subject_n

fmri3_pupil_data$cue_value <- factor(fmri3_pupil_data$cue_value,
                                levels = c("-$5","-$1","-$0","+$0","+$1","+$5"))

fmri3_pupil_data$emotion <- fmri3_pupil_data$erating

fmri3_pupil_data$emotion <- factor(fmri3_pupil_data$emotion, levels = 1:6, 
                           labels = c("Anxious","Angry","Sad","Calm","Happy","Excited"))

fmri3_pupil_data$arousal <- fmri3_pupil_data$arating
fmri3_pupil_data$valence <- fmri3_pupil_data$vrating

fmri3_pupil_data$hit <- factor(fmri3_pupil_data$hit,levels = c(1,0), labels = c("Hit","Miss"))
# fmri3_pupil_data$cue_size <- factor(fmri3_pupil_data$cue_size,levels = c(1,2), labels = c("small","large"))

fmri3_pupil_data <- fmri3_pupil_data %>% 
  mutate(emotion_cat = ifelse(emotion %in% c("Anxious","Angry","Excited"),"higharous",
                              ifelse(emotion %in% c("Sad","Calm","Happy"),"lowarous",NA)),
         emotion_cat2 = ifelse(emotion %in% c("Angry","Anxious","Sad"),
                              "pos_valence",
                              ifelse(emotion %in% c("Calm","Happy","Excited"),
                              "neg_valence",NA))) %>% 
  ungroup()%>%
  group_by(subject) %>% 
  mutate(arousal_scaled = as.numeric(scale(arousal)),
         valence_scaled = as.numeric(scale(valence)))

fmri3_pupil_data<-fmri3_pupil_data %>% 
  filter(abs(pupilDiameter_scaled)<5) %>% 
  group_by(subject, trial, Time_sec) %>% 
  mutate(sample_in_sec = row_number())

for (i in 1:fmri3_subject_n){
  ggplot(fmri3_pupil_data %>% filter(subject == fmri3_subjects[i]), aes(x = sample_in_trial_t, y = pupilDiameter_scaled))+
    geom_line()+
    facet_wrap(~trial)+
    labs(title = i)

  ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fmri3/examine_data/trial_figs/",fmri3_subjects[i],".png"),dpi = 300, height = 7, width = 14)
}


fmri3_pupil_data$cue_size <-factor(fmri3_pupil_data$cue_size, levels = c(1,2), labels = c("large","small"))

fmri3_pupil_data <- fmri3_pupil_data %>%
  filter(subject != "ag240330") #due to low hit rate
fmri3_subjects <- fmri3_subjects[fmri3_subjects!= "ag240330"]

fmri3_beh_data <- fmri3_pupil_data %>% 
  ungroup() %>% 
  group_by(subject,trial,probe,cue_value) %>% 
  slice(1) %>% 
  select(subject,trial,probe,rating_type,cue_value,binned_winpercent,hit,rt,
         vrating_t,arating_t,vrating,arating,scaledir,erating,erating_t)

fmri3_pupil_data$cue_size <- forcats::fct_recode(fmri3_pupil_data$cue_size,
                                                 small = "large",
                                                 large = "small")
```


# controlling for luminance

```{r, fig.height=4,fig.width=6}
summary_data <- fmri3_pupil_data %>% 
  mutate(probe = as.factor(probe),
         rating_type = as.factor(rating_type),
         cue_value = as.factor(cue_value),
         cue_size = as.factor(cue_size)) %>% 
  group_by(sample_in_trial_t,probe,rating_type,cue_value,hit,cue_size) %>% 
  summarise(luminance = mean(luminance),
            convolved_s1=mean(convolved_s1),
            convolved_s2 = mean(convolved_s2)) %>% 
  filter(cue_value == "+$5")

ggplot()+
  geom_line(data=summary_data,aes(x = sample_in_trial_t, y = -luminance,
            linetype = cue_size), linewidth = 0.5, color = 'skyblue')+
  geom_line(data=summary_data,aes(x = sample_in_trial_t+0.1, y = -convolved_s1,
             linetype = cue_size), linewidth = 0.5, color = 'salmon')+
    geom_line(data=summary_data,aes(x = sample_in_trial_t+0.2, y = -convolved_s2*300,
            linetype = cue_size), linewidth = 0.5, color = 'pink')+
  scale_x_continuous(breaks = seq(0,20,2))+
  facet_wrap(~rating_type+probe)

```

```{r}
# summary(l1<-lmer(scale(pupilDiameter_scaled) ~ scale(luminance) + (1|subject),fmri3_pupil_data))
# summary(l2<-lmer(scale(pupilDiameter_scaled) ~ scale(luminance_lag1) + (1|subject),fmri3_pupil_data))
summary(l3<-lmer(scale(pupilDiameter_scaled) ~ scale(convolved_s1) + (1|subject),fmri3_pupil_data))
summary(l4<-lmer(scale(pupilDiameter_scaled) ~ scale(convolved_s2) + (1|subject),fmri3_pupil_data))
summary(l5<-lmer(scale(pupilDiameter_scaled) ~ scale(convolved_s1)+scale(convolved_s2) + (1|subject),fmri3_pupil_data))

# summary(l1)$coefficient
# summary(l2)$coefficient
summary(l3)$coefficient
summary(l4)$coefficient
summary(l5)$coefficient
anova(l3,l4,l5)
r.squaredGLMM(l5)

#l4 has the largest coefficient, meaning that it might be the best model (among the 4) of luminance response of pupil
# Extract rows used in the model
model_data3 <- model.frame(l3)
used_rows3 <- as.numeric(rownames(model_data3))
# Create a residuals column in processed_data, initializing with NA
fmri3_pupil_data$residuals_conv_system1 <- NA

residuals_l3 <- residuals(l3)
# Assign residuals to the appropriate rows
fmri3_pupil_data$residuals_conv_system1[used_rows3] <- residuals_l3

model_data5 <- model.frame(l5)
used_rows5 <- as.numeric(rownames(model_data5))
# Create a residuals column in processed_data, initializing with NA
fmri3_pupil_data$residuals_conv_system1 <- NA

residuals_l5 <- residuals(l5)
# Assign residuals to the appropriate rows
fmri3_pupil_data$residuals_conv[used_rows5] <- residuals_l5
```

<!-- ## fmri4 -->
<!-- ```{r} -->
<!-- fmri4_pupil_data <- read_csv("~/Desktop/midaffemo2/analyses/pupil/derivatives/pupillometry_baselineCorrected.csv") %>%  -->
<!--   mutate(cue_value = factor(trialtype, levels = 1:6, labels = c("-$0","-$1","-$5","+$0","+$1","+$5"))) %>%  -->
<!--   filter(!is.na(subject)) %>%  -->
<!--   ungroup() -->

<!-- fmri4_bad_participants <- read_delim("~/Desktop/midaffemo2/analyses/pupil/subject_to_drop_pupil.txt", col_names = F, delim = " ") -->

<!-- fmri4_pupil_data <- fmri4_pupil_data %>%  -->
<!--   filter(!sub_id %in% fmri4_bad_participants) %>%  -->
<!--   filter(!subject %in% c("cc250121","kv250109","ha250127"))#these are manual exclusions based on data collection notes -->

<!-- fmri4_pupil_data$cue_value <- factor(fmri4_pupil_data$cue_value, -->
<!--                                 levels = c("-$5","-$1","-$0","+$0","+$1","+$5")) -->

<!-- df.beh.fmri4 <- read_csv("~/Desktop/midaffemo2/analyses/pupil/derivatives/beh.csv") -->

<!-- ## loop through each row, get (1) V/A at each time point and (2) ending location -->
<!-- df.beh.all <- df.beh.fmri4 %>%  -->
<!--   # Replace square brackets and split the strings by ';' -->
<!--   mutate_at(vars(vrating,arating,sampling_t), ~gsub("\\[|\\]", "", .x)) %>% -->
<!--   separate_rows(c(vrating,arating,sampling_t), sep = ";") %>% -->
<!--   # Optionally convert `vrating` to numeric -->
<!--   mutate_at(vars(vrating,arating,sampling_t),~ as.numeric(.x)) -->

<!-- fmri4_beh_data <- df.beh.all %>%  -->
<!--   ungroup() %>%  -->
<!--   filter(!is.na(sampling_t)) %>%  -->
<!--   group_by(subject, trial) %>%  -->
<!--   mutate(rowid = row_number()) %>%  -->
<!--   filter(rowid == max(rowid)) %>%  -->
<!--   group_by(subject) %>%  -->
<!--   mutate(arousal_scaled = as.numeric(scale(arating)), -->
<!--          valence_scaled = as.numeric(scale(vrating))) -->

<!-- fmri4_pupil_data <- fmri4_pupil_data %>%  -->
<!--   select(-vrating,-arating,-arousal_scaled,-valence_scaled) %>%  -->
<!--   left_join(df.beh.fmri4 %>% select(subject,trial,arating,vrating,arousal_scaled,valence_scaled), -->
<!--             by = c("trial","subject")) -->

<!-- fmri4_pupil_data<-fmri4_pupil_data %>%  -->
<!--   filter(abs(pupilDiameter_scaled)<5) %>%  -->
<!--   group_by(subject, trial, Time_sec) %>%  -->
<!--   mutate(sample_in_sec = row_number()) -->

<!-- fmri4_pupil_data$cue_size <- factor(fmri4_pupil_data$cue_size,levels = c(1,2),labels = c("small","large")) #note that this is different from midaffemo1 -->
<!-- ``` -->

# demographics
#number of participants

# ```{r}
# fmri4_subjects <- read_delim("../../data/fmri4/subjects_list/subjects-pupil-fmri.txt",delim = '\t', col_names = F)$X1
# fmri4_subject_n<-length(fmri4_subjects)
# ```

```{r}
vrmid1_subject_n
fmri3_subject_n
vrmid1_subject_n+fmri3_subject_n
```

```{r}
vrmid1_demographics <- qualtRics::read_survey("../../data/vrmid1/subjects_list/VRMID1 post-task survey_label.csv") %>% 
  rename(Subject = `Subject ID`) %>% 
  filter(Subject %in% vrmid1_subjects)

fmri3_demographics <-  read_csv("../../data/fmri3/subjects_list/demographics-fmri3.csv") %>% 
              rename(subject = id) %>% 
  mutate(subject = ifelse(subject == "as240304","as240303",
                          ifelse(subject == "ek240305","ek240304",
                                 ifelse(subject == "sg240305","sg240304",
                                        ifelse(subject == "qn240330","nq240330",subject))))) %>% 
  filter(subject %in% fmri3_subjects)

# fmri4_demographics <-  read_csv("../../data/fmri4/subjects_list/participant_log_fmri4.csv") %>% 
#               rename(subject = `subject id`)%>% 
#   filter(subject %in% fmri4_subjects)
```

```{r}
table(vrmid1_demographics$Sex)
table(fmri3_demographics$gender)
# table(fmri4_demographics$sex)

mosaic::fav_stats(as.numeric(vrmid1_demographics$Age),na.rm = T)
mosaic::fav_stats(as.numeric(fmri3_demographics$age),na.rm = T)
# mosaic::fav_stats(as.numeric(fmri4_demographics$age),na.rm = T)
```

# report behavioral performance 
## rt and hit rate
```{r}
vrmid1_beh_summary1<-vrmid1_beh_data %>% 
  group_by(Subject) %>% 
  summarise(hit_rate = mean(reaction_outcome == "Hit"),
            rt = mean(reaction_time,na.rm = T))

round(c(mean = mean(vrmid1_beh_summary1$hit_rate), sd = sd(vrmid1_beh_summary1$hit_rate)),2)
round(c(mean = mean(vrmid1_beh_summary1$rt), sd = sd(vrmid1_beh_summary1$rt))*1000,1)

fmri3_beh_summary1<-fmri3_beh_data %>% 
  group_by(subject) %>% 
  mutate(rt = ifelse(rt == -1, NA,rt)) %>% 
  summarise(hit_rate = mean(hit),
            rt = mean(rt,na.rm = T))

round(c(mean = mean(fmri3_beh_summary1$hit_rate), sd = sd(fmri3_beh_summary1$hit_rate)),2)
round(c(mean = mean(fmri3_beh_summary1$rt), sd = sd(fmri3_beh_summary1$rt))*1000,1)

# fmri4_beh_summary1<-fmri4_beh_data %>% 
#   group_by(subject) %>% 
#   mutate(rt = ifelse(rt == -1, NA,rt)) %>% 
#   summarise(hit_rate = mean(hit),
#             rt = mean(rt,na.rm = T))
# 
# round(c(mean = mean(fmri4_beh_summary1$hit_rate), sd = sd(fmri4_beh_summary1$hit_rate)),2)
# round(c(mean = mean(fmri4_beh_summary1$rt), sd = sd(fmri4_beh_summary1$rt))*1000,1)

vrmid1_beh_summary2<-vrmid1_beh_data %>% 
  group_by(Subject,trial_type,probe) %>% 
  summarise(hit_rate = mean(reaction_outcome == "Hit"),
            rt = mean(reaction_time,na.rm = T))

fmri3_beh_summary2<-fmri3_beh_data %>% 
  group_by(subject,cue_value,probe) %>% 
  mutate(rt = ifelse(rt == -1, NA,rt),
         probe = ifelse(probe == 1, "anti","out")) %>% 
  summarise(hit_rate = mean(hit),
            rt = mean(rt,na.rm = T))

# fmri4_beh_summary2<-fmri3_beh_data %>% 
#   group_by(subject,cue_value,probe) %>% 
#   mutate(rt = ifelse(rt == -1, NA,rt),
#          probe = ifelse(probe == 1, "anti","out")) %>% 
#   summarise(hit_rate = mean(hit),
#             rt = mean(rt,na.rm = T))

ggplot(vrmid1_beh_summary2,aes(x = trial_type, y = rt, color = trial_type))+
  geom_jitter(width = 0.1,alpha = 0.2, size = 0.5)+
  stat_summary(aes(fill = trial_type),shape = 21, color = "black")+
  scale_color_manual(values = redOrange_palette6)+
  scale_fill_manual(values = redOrange_palette6)+
  theme(legend.position = "none")+
  facet_wrap(~probe)+
  labs(y = "reaction time (sec)",
       x = "cue value",
       subtitle = "VR Study")+
ggplot(fmri3_beh_summary2,aes(x = cue_value, y = rt, color = cue_value))+
  geom_jitter(width = 0.1,alpha = 0.2, size = 0.5)+
  stat_summary(aes(fill = cue_value),shape = 21, color = "black")+
  scale_color_manual(values = redOrange_palette6)+
  scale_fill_manual(values = redOrange_palette6)+
  theme(legend.position = "none")+
  facet_wrap(~probe)+
  labs(y = "reaction time (sec)",
       x = "cue value",
       subtitle = "FMRI study")+
# ggplot(fmri4_beh_summary2,aes(x = cue_value, y = rt, color = cue_value))+
#   geom_jitter(width = 0.1,alpha = 0.2, size = 0.5)+
#   stat_summary(aes(fill = cue_value),shape = 21, color = "black")+
#   scale_color_manual(values = redOrange_palette6)+
#   scale_fill_manual(values = redOrange_palette6)+
#   theme(legend.position = "none")+
#   facet_wrap(~probe)+
#   labs(y = "reaction time (sec)",
#        x = "cue value",
#        subtitle = "FMRI validation sample")+
  plot_layout(nrow = 2)

ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/figx_beh.png"),dpi = 300, height = 5, width = 6)
```
## hit rate over time
```{r}
ggplot(vrmid1_beh_data %>% 
  group_by(Subject, trial_type) %>%
  mutate(hitrate = cummean(reaction_outcome == "Hit")) %>% 
  ungroup(),
  aes(x = trial, y = hitrate, color = Subject,
                          group = Subject))+
  geom_line()+
  scale_color_bluebrown()+
  # scale_color_manual(values = redOrange_palette6)+
  # scale_fill_manual(values = redOrange_palette6)+
  theme(legend.position = "none")+
  facet_wrap(~trial_type)+
  geom_hline(yintercept = 2/3, color = "red", linetype = "dashed")+
  labs(y = "hit rate",
       x = "trial id",
       subtitle = "VR study")+

ggplot(fmri3_beh_data %>% 
  group_by(subject, cue_value) %>%
  mutate(hitrate = cummean(hit == "Hit")) %>% 
  ungroup(),
  aes(x = trial, y = hitrate, color = subject,
                          group = subject))+
  geom_line()+
  scale_color_bluebrown()+
  # scale_color_manual(values = redOrange_palette6)+
  # scale_fill_manual(values = redOrange_palette6)+
  theme(legend.position = "none")+
  geom_hline(yintercept = 2/3, color = "red", linetype = "dashed")+
  facet_wrap(~cue_value)+
  labs(y = "hit rate",
       x = "trial id",
       subtitle = "FMRI study")+
# 
#   ggplot(fmri4_beh_data %>% 
#   group_by(subject, cue_value) %>%
#   mutate(hitrate = cummean(hit == 1)) %>% 
#   ungroup(),
#   aes(x = trial, y = hitrate, color = subject,
#                           group = subject))+
#   geom_line()+
#   scale_color_bluebrown()+
#   # scale_color_manual(values = redOrange_palette6)+
#   # scale_fill_manual(values = redOrange_palette6)+
#   theme(legend.position = "none")+
#   geom_hline(yintercept = 2/3, color = "red", linetype = "dashed")+
#   facet_wrap(~cue_value)+
#   labs(y = "hit rate",
#        x = "trial id",
#        subtitle = "Validation sample")+

ggplot(vrmid1_beh_data %>% 
  group_by(Subject) %>%
  mutate(hitrate = cummean(reaction_outcome == "Hit")) %>% 
  ungroup(),
  aes(x = trial, y = hitrate, color = Subject,
                          group = Subject))+
  geom_line()+
  scale_color_bluebrown()+
  # scale_color_manual(values = redOrange_palette6)+
  # scale_fill_manual(values = redOrange_palette6)+
  theme(legend.position = "none")+
  geom_hline(yintercept = 2/3, color = "red", linetype = "dashed")+
  labs(y = "hit rate",
       x = "trial id",
       subtitle = "VR study")+

ggplot(fmri3_beh_data %>% 
  group_by(subject) %>%
  mutate(hitrate = cummean(hit == "Hit")) %>% 
  ungroup(),
  aes(x = trial, y = hitrate, color = subject,
                          group = subject))+
  scale_color_bluebrown()+
  geom_line()+
  theme(legend.position = "none")+
  geom_hline(yintercept = 2/3, color = "red", linetype = "dashed")+
  labs(y = "hit rate",
       x = "trial id",
       subtitle = "FMRI study")+
# ggplot(fmri4_beh_data %>% 
#   group_by(subject) %>%
#   mutate(hitrate = cummean(hit == 1)) %>% 
#   ungroup(),
#   aes(x = trial, y = hitrate, color = subject,
#                           group = subject))+
#   scale_color_bluebrown()+
#   geom_line()+
#   theme(legend.position = "none")+
#   geom_hline(yintercept = 2/3, color = "red", linetype = "dashed")+
#   labs(y = "hit rate",
#        x = "trial id",
#        subtitle = "FMRI validation sample")+
plot_layout(nrow = 2, heights = c(2,1))+
  plot_annotation(tag_levels = "A")

ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/figxxx_beh.png"),dpi = 300, height = 6, width = 8)
```

## are people faster in rating valence or arousal? positive or negative?
```{r}
fmri3_beh_data %>% 
  group_by(subject) %>% 
  summarise(vrating_t = mean(vrating_t,na.rm=T),
            arating_t = mean(arating_t,na.rm=T)) %>% 
  ungroup() %>% 
  summarise(mean_valence_rt=mean(vrating_t),
         mean_arousal_rt=mean(arating_t))

summary(lmer(vrating ~ vrating_t + (1|subject),fmri3_beh_data))

summary(l1<-lmer(vrating_t ~ as.factor(vrating) + (1|subject) + (1|scaledir),
             fmri3_beh_data))
plot_model(l1, type = "pred", terms = "vrating")

summary(l2<-lmer(arating_t ~ as.factor(arating) + (1|subject) + (1|scaledir),
             fmri3_beh_data))
plot_model(l2, type = "pred", terms = "arating")

summary(l3<-lmer(erating_t ~ as.factor(erating) + (1|subject) + (1|scaledir),
             fmri3_beh_data))
plot_model(l3, type = "pred", terms = "erating")
```

# check left vs. right pupil correlation
```{r}
summary(l1<-lm(scale(pupil_L) ~ scale(pupil_R),vrmid1_pupil_data))
```

## define the time windows of interest
```{r}
vrmid1_ant_window = c(4,6)+1.5
fmri3_ant_window = c(2,4)+1.5

vrmid1_antprobe_out_window = c(15,17)+1.5
fmri3_antprobe_out_window = c(15,17)+1.5

vrmid1_outprobe_out_window = c(7,9)+1.5
fmri3_outprobe_out_window = c(5,7)+1.5
```
#plot time course
```{r}
rmarkdown::render("plot_timecourse.Rmd")
```

# pre-selected time window predicting affect

## calculate df
```{r}
vrmid1_data_antprobe <-  vrmid1_pupil_data%>%
  mutate(pupil_window = ifelse(sample_in_trial_t <= vrmid1_antprobe_out_window[2] & sample_in_trial_t > vrmid1_antprobe_out_window[1],
                               "out",
                               ifelse(sample_in_trial_t <= vrmid1_ant_window[2] & sample_in_trial_t > vrmid1_ant_window[1],
                                      "ant",NA)))%>%
  filter(probe == "anti", pupil_window %in% c("out","ant"))%>%
  ungroup()%>%
  group_by(probe,Subject,trial,reaction_outcome,trial_type,PosA_scaled,NegA_scaled,
           arousal,valence,pupil_window,last_ITI,
           arousal_scaled,valence_scaled,
           condition,reaction_time)%>%
  summarise(mean_pupil_bc = mean(pupil_Avg_bc_scaled, na.rm = T),
            mean_pupil_nobc = mean(pupil_Avg_scaled, na.rm = T),
            mean_pupil_baseline = mean(pupil_Avg_baseline_scaled, na.rm = T))%>%
  filter(abs(mean_pupil_bc) < 4,
         abs(mean_pupil_nobc) < 4,
         abs(mean_pupil_baseline) < 4)  %>% 
  pivot_wider(values_from = mean_pupil_bc:mean_pupil_baseline, names_from = pupil_window)%>%
  ungroup()%>%
  group_by(Subject)%>%
  mutate(log_rt = log(reaction_time),
         log_rt = as.numeric(scale(log_rt))) %>% 
  rowwise() %>% 
  mutate(trial_value = as.numeric(paste0(strsplit(as.character(trial_type), "\\$")[[1]][1],strsplit(as.character(trial_type), "\\$")[[1]][2]))) %>% 
  mutate(trial_outcome = ifelse(reaction_outcome == "Hit" & trial_value >= 0, trial_value,
                                ifelse(reaction_outcome == "Miss" & trial_value >= 0, 0,
                                       ifelse(reaction_outcome == "Hit" & trial_value < 0, 0,
                                              ifelse(reaction_outcome == "Miss" & trial_value < 0,trial_value))))) %>% 
  ungroup()

vrmid1_data_outprobe <-  vrmid1_pupil_data%>%
  mutate(pupil_window = ifelse(probe == "out" & sample_in_trial_t <= vrmid1_outprobe_out_window[2] & 
                                  sample_in_trial_t > vrmid1_outprobe_out_window[1],
                               "out",
                               ifelse(sample_in_trial_t <= vrmid1_ant_window[2] & 
                                        sample_in_trial_t > vrmid1_ant_window[1],
                                      "ant",NA)))%>%
  filter(probe == "out",pupil_window %in% c("out","ant"))%>% #probe == "out"
  ungroup()%>%
  group_by(probe,Subject,trial,trial_type,PosA_scaled,NegA_scaled,
           arousal,valence,pupil_window,last_ITI,
           arousal_scaled,valence_scaled,
           condition,reaction_outcome,reaction_time)%>%
  summarise(mean_pupil_bc = mean(pupil_Avg_bc_scaled, na.rm = T),
            mean_pupil_nobc = mean(pupil_Avg_scaled, na.rm = T),
            mean_pupil_baseline = mean(pupil_Avg_baseline_scaled, na.rm = T))%>%
  filter(abs(mean_pupil_bc) < 4,#this would remove trial 1 due to no baseline
         abs(mean_pupil_nobc) < 4, 
         abs(mean_pupil_baseline) < 4)  %>% 
  pivot_wider(values_from = mean_pupil_bc:mean_pupil_baseline, names_from = pupil_window)%>%
  ungroup()%>%
  group_by(Subject)%>%
  mutate(log_rt = log(reaction_time),
         log_rt = as.numeric(scale(log_rt)))%>% 
  rowwise() %>% 
  mutate(trial_value = as.numeric(paste0(strsplit(as.character(trial_type), "\\$")[[1]][1],strsplit(as.character(trial_type), "\\$")[[1]][2]))) %>% 
  mutate(trial_outcome = ifelse(reaction_outcome == "Hit" & trial_value >= 0, trial_value,
                                ifelse(reaction_outcome == "Miss" & trial_value >= 0, 0,
                                       ifelse(reaction_outcome == "Hit" & trial_value < 0, 0,
                                              ifelse(reaction_outcome == "Miss" & trial_value < 0,trial_value))))) %>% 
  ungroup()


fmri3_data_antprobe <-  fmri3_pupil_data%>%
  filter(!subject %in% c("tc240311","st240312")) %>% 
  mutate(pupil_window = ifelse(sample_in_trial_t <= fmri3_antprobe_out_window[2] & 
                                 sample_in_trial_t > fmri3_antprobe_out_window[1],
                               "out",
                               ifelse(sample_in_trial_t <= fmri3_ant_window[2] & 
                                        sample_in_trial_t > fmri3_ant_window[1],
                                      "ant",NA)))%>%
  filter(probe == 1, pupil_window %in% c("out","ant"))%>%
  ungroup()%>%
  group_by(subject) %>% 
  mutate(arousal_scaled = as.numeric(scale(arousal)),
         valence_scaled = as.numeric(scale(valence)))%>% 
  group_by(probe,subject,trial,hit,cue_value,emotion,emotion_cat,
           arousal,valence,pupil_window,rating_type,
           arousal_scaled,valence_scaled,cue_size,rt,iti,last_iti)%>%
  summarise(mean_pupil_bc_scaled = mean(pupilDiameter_bc_scaled, na.rm = T),
            mean_pupil_nobc_scaled= mean(pupilDiameter_scaled, na.rm = T),
            mean_pupil_baseline_scaled = mean(pupilDiameter_baseline_scaled, na.rm = T),
            mean_pupil_nobc_scaled_residual_conv = mean(residuals_conv,na.rm = T),
            luminance_mean = mean(luminance,na.rm = T),
            luminance_lag1_mean = mean(luminance_lag1,na.rm = T),
            luminance_convolved_mean = mean(convolved_s1,na.rm = T))%>%
  pivot_wider(values_from = c(mean_pupil_bc_scaled,mean_pupil_nobc_scaled,mean_pupil_nobc_scaled_residual_conv,luminance_mean,luminance_lag1_mean,luminance_convolved_mean), names_from = pupil_window)%>%
  ungroup()%>%
  group_by(subject)%>%
  mutate(log_rt = log(rt),
         log_rt = as.numeric(scale(log_rt)))%>% 
  rowwise() %>% 
  mutate(trial_value = as.numeric(paste0(strsplit(as.character(cue_value), "\\$")[[1]][1],strsplit(as.character(cue_value), "\\$")[[1]][2]))) %>% 
  mutate(trial_outcome = ifelse(hit == "Hit" & trial_value >= 0, trial_value,
                                ifelse(hit == "Miss" & trial_value >= 0, 0,
                                       ifelse(hit == "Hit" & trial_value < 0, 0,
                                              ifelse(hit == "Miss" & trial_value < 0,trial_value,NA))))) %>% 
  ungroup()

fmri3_data_outprobe <-  fmri3_pupil_data%>%
    filter(!subject %in% c("tc240311","st240312")) %>% 
  mutate(pupil_window = ifelse(probe == 2 & sample_in_trial_t <= fmri3_outprobe_out_window[2] 
                               & sample_in_trial_t > fmri3_outprobe_out_window[1],
                               "out",
                               ifelse(probe == 2 &  sample_in_trial_t <= fmri3_ant_window[2] 
                                      & sample_in_trial_t > fmri3_ant_window[1],
                                      "ant",NA)))%>%
  filter(probe == 2, pupil_window %in% c("out","ant"))%>%
  ungroup()%>%
  group_by(subject) %>% 
  mutate(arousal_scaled = as.numeric(scale(arousal)),
         valence_scaled = as.numeric(scale(valence)))%>% 
  group_by(probe,subject,trial,hit,cue_value,emotion,emotion_cat,
           arousal,valence,pupil_window,rating_type,
           arousal_scaled,valence_scaled,cue_size,rt,iti,last_iti)%>%
  summarise(mean_pupil_bc_scaled = mean(pupilDiameter_bc_scaled, na.rm = T),
            mean_pupil_nobc_scaled= mean(pupilDiameter_scaled, na.rm = T),
            mean_pupil_baseline_scaled = mean(pupilDiameter_baseline_scaled, na.rm = T),
            mean_pupil_nobc_scaled_residual_conv = mean(residuals_conv,na.rm = T),
            luminance_mean = mean(luminance,na.rm = T),
            luminance_lag1_mean = mean(luminance_lag1,na.rm = T),
            luminance_convolved_mean = mean(convolved_s1,na.rm = T))%>%
  pivot_wider(values_from = c(mean_pupil_bc_scaled,mean_pupil_nobc_scaled,mean_pupil_nobc_scaled_residual_conv,luminance_mean,luminance_lag1_mean,luminance_convolved_mean), names_from = pupil_window)%>%
  ungroup()%>%
  ungroup()%>%
  group_by(subject)%>%
  mutate(log_rt = log(rt),
         log_rt = as.numeric(scale(log_rt)))%>% 
  rowwise() %>% 
  mutate(trial_value = as.numeric(paste0(strsplit(as.character(cue_value), "\\$")[[1]][1],strsplit(as.character(cue_value), "\\$")[[1]][2]))) %>% 
  mutate(trial_outcome = ifelse(hit == "Hit" & trial_value >= 0, trial_value,
                                ifelse(hit == "Miss" & trial_value >= 0, 0,
                                       ifelse(hit == "Hit" & trial_value < 0, 0,
                                              ifelse(hit == "Miss" & trial_value < 0,trial_value,NA))))) %>%
  ungroup()
```


## combine two probe types
```{r}
vrmid1_data_2probes <- rbind(vrmid1_data_antprobe %>% 
                               select(probe:reaction_time,arousal,valence,trial_value,trial_outcome,
                                      mean_pupil_nobc_ant,mean_pupil_bc_ant,mean_pupil_baseline_ant,last_ITI) %>% 
                               rename(mean_pupil_nobc=mean_pupil_nobc_ant,
                                      mean_pupil_bc = mean_pupil_bc_ant,
                                      mean_pupil_baseline = mean_pupil_baseline_ant),
                             vrmid1_data_outprobe %>% 
                               select(probe:reaction_time,arousal,valence,trial_value,trial_outcome,mean_pupil_nobc_out,mean_pupil_bc_out,
                                      mean_pupil_baseline_ant,last_ITI) %>% 
                               rename(mean_pupil_nobc=mean_pupil_nobc_out,
                                      mean_pupil_bc = mean_pupil_bc_out,
                                      mean_pupil_baseline = mean_pupil_baseline_ant))

fmri3_data_2probes <- rbind(fmri3_data_antprobe %>% 
                               select(probe:rt,trial_value,trial_outcome,
                                      mean_pupil_nobc_scaled_ant,mean_pupil_bc_scaled_ant,mean_pupil_baseline_scaled,last_iti) %>% 
                               rename(mean_pupil_nobc=mean_pupil_nobc_scaled_ant,
                                      mean_pupil_bc = mean_pupil_bc_scaled_ant,
                                      mean_pupil_baseline = mean_pupil_baseline_scaled),
                             fmri3_data_outprobe %>% 
                               select(probe:rt,trial_value,trial_outcome,
                                      mean_pupil_nobc_scaled_out,mean_pupil_bc_scaled_out,mean_pupil_baseline_scaled,last_iti) %>% 
                               rename(mean_pupil_nobc=mean_pupil_nobc_scaled_out,
                                      mean_pupil_bc = mean_pupil_bc_scaled_out,
                                      mean_pupil_baseline = mean_pupil_baseline_scaled))

write_csv(vrmid1_data_2probes,"../../data/vrmid1/derivatives/vrmid1_data_2probes.csv")
write_csv(fmri3_data_2probes,"../../data/fmri3/derivatives/fmri3_data_2probes.csv")

summary(l1<-lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc) +(1|Subject) + (1|condition),
              vrmid1_data_2probes))

summary(l3<-lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc) +(1|subject) + (1|cue_size),
              fmri3_data_2probes))
```

### were ant and out pupil, tonic and phasic pupil correlated?
```{r}
#vrmid study 1
summary(lmer(scale(mean_pupil_bc_ant) ~  scale(mean_pupil_bc_out) +(1|Subject) + (1|condition) + (1|probe),
              rbind(vrmid1_data_antprobe,
                    vrmid1_data_outprobe)))

summary(lmer(scale(mean_pupil_baseline_ant) ~  scale(mean_pupil_bc_ant) +(1|Subject) + (1|condition) + (1|probe),
              rbind(vrmid1_data_antprobe,
                    vrmid1_data_outprobe)))

summary(lmer(scale(mean_pupil_baseline_ant) ~  scale(mean_pupil_bc_out) +(1|Subject) + (1|condition) + (1|probe),
              rbind(vrmid1_data_antprobe,
                    vrmid1_data_outprobe)))

#fmri study
summary(lmer(scale(mean_pupil_bc_scaled_ant) ~  scale(mean_pupil_bc_scaled_out) +(1|subject) + (1|cue_size) + (1|probe),
              rbind(fmri3_data_antprobe,
                    fmri3_data_outprobe)))

summary(lmer(scale(mean_pupil_baseline_scaled) ~  scale(mean_pupil_bc_scaled_ant) +(1|subject) + (1|cue_size) + (1|probe),
              rbind(fmri3_data_antprobe,
                    fmri3_data_outprobe)))

summary(lmer(scale(mean_pupil_baseline_scaled) ~  scale(mean_pupil_bc_scaled_out) +(1|subject) + (1|cue_size) + (1|probe),
              rbind(fmri3_data_antprobe,
                    fmri3_data_outprobe)))
```


# manipulation check for cue value and outcome
```{r}
rmarkdown::render("manipulation_check_cue.Rmd")
```

## calculate separate effect sizes for each study

### anticipation
```{r}
#vrmid1
da <- vrmid1_data_antprobe
summary(t <- lmer(scale(arousal_scaled) ~  scale(mean_pupil_baseline_ant) +(1|Subject) + (1|condition),
              da))
summary(p <-lmer(scale(arousal_scaled) ~  scale(mean_pupil_bc_ant) +(1|Subject) + (1|condition),
              da))
summary(tp <- lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc_ant) +(1|Subject) + (1|condition),
              da))
anova(t,p,tp)

v1a<- c(round(r.squaredGLMM(t)*100,2),
round(r.squaredGLMM(p)*100,2),
round(r.squaredGLMM(tp)*100,2),
t(EMAtools::lme.dscore(t,da,"lme4")),
t(EMAtools::lme.dscore(p,da,"lme4")),
t(EMAtools::lme.dscore(tp,da,"lme4")))


# fit random slope as comparison
summary(lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc_ant) +(1+scale(mean_pupil_nobc_ant)|Subject) + (1|condition),
              da))

# fit random intercept for cue_value
summary(lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc_ant) +(1+scale(mean_pupil_nobc_ant)|Subject) + (1|condition)
             + (1|trial_type),
              da))
```


```{r}
#fmri3
da <- fmri3_data_antprobe
t <- lmer(scale(arousal_scaled) ~  scale(mean_pupil_baseline_scaled) +(1|subject) + (1|cue_size),
              da)
summary(t)
p <-lmer(scale(arousal_scaled) ~  scale(mean_pupil_bc_scaled_ant) +(1|subject) + (1|cue_size),
              da)
summary(p)
tp <- lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc_scaled_ant) +(1|subject) + (1|cue_size),
              da)
summary(tp)
tp_res_conv <- lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc_scaled_residual_conv_ant) +(1|subject) + (1|cue_size),
              da)
summary(tp_res_conv)
anova(tp,tp_res_conv)

v3a<- c(round(r.squaredGLMM(t)*100,2),
round(r.squaredGLMM(p)*100,2),
round(r.squaredGLMM(tp)*100,2),
t(EMAtools::lme.dscore(t,da,"lme4")),
t(EMAtools::lme.dscore(p,da,"lme4")),
t(EMAtools::lme.dscore(tp,da,"lme4")))

# fit random slope as comparison
summary(lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc_scaled_ant) +(1+scale(mean_pupil_nobc_scaled_ant)|subject) + (1|cue_size),da))

# fit random intercept for cue_value
summary(lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc_scaled_ant) +(1|subject) + (1|cue_size)
             + (1|cue_value),
              da))
```

### outcome

```{r}
#vrmid1
do <- vrmid1_data_outprobe
t <- lmer(scale(arousal_scaled) ~  scale(mean_pupil_baseline_out) +(1|Subject) + (1|condition),
              do)
summary(t)
p <-lmer(scale(arousal_scaled) ~  scale(mean_pupil_bc_out) +(1|Subject) + (1|condition),
              do)
summary(p)
tp <- lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc_out) +(1|Subject) + (1|condition),
              do)
summary(tp)
anova(t,p,tp)

v1o<- c(round(r.squaredGLMM(t)*100,2),
round(r.squaredGLMM(p)*100,2),
round(r.squaredGLMM(tp)*100,2),
t(EMAtools::lme.dscore(t,do,"lme4")),
t(EMAtools::lme.dscore(p,do,"lme4")),
t(EMAtools::lme.dscore(tp,do,"lme4")))

summary(lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc_out) +(1+scale(mean_pupil_nobc_out)|Subject) + (1|condition),
              do))

# fit random intercept for cue_value
summary(lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc_out) +(1|Subject) + (1|condition) + (1|trial_type),
              do))
```

```{r}
#fmri3
do <- fmri3_data_outprobe
t <- lmer(scale(arousal_scaled) ~  scale(mean_pupil_baseline_scaled) +(1|subject) + (1|cue_size),
              do)
summary(t)
p <-lmer(scale(arousal_scaled) ~  scale(mean_pupil_bc_scaled_out) +(1|subject) + (1|cue_size),
              do)
summary(p)
tp <- lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc_scaled_out)+(1|subject) + (1|cue_size),
              do)
summary(tp)
tp_res_conv <- lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc_scaled_residual_conv_out) +(1|subject) + (1|cue_size),
              do)
summary(tp_res_conv)
anova(tp,tp_res_conv)

# anova(t,p,tp)

v3o<- c(round(r.squaredGLMM(t)*100,2),
round(r.squaredGLMM(p)*100,2),
round(r.squaredGLMM(tp)*100,2),
t(EMAtools::lme.dscore(t,do,"lme4")),
t(EMAtools::lme.dscore(p,do,"lme4")),
t(EMAtools::lme.dscore(tp,do,"lme4")))


summary(lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc_scaled_out)+(1+scale(mean_pupil_nobc_scaled_out)|subject) + (1|cue_size),
              do))

summary(lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc_scaled_out)+(1|subject) + (1|cue_size) + (1|cue_value),
              do))

# what about tonic * phasic interaction?
r.squaredGLMM(lmer(scale(arousal_scaled) ~  scale(mean_pupil_bc_scaled_out) * scale(mean_pupil_baseline_scaled)+(1|subject) + (1|cue_size),
              do))
r.squaredGLMM(tp)
```



```{r}
r2list <- as.data.frame(Reduce(rbind,list(v1a,v3a,v1o,v3o)))
names(r2list) <- c(paste0(c("R2m","R2c","R2m","R2c"),"_",c("tonic","tonic","phasic","phasic","t+p","t+p")),
                   paste0(c("t","df","d","t","df","d"),"_",c("tonic","tonic","tonic","phasic","phasic","phasic","t+p","t+p","t+p"))) 

r2list$study <- c("VR1",'FMRI3',"VR1",'FMRI3')

r2list$probe <- c("anticipation","anticipation","outcome","outcome")

r2list<-remove_rownames(r2list) %>% 
  relocate(study, probe)

r2list_long <- r2list %>% 
  pivot_longer(R2m_tonic:`d_t+p`,names_to = c("measure","dataType"),values_to = "value", names_sep = "_") %>% 
  pivot_wider(names_from = dataType, values_from = "value") %>% 
  filter(measure %in% c("R2m","t","d"))

r2list_long %>% 
  arrange(probe,measure) %>% 
  kable(digits = 2) %>% 
  kable_styling()%>%
  save_kable(file = "../../data/r2.html", self_contained = T)
```

### both probes
```{r}
#vrmid1
summary(t <- lmer(scale(arousal_scaled) ~  scale(mean_pupil_baseline) +(1|Subject) + (1|condition) + (1|probe),
              vrmid1_data_2probes))
summary(p <-lmer(scale(arousal_scaled) ~  scale(mean_pupil_bc) +(1|Subject) + (1|condition)+ (1|probe),
              vrmid1_data_2probes))
summary(tp <- lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc) +(1|Subject) + (1|condition)+ (1|probe),
              vrmid1_data_2probes))
anova(t,p,tp)

rbind(round(r.squaredGLMM(t)*100,2),
round(r.squaredGLMM(p)*100,2),
round(r.squaredGLMM(tp)*100,2))

```

```{r}
#fmri3
summary(t <- lmer(scale(arousal_scaled) ~  scale(mean_pupil_baseline) +(1|subject) + (1|cue_size)+ (1|probe),
              fmri3_data_2probes))
summary(p <-lmer(scale(arousal_scaled) ~  scale(mean_pupil_bc) +(1|subject) + (1|cue_size)+ (1|probe),
              fmri3_data_2probes))
summary(tp <- lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc) +(1|subject) + (1|cue_size)+ (1|probe),
              fmri3_data_2probes))


rbind(round(r.squaredGLMM(t)*100,2),
round(r.squaredGLMM(p)*100,2),
round(r.squaredGLMM(tp)*100,2))

```


### make figures (all studies and probes)
```{r}
l1a<-lmer(arousal_scaled ~  mean_pupil_nobc_ant + (1|Subject) + (1|condition),vrmid1_data_antprobe)
l1b<-lmer(valence_scaled ~  mean_pupil_nobc_ant + (1|Subject) + (1|condition),vrmid1_data_antprobe)
l1c<-lmer(arousal_scaled ~  mean_pupil_nobc_out + (1|Subject) + (1|condition),vrmid1_data_outprobe)
l1d<-lmer(valence_scaled ~  mean_pupil_nobc_out + (1|Subject) + (1|condition),vrmid1_data_outprobe)

p1a<-plot_model(l1a, type = "pred", terms = "mean_pupil_nobc_ant",
           show.data = T, dot.size = 0.5, color = 'orange')+
  labs(y = "z-scored arousal rating", x = "z-scored phasic pupil size \n(non baseline-corrected)",
       title = "VR study",subtitle = "anticipation probe")

p1b<-plot_model(l1b, type = "pred", terms = "mean_pupil_nobc_ant",
           show.data = T, dot.size = 0.5, color = 'orange')+
  labs(y = "z-scored valence rating", x = "z-scored phasic pupil size \n(non baseline-corrected)",
       title = "VR Study",subtitle = "anticipation probe")

p1c<-plot_model(l1c, type = "pred", terms = "mean_pupil_nobc_out",
           show.data = T, dot.size = 0.5, color = 'orange')+
  labs(y = "z-scored arousal rating", x = "z-scored phasic pupil size \n(non baseline-corrected)",
       title = "VR Study",subtitle = "outcome probe")

p1d<-plot_model(l1d, type = "pred", terms = "mean_pupil_nobc_out",
           show.data = T, dot.size = 0.5, color = 'orange')+
  labs(y = "z-scored valence rating", x = "z-scored phasic pupil size \n(non baseline-corrected)",
       title = "VR Study",subtitle = "outcome probe")

l3a<-lmer(arousal_scaled ~  mean_pupil_nobc_scaled_ant + (1|subject) + (1|cue_size),fmri3_data_antprobe)
l3b<-lmer(valence_scaled ~  mean_pupil_nobc_scaled_ant + (1|subject) + (1|cue_size),fmri3_data_antprobe)
l3c<-lmer(arousal_scaled ~  mean_pupil_nobc_scaled_out + (1|subject) + (1|cue_size),fmri3_data_outprobe)
l3d<-lmer(valence_scaled ~  mean_pupil_nobc_scaled_out + (1|subject) + (1|cue_size),fmri3_data_outprobe)

p3a<-plot_model(l3a, type = "pred", terms = "mean_pupil_nobc_scaled_ant",
           show.data = T, dot.size = 0.5, color = 'orange')+
  labs(y = "z-scored arousal rating", x = "z-scored phasic pupil size \n(non baseline-corrected)",
       title = "FMRI study",subtitle = "anticipation probe")

p3b<-plot_model(l3b, type = "pred", terms = "mean_pupil_nobc_scaled_ant",
           show.data = T, dot.size = 0.5, color = 'orange')+
  labs(y = "z-scored valence rating", x = "z-scored phasic pupil size \n(non baseline-corrected)",
       title = "FMRI study",subtitle = "anticipation probe")

p3c<-plot_model(l3c, type = "pred", terms = "mean_pupil_nobc_scaled_out",
           show.data = T, dot.size = 0.5, color = 'orange')+
  labs(y = "z-scored arousal rating", x = "z-scored phasic pupil size \n(non baseline-corrected)",
       title = "FMRI study",subtitle = "outcome probe")

p3d<-plot_model(l3d, type = "pred", terms = "mean_pupil_nobc_scaled_out",
           show.data = T, dot.size = 0.5, color = 'orange')+
  labs(y = "z-scored valence rating", x = "z-scored phasic pupil size \n(non baseline-corrected)",
       title = "FMRI study",subtitle = "outcome probe")

p1a+p1b+p1c+p1d+
  p3a+p3b+p3c+p3d+
  plot_layout(nrow = 2)
ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig4_scatter.png"),dpi = 300, height = 6, width = 8)
```

## pool the effect sizes and make summary plots
```{r}
data_antprobe <- Reduce(rbind,list(vrmid1_data_antprobe %>% select(Subject,trial,trial_type,condition,arousal_scaled,valence_scaled,mean_pupil_nobc_ant) %>% 
                                     mutate(study="VRStudy"),
                              fmri3_data_antprobe %>%
                                filter(rating_type == 1) %>% 
                                select(subject,trial,cue_value,cue_size,arousal_scaled,
                                       valence_scaled,mean_pupil_nobc_scaled_ant) %>% 
                                rename(Subject = subject,trial_type = cue_value,condition= cue_size,mean_pupil_nobc_ant=mean_pupil_nobc_scaled_ant)%>% 
                                     mutate(study="FMRIStudy")))

summary(l1<-lmer(arousal_scaled ~  mean_pupil_nobc_ant + (1|Subject/study) + (1|condition) + (mean_pupil_nobc_ant|study),data_antprobe))
summary(lmer(arousal_scaled ~  mean_pupil_nobc_ant + (1|trial_type)  + (1|Subject/study) + (1|condition),data_antprobe))

summary(lmer(arousal_scaled ~  mean_pupil_nobc_ant  + (1+mean_pupil_nobc_ant|Subject/study) + (1|condition),data_antprobe))

fixed_effects <- ggpredict(l1)$mean_pupil_nobc_ant
# Extract random effects
combined_effects <- ranef(l1)$study
combined_effects$`(Intercept)` <- combined_effects$`(Intercept)`+summary(l1)$coefficient[1,1]
combined_effects$mean_pupil_nobc_ant <- combined_effects$mean_pupil_nobc_ant+summary(l1)$coefficient[2,1]

random_slopes_df <- data.frame(
  study = rownames(combined_effects),
  slope = combined_effects[, "mean_pupil_nobc_ant"],
  intercept = combined_effects[, "(Intercept)" ]
)

x_values <- seq(-5, 5, length.out = 100)
# Calculate y values for each study
df_plot <- do.call(rbind, lapply(1:nrow(random_slopes_df), function(i) {
  data.frame(
    x = x_values,
    y = random_slopes_df$slope[i] * x_values + random_slopes_df$intercept[i],
    study = random_slopes_df$study[i]
  )
}))

# Plot the regression lines
p1<-ggplot() +
  geom_point(data=data_antprobe, aes(x = mean_pupil_nobc_ant, y = arousal_scaled, color = study),
            size = 0.5, alpha = 0.4) +
  geom_line(data=df_plot, aes(x = x, y = y, color = study),
            size = 2) +
  geom_line(data = fixed_effects, aes(x = x, y = predicted),
            color = "black",size = 2,alpha = 0.7, linetype = "dashed")+
  geom_ribbon(data = fixed_effects, aes(x = x, y = predicted,
                                        ymin = conf.low,
                                        ymax = conf.high),
            color = "black",alpha = 0.1)+
  labs(title = "Anticipation arousal", 
       x = "z-scored phasic pupil size \n(non baseline-corrected)", 
       y = "z-scored arousal rating")+
  scale_color_brewer(palette = "Dark2")+
  xlim(range(data_antprobe$mean_pupil_nobc_ant,na.rm = T))+
  xlim(range(data_antprobe$arousal_scaled,na.rm = T))+
  theme(legend.position = "left")+
  ylim(-3.5,3.5)+
  xlim(-5,5)

summary(l1<-lmer(valence_scaled ~  mean_pupil_nobc_ant + (1|Subject/study) + (1|condition) + (mean_pupil_nobc_ant|study),data_antprobe))

fixed_effects <- ggpredict(l1)$mean_pupil_nobc_ant
# Extract random effects
combined_effects <- ranef(l1)$study
combined_effects$`(Intercept)` <- combined_effects$`(Intercept)`+summary(l1)$coefficient[1,1]
combined_effects$mean_pupil_nobc_ant <- combined_effects$mean_pupil_nobc_ant+summary(l1)$coefficient[2,1]

random_slopes_df <- data.frame(
  study = rownames(combined_effects),
  slope = combined_effects[, "mean_pupil_nobc_ant"],
  intercept = combined_effects[, "(Intercept)" ]
)

x_values <- seq(-5, 5, length.out = 100)
# Calculate y values for each study
df_plot <- do.call(rbind, lapply(1:nrow(random_slopes_df), function(i) {
  data.frame(
    x = x_values,
    y = random_slopes_df$slope[i] * x_values + random_slopes_df$intercept[i],
    study = random_slopes_df$study[i]
  )
}))

# Plot the regression lines
p2<-ggplot() +
  geom_point(data=data_antprobe, aes(x = mean_pupil_nobc_ant, y = valence_scaled, color = study),
            size = 0.5, alpha = 0.4) +
  geom_line(data=df_plot, aes(x = x, y = y, color = study),
            size = 2) +
  geom_line(data = fixed_effects, aes(x = x, y = predicted),
            color = "black",size = 2,alpha = 0.7, linetype = "dashed")+
  geom_ribbon(data = fixed_effects, aes(x = x, y = predicted,
                                        ymin = conf.low,
                                        ymax = conf.high),
            color = "black",alpha = 0.1)+
  labs(title = "Anticipation valence", 
       x = "z-scored phasic pupil size \n(non baseline-corrected)", 
       y = "z-scored valence rating")+
  scale_color_brewer(palette = "Dark2")+
  xlim(range(data_antprobe$mean_pupil_nobc_ant,na.rm = T))+
  xlim(range(data_antprobe$arousal_scaled,na.rm = T))+
  theme(legend.position = "none")+
  ylim(-3.5,3.5)+
  xlim(-5,5)

data_outprobe <- Reduce(rbind,list(vrmid1_data_outprobe %>%
                                     select(Subject,trial,condition,
                                            arousal_scaled,valence_scaled,mean_pupil_nobc_out) %>% 
                                     mutate(study="VRStudy"),
                              fmri3_data_outprobe %>%
                                filter(rating_type == 1) %>% 
                                select(subject,trial,cue_size,arousal_scaled,valence_scaled,
                                                              mean_pupil_nobc_scaled_out) %>% 
                                rename(Subject = subject,condition= cue_size,mean_pupil_nobc_out=mean_pupil_nobc_scaled_out)%>% 
                                     mutate(study="FMRIStudy"))) %>% 
  ungroup()

summary(l1<-lmer(arousal_scaled ~  mean_pupil_nobc_out + (1|Subject/study) + (1|condition)+ (mean_pupil_nobc_out|study),data_outprobe))
summary(lmer(arousal_scaled ~  mean_pupil_nobc_out  + (1+mean_pupil_nobc_out|Subject/study) + (1|condition),data_outprobe))

fixed_effects <- ggpredict(l1)$mean_pupil_nobc_out
# Extract random effects
combined_effects <- ranef(l1)$study
combined_effects$`(Intercept)` <- combined_effects$`(Intercept)`+summary(l1)$coefficient[1,1]
combined_effects$mean_pupil_nobc_out <- combined_effects$mean_pupil_nobc_out+summary(l1)$coefficient[2,1]

random_slopes_df <- data.frame(
  study = rownames(combined_effects),
  slope = combined_effects[, "mean_pupil_nobc_out"],
  intercept = combined_effects[, "(Intercept)" ]
)

x_values <- seq(-5, 5, length.out = 100)
# Calculate y values for each study
df_plot <- do.call(rbind, lapply(1:nrow(random_slopes_df), function(i) {
  data.frame(
    x = x_values,
    y = random_slopes_df$slope[i] * x_values + random_slopes_df$intercept[i],
    study = random_slopes_df$study[i]
  )
}))

# Plot the regression lines
p3<-ggplot() +
  geom_point(data=data_outprobe, aes(x = mean_pupil_nobc_out, y = arousal_scaled, color = study),
            size = 0.5, alpha = 0.4) +
geom_line(data=df_plot, aes(x = x, y = y, color = study),
            size = 2) +
  geom_line(data = fixed_effects, aes(x = x, y = predicted),
            color = "black",size = 2,alpha = 0.7, linetype = "dashed")+
  geom_ribbon(data = fixed_effects, aes(x = x, y = predicted,
                                        ymin = conf.low,
                                        ymax = conf.high),
            color = "black",alpha = 0.1)+
  labs(title = "Outcome arousal", 
       x = "z-scored phasic pupil size \n(non baseline-corrected)", 
       y = "z-scored arousal rating")+
  scale_color_brewer(palette = "Dark2")+
  xlim(range(data_antprobe$mean_pupil_nobc_ant,na.rm = T))+
  xlim(range(data_antprobe$arousal_scaled,na.rm = T))+
  theme(legend.position = "none")+
  ylim(-3.5,3.5)+
  xlim(-5,5)

summary(l1<-lmer(valence_scaled ~  mean_pupil_nobc_out + (1|Subject/study) + (1|condition)+ (mean_pupil_nobc_out|study),data_outprobe))
fixed_effects <- ggpredict(l1)$mean_pupil_nobc_out
# Extract random effects
combined_effects <- ranef(l1)$study
combined_effects$`(Intercept)` <- combined_effects$`(Intercept)`+summary(l1)$coefficient[1,1]
combined_effects$mean_pupil_nobc_out <- combined_effects$mean_pupil_nobc_out+summary(l1)$coefficient[2,1]

random_slopes_df <- data.frame(
  study = rownames(combined_effects),
  slope = combined_effects[, "mean_pupil_nobc_out"],
  intercept = combined_effects[, "(Intercept)" ]
)

x_values <- seq(-5, 5, length.out = 100)
# Calculate y values for each study
df_plot <- do.call(rbind, lapply(1:nrow(random_slopes_df), function(i) {
  data.frame(
    x = x_values,
    y = random_slopes_df$slope[i] * x_values + random_slopes_df$intercept[i],
    study = random_slopes_df$study[i]
  )
}))

# Plot the regression lines
p4<-ggplot() +
  geom_point(data=data_outprobe, aes(x = mean_pupil_nobc_out, y = valence_scaled, color = study),
            size = 0.5, alpha = 0.4) +
geom_line(data=df_plot, aes(x = x, y = y, color = study),
            size = 2) +
  geom_line(data = fixed_effects, aes(x = x, y = predicted),
            color = "black",size = 2,alpha = 0.7, linetype = "dashed")+
  geom_ribbon(data = fixed_effects, aes(x = x, y = predicted,
                                        ymin = conf.low,
                                        ymax = conf.high),
            color = "black",alpha = 0.1)+
  labs(title = "Outcome valence", 
       x = "z-scored phasic pupil size \n(non baseline-corrected)", 
       y = "z-scored arousal rating")+
  scale_color_brewer(palette = "Dark2")+
  xlim(range(data_antprobe$mean_pupil_nobc_ant,na.rm = T))+
  xlim(range(data_antprobe$arousal_scaled,na.rm = T))+
  theme(legend.position = "none")+
  ylim(-3.5,3.5)+
  xlim(-5,5)

p1+p3+p2+p4+plot_layout(nrow = 2)
ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig4_pooled_effects.tiff"),dpi = 300, height = 6, width = 8)
ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig4_pooled_effects.png"),dpi = 300, height = 6, width = 8)
```

# behavioral implications of pupil-linked arousal
## fatigue: visualise tonic activity over time
```{r}
vrmid1_pupil_data_tonic <- vrmid1_pupil_data%>%
  filter(Time_sec >= vrmid1_ant_window[1], Time_sec <= vrmid1_ant_window[2])%>% 
  select(Subject,probe,condition,trial,pupil_Avg_baseline_scaled,pupil_Avg_bc_scaled,pupil_Avg_scaled,
         last_ITI,arousal_scaled,valence_scaled,reaction_outcome)%>%
  group_by(Subject,trial,probe,condition,
         arousal_scaled,valence_scaled,reaction_outcome)%>%
  summarise(pupil_Avg_baseline_scaled = mean(pupil_Avg_baseline_scaled,na.rm = T),
                   pupil_Avg_bc_scaled = mean(pupil_Avg_bc_scaled,na.rm=T),
            pupil_Avg_scaled = mean(pupil_Avg_scaled, na.rm = T)) %>% 
  mutate(hit = (reaction_outcome == "Hit"))%>%
  ungroup() %>% 
  group_by(Subject) %>% 
  mutate(half = ifelse(trial >= 48,"second","first"),
         hit = zoo::rollmean(hit, k = 5, align = "right", fill = NA)
  )

vrmid1_pupil_data_phasicarousal <- vrmid1_pupil_data%>%
  mutate(half = ifelse(trial >= 48,"second","first"))%>%
  select(Subject,probe,trial,half,
         last_ITI,arousal_scaled,valence_scaled,
         trial_type,reaction_outcome)%>%
  group_by(Subject,trial,trial_type,
         arousal_scaled,valence_scaled)%>%
  mutate(rowid = row_number(),
         hit = (reaction_outcome == "Hit")) %>% 
  filter(rowid == 1) %>% 
  ungroup() %>% 
  group_by(Subject,half) %>% 
  mutate(hit_rate = mean(hit)) %>% 
  group_by(Subject,half,trial_type,hit_rate)%>%
  summarise(arousal_scaled = mean(arousal_scaled,na.rm = T)) %>% 
  pivot_wider(names_from = trial_type, values_from = arousal_scaled) %>% 
  mutate(plus5_plus0 = `+$5` - `+$0`,
         minus5_minus0 = `-$5` - `-$0`,
         five_vs_zero = (plus5_plus0+minus5_minus0)/2)
  
summary(l1<-lmer(scale(pupil_Avg_baseline_scaled) ~ scale(trial)+scale(hit) + (1+scale(trial)+scale(hit)|Subject),vrmid1_pupil_data_tonic))

mytext=summary(l1)$coefficients

mytext = ifelse(mytext[2,5] >= 0.05, "n.s.",
                ifelse(mytext[2,5] >= 0.01, "*",
                       ifelse(mytext[2,5] >= 0.001, "**","***")))

# Extract random effects (BLUPs) for each participant
# Extract fixed and random effects from model
fixed_eff  <- fixef(l1)["scale(trial)"]
rand_eff   <- ranef(l1)$Subject[,"scale(trial)"]

# Combine into dataframe
df_slopes <- data.frame(Subject = rownames(ranef(l1)$Subject),
                        slope_trial = fixed_eff + rand_eff)

# Prepare trial values (use your observed range)
trial_seq <- 1:96

# Build dataframe of all predicted lines
df_lines <- do.call(rbind, lapply(unique(df_slopes$Subject), function(subj){
  intercept <- fixef(l1)[1] + ranef(l1)$Subject[subj,"(Intercept)"]
  slope     <- df_slopes[df_slopes$Subject == subj, "slope_trial"]
  
  data.frame(
    Subject = subj,
    trial   = trial_seq,
    pred    = intercept + slope * scale(trial_seq))
}))

df_lines2 <- data.frame(
    trial   = trial_seq,
    pred    = fixef(l1)[1] + fixed_eff * scale(trial_seq))

pt11 <- ggplot(data = df_lines) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  # add model-predicted lines
  geom_line(
            aes(x = trial, y = pred, group = Subject),
            color = "grey", alpha = 0.4, size = 0.4) +
  stat_summary(data = df_lines2,aes(x = trial, y = pred, group=1),
               size =1, geom = "line")+
  labs(y = "z-scored pupil",
       subtitle = "VR study",
       title = "Tonic pupil") +
  annotate("text", x = 48, y = 1, label = mytext)+
  scale_x_continuous(breaks = c(1,24,48,72,96))

summary(l1<-lmer(scale(pupil_Avg_bc_scaled) ~ scale(trial)+scale(hit) + (1+scale(trial)+scale(hit)|Subject),vrmid1_pupil_data_tonic))

mytext=summary(l1)$coefficients

mytext = ifelse(mytext[2,5] >= 0.05, "n.s.",
                ifelse(mytext[2,5] >= 0.01, "*",
                       ifelse(mytext[2,5] >= 0.001, "**","***")))

# Extract random effects (BLUPs) for each participant
# Extract fixed and random effects from model
fixed_eff  <- fixef(l1)["scale(trial)"]
rand_eff   <- ranef(l1)$Subject[,"scale(trial)"]

# Combine into dataframe
df_slopes <- data.frame(Subject = rownames(ranef(l1)$Subject),
                        slope_trial = fixed_eff + rand_eff)

# Prepare trial values (use your observed range)
trial_seq <- 1:96

# Build dataframe of all predicted lines
df_lines <- do.call(rbind, lapply(unique(df_slopes$Subject), function(subj){
  intercept <- fixef(l1)[1] + ranef(l1)$Subject[subj,"(Intercept)"]
  slope     <- df_slopes[df_slopes$Subject == subj, "slope_trial"]
  
  data.frame(
    Subject = subj,
    trial   = trial_seq,
    pred    = intercept + slope * scale(trial_seq))
}))


df_lines2 <- data.frame(
    trial   = trial_seq,
    pred    = fixef(l1)[1] + fixed_eff * scale(trial_seq))

pt12 <- ggplot(data = df_lines) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  # add model-predicted lines
  geom_line(aes(x = trial, y = pred, group = Subject),
            color = "grey", alpha = 0.4, size = 0.4) +
  stat_summary(data = df_lines2,aes(x = trial, y = pred, group=1),
               size =1, geom = "line")+
  labs(y = "z-scored pupil",
       subtitle = "VR study",
       title = "Corrected phasic pupil") +
  annotate("text", x = 48, y = 1, label = mytext)+
  scale_x_continuous(breaks = c(1,24,48,72,96))

summary(l1<-lmer(scale(arousal_scaled) ~ scale(trial)+scale(hit) + (1+scale(trial)+scale(hit)|Subject),vrmid1_pupil_data_tonic))

mytext=summary(l1)$coefficients

mytext = ifelse(mytext[2,5] >= 0.05, "n.s.",
                ifelse(mytext[2,5] >= 0.01, "*",
                       ifelse(mytext[2,5] >= 0.001, "**","***")))

# Extract random effects (BLUPs) for each participant
# Extract fixed and random effects from model
fixed_eff  <- fixef(l1)["scale(trial)"]
rand_eff   <- ranef(l1)$Subject[,"scale(trial)"]

# Combine into dataframe
df_slopes <- data.frame(Subject = rownames(ranef(l1)$Subject),
                        slope_trial = fixed_eff + rand_eff)

# Prepare trial values (use your observed range)
trial_seq <- 1:96

# Build dataframe of all predicted lines
df_lines <- do.call(rbind, lapply(unique(df_slopes$Subject), function(subj){
  intercept <- fixef(l1)[1] + ranef(l1)$Subject[subj,"(Intercept)"]
  slope     <- df_slopes[df_slopes$Subject == subj, "slope_trial"]
  
  data.frame(
    Subject = subj,
    trial   = trial_seq,
    pred    = intercept + slope * scale(trial_seq))
}))

df_lines2 <- data.frame(
    trial   = trial_seq,
    pred    = fixef(l1)[1] + fixed_eff * scale(trial_seq))

pt13 <- ggplot(data = df_lines) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  # add model-predicted lines
  geom_line(
            aes(x = trial, y = pred, group = Subject),
            color = "grey", alpha = 0.4, size = 0.4) +
  stat_summary(data = df_lines2,aes(x = trial, y = pred, group=1),
               size =1, geom = "line")+
  labs(y = "z-scored pupil",
       title = "VR Study",
       subtitle = "Mean reported arousal") +
  annotate("text", x = 48, y = 0.5, label = mytext)+
  scale_x_continuous(breaks = c(1,24,48,72,96))

summary(l1<-lmer(scale(valence_scaled) ~ scale(trial)+scale(hit) + (1+scale(trial)+scale(hit)|Subject),vrmid1_pupil_data_tonic))

mytext=summary(l1)$coefficients

mytext = ifelse(mytext[2,5] >= 0.05, "n.s.",
                ifelse(mytext[2,5] >= 0.01, "*",
                       ifelse(mytext[2,5] >= 0.001, "**","***")))

# Extract random effects (BLUPs) for each participant
# Extract fixed and random effects from model
fixed_eff  <- fixef(l1)["scale(trial)"]
rand_eff   <- ranef(l1)$Subject[,"scale(trial)"]

# Combine into dataframe
df_slopes <- data.frame(Subject = rownames(ranef(l1)$Subject),
                        slope_trial = fixed_eff + rand_eff)

# Prepare trial values (use your observed range)
trial_seq <- 1:96

# Build dataframe of all predicted lines
df_lines <- do.call(rbind, lapply(unique(df_slopes$Subject), function(subj){
  intercept <- fixef(l1)[1] + ranef(l1)$Subject[subj,"(Intercept)"]
  slope     <- df_slopes[df_slopes$Subject == subj, "slope_trial"]
  
  data.frame(
    Subject = subj,
    trial   = trial_seq,
    pred    = intercept + slope * scale(trial_seq))
}))

df_lines2 <- data.frame(
    trial   = trial_seq,
    pred    = fixef(l1)[1] + fixed_eff * scale(trial_seq))

pt14 <- ggplot(data = df_lines) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  # add model-predicted lines
  geom_line(
            aes(x = trial, y = pred, group = Subject),
            color = "grey", alpha = 0.4, size = 0.4) +
  stat_summary(data = df_lines2,aes(x = trial, y = pred, group=1),
               size =1, geom = "line")+
  labs(y = "z-scored pupil",
       title = "VR Study",
       subtitle = "Mean reported valence") +
  annotate("text", x = 48, y = 0.5, label = mytext)+
  scale_x_continuous(breaks = c(1,24,48,72,96))

summary(lmer(scale(five_vs_zero) ~ half + scale(hit_rate) +  (1|Subject),
             vrmid1_pupil_data_phasicarousal))
mytext=summary(lmer(scale(five_vs_zero) ~ half +hit_rate +  (1|Subject),vrmid1_pupil_data_phasicarousal))$coefficients
mytext = ifelse(mytext[2,5] >= 0.05, "n.s.",
                ifelse(mytext[2,5] >= 0.01, "*",
                       ifelse(mytext[2,5] >= 0.001, "**","***")))
pt15 <- ggplot(vrmid1_pupil_data_phasicarousal)+
  geom_hline(yintercept = 0, linetype = 'dashed')+
  stat_summary(aes(group = Subject, x = half, y = five_vs_zero),geom = "line",size = 0.3, alpha = 0.3,
            color = "grey")+
  stat_summary(aes(x = half, y = five_vs_zero),fun.data = "mean_cl_boot",geom = "pointrange",
               size = 0.2)+
  labs(y = "arousal ±$5-$0",
       subtitle = "arousal ±$5 minus ±$0",
       title = "VR Study")+
    annotate("text",x = 1.5, y = 1,label = mytext)+
  theme(plot.subtitle = element_text(size = 10))

fmri3_pupil_data_tonic <- fmri3_pupil_data%>%
  filter(Time_sec >= fmri3_ant_window[1], Time_sec <= fmri3_ant_window[2])%>% 
  select(subject,probe,cue_size,trial,pupilDiameter_baseline_scaled,pupilDiameter_bc_scaled,
         pupilDiameter_scaled,
         last_iti,arousal_scaled,valence_scaled,hit)%>%
  group_by(subject,trial,probe,cue_size,
         arousal_scaled,valence_scaled,hit,)%>%
  filter(last_iti != 0) %>% 
  summarise(pupilDiameter_baseline_scaled = mean(pupilDiameter_baseline_scaled,na.rm = T),
                   pupilDiameter_bc_scaled = mean(pupilDiameter_bc_scaled,na.rm=T),
            pupilDiameter_scaled = mean(pupilDiameter_scaled, na.rm = T)) %>% 
  ungroup()%>%
  mutate(half = ifelse(trial >= 48,"second","first"),
         hit = zoo::rollmean(as.numeric(hit=="Hit"), k = 5, align = "right", fill = NA))

fmri3_pupil_data_phasicarousal <- fmri3_pupil_data%>% 
   filter(!subject %in% c("tc240311","st240312"))%>%
  filter(rating_type == 1) %>%
  group_by(subject,trial,cue_value,
         arousal_scaled,valence_scaled,hit)%>%
  mutate(rowid = row_number()) %>% 
  filter(rowid == 1) %>% 
  group_by(subject)%>%
  mutate(trial = row_number()) %>% 
  mutate(half = ifelse(trial >= 24,"second","first"))%>%
  group_by(subject,half) %>% 
  mutate(hit_rate = mean(hit=="Hit")) %>% 
  group_by(subject,half,cue_value,hit_rate)%>%
  summarise(arousal_scaled = mean(arousal_scaled,na.rm = T)) %>%
  pivot_wider(names_from = cue_value, values_from = arousal_scaled) %>% 
  mutate(plus5_plus0 = `+$5` - `+$0`,
         minus5_minus0 = `-$5` - `-$0`,
         five_vs_zero = (plus5_plus0+minus5_minus0)/2)

summary(l3<-lmer(scale(pupilDiameter_baseline_scaled) ~ scale(trial)+scale(hit) + (1+scale(trial)+scale(hit)|subject),fmri3_pupil_data_tonic))

mytext=summary(l3)$coefficients

mytext = ifelse(mytext[2,5] >= 0.05, "n.s.",
                ifelse(mytext[2,5] >= 0.01, "*",
                       ifelse(mytext[2,5] >= 0.001, "**","***")))

# Extract random effects (BLUPs) for each participant
# Extract fixed and random effects from model
fixed_eff  <- fixef(l3)["scale(trial)"]
rand_eff   <- ranef(l3)$subject[,"scale(trial)"]

# Combine into dataframe
df_slopes <- data.frame(subject = rownames(ranef(l3)$subject),
                        slope_trial = fixed_eff + rand_eff)

# Prepare trial values (use your observed range)
trial_seq <- 1:96

# Build dataframe of all predicted lines
df_lines <- do.call(rbind, lapply(unique(df_slopes$subject), function(subj){
  intercept <- fixef(l3)[1] + ranef(l3)$subject[subj,"(Intercept)"]
  slope     <- df_slopes[df_slopes$subject == subj, "slope_trial"]
  
  data.frame(
    subject = subj,
    trial   = trial_seq,
    pred    = intercept + slope * scale(trial_seq))
}))


df_lines2 <- data.frame(
    trial   = trial_seq,
    pred    = fixef(l3)[1] + fixed_eff * scale(trial_seq))

pt31 <- ggplot(data = df_lines) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  # add model-predicted lines
  geom_line(
            aes(x = trial, y = pred, group = subject),
            color = "grey", alpha = 0.4, size = 0.4) +
  stat_summary(data = df_lines2,aes(x = trial, y = pred, group=1),
               size =1, geom = "line")+
  labs(y = "z-scored pupil",
       subtitle = "FMRI Study",
       # subtitle = "Tonic pupil"
       ) +
  annotate("text", x = 48, y = 1, label = mytext)+
  scale_x_continuous(breaks = c(1,24,48,72,96))

summary(l3<-lmer(scale(pupilDiameter_bc_scaled) ~ scale(trial)+scale(hit) + (1+scale(trial)+scale(hit)|subject),fmri3_pupil_data_tonic))

mytext=summary(l3)$coefficients

mytext = ifelse(mytext[2,5] >= 0.05, "n.s.",
                ifelse(mytext[2,5] >= 0.01, "*",
                       ifelse(mytext[2,5] >= 0.001, "**","***")))

# Extract random effects (BLUPs) for each participant
# Extract fixed and random effects from model
fixed_eff  <- fixef(l3)["scale(trial)"]
rand_eff   <- ranef(l3)$subject[,"scale(trial)"]

# Combine into dataframe
df_slopes <- data.frame(subject = rownames(ranef(l3)$subject),
                        slope_trial = fixed_eff + rand_eff)

# Prepare trial values (use your observed range)
trial_seq <- 1:96

# Build dataframe of all predicted lines
df_lines <- do.call(rbind, lapply(unique(df_slopes$subject), function(subj){
  intercept <- fixef(l3)[1] + ranef(l3)$subject[subj,"(Intercept)"]
  slope     <- df_slopes[df_slopes$subject == subj, "slope_trial"]
  
  data.frame(
    subject = subj,
    trial   = trial_seq,
    pred    = intercept + slope * scale(trial_seq))
}))


df_lines2 <- data.frame(
    trial   = trial_seq,
    pred    = fixef(l3)[1] + fixed_eff * scale(trial_seq))

pt32 <- ggplot(data = df_lines) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  # add model-predicted lines
  geom_line(
            aes(x = trial, y = pred, group = subject),
            color = "grey", alpha = 0.4, size = 0.4) +
  stat_summary(data = df_lines2,aes(x = trial, y = pred, group=1),
               size =1, geom = "line")+
  labs(y = "z-scored pupil",
       subtitle = "FMRI Study",
       # subtitle = "Corrected phasic pupil"
       ) +
  annotate("text", x = 48, y = 1, label = mytext)+
  scale_x_continuous(breaks = c(1,24,48,72,96))

summary(l3<-lmer(scale(arousal_scaled) ~ scale(trial)+scale(hit) + (1+scale(trial)+scale(hit)|subject),fmri3_pupil_data_tonic))

mytext=summary(l3)$coefficients

mytext = ifelse(mytext[2,5] >= 0.05, "n.s.",
                ifelse(mytext[2,5] >= 0.01, "*",
                       ifelse(mytext[2,5] >= 0.001, "**","***")))

# Extract random effects (BLUPs) for each participant
# Extract fixed and random effects from model
fixed_eff  <- fixef(l3)["scale(trial)"]
rand_eff   <- ranef(l3)$subject[,"scale(trial)"]

# Combine into dataframe
df_slopes <- data.frame(subject = rownames(ranef(l3)$subject),
                        slope_trial = fixed_eff + rand_eff)

# Prepare trial values (use your observed range)
trial_seq <- 1:96

# Build dataframe of all predicted lines
df_lines <- do.call(rbind, lapply(unique(df_slopes$subject), function(subj){
  intercept <- fixef(l3)[1] + ranef(l3)$subject[subj,"(Intercept)"]
  slope     <- df_slopes[df_slopes$subject == subj, "slope_trial"]
  
  data.frame(
    subject = subj,
    trial   = trial_seq,
    pred    = intercept + slope * scale(trial_seq))
}))


df_lines2 <- data.frame(
    trial   = trial_seq,
    pred    = fixef(l3)[1] + fixed_eff * scale(trial_seq))

pt33 <- ggplot(data = df_lines) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  # add model-predicted lines
  geom_line(
            aes(x = trial, y = pred, group = subject),
            color = "grey", alpha = 0.4, size = 0.4) +
  stat_summary(data = df_lines2,aes(x = trial, y = pred, group=1),
               size =1, geom = "line")+
  labs(y = "z-scored pupil",
       title = "FMRI Study",
       subtitle = "Mean reported arousal") +
  annotate("text", x = 48, y = 1, label = mytext)+
  scale_x_continuous(breaks = c(1,24,48,72,96))

summary(l3<-lmer(scale(valence_scaled) ~ scale(trial)+scale(hit) + (1+scale(trial)+scale(hit)|subject),fmri3_pupil_data_tonic))

mytext=summary(l3)$coefficients

mytext = ifelse(mytext[2,5] >= 0.05, "n.s.",
                ifelse(mytext[2,5] >= 0.01, "*",
                       ifelse(mytext[2,5] >= 0.001, "**","***")))

# Extract random effects (BLUPs) for each participant
# Extract fixed and random effects from model
fixed_eff  <- fixef(l3)["scale(trial)"]
rand_eff   <- ranef(l3)$subject[,"scale(trial)"]

# Combine into dataframe
df_slopes <- data.frame(subject = rownames(ranef(l3)$subject),
                        slope_trial = fixed_eff + rand_eff)

# Prepare trial values (use your observed range)
trial_seq <- 1:96

# Build dataframe of all predicted lines
df_lines <- do.call(rbind, lapply(unique(df_slopes$subject), function(subj){
  intercept <- fixef(l3)[1] + ranef(l3)$subject[subj,"(Intercept)"]
  slope     <- df_slopes[df_slopes$subject == subj, "slope_trial"]
  
  data.frame(
    subject = subj,
    trial   = trial_seq,
    pred    = intercept + slope * scale(trial_seq))
}))


df_lines2 <- data.frame(
    trial   = trial_seq,
    pred    = fixef(l3)[1] + fixed_eff * scale(trial_seq))

pt34 <- ggplot(data = df_lines) +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  # add model-predicted lines
  geom_line(
            aes(x = trial, y = pred, group = subject),
            color = "grey", alpha = 0.4, size = 0.4) +
  stat_summary(data = df_lines2,aes(x = trial, y = pred, group=1),
               size =1, geom = "line")+
  labs(y = "z-scored pupil",
       title = "FMRI Study",
       subtitle = "Mean reported valence") +
  annotate("text", x = 48, y = 1, label = mytext)+
  scale_x_continuous(breaks = c(1,24,48,72,96))

summary(lmer(scale(five_vs_zero) ~ half + scale(hit_rate) +  (1|subject),
             fmri3_pupil_data_phasicarousal))
mytext=summary(lmer(five_vs_zero ~ half + hit_rate + (1|subject),fmri3_pupil_data_phasicarousal))$coefficients
mytext = ifelse(mytext[2,5] >= 0.05/4, "n.s.",
                ifelse(mytext[2,5] >= 0.01/4, "*",
                       ifelse(mytext[2,5] >= 0.001/4, "**","***")))
pt35 <- ggplot(fmri3_pupil_data_phasicarousal)+
  geom_hline(yintercept = 0, linetype = 'dashed')+
  stat_summary(aes(group = subject, x = half, y = five_vs_zero),geom = "line",size = 0.3, alpha = 0.3,
            color = "grey")+
  stat_summary(aes(x = half, y = five_vs_zero),fun.data = "mean_cl_boot",geom = "pointrange",
               size = 0.2)+
  labs(y = "arousal ±$5-±$0",
       subtitle = "arousal ±$5 minus ±$0",
       title = "FMRI Study")+
    annotate("text",x = 1.5, y = 0.4,label = mytext)+
   theme(plot.subtitle = element_text(size = 10))
  # annotate("text",x = 1.5, y = 0.4,label = paste0("t = ", round(mytext[2,4],2),", p = ",round(mytext[2,5],2)))
```

## were tonic and phasic both related to previous arousal?
### The original version
```{r}
vrmid1_pupil_data_tonic_history <- vrmid1_pupil_data_tonic %>% 
  group_by(Subject) %>%
  mutate(    # Generate recent average win percentages for windows 1 to 20
    map_dfc(0:9, function(k) {
      col <- lag(arousal_scaled, k)
      setNames(data.frame(col), paste0("arousal_scaled_lag", k))
    }))

vrmid1_pupil_data_tonic_history <- vrmid1_pupil_data_tonic_history %>%
  pivot_longer(arousal_scaled_lag0:arousal_scaled_lag9,
               names_to = "lag", values_to = "arousal",
               names_prefix = "arousal_scaled_lag")

dftemp1 <- NULL

for (l in 0:9){
  l1<-summary(lmer(arousal ~ pupil_Avg_baseline_scaled + (1|Subject) + (1|probe) + (1|condition),
               vrmid1_pupil_data_tonic_history %>% filter(lag == l)))
  l2<-summary(lmer(arousal ~ pupil_Avg_bc_scaled + (1|Subject)+ (1|probe) + (1|condition),
               vrmid1_pupil_data_tonic_history %>% filter(lag == l)))
  l3<-summary(lmer(arousal ~ pupil_Avg_scaled + (1|Subject)+ (1|probe) + (1|condition),
               vrmid1_pupil_data_tonic_history %>% filter(lag == l)))
  dftemp1 <- rbind(dftemp1,
                  rbind(l1$coefficients[2,],
                        l2$coefficients[2,],
                        l3$coefficients[2,]))
}
  
dftemp1 <- as.data.frame(dftemp1)
dftemp1$lag <- rep(0:9,each=3)
dftemp1$measure <- rep(c("tonic","corrected phasic","uncorrected phasic"),10)
dftemp1 <- dftemp1 %>% 
  mutate(p_corrected = `Pr(>|t|)`*10,
         shape = ifelse(`Pr(>|t|)` < .05/10, 19, 1))  # numeric alpha

p1 <- ggplot(dftemp1 %>% filter(measure != "uncorrected phasic"), aes(x = lag, y = Estimate, color = measure,shape = shape)) +
  annotate("rect", xmin = -0.5, ymin = -0.1, xmax = 0.5, ymax = 0.3, alpha = 0.1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`),
                width = 0.1) +
  labs(x = "arousal rating __ trials ago",
       y = "std. beta",
       title = "VR Study",
       color = NULL) +
  theme(legend.position = "top") +
  scale_color_manual(values = c("red4", "steelblue")) +
  scale_shape_identity()+
  guides(color = guide_legend(nrow = 2))+
  scale_x_reverse(breaks = 0:9)

fmri3_pupil_data_tonic_history <- fmri3_pupil_data_tonic %>% 
  group_by(subject) %>%
  mutate(    # Generate recent average win percentages for windows 1 to 20
    map_dfc(0:9, function(k) {
      col <- lag(arousal_scaled, k)
      setNames(data.frame(col), paste0("arousal_scaled_lag", k))
    }))

fmri3_pupil_data_tonic_history <- fmri3_pupil_data_tonic_history %>%
  pivot_longer(arousal_scaled_lag0:arousal_scaled_lag9,
               names_to = "lag", values_to = "arousal",
               names_prefix = "arousal_scaled_lag")


dftemp3 <- NULL

for (l in 0:9){
  l1<-summary(lmer(arousal ~ pupilDiameter_baseline_scaled + (1|subject)+ (1|probe) + (1|cue_size),
               fmri3_pupil_data_tonic_history %>% filter(lag == l)))
  l2<-summary(lmer(arousal ~ pupilDiameter_bc_scaled + (1|subject)+ (1|probe)+ (1|cue_size),
               fmri3_pupil_data_tonic_history %>% filter(lag == l)))
  l3<-summary(lmer(arousal ~ pupilDiameter_scaled + (1|subject)+ (1|probe)+ (1|cue_size),
               fmri3_pupil_data_tonic_history %>% filter(lag == l)))
  dftemp3 <- rbind(dftemp3,
                  rbind(l1$coefficients[2,],
                        l2$coefficients[2,],
                        l3$coefficients[2,]))
}
  
dftemp3 <- as.data.frame(dftemp3)
dftemp3$lag <- rep(0:9,each=3)
dftemp3$measure <- rep(c("tonic","corrected phasic","uncorrected phasic"),10)
dftemp3 <- dftemp3  %>% 
  mutate(p_corrected = `Pr(>|t|)`*10,
         shape = ifelse(`Pr(>|t|)` < .05/10, 19, 1))  # numeric alpha

p3 <- ggplot(dftemp3%>% filter(measure != "uncorrected phasic"), aes(x = lag, y = Estimate, color = measure,shape=shape)) +
  annotate("rect", xmin = -0.5, ymin = -0.1, xmax = 0.5, ymax = 0.4, alpha = 0.1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`),
                width = 0.1) +
  scale_x_continuous(breaks = 0:9) +
  labs(x = "arousal rating __ trials ago",
       y = "std. beta",
       title = "FMRI study") +
  theme(legend.position = "none") +
  scale_color_manual(values = c("red4", "steelblue")) +
  scale_shape_identity()+   # use alpha directly
  scale_x_reverse(breaks = 0:9)

p1+p3
```

### The version with residualized arousal rating
```{r}
# Step 1: Create lagged arousal columns
vrmid1_pupil_data_tonic_history <- vrmid1_pupil_data_tonic %>% 
  group_by(Subject) %>%
  mutate(map_dfc(0:4, function(k) {
    col <- lag(arousal_scaled, k)
    setNames(data.frame(col), paste0("arousal_scaled_lag", k))
  }))

# Step 2: Residualize each lag wrt closer lags (fixing NA alignment issue)
for (k in 0:4) {
  if (k == 0){
    vrmid1_pupil_data_tonic_history[[paste0("arousal_scaled_lag", k, "_resid")]] <- vrmid1_pupil_data_tonic_history$arousal_scaled_lag0
  } else {
    formula_str <- paste0("arousal_scaled_lag", k, " ~ ", 
                        paste0("arousal_scaled_lag", 0:(k-1), collapse = " + "))
  
  # Identify rows with complete data for this model
  rows_complete <- complete.cases(vrmid1_pupil_data_tonic_history[, paste0("arousal_scaled_lag", 0:k)])
  
  # Fit model only on those rows
  model <- lm(as.formula(formula_str),
              data = vrmid1_pupil_data_tonic_history[rows_complete, ])
  
  # Initialize full-length residual vector with NAs
  resid_full <- rep(NA, nrow(vrmid1_pupil_data_tonic_history))
  
  # Fill in residuals where model was estimated
  resid_full[rows_complete] <- resid(model)
  
  # Store residuals in data frame
  vrmid1_pupil_data_tonic_history[[paste0("arousal_scaled_lag", k, "_resid")]] <- resid_full
  }
}

# Step 3: Reshape to long format (for residualized variables)
vrmid1_pupil_data_tonic_history_long <- vrmid1_pupil_data_tonic_history %>%
  pivot_longer(cols = matches("arousal_scaled_lag[0-9]_resid"),
               names_to = "lag", values_to = "arousal_resid",
               names_pattern = "arousal_scaled_lag([0-9])_resid") %>%
  mutate(lag = as.numeric(lag))

# Step 4: Fit mixed models for each lag
dftemp1 <- NULL

for (l in 0:4){  # start at 1 because lag0 residual is undefined
  df_subset <- vrmid1_pupil_data_tonic_history_long %>% filter(lag == l)
  
  l1 <- summary(lmer(arousal_resid ~ pupil_Avg_baseline_scaled + (1|Subject) + (1|probe)
                     +(1|condition), df_subset))
  l2 <- summary(lmer(arousal_resid ~ pupil_Avg_bc_scaled + (1|Subject) + (1|probe)
                     +(1|condition), df_subset))
  l3 <- summary(lmer(arousal_resid ~ pupil_Avg_scaled + (1|Subject) + (1|probe)
                     +(1|condition), df_subset))
  
  dftemp1 <- rbind(
    dftemp1,
    rbind(l1$coefficients[2,],
          l2$coefficients[2,],
          l3$coefficients[2,])
  )
}

dftemp1 <- as.data.frame(dftemp1)
dftemp1$lag <- rep(0:4,each=3)
dftemp1$measure <- rep(c("tonic","corrected phasic","uncorrected phasic"),5)
dftemp1 <- dftemp1  %>% 
  mutate(p_corrected = `Pr(>|t|)`*5,
         shape = ifelse(`Pr(>|t|)` < .05/5, 19, 1))  # numeric alpha

p1 <- ggplot(dftemp1 %>% filter(measure != "uncorrected phasic"), aes(x = lag, y = Estimate, color = measure,shape = shape)) +
  annotate("rect", xmin = -0.5, ymin = -0.1, xmax = 0.5, ymax = 0.3, alpha = 0.1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`),
                width = 0.1) +
  labs(x = "arousal rating __ trials ago",
       y = "std. beta",
       title = "VR Study",
       color = NULL) +
  theme(legend.position = "top") +
  scale_color_manual(values = c("red4", "steelblue")) +
  scale_shape_identity()+
  guides(color = guide_legend(nrow = 2))+
  scale_x_reverse(breaks = 0:4)

fmri3_pupil_data_tonic_history <- fmri3_pupil_data_tonic %>% 
  group_by(subject) %>%
  mutate(map_dfc(0:4, function(k) {
    col <- lag(arousal_scaled, k)
    setNames(data.frame(col), paste0("arousal_scaled_lag", k))
  }))

for (k in 0:4) {
  if (k == 0){
    fmri3_pupil_data_tonic_history[[paste0("arousal_scaled_lag", k, "_resid")]] <- fmri3_pupil_data_tonic_history$arousal_scaled_lag0
  } else {
    formula_str <- paste0("arousal_scaled_lag", k, " ~ ", 
                        paste0("arousal_scaled_lag", 0:(k-1), collapse = " + "))
  
  # Identify rows with complete data for this model
  rows_complete <- complete.cases(fmri3_pupil_data_tonic_history[, paste0("arousal_scaled_lag", 0:k)])
  
  # Fit model only on those rows
  model <- lm(as.formula(formula_str),
              data = fmri3_pupil_data_tonic_history[rows_complete, ])
  
  # Initialize full-length residual vector with NAs
  resid_full <- rep(NA, nrow(fmri3_pupil_data_tonic_history))
  
  # Fill in residuals where model was estimated
  resid_full[rows_complete] <- resid(model)
  
  # Store residuals in data frame
  fmri3_pupil_data_tonic_history[[paste0("arousal_scaled_lag", k, "_resid")]] <- resid_full
  }
}

fmri3_pupil_data_tonic_history_long <- fmri3_pupil_data_tonic_history %>%
  pivot_longer(cols = matches("arousal_scaled_lag[0-9]_resid"),
               names_to = "lag", values_to = "arousal_resid",
               names_pattern = "arousal_scaled_lag([0-9])_resid") %>%
  mutate(lag = as.numeric(lag))

dftemp3 <- NULL

for (l in 0:4){  # start at 1 because lag0 residual is undefined
  df_subset <- fmri3_pupil_data_tonic_history_long %>% filter(lag == l)
  
  l1 <- summary(lmer(arousal_resid ~ pupilDiameter_baseline_scaled + (1|subject) + (1|probe)
                     +(1|cue_size), df_subset))
  l2 <- summary(lmer(arousal_resid ~ pupilDiameter_bc_scaled + (1|subject) + (1|probe)
                     +(1|cue_size), df_subset))
  l3 <- summary(lmer(arousal_resid ~ pupilDiameter_scaled + (1|subject) + (1|probe)
                     +(1|cue_size), df_subset))
  
  dftemp3 <- rbind(
    dftemp3,
    rbind(l1$coefficients[2,],
          l2$coefficients[2,],
          l3$coefficients[2,])
  )
}

dftemp3 <- as.data.frame(dftemp3)
dftemp3$lag <- rep(0:4,each=3)
dftemp3$measure <- rep(c("tonic","corrected phasic","uncorrected phasic"),5)
dftemp3 <- dftemp3  %>% 
  mutate(p_corrected = `Pr(>|t|)`,
         shape = ifelse(`Pr(>|t|)` < .05, 19, 1))  # numeric alpha

p3 <- ggplot(dftemp3 %>% filter(measure != "uncorrected phasic"), aes(x = lag, y = Estimate, color = measure,shape = shape)) +
  annotate("rect", xmin = -0.5, ymin = -0.1, xmax = 0.5, ymax = 0.3, alpha = 0.1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`),
                width = 0.1) +
  labs(x = "arousal rating __ trials ago",
       y = "std. beta",
       title = "FMRI Study",
       color = NULL) +
  theme(legend.position = "top") +
  scale_color_manual(values = c("red4", "steelblue")) +
  scale_shape_identity()+
  guides(color = guide_legend(nrow = 2))+
  scale_x_reverse(breaks = 0:4)
```

### The version with rolling mean
```{r}
vrmid1_pupil_data_tonic_history <- vrmid1_pupil_data_tonic %>% 
  group_by(Subject) %>%
  mutate(
    map_dfc(0:9, function(k) {
      mean_lag <- map_dbl(seq_len(n()), function(i) {
        if (i <= (k+1) - 1) {
          NA  # Not enough previous data points
        } else {
          mean(arousal_scaled[(i - (k+1) + 1):i], na.rm = TRUE)
        }
      })
      setNames(data.frame(mean_lag), paste0("arousal_scaled_lag", k))
    })
  )

vrmid1_pupil_data_tonic_history <- vrmid1_pupil_data_tonic_history %>%
  pivot_longer(arousal_scaled_lag0:arousal_scaled_lag9,
               names_to = "lag", values_to = "arousal",
               names_prefix = "arousal_scaled_lag")

dftemp1 <- NULL

for (l in 0:9){
  l1<-summary(lmer(arousal ~ pupil_Avg_baseline_scaled + (1|Subject) + (1|probe)
                   +(1|condition),
               vrmid1_pupil_data_tonic_history %>% filter(lag == l)))
  l2<-summary(lmer(arousal ~ pupil_Avg_bc_scaled + (1|Subject)+ (1|probe)
                   +(1|condition),
               vrmid1_pupil_data_tonic_history %>% filter(lag == l)))
  l3<-summary(lmer(arousal ~ pupil_Avg_scaled + (1|Subject)+ (1|probe)
                   +(1|condition),
               vrmid1_pupil_data_tonic_history %>% filter(lag == l)))
  dftemp1 <- rbind(dftemp1,
                  rbind(l1$coefficients[2,],
                        l2$coefficients[2,],
                        l3$coefficients[2,]))
}
  
dftemp1 <- as.data.frame(dftemp1)
dftemp1$lag <- rep(0:9,each=3)
dftemp1$measure <- rep(c("tonic","corrected phasic","uncorrected phasic"),10)
dftemp1 <- dftemp1 %>% 
  mutate(p_corrected = `Pr(>|t|)`*10,
         shape = ifelse(`Pr(>|t|)` < .05/10, 19, 1))  # numeric alpha

p1 <- ggplot(dftemp1 %>% filter(measure != "uncorrected phasic"), aes(x = lag, y = Estimate, color = measure,shape = shape)) +
  annotate("rect", xmin = -0.5, ymin = -0.1, xmax = 0.5, ymax = 0.3, alpha = 0.1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`),
                width = 0.1) +
  labs(x = "Rolling window size",
       y = "std. beta",
       title = "VR Study",
       color = NULL) +
  theme(legend.position = "top") +
  scale_color_manual(values = c("red4", "steelblue")) +
  scale_shape_identity()+
  guides(color = guide_legend(nrow = 2))+
  scale_x_reverse(breaks = 0:9)

fmri3_pupil_data_tonic_history <- fmri3_pupil_data_tonic %>% 
  group_by(subject) %>%
  mutate(
    map_dfc(0:9, function(k) {
      mean_lag <- map_dbl(seq_len(n()), function(i) {
        if (i <= (k+1) - 1) {
          NA  # Not enough previous data points
        } else {
          mean(arousal_scaled[(i - (k+1) + 1):i], na.rm = TRUE)
        }
      })
      setNames(data.frame(mean_lag), paste0("arousal_scaled_lag", k))
    })
  )

fmri3_pupil_data_tonic_history <- fmri3_pupil_data_tonic_history %>%
  pivot_longer(arousal_scaled_lag0:arousal_scaled_lag9,
               names_to = "lag", values_to = "arousal",
               names_prefix = "arousal_scaled_lag")


dftemp3 <- NULL

for (l in 0:9){
  l1<-summary(lmer(arousal ~ pupilDiameter_baseline_scaled + (1|subject)+ (1|probe)
                   +(1|cue_size),
               fmri3_pupil_data_tonic_history %>% filter(lag == l)))
  l2<-summary(lmer(arousal ~ pupilDiameter_bc_scaled + (1|subject)+ (1|probe)
                   +(1|cue_size),
               fmri3_pupil_data_tonic_history %>% filter(lag == l)))
  l3<-summary(lmer(arousal ~ pupilDiameter_scaled + (1|subject)+ (1|probe)
                   +(1|cue_size),
               fmri3_pupil_data_tonic_history %>% filter(lag == l)))
  dftemp3 <- rbind(dftemp3,
                  rbind(l1$coefficients[2,],
                        l2$coefficients[2,],
                        l3$coefficients[2,]))
}
  
dftemp3 <- as.data.frame(dftemp3)
dftemp3$lag <- rep(0:9,each=3)
dftemp3$measure <- rep(c("tonic","corrected phasic","uncorrected phasic"),10)
dftemp3 <- dftemp3  %>% 
  mutate(p_corrected = `Pr(>|t|)`*10,
         shape = ifelse(`Pr(>|t|)` < .05/10, 19, 1))  # numeric alpha

p3 <- ggplot(dftemp3%>% filter(measure != "uncorrected phasic"), aes(x = lag, y = Estimate, color = measure,shape=shape)) +
  annotate("rect", xmin = -0.5, ymin = -0.1, xmax = 0.5, ymax = 0.4, alpha = 0.1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`),
                width = 0.1) +
  labs(x = "Rolling window size",
       y = "std. beta",
       title = "FMRI study") +
  theme(legend.position = "none") +
  scale_color_manual(values = c("red4", "steelblue")) +
  scale_shape_identity()+   # use alpha directly
  scale_x_reverse(breaks = 0:9)

p1+p3+
  plot_layout(nrow = 1)
```



## do the reverse: were arousal related to previous tonic / phasic?

### the original version
```{r}
vrmid1_pupil_data_arousal_history <- vrmid1_pupil_data_tonic %>%
  group_by(Subject) %>%
  mutate(
    map_dfc(0:9, function(k) {
      col <- lag(pupil_Avg_baseline_scaled, k)
      setNames(data.frame(col), paste0("pupil_Avg_baseline_scaled_lag", k))
    }),
    map_dfc(0:9, function(k) {
      col <- lag(pupil_Avg_bc_scaled, k)
      setNames(data.frame(col), paste0("pupil_Avg_bc_scaled_lag", k))
    }),
    map_dfc(0:9, function(k) {
      col <- lag(pupil_Avg_scaled, k)
      setNames(data.frame(col), paste0("pupil_Avg_scaled_lag", k))
    }))

vrmid1_pupil_data_arousal_history <- vrmid1_pupil_data_arousal_history %>%
  pivot_longer(pupil_Avg_baseline_scaled_lag0:pupil_Avg_scaled_lag9,
               names_to = c("measure","lag"),names_pattern = "(.*)_lag(\\d+)", values_to = "pupil_size",
               names_prefix = "pupil_lag")

dftemp4 <- NULL

for (l in 0:9){
  l1<-summary(lmer(arousal_scaled ~ pupil_size + (1|Subject) + (1|probe) + (1|condition),
               vrmid1_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupil_Avg_baseline_scaled")))
  l2<-summary(lmer(arousal_scaled ~ pupil_size + (1|Subject) + (1|probe) + (1|condition),
               vrmid1_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupil_Avg_bc_scaled")))
  l3<-summary(lmer(arousal_scaled ~ pupil_size + (1|Subject) + (1|probe) + (1|condition),
               vrmid1_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupil_Avg_scaled")))
  dftemp4 <- rbind(dftemp4,
                  rbind(l1$coefficients[2,],
                        l2$coefficients[2,],
                        l3$coefficients[2,]))
}

dftemp4 <- as.data.frame(dftemp4)
dftemp4$lag <- rep(0:9,each=3)
dftemp4$measure <- rep(c("tonic","corrected phasic","uncorrected phasic"),10)
dftemp4 <- dftemp4 %>%
  group_by(measure) %>% 
  mutate(p_corrected = p.adjust(`Pr(>|t|)`, method = "fdr")) %>%
  mutate(shape = ifelse(p_corrected < .05, 19, 1))

p4 <- ggplot(dftemp4%>% filter(measure != "uncorrected phasic"), aes(x = lag, y = Estimate, color = measure,shape=shape)) +
  annotate("rect", xmin = -0.5, ymin = -0.1, xmax = 0.5, ymax = 0.4, alpha = 0.1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`),
                width = 0.1) +
  labs(x = "Pupil size __ trials ago",
       y = "std. beta",
       title = "VR Study") +
  theme(legend.position = "top") +
  scale_color_manual(values = c("red4", "steelblue")) +
  scale_shape_identity()+   # use alpha directly
  scale_x_reverse(breaks = 0:9)

p4

fmri3_pupil_data_arousal_history <- fmri3_pupil_data_tonic %>%
  group_by(subject)  %>%
  mutate(
    map_dfc(0:9, function(k) {
      col <- lag(pupilDiameter_baseline_scaled, k)
      setNames(data.frame(col), paste0("pupilDiameter_baseline_scaled_lag", k))
    }),
    map_dfc(0:9, function(k) {
      col <- lag(pupilDiameter_bc_scaled, k)
      setNames(data.frame(col), paste0("pupilDiameter_bc_scaled_lag", k))
    }),
    map_dfc(0:9, function(k) {
      col <- lag(pupilDiameter_scaled, k)
      setNames(data.frame(col), paste0("pupilDiameter_scaled_lag", k))
    }))


fmri3_pupil_data_arousal_history <- fmri3_pupil_data_arousal_history %>%
  pivot_longer(pupilDiameter_baseline_scaled_lag0:pupilDiameter_scaled_lag9,
               names_to = c("measure","lag"),names_pattern = "(.*)_lag(\\d+)", values_to = "pupil_size",
               names_prefix = "pupil_lag")

dftemp6 <- NULL

for (l in 0:9){
  l1<-summary(lmer(arousal_scaled ~ pupil_size + (1|subject) + (1|probe) + (1|cue_size),
               fmri3_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupilDiameter_baseline_scaled")))
  l2<-summary(lmer(arousal_scaled ~ pupil_size + (1|subject) + (1|probe)+ (1|cue_size),
               fmri3_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupilDiameter_bc_scaled")))
  l3<-summary(lmer(arousal_scaled ~ pupil_size + (1|subject) + (1|probe)+ (1|cue_size),
               fmri3_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupilDiameter_scaled")))
  dftemp6 <- rbind(dftemp6,
                  rbind(l1$coefficients[2,],
                        l2$coefficients[2,],
                        l3$coefficients[2,]))
}

dftemp6 <- as.data.frame(dftemp6)
dftemp6$lag <- rep(0:9,each=3)
dftemp6$measure <- rep(c("tonic","corrected phasic","uncorrected phasic"),10)
dftemp6 <- dftemp6  %>%
  group_by(measure) %>% 
  mutate(p_corrected = p.adjust(`Pr(>|t|)`, method = "fdr")) %>%
  mutate(shape = ifelse(p_corrected < .05, 19, 1))

p6 <- ggplot(dftemp6%>% filter(measure != "uncorrected phasic"), aes(x = lag, y = Estimate, color = measure,shape=shape)) +
  annotate("rect", xmin = -0.5, ymin = -0.1, xmax = 0.5, ymax = 0.4, alpha = 0.1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`),
                width = 0.1) +
  labs(x = "Pupil size __ trials ago",
       y = "std. beta",
       title = "FMRI Study") +
  theme(legend.position = "none") +
  scale_color_manual(values = c("red4", "steelblue")) +
  scale_shape_identity()+   # use alpha directly
  scale_x_reverse(breaks = 0:9)

p4+p6
```

### the version with residualized pupil size
```{r}
vrmid1_pupil_data_arousal_history <- vrmid1_pupil_data_tonic %>%
  group_by(Subject) %>%
  mutate(
    map_dfc(0:9, function(k) {
      col <- lag(pupil_Avg_baseline_scaled, k)
      setNames(data.frame(col), paste0("pupil_Avg_baseline_scaled_lag", k))
    }),
    map_dfc(0:9, function(k) {
      col <- lag(pupil_Avg_bc_scaled, k)
      setNames(data.frame(col), paste0("pupil_Avg_bc_scaled_lag", k))
    }),
    map_dfc(0:9, function(k) {
      col <- lag(pupil_Avg_scaled, k)
      setNames(data.frame(col), paste0("pupil_Avg_scaled_lag", k))
    }))

# Step 2: Residualize each lag wrt closer lags (fixing NA alignment issue)
# Step 2: Residualize each pupil variable's lags wrt closer lags (fixing NA alignment issue)

for (var in c("pupil_Avg_baseline_scaled", "pupil_Avg_bc_scaled", "pupil_Avg_scaled")) {
  for (k in 0:9) {
    if (k == 0) {
      vrmid1_pupil_data_arousal_history[[paste0(var, "_lag", k, "_resid")]] <- 
        vrmid1_pupil_data_arousal_history[[paste0(var, "_lag0")]]
    } else {
      formula_str <- paste0(var, "_lag", k, " ~ ", 
                            paste0(var, "_lag", 0:(k-1), collapse = " + "))
      
      # Identify rows with complete data for this model
      rows_complete <- complete.cases(vrmid1_pupil_data_arousal_history[, paste0(var, "_lag", 0:k)])
      
      # Fit model only on those rows
      model <- lm(as.formula(formula_str),
                  data = vrmid1_pupil_data_arousal_history[rows_complete, ])
      
      # Initialize full-length residual vector with NAs
      resid_full <- rep(NA, nrow(vrmid1_pupil_data_arousal_history))
      
      # Fill in residuals where model was estimated
      resid_full[rows_complete] <- resid(model)
      
      # Store residuals in data frame
      vrmid1_pupil_data_arousal_history[[paste0(var, "_lag", k, "_resid")]] <- resid_full
    }
  }
}

vrmid1_pupil_data_arousal_history <- vrmid1_pupil_data_arousal_history %>%
  pivot_longer(pupil_Avg_baseline_scaled_lag0_resid:pupil_Avg_scaled_lag9_resid,
               names_to = c("measure","lag"),names_pattern = "(.*)_lag(\\d+)", values_to = "pupil_size",
               names_prefix = "pupil_lag")

dftemp4 <- NULL

for (l in 0:9){
  l1<-summary(lmer(arousal_scaled ~ pupil_size + (1|Subject) + (1|probe) + (1|condition),
               vrmid1_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupil_Avg_baseline_scaled")))
  l2<-summary(lmer(arousal_scaled ~ pupil_size + (1|Subject) + (1|probe) + (1|condition),
               vrmid1_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupil_Avg_bc_scaled")))
  l3<-summary(lmer(arousal_scaled ~ pupil_size + (1|Subject) + (1|probe) + (1|condition),
               vrmid1_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupil_Avg_scaled")))
  dftemp4 <- rbind(dftemp4,
                  rbind(l1$coefficients[2,],
                        l2$coefficients[2,],
                        l3$coefficients[2,]))
}

dftemp4 <- as.data.frame(dftemp4)
dftemp4$lag <- rep(0:9,each=3)
dftemp4$measure <- rep(c("tonic","corrected phasic","uncorrected phasic"),10)
dftemp4 <- dftemp4 %>%
  group_by(measure) %>% 
  mutate(p_corrected = p.adjust(`Pr(>|t|)`, method = "fdr")) %>%
  mutate(shape = ifelse(p_corrected < .05, 19, 1))

p4 <- ggplot(dftemp4%>% filter(measure != "uncorrected phasic"), aes(x = lag, y = Estimate, color = measure,shape=shape)) +
  annotate("rect", xmin = -0.5, ymin = -0.1, xmax = 0.5, ymax = 0.4, alpha = 0.1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`),
                width = 0.1) +
  labs(x = "Pupil size __ trials ago",
       y = "std. beta",
       title = "VR Study") +
  theme(legend.position = "none") +
  scale_color_manual(values = c("red4", "steelblue")) +
  scale_shape_identity()+   # use alpha directly
  scale_x_reverse(breaks = 0:9)

p4

fmri3_pupil_data_arousal_history <- fmri3_pupil_data_tonic %>%
  group_by(subject)  %>%
  mutate(
    map_dfc(0:9, function(k) {
      col <- lag(pupilDiameter_baseline_scaled, k)
      setNames(data.frame(col), paste0("pupilDiameter_baseline_scaled_lag", k))
    }),
    map_dfc(0:9, function(k) {
      col <- lag(pupilDiameter_bc_scaled, k)
      setNames(data.frame(col), paste0("pupilDiameter_bc_scaled_lag", k))
    }),
    map_dfc(0:9, function(k) {
      col <- lag(pupilDiameter_scaled, k)
      setNames(data.frame(col), paste0("pupilDiameter_scaled_lag", k))
    }))

for (var in c("pupilDiameter_baseline_scaled", "pupilDiameter_bc_scaled", "pupilDiameter_scaled")) {
  for (k in 0:9) {
    if (k == 0) {
      fmri3_pupil_data_arousal_history[[paste0(var, "_lag", k, "_resid")]] <- 
        fmri3_pupil_data_arousal_history[[paste0(var, "_lag0")]]
    } else {
      formula_str <- paste0(var, "_lag", k, " ~ ", 
                            paste0(var, "_lag", 0:(k-1), collapse = " + "))
      
      # Identify rows with complete data for this model
      rows_complete <- complete.cases(fmri3_pupil_data_arousal_history[, paste0(var, "_lag", 0:k)])
      
      # Fit model only on those rows
      model <- lm(as.formula(formula_str),
                  data = fmri3_pupil_data_arousal_history[rows_complete, ])
      
      # Initialize full-length residual vector with NAs
      resid_full <- rep(NA, nrow(fmri3_pupil_data_arousal_history))
      
      # Fill in residuals where model was estimated
      resid_full[rows_complete] <- resid(model)
      
      # Store residuals in data frame
      fmri3_pupil_data_arousal_history[[paste0(var, "_lag", k, "_resid")]] <- resid_full
    }
  }
}

fmri3_pupil_data_arousal_history <- fmri3_pupil_data_arousal_history %>%
  pivot_longer(pupilDiameter_baseline_scaled_lag0_resid:pupilDiameter_scaled_lag9_resid,
               names_to = c("measure","lag"),names_pattern = "(.*)_lag(\\d+)", values_to = "pupil_size",
               names_prefix = "pupil_lag")

dftemp6 <- NULL

for (l in 0:9){
  l1<-summary(lmer(arousal_scaled ~ pupil_size + (1|subject) + (1|probe)+(1|cue_size),
               fmri3_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupilDiameter_baseline_scaled")))
  l2<-summary(lmer(arousal_scaled ~ pupil_size + (1|subject) + (1|probe)+(1|cue_size),
               fmri3_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupilDiameter_bc_scaled")))
  l3<-summary(lmer(arousal_scaled ~ pupil_size + (1|subject) + (1|probe)+(1|cue_size),
               fmri3_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupilDiameter_scaled")))
  dftemp6 <- rbind(dftemp6,
                  rbind(l1$coefficients[2,],
                        l2$coefficients[2,],
                        l3$coefficients[2,]))
}

dftemp6 <- as.data.frame(dftemp6)
dftemp6$lag <- rep(0:9,each=3)
dftemp6$measure <- rep(c("tonic","corrected phasic","uncorrected phasic"),10)
dftemp6 <- dftemp6  %>%
  group_by(measure) %>% 
  mutate(p_corrected = p.adjust(`Pr(>|t|)`, method = "fdr")) %>%
  mutate(shape = ifelse(p_corrected < .05, 19, 1))

p6 <- ggplot(dftemp6%>% filter(measure != "uncorrected phasic"), aes(x = lag, y = Estimate, color = measure,shape=shape)) +
  annotate("rect", xmin = -0.5, ymin = -0.1, xmax = 0.5, ymax = 0.4, alpha = 0.1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`),
                width = 0.1) +
  labs(x = "Pupil size __ trials ago",
       y = "std. beta",
       title = "FMRI Study") +
  theme(legend.position = "none") +
  scale_color_manual(values = c("red4", "steelblue")) +
  scale_shape_identity()+   # use alpha directly
  scale_x_reverse(breaks = 0:9)

p4+p6
```

### the rolling mean version of arousal ~pupil
```{r}
vrmid1_pupil_data_arousal_history <- vrmid1_pupil_data_tonic %>%
  group_by(Subject) %>%
  mutate(
    map_dfc(0:9, function(k) {
      mean_lag <- map_dbl(seq_len(n()), function(i) {
        if (i <= (k+1) - 1) {
          NA  # Not enough previous data points
        } else {
          mean(pupil_Avg_baseline_scaled[(i - (k+1) + 1):i], na.rm = TRUE)
        }})
      setNames(data.frame(mean_lag), paste0("pupil_Avg_baseline_scaled_lag", k))
    }),
    map_dfc(0:9, function(k) {
      mean_lag <- map_dbl(seq_len(n()), function(i) {
        if (i <= (k+1) - 1) {
          NA  # Not enough previous data points
        } else {
          mean(pupil_Avg_bc_scaled[(i - (k+1) + 1):i], na.rm = TRUE)
        }})
      setNames(data.frame(mean_lag), paste0("pupil_Avg_bc_scaled_lag", k))
    }),
    map_dfc(0:9, function(k) {
      mean_lag <- map_dbl(seq_len(n()), function(i) {
        if (i <= (k+1) - 1) {
          NA  # Not enough previous data points
        } else {
          mean(pupil_Avg_scaled[(i - (k+1) + 1):i], na.rm = TRUE)
        }})
      setNames(data.frame(mean_lag), paste0("pupil_Avg_scaled_lag", k))
    }))

vrmid1_pupil_data_arousal_history <- vrmid1_pupil_data_arousal_history %>%
  pivot_longer(pupil_Avg_baseline_scaled_lag0:pupil_Avg_scaled_lag9,
               names_to = c("measure","lag"),names_pattern = "(.*)_lag(\\d+)", values_to = "pupil_size",
               names_prefix = "pupil_lag")

dftemp4 <- NULL

for (l in 0:9){
  l1<-summary(lmer(arousal_scaled ~ pupil_size + (1|Subject) + (1|probe)+(1|condition),
               vrmid1_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupil_Avg_baseline_scaled")))
  l2<-summary(lmer(arousal_scaled ~ pupil_size + (1|Subject) + (1|probe)+(1|condition),
               vrmid1_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupil_Avg_bc_scaled")))
  l3<-summary(lmer(arousal_scaled ~ pupil_size + (1|Subject) + (1|probe)+(1|condition),
               vrmid1_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupil_Avg_scaled")))
  dftemp4 <- rbind(dftemp4,
                  rbind(l1$coefficients[2,],
                        l2$coefficients[2,],
                        l3$coefficients[2,]))
}

dftemp4 <- as.data.frame(dftemp4)
dftemp4$lag <- rep(0:9,each=3)
dftemp4$measure <- rep(c("tonic","corrected phasic","uncorrected phasic"),10)
dftemp4 <- dftemp4 %>%
  group_by(measure) %>% 
  mutate(p_corrected = p.adjust(`Pr(>|t|)`, method = "fdr")) %>%
  mutate(shape = ifelse(p_corrected < .05, 19, 1))

p4 <- ggplot(dftemp4%>% filter(measure != "uncorrected phasic"), aes(x = lag, y = Estimate, color = measure,shape=shape)) +
  annotate("rect", xmin = -0.5, ymin = -0.1, xmax = 0.5, ymax = 0.4, alpha = 0.1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`),
                width = 0.1) +
  labs(x = "Rolling window size",
       y = "std. beta",
       title = "VR Study") +
  theme(legend.position = "none") +
  scale_color_manual(values = c("red4", "steelblue")) +
  scale_shape_identity()+   # use alpha directly
  scale_x_reverse(breaks = 0:9, labels = 1:10)

fmri3_pupil_data_arousal_history <- fmri3_pupil_data_tonic %>%
  group_by(subject) %>%
  mutate(
    map_dfc(0:9, function(k) {
      mean_lag <- map_dbl(seq_len(n()), function(i) {
        if (i <= (k+1) - 1) {
          NA  # Not enough previous data points
        } else {
          mean(pupilDiameter_baseline_scaled[(i - (k+1) + 1):i], na.rm = TRUE)
        }})
      setNames(data.frame(mean_lag), paste0("pupilDiameter_baseline_scaled_lag", k))
    }),
    map_dfc(0:9, function(k) {
      mean_lag <- map_dbl(seq_len(n()), function(i) {
        if (i <= (k+1) - 1) {
          NA  # Not enough previous data points
        } else {
          mean(pupilDiameter_bc_scaled[(i - (k+1) + 1):i], na.rm = TRUE)
        }})
      setNames(data.frame(mean_lag), paste0("pupilDiameter_bc_scaled_lag", k))
    }),
    map_dfc(0:9, function(k) {
      mean_lag <- map_dbl(seq_len(n()), function(i) {
        if (i <= (k+1) - 1) {
          NA  # Not enough previous data points
        } else {
          mean(pupilDiameter_scaled[(i - (k+1) + 1):i], na.rm = TRUE)
        }})
      setNames(data.frame(mean_lag), paste0("pupilDiameter_scaled_lag", k))
    }))


fmri3_pupil_data_arousal_history <- fmri3_pupil_data_arousal_history %>%
  pivot_longer(pupilDiameter_baseline_scaled_lag0:pupilDiameter_scaled_lag9,
               names_to = c("measure","lag"),names_pattern = "(.*)_lag(\\d+)", values_to = "pupil_size",
               names_prefix = "pupil_lag")

dftemp6 <- NULL

for (l in 0:9){
  l1<-summary(lmer(arousal_scaled ~ pupil_size + (1|subject) + (1|probe)+(1|cue_size),
               fmri3_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupilDiameter_baseline_scaled")))
  l2<-summary(lmer(arousal_scaled ~ pupil_size + (1|subject) + (1|probe)+(1|cue_size),
               fmri3_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupilDiameter_bc_scaled")))
  l3<-summary(lmer(arousal_scaled ~ pupil_size + (1|subject) + (1|probe)+(1|cue_size),
               fmri3_pupil_data_arousal_history %>% filter(lag == l,
                                                          measure == "pupilDiameter_scaled")))
  dftemp6 <- rbind(dftemp6,
                  rbind(l1$coefficients[2,],
                        l2$coefficients[2,],
                        l3$coefficients[2,]))
}

dftemp6 <- as.data.frame(dftemp6)
dftemp6$lag <- rep(0:9,each=3)
dftemp6$measure <- rep(c("tonic","corrected phasic","uncorrected phasic"),10)
dftemp6 <- dftemp6  %>%
  group_by(measure) %>% 
  mutate(p_corrected = p.adjust(`Pr(>|t|)`, method = "fdr")) %>%
  mutate(shape = ifelse(p_corrected < .05, 19, 1))

p6 <- ggplot(dftemp6%>% filter(measure != "uncorrected phasic"), aes(x = lag, y = Estimate, color = measure,shape=shape)) +
  annotate("rect", xmin = -0.5, ymin = -0.1, xmax = 0.5, ymax = 0.4, alpha = 0.1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`),
                width = 0.1) +
  labs(x = "Rolling window size",
       y = "std. beta",
       title = "FMRI Study") +
  theme(legend.position = "none") +
  scale_color_manual(values = c("red4", "steelblue")) +
  scale_shape_identity()+   # use alpha directly
  scale_x_reverse(breaks = 0:9, labels = 1:10)

p4+p6
```


## rt: should be predicted by arousal and pupil dilation
```{r}
vrmid1_data_rt <- vrmid1_pupil_data%>%
  filter(sample_in_trial_t <= vrmid1_ant_window[2] & sample_in_trial_t > vrmid1_ant_window[1]) %>% 
  group_by(probe,Subject,trial,reaction_outcome,trial_type,PosA_scaled,NegA_scaled,
           arousal,valence,last_ITI,
           arousal_scaled,valence_scaled,
           condition,reaction_time)%>%
  summarise(mean_pupil_bc = mean(pupil_Avg_bc_scaled, na.rm = T),
            mean_pupil_nobc = mean(pupil_Avg_scaled, na.rm = T),
            mean_pupil_baseline = mean(pupil_Avg_baseline_scaled, na.rm = T))%>%
  filter(abs(mean_pupil_bc) < 4,
         abs(mean_pupil_nobc) < 4,
         abs(mean_pupil_baseline) < 4)  %>% 
  group_by(Subject)%>%
  mutate(log_rt = log(reaction_time),
         log_rt = as.numeric(scale(log_rt)),
         hit = ifelse(reaction_outcome == "Hit",1,0)) 

fmri3_data_rt <- fmri3_pupil_data%>%
  filter(sample_in_trial_t <= fmri3_ant_window[2] & sample_in_trial_t > fmri3_ant_window[1]) %>% 
  group_by(probe,subject,trial,hit,cue_value,
           arousal,valence,last_iti,
           arousal_scaled,valence_scaled,
           cue_size,rt)%>%
  summarise(mean_pupil_bc = mean(pupilDiameter_bc_scaled, na.rm = T),
            mean_pupil_nobc = mean(pupilDiameter_scaled, na.rm = T),
            mean_pupil_baseline = mean(pupilDiameter_baseline_scaled, na.rm = T))%>%
  filter(abs(mean_pupil_bc) < 4,
         abs(mean_pupil_nobc) < 4,
         abs(mean_pupil_baseline) < 4)  %>% 
  group_by(subject)%>%
  mutate(log_rt = log(rt),
         log_rt = as.numeric(scale(log_rt)))

# summary(lmer(scale(log_rt) ~ scale(mean_pupil_baseline) +scale(mean_pupil_bc)+scale(arousal_scaled)+ (1|Subject) + (1|probe),vrmid1_data_rt %>% filter(hit == 1)))
# summary(lmer(scale(log_rt) ~ scale(mean_pupil_baseline) +scale(mean_pupil_bc)+scale(arousal_scaled)+ (1|Subject) + (1|probe),vrmid2_data_rt %>% filter(hit == 1)))
# summary(lmer(scale(log_rt) ~ scale(mean_pupil_baseline) + scale(mean_pupil_bc) + scale(arousal_scaled) + (1|subject),fmri3_data_rt %>% filter(hit == 1)))

rt_reg_coef <- as.data.frame(
  Reduce(rbind,list(
  summary(lmer(scale(log_rt) ~ scale(mean_pupil_bc) + scale(mean_pupil_baseline)+ (1|probe)+ (1|Subject),vrmid1_data_rt %>% filter(hit == 1)))$coefficients,
summary(lmer(scale(log_rt) ~ scale(arousal_scaled) + (1|Subject),vrmid1_data_rt %>% filter(hit == 1, probe == "anti")))$coefficients,

summary(lmer(scale(log_rt) ~ scale(mean_pupil_bc) + scale(mean_pupil_baseline)  + (1|probe) + (1|subject),fmri3_data_rt%>% filter(hit == "Hit")))$coefficients,
summary(lmer(scale(log_rt) ~ scale(arousal_scaled) + (1|subject),fmri3_data_rt %>% filter(hit == "Hit", probe == 1)))$coefficients))
) %>% 
  rownames_to_column() %>% 
  filter(!grepl("Intercept",rowname))

rt_reg_coef$study <- c("VRstudy","VRstudy","VRstudy","FMRIstudy","FMRIstudy","FMRIstudy")
rt_reg_coef$predictor <- rep(c("phasic_pupil","tonic_pupil","arousal"),2)

rt_reg_coef<-rt_reg_coef %>% 
  mutate(sig = ifelse(`Pr(>|t|)` >= .05, "n.s.",
                      ifelse(`Pr(>|t|)` >= .01, "*",
                             ifelse(`Pr(>|t|)` >= .005,"**","***"))))

rt_reg_coef$predictor <- factor(rt_reg_coef$predictor, levels = c("phasic_pupil","tonic_pupil","arousal"),
                                labels = c("corrected phasic pupil","tonic pupil","subjective arousal"))
rt_reg_coef$study <- factor(rt_reg_coef$study, levels = c("VRstudy","FMRIstudy"),
                                labels = c("VR study","FMRI study"))
pp<-ggplot(rt_reg_coef %>% filter(predictor != "subjective arousal"), aes(x = study, y = Estimate,
                        color = study))+
  geom_hline(yintercept = 0, linetype = "dashed")+
  geom_text(aes(x = study, y = Estimate+0.05,
                        color = study, label = sig))+
  geom_errorbar(aes(x = study, y = Estimate,ymin = Estimate-`Std. Error`,
                    ymax = Estimate+`Std. Error`,
                        color = study), width = 0.1)+
  geom_point(size = 3, shape = 5)+
  theme_bw()+
  facet_wrap(~predictor)+
  scale_color_brewer(palette = "Dark2")+
  theme(legend.position = "none",
        panel.grid = element_blank())+
  labs(y = "std. beta",
       x = "",
       title = "rt ~ tonic + phasic")
```


### get autocorrelation of phasic, tonic and arousal
```{r}
acf_results_vrmid1 <- vrmid1_pupil_data_tonic %>%
  group_by(Subject) %>% 
  summarise(across(
    c(arousal_scaled, valence_scaled, pupil_Avg_baseline_scaled,
      pupil_Avg_bc_scaled, pupil_Avg_scaled),
    ~ acf(na.omit(.x), plot = FALSE)$acf[2],
    .names = "{.col}"
  )) %>% 
  pivot_longer(arousal_scaled:pupil_Avg_scaled, names_to = "variable",values_to = "AR")

acf_results_vrmid1$variable <- factor(acf_results_vrmid1$variable,
                                     levels = c("arousal_scaled","valence_scaled",
                                                "pupil_Avg_baseline_scaled",
                                                "pupil_Avg_bc_scaled","pupil_Avg_scaled"),
                                     labels = c("arousal","valence","tonic","corrected phasic",
                                                "uncorrected phasic"))

t.test(acf_results_vrmid1$AR[acf_results_vrmid1$variable == "corrected phasic"])
t.test(acf_results_vrmid1$AR[acf_results_vrmid1$variable == "tonic"],
       acf_results_vrmid1$AR[acf_results_vrmid1$variable == "corrected phasic"],paired = T)

lar1 <- lmer(AR~variable + (1|Subject),acf_results_vrmid1)
cld_results <- multcomp::cld(emmeans(lar1, ~ variable), Letters = letters, adjust = "tukey")

cld_df <- as.data.frame(cld_results)

par1<-ggplot() +
  geom_violin(data=acf_results_vrmid1, aes(x = variable, y = AR),
              fill = "gray90", color = NA, width = 0.8) +
  # individual data points
  geom_jitter(data=acf_results_vrmid1, aes(x = variable, y = AR),
              width = 0.15, size = 1.2, alpha = 0.4, color = "gray40") +
  # mean and CI
  geom_point(data=cld_df,aes(x = variable, y = emmean),
             size = 1,color = "#2E86AB") +
  geom_errorbar(data=cld_df,aes(x = variable, ymin = emmean - SE, ymax = emmean + SE),  color = "#2E86AB", linewidth = 0.8,width = 0.2) +
  geom_text(data=cld_df,aes(x = variable, label = .group, y = emmean + SE + 0.1), vjust = 0) +
  labs(
    x = NULL,
    y = "Autocorrelation (lag 1)",
    subtitle = "VR Study",
  )+
  ylim(-0.5,1)+
  coord_flip()+
  # add semi-transparent white squares behind "valence" and "uncorrected phasic"
  annotate("rect",
           xmin = 1.5, xmax = 2.5,  # for "valence"
           ymin = -Inf, ymax = Inf,
           fill = "white", alpha = 0.5) +
  annotate("rect",
           xmin = 4.5, xmax = 5.5,  # for "uncorrected phasic"
           ymin = -Inf, ymax = Inf,
           fill = "white", alpha = 0.5)+
  annotate("rect",
           xmin = 0.5, xmax = 1.5,  # for "arousal"
           ymin = -Inf, ymax = Inf,
           fill = "white", alpha = 0.5)+
  geom_hline(yintercept = 0)


acf_results_fmri3 <- fmri3_pupil_data_tonic %>%
  group_by(subject) %>% 
  summarise(across(
    c(arousal_scaled, valence_scaled, pupilDiameter_baseline_scaled,
      pupilDiameter_bc_scaled, pupilDiameter_scaled),
    ~ acf(na.omit(.x), plot = FALSE)$acf[2],
    .names = "{.col}"
  )) %>% 
  pivot_longer(arousal_scaled:pupilDiameter_scaled, names_to = "variable",values_to = "AR")

acf_results_fmri3$variable <- factor(acf_results_fmri3$variable,
                                     levels = c("arousal_scaled","valence_scaled",
                                                "pupilDiameter_baseline_scaled",
                                                "pupilDiameter_bc_scaled","pupilDiameter_scaled"),
                                     labels = c("arousal","valence","tonic","corrected phasic",
                                                "uncorrected phasic"))

t.test(acf_results_fmri3$AR[acf_results_fmri3$variable == "corrected phasic"])
t.test(acf_results_fmri3$AR[acf_results_fmri3$variable == "tonic"],
       acf_results_fmri3$AR[acf_results_fmri3$variable == "corrected phasic"],paired = T)

lar3 <- lmer(AR~variable + (1|subject),acf_results_fmri3)
cld_results <- multcomp::cld(emmeans(lar3, ~ variable), Letters = letters, adjust = "tukey")

cld_df <- as.data.frame(cld_results)

par3<-ggplot() +
  geom_violin(data=acf_results_fmri3, aes(x = variable, y = AR),
              fill = "gray90", color = NA, width = 0.8) +
  # individual data points
  geom_jitter(data=acf_results_fmri3, aes(x = variable, y = AR),
              width = 0.15, size = 1.2, alpha = 0.4, color = "gray40") +
  # mean and CI
  geom_point(data=cld_df,aes(x = variable, y = emmean),
             size = 1,color = "#2E86AB") +
  geom_errorbar(data=cld_df,aes(x = variable, ymin = emmean - SE, ymax = emmean + SE),  color = "#2E86AB", linewidth = 0.8,width = 0.2) +
  geom_text(data=cld_df,aes(x = variable, label = .group, y = emmean + SE + 0.1), vjust = 0) +
  labs(
    x = NULL,
    y = "Autocorrelation (lag 1)",
    subtitle = "FMRI Study",
  )+
  ylim(-0.5,1)+
  coord_flip()+
  # add semi-transparent white squares behind "valence" and "uncorrected phasic"
  annotate("rect",
           xmin = 1.5, xmax = 2.5,  # for "valence"
           ymin = -Inf, ymax = Inf,
           fill = "white", alpha = 0.5) +
  annotate("rect",
           xmin = 4.5, xmax = 5.5,  # for "uncorrected phasic"
           ymin = -Inf, ymax = Inf,
           fill = "white", alpha = 0.5)+
  annotate("rect",
           xmin = 0.5, xmax = 1.5,  # for "arousal"
           ymin = -Inf, ymax = Inf,
           fill = "white", alpha = 0.5)+
  geom_hline(yintercept = 0)
par1+par3
ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/ar.png"),dpi = 300, height = 3, width = 9)
```

```{r}
(pt12|pt32|pt11|pt31)/
(par1+par3)
  # plot_annotation(tag_levels = "a")

ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig5_beh.png"),dpi = 300, height = 6, width = 10)

fig5 <- image_read("~/Desktop/VRMID-analysis/mid-pupil/figures/fig5_beh.png")
fig5 <- image_annotate(fig5, "A", size = 55, location = "+250+00", color = "black", gravity = "northwest")
fig5 <- image_annotate(fig5, "B", size = 55, location = "+1600+00", color = "black", gravity = "northwest")
fig5 <- image_annotate(fig5, "C", size = 55, location = "+250+950", color = "black", gravity = "northwest")
# fig5 <- image_annotate(fig5, "D", size = 55, location = "+1600+950", color = "black", gravity = "northwest")
image_write(fig5, "~/Desktop/VRMID-analysis/mid-pupil/figures/fig5_beh.png")
image_write(fig5, "~/Desktop/VRMID-analysis/mid-pupil/figures/fig5_beh.jpeg")
```

```{r}
pp<-ggplot(rt_reg_coef %>% filter(predictor == "subjective arousal"), aes(x = study, y = Estimate,
                        color = study))+
  geom_hline(yintercept = 0, linetype = "dashed")+
  geom_text(aes(x = study, y = Estimate+`Std. Error`+0.01,
                        color = study, label = sig))+
  geom_errorbar(aes(x = study, y = Estimate,ymin = Estimate-`Std. Error`,
                    ymax = Estimate+`Std. Error`,
                        color = study), width = 0.1)+
  geom_point(size = 3, shape = 5)+
  theme_bw()+
  facet_wrap(~predictor)+
  scale_color_brewer(palette = "Dark2")+
  theme(legend.position = "none",
        panel.grid = element_blank())+
  labs(y = "std. beta",
       x = "",
       title = "rt ~ arousal")

pt13+pt33+pt15+pt35+pp+
  plot_layout(nrow = 3)+
  plot_annotation(title = "Self-reported arousal",
                  tag_levels = "A")


ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig5_beh2.png"),dpi = 300, height = 9, width = 5)
```


# is pupil dilation  explained by valence or emotion categories?
(Can't make comparison between emotion vs. arousal because they are not the same trials)
## the valence bit
### vrmid1
```{r}
summary(lv1<-lmer(scale(mean_pupil_nobc_ant) ~  valence_scaled +(1|Subject) + (1|condition),
         vrmid1_data_antprobe))
summary(lv2<-lmer(scale(mean_pupil_bc_ant) ~  valence_scaled +(1|Subject) + (1|condition),
         vrmid1_data_antprobe))
summary(lv3<-lmer(scale(mean_pupil_baseline_ant) ~  valence_scaled +(1|Subject) + (1|condition),
         vrmid1_data_antprobe))

# Create a list of models for easy looping
models <- list(nobc = lv1, bc = lv2, baseline = lv3)

# Extract statistics into a dataframe
modcomp_results1 <- do.call(rbind, lapply(names(models), function(name) {
  model <- models[[name]]
  data.frame(
    model = name,
    coef = summary(model)$coefficients[2,1],
    t_val = summary(model)$coefficients[2,4],
    p_val = summary(model)$coefficients[2,5],
    R2_marginal = r.squaredGLMM(model)[1] * 100,  # Fixed-effects variance explained
    R2_conditional = r.squaredGLMM(model)[2] * 100 # Full model variance explained
  )
}))

summary(lv1<-lmer(scale(mean_pupil_nobc_out) ~  valence_scaled +(1|Subject) + (1|condition),
         vrmid1_data_outprobe))
summary(lv2<-lmer(scale(mean_pupil_bc_out) ~  valence_scaled +(1|Subject) + (1|condition),
         vrmid1_data_outprobe))
summary(lv3<-lmer(scale(mean_pupil_baseline_out) ~  valence_scaled +(1|Subject) + (1|condition),
         vrmid1_data_outprobe))

models <- list(nobc = lv1, bc = lv2, baseline = lv3)
# Extract statistics into a dataframe
modcomp_results2 <- do.call(rbind, lapply(names(models), function(name) {
  model <- models[[name]]
  data.frame(
    model = name,
    coef = summary(model)$coefficients[2,1],
    t_val = summary(model)$coefficients[2,4],
    p_val = summary(model)$coefficients[2,5],
    R2_marginal = r.squaredGLMM(model)[1] * 100,  # Fixed-effects variance explained
    R2_conditional = r.squaredGLMM(model)[2] * 100 # Full model variance explained
  )
}))

modcomp_results <- rbind(modcomp_results1 %>% 
                           mutate(probe = "anti"),
                         modcomp_results2 %>% 
                           mutate(probe = "out"))
kable(modcomp_results,digits = 3)
```


### fmri3
```{r}
summary(lv1<-lmer(scale(mean_pupil_nobc_scaled_ant) ~  valence_scaled +(1|subject) + (1|cue_size),
         fmri3_data_antprobe))
summary(lv2<-lmer(scale(mean_pupil_bc_scaled_ant) ~  valence_scaled +(1|subject) + (1|cue_size),
         fmri3_data_antprobe))
summary(lv3<-lmer(scale(mean_pupil_baseline_scaled) ~  valence_scaled +(1|subject) + (1|cue_size),
         fmri3_data_antprobe))

# Create a list of models for easy looping
models <- list(nobc = lv1, bc = lv2, baseline = lv3)

# Extract statistics into a dataframe
modcomp_results1 <- do.call(rbind, lapply(names(models), function(name) {
  model <- models[[name]]
  data.frame(
    model = name,
    coef = summary(model)$coefficients[2,1],
    t_val = summary(model)$coefficients[2,4],
    p_val = summary(model)$coefficients[2,5],
    R2_marginal = r.squaredGLMM(model)[1] * 100,  # Fixed-effects variance explained
    R2_conditional = r.squaredGLMM(model)[2] * 100 # Full model variance explained
  )
}))

summary(lv1<-lmer(scale(mean_pupil_nobc_scaled_out) ~  valence_scaled +(1|subject) + (1|cue_size),
         fmri3_data_outprobe))
summary(lv2<-lmer(scale(mean_pupil_bc_scaled_out) ~  valence_scaled +(1|subject) + (1|cue_size),
         fmri3_data_outprobe))
summary(lv3<-lmer(scale(mean_pupil_baseline_scaled) ~  valence_scaled +(1|subject) + (1|cue_size),
         fmri3_data_outprobe))


models <- list(nobc = lv1, bc = lv2, baseline = lv3)

# Extract statistics into a dataframe
modcomp_results2 <- do.call(rbind, lapply(names(models), function(name) {
  model <- models[[name]]
  data.frame(
    model = name,
    coef = summary(model)$coefficients[2,1],
    t_val = summary(model)$coefficients[2,4],
    p_val = summary(model)$coefficients[2,5],
    R2_marginal = r.squaredGLMM(model)[1] * 100,  # Fixed-effects variance explained
    R2_conditional = r.squaredGLMM(model)[2] * 100 # Full model variance explained
  )
}))

modcomp_results <- rbind(modcomp_results1 %>% 
                           mutate(probe = "anti"),
                         modcomp_results2 %>% 
                           mutate(probe = "out"))
kable(modcomp_results)
```

## the categorical emotion bit

### tally the count of emotions
```{r}
fmri3_data_antprobe_emo_tally <- fmri3_data_antprobe %>% 
  filter(rating_type == 2) %>% 
  group_by(subject) %>% 
  count(emotion) %>% 
  ungroup() %>% 
  group_by(emotion) %>% 
  summarise(freq = mean(n),
         se = sd(n)/sqrt(n()))%>% 
  mutate(emotion = factor(emotion, levels = c("Angry","Anxious","Sad","Calm","Happy","Excited")))

fmri3_data_outprobe_emo_tally <- fmri3_data_outprobe  %>% 
  filter(rating_type == 2) %>% 
  group_by(subject) %>% 
  count(emotion) %>% 
  ungroup() %>% 
  group_by(emotion) %>% 
  summarise(freq = mean(n),
         se = sd(n)/sqrt(n()))%>% 
  mutate(emotion = factor(emotion, levels = c("Angry","Anxious","Sad","Calm","Happy","Excited")))

  
pe0<- ggplot(fmri3_data_antprobe_emo_tally, 
       aes(x = emotion, y = freq, fill = emotion))+
  geom_col()+
    geom_errorbar(aes(x=emotion, y = freq, ymax = freq+se,
                    ymin=freq-se,fill = emotion),width=0.2)+
  scale_fill_manual(values = emotions_palette6)+
  labs(title = "anticipation probe",
       subtitle = "FMRI study")+
  theme(legend.position = "none")+
  
ggplot(fmri3_data_outprobe_emo_tally, 
       aes(x = emotion, y = freq, fill = emotion))+
  geom_col()+
    geom_errorbar(aes(x=emotion, y = freq, ymax = freq+se,
                    ymin=freq-se,fill = emotion),width=0.2)+
  scale_fill_manual(values = emotions_palette6)+
  labs(title = "outcome probe",
       subtitle = "")+
  theme(legend.position = "none")

```
### fmri3
```{r}
fmri3_data_antprobe <- fmri3_data_antprobe %>% mutate(emotion = factor(emotion, levels = c("Angry","Anxious","Sad","Calm","Happy","Excited")))
fmri3_data_outprobe <- fmri3_data_outprobe %>% mutate(emotion = factor(emotion, levels = c("Angry","Anxious","Sad","Calm","Happy","Excited")))

summary(lea1<-lmer(mean_pupil_nobc_scaled_ant ~  emotion +(1|subject) + (1|cue_size),
         fmri3_data_antprobe))
r.squaredGLMM(lea1)
cld_results <- multcomp::cld(emmeans(lea1, ~ emotion), Letters = letters, adjust = "tukey")

cld_df <- as.data.frame(cld_results)

pe3<-ggplot(cld_df, aes(x = emotion, y = emmean, color = emotion)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), width = 0.15) +
  geom_text(aes(label = .group, y = emmean + SE + 0.02), vjust = 0) +
  scale_color_manual(values = emotions_palette6)+
  labs(x = "Emotion", y = "Estimated marginal mean (pupil)",
       subtitle = "FMRI Study",
       title = "Anticipatory pupil size")+
  theme(legend.position = "none")+
  ylim(-0.4,0.8)+
  scale_x_discrete(breaks= c("Angry","Anxious","Sad","Calm","Happy","Excited"))

summary(leo1<-lmer(mean_pupil_nobc_scaled_ant ~  emotion +(1|subject) + (1|cue_size),
         fmri3_data_outprobe))
r.squaredGLMM(leo1)
cld_results <- multcomp::cld(emmeans(leo1, ~ emotion), Letters = letters, adjust = "tukey")

cld_df <- as.data.frame(cld_results)

pe4<-ggplot(cld_df, aes(x = emotion, y = emmean, color = emotion)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), width = 0.15) +
  geom_text(aes(label = .group, y = emmean + SE + 0.02), vjust = 0) +
  scale_color_manual(values = emotions_palette6)+
  labs(x = "Emotion", y = "Estimated marginal mean (pupil)",
       subtitle = "FMRI Study",
       title = "Outcome pupil size")+
  theme(legend.position = "none")+
  ylim(-0.4,0.8)+
  scale_x_discrete(breaks= c("Angry","Anxious","Sad","Calm","Happy","Excited"))
```

```{r}
pe0+
pe1+pe2+
pe3+pe4+
  plot_annotation(tag_levels = "A")+
  plot_layout(nrow = 3)

ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig_emo.png"),dpi = 300, height = 10, width = 8)
```

# finding the affective dimension that best matches pupil dilation (full signal)
```{r message = F, warning=F}
da <- vrmid1_data_antprobe
do <- vrmid1_data_outprobe

nbins = 360
angles = seq(0,pi/2, by = pi/(2*nbins))
angles = data.frame(angle1d = angles*180/pi,
                    angle1r = angles,
                    sin1 = sin(angles),
                    cos1 = cos(angles))

angles <- angles%>%
  mutate(angle2d = angle1d + 90,
         angle2r = angle1r + pi/2,
         sin2 = sin(angle2r),
         cos2 = cos(angle2r))

lmer_out1 <- {}

for (i in 1:nrow(angles)){
  angle_info = angles[i,]
  data_lm_anti_temp <- da%>%
    mutate(axis1 = valence_scaled * angle_info$cos1 + arousal_scaled * angle_info$sin1,
           axis2 = valence_scaled * angle_info$cos2 + arousal_scaled * angle_info$sin2)
  sum_temp1 <- summary(lmer(scale(axis1) ~ scale(mean_pupil_nobc_ant) + (1|Subject) + (1|condition),
              data_lm_anti_temp))
  sum_temp2 <- summary(lmer(scale(axis2) ~ scale(mean_pupil_nobc_ant) + (1|Subject) + (1|condition),
              data_lm_anti_temp))
  lmer_out1 <- rbind(lmer_out1, sum_temp1$coefficients[2,],sum_temp2$coefficients[2,])
}

lmer_out1 <- as.data.frame(lmer_out1)
lmer_out1$axis = rep(c("axis1","axis2"),nrow(angles))
  
lmer_out1[seq(1,nrow(angles)*2,by = 2),"angle"] = angles$angle1d
lmer_out1[seq(2,nrow(angles)*2,by = 2),"angle"] = angles$angle2d

lmer_out1[seq(1,nrow(angles)*2,by = 2),"sin"] = angles$sin1
lmer_out1[seq(2,nrow(angles)*2,by = 2),"sin"] = angles$sin2

lmer_out1[seq(1,nrow(angles)*2,by = 2),"cos"] = angles$cos1
lmer_out1[seq(2,nrow(angles)*2,by = 2),"cos"] = angles$cos2

lmer_out1$p_val <- (lmer_out1$`Pr(>|t|)` < 0.001)

a1f <- lmer_out1[which.max(abs(lmer_out1$Estimate)),]

lmer_out2 <- {}

for (i in 1:nrow(angles)){
  angle_info = angles[i,]
  data_lm_out_temp <- do%>%
    mutate(axis1 = valence_scaled * angle_info$cos1 + arousal_scaled * angle_info$sin1,
           axis2 = valence_scaled * angle_info$cos2 + arousal_scaled * angle_info$sin2)
  sum_temp1 <- summary(lmer(scale(axis1) ~ scale(mean_pupil_nobc_out) + (1|Subject) + (1|condition),
              data_lm_out_temp))
  sum_temp2 <- summary(lmer(scale(axis2) ~ scale(mean_pupil_nobc_out) + (1|Subject) + (1|condition),
              data_lm_out_temp))
  lmer_out2 <- rbind(lmer_out2, sum_temp1$coefficients[2,],sum_temp2$coefficients[2,])
}

lmer_out2 <- as.data.frame(lmer_out2)
lmer_out2$axis = rep(c("axis1","axis2"),nrow(angles))
  
lmer_out2[seq(1,nrow(angles)*2,by = 2),"angle"] = angles$angle1d
lmer_out2[seq(2,nrow(angles)*2,by = 2),"angle"] = angles$angle2d

lmer_out2[seq(1,nrow(angles)*2,by = 2),"sin"] = angles$sin1
lmer_out2[seq(2,nrow(angles)*2,by = 2),"sin"] = angles$sin2

lmer_out2[seq(1,nrow(angles)*2,by = 2),"cos"] = angles$cos1
lmer_out2[seq(2,nrow(angles)*2,by = 2),"cos"] = angles$cos2

lmer_out2$p_val <- (lmer_out2$`Pr(>|t|)` < 0.001)

a2f <- lmer_out2[which.max(abs(lmer_out2$Estimate)),]

vrmid1_axes <- rbind(a1f,a2f)
vrmid1_axes$condition <- c("anti","outcome")

vrmid1_axes <- vrmid1_axes%>%
  mutate(rad = angle/180 *pi,
         cos = cos(rad),
         sin = sin(rad))
```


```{r message = F, warning=F}
da <- fmri3_data_antprobe
do <- fmri3_data_outprobe

nbins = 360
angles = seq(0,pi/2, by = pi/(2*nbins))
angles = data.frame(angle1d = angles*180/pi,
                    angle1r = angles,
                    sin1 = sin(angles),
                    cos1 = cos(angles))

angles <- angles%>%
  mutate(angle2d = angle1d + 90,
         angle2r = angle1r + pi/2,
         sin2 = sin(angle2r),
         cos2 = cos(angle2r))

lmer_out1 <- {}

for (i in 1:nrow(angles)){
  angle_info = angles[i,]
  data_lm_anti_temp <- da%>%
    mutate(axis1 = valence_scaled * angle_info$cos1 + arousal_scaled * angle_info$sin1,
           axis2 = valence_scaled * angle_info$cos2 + arousal_scaled * angle_info$sin2)
  sum_temp1 <- summary(lmer(scale(axis1) ~ scale(mean_pupil_nobc_scaled_ant) + (1|subject) + (1|cue_size),
              data_lm_anti_temp))
  sum_temp2 <- summary(lmer(scale(axis2) ~ scale(mean_pupil_nobc_scaled_ant) + (1|subject) + (1|cue_size),
              data_lm_anti_temp))
  lmer_out1 <- rbind(lmer_out1, sum_temp1$coefficients[2,],sum_temp2$coefficients[2,])
}

lmer_out1 <- as.data.frame(lmer_out1)
lmer_out1$axis = rep(c("axis1","axis2"),nrow(angles))
  
lmer_out1[seq(1,nrow(angles)*2,by = 2),"angle"] = angles$angle1d
lmer_out1[seq(2,nrow(angles)*2,by = 2),"angle"] = angles$angle2d

lmer_out1[seq(1,nrow(angles)*2,by = 2),"sin"] = angles$sin1
lmer_out1[seq(2,nrow(angles)*2,by = 2),"sin"] = angles$sin2

lmer_out1[seq(1,nrow(angles)*2,by = 2),"cos"] = angles$cos1
lmer_out1[seq(2,nrow(angles)*2,by = 2),"cos"] = angles$cos2

lmer_out1$p_val <- (lmer_out1$`Pr(>|t|)` < 0.001)

a1f <- lmer_out1[which.max(abs(lmer_out1$Estimate)),]

lmer_out2 <- {}

for (i in 1:nrow(angles)){
  angle_info = angles[i,]
  data_lm_out_temp <- do%>%
    mutate(axis1 = valence_scaled * angle_info$cos1 + arousal_scaled * angle_info$sin1,
           axis2 = valence_scaled * angle_info$cos2 + arousal_scaled * angle_info$sin2)
  sum_temp1 <- summary(lmer(scale(axis1) ~ scale(mean_pupil_nobc_scaled_out) + (1|subject) + (1|cue_size),
              data_lm_out_temp))
  sum_temp2 <- summary(lmer(scale(axis2) ~ scale(mean_pupil_nobc_scaled_out) + (1|subject) + (1|cue_size),
              data_lm_out_temp))
  lmer_out2 <- rbind(lmer_out2, sum_temp1$coefficients[2,],sum_temp2$coefficients[2,])
}

lmer_out2 <- as.data.frame(lmer_out2)
lmer_out2$axis = rep(c("axis1","axis2"),nrow(angles))
  
lmer_out2[seq(1,nrow(angles)*2,by = 2),"angle"] = angles$angle1d
lmer_out2[seq(2,nrow(angles)*2,by = 2),"angle"] = angles$angle2d

lmer_out2[seq(1,nrow(angles)*2,by = 2),"sin"] = angles$sin1
lmer_out2[seq(2,nrow(angles)*2,by = 2),"sin"] = angles$sin2

lmer_out2[seq(1,nrow(angles)*2,by = 2),"cos"] = angles$cos1
lmer_out2[seq(2,nrow(angles)*2,by = 2),"cos"] = angles$cos2

lmer_out2$p_val <- (lmer_out2$`Pr(>|t|)` < 0.001)

a2f <- lmer_out2[which.max(abs(lmer_out2$Estimate)),]

fmri3_axes <- rbind(a1f,a2f)
fmri3_axes$condition <- c("anti","outcome")

fmri3_axes <- fmri3_axes%>%
  mutate(rad = angle/180 *pi,
         cos = cos(rad),
         sin = sin(rad))
```

## plot the axes
```{r}
p1<-ggplot(vrmid1_axes%>%
         mutate(cos = cos * abs(Estimate),
                sin = sin * abs(Estimate)))+
  geom_segment(aes(x = -0.4, y = 0,
                   xend = 0.4, yend = 0),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "grey")+
  geom_segment(aes(x = 0, y = -0.4,
                   xend = 0, yend = 0.4),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "grey")+
  geom_segment(aes(x = 0,y = 0,
                   xend = cos, yend = sin,
                   color = condition),
               size = 1, arrow = arrow(length = unit(0.03, "npc")))+
  geom_segment(aes(x = 0, y = 0,
                   xend = -0.3, yend = 0.3),
               size = 1, linetype = "dashed",
               color = "grey")+ #45 degree line
  geom_text(aes(x = cos * 1.2, y = sin * 1.1, color = condition, label = round(Estimate,2)),
            size = 5,check_overlap = F)+
  scale_color_manual(values = c("purple","skyblue"))+
  scale_y_continuous()+
  labs(x = "",
       y = "",
       subtitle = "VR study",
       title = "all trials combined")+
  theme_blank()+
  theme(legend.position = "none",
         axis.ticks = element_blank(),
    axis.text = element_blank())+
  annotate("text",x=0.21,y = -0.1, label = "anticipation probe", color = "purple")+
  annotate("text",x=0.2,y = -0.15, label = "outcome probe", color = "skyblue")+
  annotate("text",x=0.43,y = 0, label = "z-scored valence rating", color = "grey", angle = 90)+
  annotate("text",x=-0.04,y = -0.43, label = "z-scored arousal rating", color = "grey")



p3<-ggplot(fmri3_axes%>%
         mutate(cos = cos * abs(Estimate),
                sin = sin * abs(Estimate)))+
  geom_segment(aes(x = -0.4, y = 0,
                   xend = 0.4, yend = 0),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "grey")+
  geom_segment(aes(x = 0, y = -0.4,
                   xend = 0, yend = 0.4),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "grey")+
    geom_segment(aes(x = 0, y = 0,
                   xend = -0.3, yend = 0.3),
               size = 1, linetype = "dashed",
               color = "grey")+
  geom_segment(aes(x = 0,y = 0,
                   xend = cos, yend = sin,
                   color = condition),
               size = 1, arrow = arrow(length = unit(0.03, "npc")))+
  geom_text(aes(x = cos * 1.2, y = sin * 1.2, color = condition, label = round(Estimate,2)),
            size = 5,check_overlap = F)+
  scale_color_manual(values = c("purple","skyblue"))+
  labs(x = "",
       y = "",
       subtitle = "FMRI study")+
  theme_blank()+
  theme(legend.position = "none",
         axis.ticks = element_blank(),
    axis.text = element_blank())+
  annotate("text",x=0.43,y = 0, label = "z-scored valence rating", color = "grey", angle = 90)+
  annotate("text",x=-0.04,y = -0.43, label = "z-scored arousal rating", color = "grey")

p1+p3

ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig2_axes.png"),dpi = 300, height = 4, width = 7)

```

# finding the affective dimension that best matches pupil dilation, dependent on valence
```{r message = F, warning=F}
da <- vrmid1_data_antprobe
do <- vrmid1_data_outprobe

lmer_out1 <- {}

for (v in 1:2){
  for (i in 1:nrow(angles)){
    if (v == 1){
      cues = c("+$5","+$1","+$0")
    } else {
      cues = c("-$5","-$1","-$0")
    }
    
    angle_info = angles[i,]
    data_lm_anti_temp <- da%>%
      filter(trial_type %in% cues) %>% 
      mutate(axis1 = valence_scaled * angle_info$cos1 + arousal_scaled * angle_info$sin1,
             axis2 = valence_scaled * angle_info$cos2 + arousal_scaled * angle_info$sin2)
    sum_temp1 <- summary(lmer(scale(axis1) ~ scale(mean_pupil_nobc_ant) + (1|Subject) + (1|condition),
                data_lm_anti_temp))
    sum_temp2 <- summary(lmer(scale(axis2) ~ scale(mean_pupil_nobc_ant) + (1|Subject) + (1|condition),
                data_lm_anti_temp))
    lmer_out1 <- rbind(lmer_out1, sum_temp1$coefficients[2,],sum_temp2$coefficients[2,])
}
}


lmer_out1 <- as.data.frame(lmer_out1)
lmer_out1$valence <- rep(c("pos","neg"), each = nrow(angles)*2)
lmer_out1$axis <- rep(c("axis1","axis2"), times = nrow(angles)*2)
  
lmer_out1[seq(1,nrow(angles)*4,by = 2),"angle"] = angles$angle1d
lmer_out1[seq(2,nrow(angles)*4,by = 2),"angle"] = angles$angle2d

lmer_out1[seq(1,nrow(angles)*4,by = 2),"sin"] = angles$sin1
lmer_out1[seq(2,nrow(angles)*4,by = 2),"sin"] = angles$sin2

lmer_out1[seq(1,nrow(angles)*4,by = 2),"cos"] = angles$cos1
lmer_out1[seq(2,nrow(angles)*4,by = 2),"cos"] = angles$cos2

lmer_out1$p_val <- (lmer_out1$`Pr(>|t|)` < 0.001)

lmer_out1a <- lmer_out1 %>% filter(valence == "pos")
lmer_out1b <- lmer_out1 %>% filter(valence == "neg")
a1fv <- rbind(lmer_out1a[which.max(abs(lmer_out1a$Estimate)),],
              lmer_out1b[which.max(abs(lmer_out1b$Estimate)),])


lmer_out2 <- {}

for (v in 1:2){
  if (v == 1){
    out = "Hit"
  } else {
    out = "Miss"
  }
  for (i in 1:nrow(angles)){
    angle_info = angles[i,]
    data_lm_out_temp <- do%>%
      filter(reaction_outcome == out) %>% 
      mutate(axis1 = valence_scaled * angle_info$cos1 + arousal_scaled * angle_info$sin1,
             axis2 = valence_scaled * angle_info$cos2 + arousal_scaled * angle_info$sin2)
    sum_temp1 <- summary(lmer(scale(axis1) ~ scale(mean_pupil_nobc_out) + (1|Subject) + (1|condition),
                data_lm_out_temp))
    sum_temp2 <- summary(lmer(scale(axis2) ~ scale(mean_pupil_nobc_out) + (1|Subject) + (1|condition),
                data_lm_out_temp))
    lmer_out2 <- rbind(lmer_out2, sum_temp1$coefficients[2,],sum_temp2$coefficients[2,])
}
}


lmer_out2 <- as.data.frame(lmer_out2)
lmer_out2$valence <- rep(c("pos","neg"), each = nrow(angles)*2)
lmer_out2$axis <- rep(c("axis1","axis2"), times = nrow(angles)*2)

  
lmer_out2[seq(1,nrow(angles)*4,by = 2),"angle"] = angles$angle1d
lmer_out2[seq(2,nrow(angles)*4,by = 2),"angle"] = angles$angle2d

lmer_out2[seq(1,nrow(angles)*4,by = 2),"sin"] = angles$sin1
lmer_out2[seq(2,nrow(angles)*4,by = 2),"sin"] = angles$sin2

lmer_out2[seq(1,nrow(angles)*4,by = 2),"cos"] = angles$cos1
lmer_out2[seq(2,nrow(angles)*4,by = 2),"cos"] = angles$cos2

lmer_out2$p_val <- (lmer_out2$`Pr(>|t|)` < 0.001)

lmer_out2a <- lmer_out2 %>% filter(valence == "pos")
lmer_out2b <- lmer_out2 %>% filter(valence == "neg")
a2fv <- rbind(lmer_out2a[which.max(abs(lmer_out2a$Estimate)),],
              lmer_out2b[which.max(abs(lmer_out2b$Estimate)),])

vrmid1_axes_v <- rbind(a1fv,a2fv)
vrmid1_axes_v$condition <- rep(c("anti","outcome"),each=2)

vrmid1_axes_v <- vrmid1_axes_v%>%
  mutate(rad = angle/180 *pi,
         cos = cos(rad),
         sin = sin(rad))
```


```{r message = F, warning=F}
da <- fmri3_data_antprobe
do <- fmri3_data_outprobe

lmer_out1 <- {}

for (v in 1:2){
  for (i in 1:nrow(angles)){
    if (v == 1){
      cues = c("+$5","+$1","+$0")
    } else {
      cues = c("-$5","-$1","-$0")
    }
    
    angle_info = angles[i,]
    data_lm_anti_temp <- da%>%
      filter(cue_value %in% cues) %>% 
      mutate(axis1 = valence_scaled * angle_info$cos1 + arousal_scaled * angle_info$sin1,
             axis2 = valence_scaled * angle_info$cos2 + arousal_scaled * angle_info$sin2)
    sum_temp1 <- summary(lmer(scale(axis1) ~ scale(mean_pupil_nobc_scaled_ant) + (1|subject) + (1|cue_size),
                data_lm_anti_temp))
    sum_temp2 <- summary(lmer(scale(axis2) ~ scale(mean_pupil_nobc_scaled_ant) + (1|subject) + (1|cue_size),
                data_lm_anti_temp))
    lmer_out1 <- rbind(lmer_out1, sum_temp1$coefficients[2,],sum_temp2$coefficients[2,])
}
}


lmer_out1 <- as.data.frame(lmer_out1)
lmer_out1$valence <- rep(c("pos","neg"), each = nrow(angles)*2)
lmer_out1$axis <- rep(c("axis1","axis2"), times = nrow(angles)*2)
  
lmer_out1[seq(1,nrow(angles)*4,by = 2),"angle"] = angles$angle1d
lmer_out1[seq(2,nrow(angles)*4,by = 2),"angle"] = angles$angle2d

lmer_out1[seq(1,nrow(angles)*4,by = 2),"sin"] = angles$sin1
lmer_out1[seq(2,nrow(angles)*4,by = 2),"sin"] = angles$sin2

lmer_out1[seq(1,nrow(angles)*4,by = 2),"cos"] = angles$cos1
lmer_out1[seq(2,nrow(angles)*4,by = 2),"cos"] = angles$cos2

lmer_out1$p_val <- (lmer_out1$`Pr(>|t|)` < 0.001)

lmer_out1a <- lmer_out1 %>% filter(valence == "pos")
lmer_out1b <- lmer_out1 %>% filter(valence == "neg")
a1fv <- rbind(lmer_out1a[which.max(abs(lmer_out1a$Estimate)),],
              lmer_out1b[which.max(abs(lmer_out1b$Estimate)),])


lmer_out2 <- {}

for (v in 1:2){
  if (v == 1){
    out = "Hit"
  } else {
    out = "Miss"
  }
  for (i in 1:nrow(angles)){
    angle_info = angles[i,]
    data_lm_out_temp <- do%>%
      filter(hit == out) %>% 
      mutate(axis1 = valence_scaled * angle_info$cos1 + arousal_scaled * angle_info$sin1,
             axis2 = valence_scaled * angle_info$cos2 + arousal_scaled * angle_info$sin2)
    sum_temp1 <- summary(lmer(scale(axis1) ~ scale(mean_pupil_nobc_scaled_out) + (1|subject) + (1|cue_size),
                data_lm_out_temp))
    sum_temp2 <- summary(lmer(scale(axis2) ~ scale(mean_pupil_nobc_scaled_out)+ (1|subject) + (1|cue_size),
                data_lm_out_temp))
    lmer_out2 <- rbind(lmer_out2, sum_temp1$coefficients[2,],sum_temp2$coefficients[2,])
}
}


lmer_out2 <- as.data.frame(lmer_out2)
lmer_out2$valence <- rep(c("pos","neg"), each = nrow(angles)*2)
lmer_out2$axis <- rep(c("axis1","axis2"), times = nrow(angles)*2)

  
lmer_out2[seq(1,nrow(angles)*4,by = 2),"angle"] = angles$angle1d
lmer_out2[seq(2,nrow(angles)*4,by = 2),"angle"] = angles$angle2d

lmer_out2[seq(1,nrow(angles)*4,by = 2),"sin"] = angles$sin1
lmer_out2[seq(2,nrow(angles)*4,by = 2),"sin"] = angles$sin2

lmer_out2[seq(1,nrow(angles)*4,by = 2),"cos"] = angles$cos1
lmer_out2[seq(2,nrow(angles)*4,by = 2),"cos"] = angles$cos2

lmer_out2$p_val <- (lmer_out2$`Pr(>|t|)` < 0.001)

lmer_out2a <- lmer_out2 %>% filter(valence == "pos")
lmer_out2b <- lmer_out2 %>% filter(valence == "neg")
a2fv <- rbind(lmer_out2a[which.max(abs(lmer_out2a$Estimate)),],
              lmer_out2b[which.max(abs(lmer_out2b$Estimate)),])

fmri3_axes_v <- rbind(a1fv,a2fv)
fmri3_axes_v$condition <- rep(c("anti","outcome"),each=2)

fmri3_axes_v <- fmri3_axes_v%>%
  mutate(rad = angle/180 *pi,
         cos = cos(rad),
         sin = sin(rad))
```

## plot the axes
```{r}
p1<-ggplot(vrmid1_axes_v%>%
         mutate(cos = cos * abs(Estimate),
                sin = sin * abs(Estimate)))+
  geom_segment(aes(x = -0.4, y = 0,
                   xend = 0.4, yend = 0),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "grey")+
  geom_segment(aes(x = 0, y = -0.4,
                   xend = 0, yend = 0.4),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "grey")+
  geom_segment(aes(x = 0,y = 0,
                   xend = cos, yend = sin,
                   color = condition,
                   linetype = valence),
               size = 1, arrow = arrow(length = unit(0.03, "npc")))+
  geom_segment(aes(x = 0, y = 0,
                   xend = -0.3, yend = 0.3),
               size = 1, linetype = "dashed",
               color = "grey")+ #45 degree line
  # geom_text(aes(x = cos * 1.2, y = sin * 1.1, color = condition, label = round(Estimate,2)),
  #           size = 5,check_overlap = F)+
  
  scale_color_manual(values = c("purple","skyblue"))+
  scale_y_continuous()+
  labs(x = "",
       y = "",
       title = "By cue valence",
       subtitle = "VR study")+
  theme_blank()+
  theme(legend.position = "none",
         axis.ticks = element_blank(),
    axis.text = element_blank())+
  scale_linetype_manual(values = c("pos" = "solid", "neg" = "dotted")) +
  annotate("text",x=0.21,y = -0.1, label = "anticipation probe", color = "purple")+
  annotate("text",x=0.2,y = -0.15, label = "outcome probe", color = "skyblue")+
  annotate("text",x=0.43,y = 0, label = "z-scored valence rating", color = "grey", angle = 90)+
  annotate("text",x=-0.04,y = -0.43, label = "z-scored arousal rating", color = "grey")

p3<-ggplot(fmri3_axes_v%>%
         mutate(cos = cos * abs(Estimate),
                sin = sin * abs(Estimate)))+
  geom_segment(aes(x = -0.4, y = 0,
                   xend = 0.4, yend = 0),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "grey")+
  geom_segment(aes(x = 0, y = -0.4,
                   xend = 0, yend = 0.4),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "grey")+
    geom_segment(aes(x = 0, y = 0,
                   xend = -0.3, yend = 0.3),
               size = 1, linetype = "dashed",
               color = "grey")+
  geom_segment(aes(x = 0,y = 0,
                   xend = cos, yend = sin,
                   color = condition,
                   linetype = valence),
               size = 1, arrow = arrow(length = unit(0.03, "npc")))+
  # geom_text(aes(x = cos * 1.2, y = sin * 1.2, color = condition, label = round(Estimate,2)),
  #           size = 5,check_overlap = F)+
  scale_color_manual(values = c("purple","skyblue"))+
  scale_linetype_manual(values = c("pos" = "solid", "neg" = "dotted")) +
  labs(x = "",
       y = "",
       subtitle = "FMRI study",
       caption = "solid = positive, dotted = negative")+
  theme_blank()+
  theme(legend.position = "none",
         axis.ticks = element_blank(),
    axis.text = element_blank())+
  annotate("text",x=0.43,y = 0, label = "z-scored valence rating", color = "grey", angle = 90)+
  annotate("text",x=-0.04,y = -0.43, label = "z-scored arousal rating", color = "grey")
```

```{r}
p1+p3

ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig2_axes2.png"),dpi = 300, height = 4, width = 7)

fig2a <- image_read("~/Desktop/VRMID-analysis/mid-pupil/figures/fig2_axes.png")
fig2b <- image_read("~/Desktop/VRMID-analysis/mid-pupil/figures/fig2_axes2.png")
fig2a <- image_annotate(fig2a, "A", size = 60, location = "+30+10", color = "black", gravity = "northwest")
fig2b <- image_annotate(fig2b, "B", size = 60, location = "+30+10", color = "black", gravity = "northwest")
# Stack the images vertically
combined <- image_append(c(fig2a, fig2b), stack = TRUE)

# Save the combined image
image_write(combined, "~/Desktop/VRMID-analysis/mid-pupil/figures/fig2_axes3.png")
```



# time course correlation

## get the correlation time series
```{r warning = F, message=F}
vrmid1_regression_coefs_ant_nobc <- {}

for (t in 1:20) {
  coefs <- {}
  print(t)
  for (s in 1:120){
  df_ant_temp <- vrmid1_pupil_data%>%
  filter(probe == "anti",Time_sec == t, sample_in_sec == s)
  lm_ant_temp <- lmer(scale(arousal_scaled) ~ scale(pupil_Avg_scaled) + (1|Subject) + (1|condition),df_ant_temp)
  lm_out <- c(summary(lm_ant_temp)$coefficient[2,],'r2m' = r.squaredGLMM(lm_ant_temp)[1])
  coefs <- rbind(coefs,lm_out)
  }
  coefs <- as.data.frame(coefs)%>%
    mutate(sample_in_sec = row_number(),
           Time_sec = t)
  rownames(coefs) <- NULL
  vrmid1_regression_coefs_ant_nobc <- rbind(vrmid1_regression_coefs_ant_nobc,coefs)
}

vrmid1_regression_coefs_ant_nobc <- vrmid1_regression_coefs_ant_nobc%>%
  mutate(sample_point = row_number())%>%
  rename(p_val = `Pr(>|t|)`) %>% 
  mutate(p_val_fdr = p.adjust(p_val, method = "fdr")) #applies the Benjamini–Hochberg correction

write.csv(vrmid1_regression_coefs_ant_nobc, "../../data/vrmid1/derivatives/vrmid1_regression_coefs_ant_nobc.csv")
vrmid1_regression_coefs_ant_nobc<-read_csv("../../data/vrmid1/derivatives/vrmid1_regression_coefs_ant_nobc.csv")

vrmid1_regression_coefs_out_nobc <- {}

for (t in 1:20) {
  coefs <- {}
  print(t)
  for (s in 1:120){
  df_out_temp <- vrmid1_pupil_data%>%
  filter(probe == "out",Time_sec == t, sample_in_sec == s)
  lm_out_temp <- lmer(scale(arousal_scaled) ~ scale(pupil_Avg_bc_scaled) + (1|Subject) + (1|condition),df_out_temp)
  lm_out <- summary(lm_out_temp)$coefficient[2,]
  coefs <- rbind(coefs,lm_out) 
  }
  coefs <- as.data.frame(coefs)%>%
    mutate(sample_in_sec = row_number(),
           Time_sec = t)
  rownames(coefs) <- NULL
  vrmid1_regression_coefs_out_nobc <- rbind(vrmid1_regression_coefs_out_nobc,coefs)
}

vrmid1_regression_coefs_out_nobc <- vrmid1_regression_coefs_out_nobc%>%
  mutate(sample_point = row_number())%>%
  rename(p_val = `Pr(>|t|)`) %>% 
  mutate(p_val_fdr = p.adjust(p_val, method = "fdr")) #applies the Benjamini–Hochberg correction

write.csv(vrmid1_regression_coefs_out_nobc,  "../../data/vrmid1/derivatives/vrmid1_regression_coefs_out_nobc.csv")
vrmid1_regression_coefs_out_nobc<-read_csv("../../data/vrmid1/derivatives/vrmid1_regression_coefs_out_nobc.csv")

fmri3_regression_coefs_ant_nobc <- {}

for (t in 1:20) {
  coefs <- {}
  print(t)
  for (s in 1:200){
  df_ant_temp <- fmri3_pupil_data%>%
  filter(probe == 1,Time_sec == t, sample_in_sec == s)
  lm_ant_temp <- lmer(scale(arousal_scaled) ~ scale(pupilDiameter_scaled) + (1|subject) + (1|cue_size),df_ant_temp)
  lm_out <- c(summary(lm_ant_temp)$coefficient[2,],'r2m' = r.squaredGLMM(lm_ant_temp)[1])
  coefs <- rbind(coefs,lm_out)
  }
  coefs <- as.data.frame(coefs)%>%
    mutate(sample_in_sec = row_number(),
           Time_sec = t)
  rownames(coefs) <- NULL
  fmri3_regression_coefs_ant_nobc <- rbind(fmri3_regression_coefs_ant_nobc,coefs)
}

fmri3_regression_coefs_ant_nobc <- fmri3_regression_coefs_ant_nobc%>%
  mutate(sample_point = row_number())%>%
    rename(p_val = `Pr(>|t|)`) %>% 
  mutate(p_val_fdr = p.adjust(p_val, method = "fdr")) #applies the Benjamini–Hochberg correction

write.csv(fmri3_regression_coefs_ant_nobc, "../../data/fmri3//derivatives/fmri3_regression_coefs_ant_nobc.csv")
fmri3_regression_coefs_ant_nobc<-read_csv("../../data/fmri3/derivatives/fmri3_regression_coefs_ant_nobc.csv")

fmri3_regression_coefs_out_nobc <- {}

for (t in 1:20) {
  coefs <- {}
  print(t)
  for (s in 1:200){
  df_out_temp <- fmri3_pupil_data%>%
  filter(probe == 2,Time_sec == t, sample_in_sec == s)
  lm_out_temp <-  lmer(scale(arousal_scaled) ~ scale(pupilDiameter_scaled) + (1|subject) + (1|cue_size),df_out_temp)
  lm_out <- summary(lm_out_temp)$coefficient[2,]
  coefs <- rbind(coefs,lm_out) 
  }
  coefs <- as.data.frame(coefs)%>%
    mutate(sample_in_sec = row_number(),
           Time_sec = t)
  rownames(coefs) <- NULL
  fmri3_regression_coefs_out_nobc <- rbind(fmri3_regression_coefs_out_nobc,coefs)
}

fmri3_regression_coefs_out_nobc <- fmri3_regression_coefs_out_nobc%>%
  mutate(sample_point = row_number())%>%
    rename(p_val = `Pr(>|t|)`) %>% 
  mutate(p_val_fdr = p.adjust(p_val, method = "fdr")) #applies the Benjamini–Hochberg correction

write.csv(fmri3_regression_coefs_out_nobc,  "../../data/fmri3/derivatives/fmri3_regression_coefs_out_nobc.csv")
fmri3_regression_coefs_out_nobc <- read_csv("../../data/fmri3/derivatives/fmri3_regression_coefs_out_nobc.csv")
```
## make clusters
```{r}

# threshold and min cluster length
p_thresh <- 1e-3
mark_clusters <- function(df, p_thresh, min_cluster_length, merge_gap) {
  # df must contain columns: p_val_fdr and sample_in_sec (or any per-row index)
  # min_cluster_length and merge_gap are in SAMPLES (not seconds).
  
  # Ensure ordering and create sample index (1..N)
  df <- df %>%
    arrange(Time_sec, sample_in_sec) %>%
    mutate(.row_idx = seq_len(n()))
  
  # Logical vector: below threshold
  below <- df$p_val_fdr < p_thresh
  
  # Identify runs of TRUE / FALSE using rle
  r <- rle(below)
  lens <- r$lengths
  vals <- r$values
  ends <- cumsum(lens)
  starts <- ends - lens + 1
  runs <- tibble(
    run_id = seq_along(lens),
    start_idx = starts,
    end_idx = ends,
    length = lens,
    is_true = vals
  )
  
  # Keep only TRUE runs (candidate significant clusters)
  true_runs <- runs %>% filter(is_true)
  
  if (nrow(true_runs) == 0) {
    df$sig_cluster <- NA
    return(df %>% select(-.row_idx))
  }
  
  # Compute gaps between consecutive TRUE runs
  true_runs <- true_runs %>%
    arrange(start_idx) %>%
    mutate(
      prev_end = lag(end_idx),
      gap = if_else(is.na(prev_end), NA, start_idx - prev_end - 1L)
    )
  
  # start new merge group whenever gap > merge_gap or NA
  true_runs <- true_runs %>%
    mutate(new_group = cumsum(if_else(is.na(gap) | gap > merge_gap, 1L, 0L)))
  
  # Summarize merged groups
  merged <- true_runs %>%
    group_by(new_group) %>%
    summarise(
      start_idx = first(start_idx),
      end_idx = last(end_idx),
      size = sum(length),
      .groups = "drop"
    ) %>%
    filter(size >= min_cluster_length)
  
  # If no merged cluster passes min length, return NA sig_cluster
  if (nrow(merged) == 0) {
    df$sig_cluster <- NA
    return(df %>% select(-.row_idx))
  }
  
  # Create logical mask of significant samples
  sig_mask <- rep(FALSE, nrow(df))
  for (i in seq_len(nrow(merged))) {
    si <- merged$start_idx[i]
    ei <- merged$end_idx[i]
    si <- max(1L, as.integer(si))
    ei <- min(nrow(df), as.integer(ei))
    sig_mask[si:ei] <- TRUE
  }
  
  # Assign sig_cluster column (1 = significant, NA = not)
  df$sig_cluster <- ifelse(sig_mask, 1L, NA)
  
  # Drop helper column and return
  df <- df %>% select(-.row_idx)
  return(df)
}



min_cluster_length <- 1 * 120  # 1s
merge_gap <- 0.3 * 120          # 0.1s

# Apply to all datasets
vrmid1_regression_coefs_out_nobc <- mark_clusters(vrmid1_regression_coefs_out_nobc, p_thresh, min_cluster_length,merge_gap)
vrmid1_regression_coefs_ant_nobc <- mark_clusters(vrmid1_regression_coefs_ant_nobc, p_thresh, min_cluster_length,merge_gap)

min_cluster_length <- 1 * 200  # 0.5s * 200 samples/sec = 100 samples
merge_gap <- 0.3 * 200          # 0.1s * 200 samples/sec = 20 samples
fmri3_regression_coefs_ant_nobc  <- mark_clusters(fmri3_regression_coefs_ant_nobc,  p_thresh, min_cluster_length,merge_gap)
fmri3_regression_coefs_out_nobc  <- mark_clusters(fmri3_regression_coefs_out_nobc,  p_thresh, min_cluster_length,merge_gap)
```

## plots
```{r}
axis_range=c(min(c(vrmid1_regression_coefs_ant_nobc$Estimate-vrmid1_regression_coefs_ant_nobc$`Std. Error`,
                   #vrmid2_regression_coefs_ant_nobc$Estimate-vrmid2_regression_coefs_ant_nobc$`Std. Error`,
                   fmri3_regression_coefs_ant_nobc$Estimate-fmri3_regression_coefs_ant_nobc$`Std. Error`,
                   vrmid1_regression_coefs_out_nobc$Estimate-vrmid1_regression_coefs_out_nobc$`Std. Error`,
                   #vrmid2_regression_coefs_out_nobc$Estimate-vrmid2_regression_coefs_out_nobc$`Std. Error`,
                   fmri3_regression_coefs_out_nobc$Estimate-fmri3_regression_coefs_out_nobc$`Std. Error`)),
             max(vrmid1_regression_coefs_ant_nobc$Estimate+vrmid1_regression_coefs_ant_nobc$`Std. Error`,
                   #vrmid2_regression_coefs_ant_nobc$Estimate+vrmid2_regression_coefs_ant_nobc$`Std. Error`,
                   fmri3_regression_coefs_ant_nobc$Estimate+fmri3_regression_coefs_ant_nobc$`Std. Error`,
                   vrmid1_regression_coefs_out_nobc$Estimate+vrmid1_regression_coefs_out_nobc$`Std. Error`,
                   #vrmid2_regression_coefs_out_nobc$Estimate+vrmid2_regression_coefs_out_nobc$`Std. Error`,
                   fmri3_regression_coefs_out_nobc$Estimate+fmri3_regression_coefs_out_nobc$`Std. Error`))

p1a<-ggplot(vrmid1_regression_coefs_ant_nobc, aes(x = sample_point,y = Estimate))+
    geom_vline(xintercept = c(0,4,6,14,16,18)*120, size = 1, color = "grey")+
  geom_vline(xintercept = c(2030,783), size = 1, color = "orange", linetype = "dashed")+
  annotate("text", x = 2*120,y = 0.1, label = "C",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 5*120,y = 0.1, label = "F",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 15*120,y = 0.1, label = "T",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 17*120,y = 0.1, label = "O",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 10*120,y = 0.1, label = "R",
          color = "black",size = unit(4,"pt"))+
  geom_line(aes(color = Estimate),
             size = 1)+
   geom_ribbon(aes(x = sample_point, y = Estimate, ymin = Estimate - `Std. Error`,
                  ymax = Estimate + `Std. Error`),alpha = 0.1,
             size = 0.1)+
  geom_point(aes(x = sample_point, y = sig_cluster-1),
             size = 0.1)+
  scale_x_continuous(breaks = seq(0,120*20,5*120), labels =  seq(0,20,5))+
  labs(x = "time (sec)",
       y =  "Standardized beta",
       title = "VR study",
       subtitle = "anticipation probe",
       color = "")+
  scale_color_viridis_c(limits=axis_range)+
  ylim(axis_range)+
  theme_blank()+
  theme(legend.position = "left")+
  annotation_custom(
    grob = grid::rectGrob(gp = grid::gpar(fill = "white", alpha = 1, col = NA)),
    xmin = 14.1*120, xmax = 21*120, ymin = -Inf, ymax = Inf
  )

p1b<-ggplot(vrmid1_regression_coefs_out_nobc, aes(x = sample_point,y = Estimate))+
  geom_vline(xintercept = c(0,4,6,8,10,18)*120, size = 1, color = "grey")+
  geom_vline(xintercept = c(1134), size = 1, color = "orange", linetype = "dashed")+
  geom_point(aes(x = sample_point, y = sig_cluster-1),
             size = 0.1)+
  geom_ribbon(aes(x = sample_point, y = Estimate, ymin = Estimate - `Std. Error`,
                  ymax = Estimate + `Std. Error`),alpha = 0.1,
             size = 0.1)+
  annotate("text", x = 2*120,y = 0.02, label = "C",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 5*120,y =0.02, label = "F",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 7*120,y = 0.02, label = "T",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 9*120,y = 0.02, label = "O",
          color = "black",size = unit(4,"pt"))+
    annotate("text", x = 14*120,y = 0.02, label = "R",
          color = "black",size = unit(4,"pt"))+
   geom_line(aes(color = Estimate),
             size = 1)+
  scale_x_continuous(breaks = seq(0,120*20,5*120), label = seq(0,20,5))+
  labs(x = "time (sec)",
       y =  "",
       title = "VR study",
       subtitle = "outcome probe")+
  scale_color_viridis_c(limits=axis_range)+
  theme_blank()+
  ylim(axis_range)+
    theme(legend.position = "none")+
  annotation_custom(
    grob = grid::rectGrob(gp = grid::gpar(fill = "white", alpha = 1, col = NA)),
    xmin = 18.1*120, xmax = 20.5*120, ymin = -Inf, ymax = Inf
  )

p3a<-ggplot(fmri3_regression_coefs_ant_nobc, aes(x = sample_point,y = Estimate))+
  geom_vline(xintercept = c(0,2,4,12,14,16,18)*200, size = 1, color = "grey")+
  geom_vline(xintercept = c(826,3291), size = 1, color = "orange", linetype = "dashed")+
  geom_point(aes(x = sample_point, y = sig_cluster-1),
             size = 0.1)+
     geom_ribbon(aes(x = sample_point, y = Estimate, ymin = Estimate - `Std. Error`,
                  ymax = Estimate + `Std. Error`),alpha = 0.1,
             size = 0.1)+
  annotate("text", x = 1*200,y = 0.1, label = "C",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 3*200,y = 0.1, label = "F",
          color = "black",size = unit(4,"pt"))+
    annotate("text", x = 13*200,y = 0.1, label = "F",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 15*200,y = 0.1, label = "T",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 17*200,y = 0.1, label = "O",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 8*200,y = 0.1, label = "R",
          color = "black",size = unit(4,"pt"))+
  geom_line(aes(color = Estimate),
             size = 1)+
  scale_x_continuous(breaks = seq(0,200*20,5*200), labels =  seq(0,20,5))+
  labs(x = "time (sec)",
       y =  "",
       title = "FMRI study",
       subtitle = "anticipation probe")+
  scale_color_viridis_c(limits=axis_range)+
  theme_blank()+
  ylim(axis_range)+
  theme(legend.position = "none")+
  annotation_custom(
    grob = grid::rectGrob(gp = grid::gpar(fill = "white", alpha = 1, col = NA)),
    xmin = 12.1*200, xmax = 21*200, ymin = -Inf, ymax = Inf
  )

p3b<-ggplot(fmri3_regression_coefs_out_nobc %>% filter(sample_point <= 18*200), aes(x = sample_point,y = Estimate))+
  geom_vline(xintercept = c(0,2,4,6,8,16)*200, size = 1, color = "grey")+
  geom_vline(xintercept = c(1294), size = 1, color = "orange", linetype = "dashed")+
  geom_point(aes(x = sample_point, y = sig_cluster-1),
             size = 0.1)+
   geom_ribbon(aes(x = sample_point, y = Estimate, ymin = Estimate - `Std. Error`,
                  ymax = Estimate + `Std. Error`),alpha = 0.1,
             size = 0.1)+
  annotate("text", x = 1*200,y = 0.02, label = "C",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 3*200,y =0.02, label = "F",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 5*200,y = 0.02, label = "T",
          color = "black",size = unit(4,"pt"))+
  annotate("text", x = 7*200,y = 0.02, label = "O",
          color = "black",size = unit(4,"pt"))+
    annotate("text", x = 12*200,y = 0.02, label = "R",
          color = "black",size = unit(4,"pt"))+
    geom_line(aes(color = Estimate),
             size = 1)+
 scale_x_continuous(breaks = seq(0,200*20,5*200), labels =  seq(0,20,5))+
  labs(x = "time (sec)",
       y =  "",
       title = "FMRI study",
       subtitle = "outcome probe",
      caption = "C = Cue, F = Fixation, \nT = Target, O = Outcome, R = Rating")+
  scale_color_viridis_c(limits=axis_range)+
  theme_blank()+
  ylim(axis_range)+
  theme(legend.position = "none")+
  annotation_custom(
    grob = grid::rectGrob(gp = grid::gpar(fill = "white", alpha = 1, col = NA)),
    xmin = 16.1*200, xmax = 19*200, ymin = -Inf, ymax = Inf
  )
```


# combining two probes
# is tonic pupil a function of the previous iti?
```{r}
summary(lmer(scale(mean_pupil_baseline) ~  scale(last_ITI) +(1|Subject),
              vrmid1_data_2probes))

summary(lmer(scale(mean_pupil_baseline) ~  scale(last_iti) +(1|subject),
              fmri3_data_2probes))
```

## group all 3 studies together for a master correlation
```{r}
wrap_elements(full = grid::textGrob("Separated by probe type", gp = grid::gpar(fontsize = 14, fontface = "bold"), just = "left"))/
(p1a+p1b)/(p3a+p3b)+        
plot_layout(heights = c(0.2,1.5,1.5))


ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig7_howlongago2.png"),dpi = 300, height = 8, width = 8)

fig1 <- magick::image_read("~/Desktop/VRMID-analysis/mid-pupil/figures/fig7_howlongago2.png")
fig1 <-  magick::image_annotate(fig1, "A", size = 70, location = "+200+120", color = "black", gravity = "northwest")
fig1 <-  magick::image_annotate(fig1, "B", size = 70, location = "+200+1200", color = "black", gravity = "northwest")

magick::image_write(fig1, "~/Desktop/VRMID-analysis/mid-pupil/figures/fig7_howlongago2.png")
```

