---
title: "pooled_analyses"
output: html_document
date: "2024-10-21"
---

```{r setup, include=FALSE}
source("~/Desktop/VRMID-analysis/mid-pupil/analyses/load_libraries.R")
knitr::opts_chunk$set(echo = TRUE)

theme_set(theme_blank() + #set the theme 
            theme(text = element_text(family = "Helvetica",size = 12))) #set the default text size

redOrange_palette6 = c("red","salmon","darkred","goldenrod3","orange","gold")
redOrange_palette2 = c("tomato4","gold")
emotions_palette6 = c( "Angry"="red", "Anxious"="orange","Excited"="gold", "Happy"="green3","Calm"="skyblue3","Sad"="purple")
emotions_palette2 = c("orangered","pink1")
emotions_palette2b = c("orange","red")
```

```{r}
# run this to re-load the data
rm(list = ls())
```

## define the time windows of interest (1.5-3.5s after fixation onset, or 0.5-2.5s after outcome onset)
```{r}
vrmid1_ant_window = c(4,6)+1.5
fmri3_ant_window = c(2,4)+1.5

vrmid1_antprobe_out_window = c(15,17)+1.5
fmri3_antprobe_out_window = c(15,17)+1.5

vrmid1_outprobe_out_window = c(7,9)+1.5
fmri3_outprobe_out_window = c(5,7)+1.5
```


# read in pupil data
```{r}
source("~/Desktop/VRMID-analysis/mid-pupil/analyses/step2_pooled_analyses/helper/load_pupil_data.R")
```


# demographics

```{r}
## number of participants
vrmid1_subject_n
fmri3_subject_n
vrmid1_subject_n+fmri3_subject_n
```

```{r}
vrmid1_demographics <- qualtRics::read_survey("../../data/vrmid1/subjects_list/VRMID1 post-task survey_label.csv") %>% 
  rename(Subject = `Subject ID`) %>% 
  filter(Subject %in% vrmid1_subjects)

#deal with the subject name mismatch
fmri3_demographics <-  read_csv("../../data/fmri3/subjects_list/demographics-fmri3.csv") %>% 
              rename(subject = id) %>% 
  mutate(subject = ifelse(subject == "as240304","as240303",
                          ifelse(subject == "ek240305","ek240304",
                                 ifelse(subject == "sg240305","sg240304",
                                        ifelse(subject == "qn240330","nq240330",subject))))) %>% 
  filter(subject %in% fmri3_subjects)
```

```{r}
table(vrmid1_demographics$Sex)
table(fmri3_demographics$gender)

mosaic::fav_stats(as.numeric(vrmid1_demographics$Age),na.rm = T)
mosaic::fav_stats(as.numeric(fmri3_demographics$age),na.rm = T)
```

# report behavioral performance 
```{r}
rmarkdown::render("analyses_by_sections/s1_beh_performance.Rmd")
```

# check left vs. right pupil correlation
```{r}
summary(l1<-lm(scale(pupil_L) ~ scale(pupil_R),vrmid1_pupil_data))
```


#plot pupil time course
```{r}
rmarkdown::render("analyses_by_sections/s2_plot_timecourse.Rmd")
```

# pre-selected time window predicting affect
```{r}
source("~/Desktop/VRMID-analysis/mid-pupil/analyses/step2_pooled_analyses/helper/calculate_df.R")
```

# manipulation check for how incentive value influence rating and pupil size
```{r}
rmarkdown::render("analyses_by_sections/s3_manipulation_check_cue.Rmd")
```

# calculate separate effect sizes for each study
```{r}
rmarkdown::render("analyses_by_sections/s4a_reg_by_study.Rmd")
```

## get cross-validated accuracy for the lmers above
```{r}
rmarkdown::render("analyses_by_sections/s4b_lmer_cross_validation.Rmd")
```
# in addition to lmer, also try a machine learning approach in predicting arousal
```{r}
rmarkdown::render("analyses_by_sections/s5_pupil_svr.Rmd")
```

# behavioral implications of pupil-linked arousal (fatigue and rt)
```{r}
rmarkdown::render("analyses_by_sections/s6_tonic_phasic_behavior.Rmd")
```

# is pupil size  explained by valence or emotion categories?
```{r}
rmarkdown::render("analyses_by_sections/s7_affect_dimension.Rmd")
```

# finding the combination of valence and arousal that best matches pupil dilation
```{r}
rmarkdown::render("analyses_by_sections/s8_affect_rotation.Rmd")
```

# time course analysis for the regression weights
```{r}
rmarkdown::render("analyses_by_sections/s9_reg_timecourse.Rmd")
```

# for the fmri study, check whether the template could predict pupil size in held-out trials
```{r}
rmarkdown::render("analyses_by_sections/s10_template_similarity.Rmd")
```

# for the fmri study, get the cluster table
```{r}
rmarkdown::render("analyses_by_sections/s11_cluster_table.Rmd")
```