---
title: "pooled_analyses"
output: html_document
date: "2024-10-21"
---

```{r setup, include=FALSE}
source("~/Desktop/VRMID-analysis/mid-pupil/analyses/load_libraries.R")
knitr::opts_chunk$set(echo = TRUE)
theme_set(theme_blank() + #set the theme 
            theme(text = element_text(family = "Helvetica",size = 12))) #set the default text size
purpleOrange_palette6 = c("purple4","purple2","plum3","khaki","gold","goldenrod4")
purpleOrange_palette2 = c("purple4","gold")
emotions_palette6 = c( "Angry"="red", "Anxious"="orange","Excited"="gold", "Happy"="green3","Calm"="skyblue3","Sad"="purple")
emotions_palette2 = c("orangered","pink1")
```

# read in pupil data

## vrmid1
```{r}
vrmid1_pupil_data <- read_csv("~/Desktop/VRMID-analysis/mid-pupil/data/vrmid1/derivatives/pupillometry_lowpass_baselineCorrected.csv")%>%
  group_by(Subject)%>%
  mutate(arousal_scaled = as.numeric(scale(arousal)),
         valence_scaled = as.numeric(scale(valence)))%>%
  ungroup()

vrmid1_bad_participants <- read_delim("../../data/vrmid1/subjects_list/subject_to_drop_pupil.txt", col_names = F, delim = " ")

vrmid1_pupil_data <- vrmid1_pupil_data %>% 
  filter(!Subject %in% c("cn221206","vx220916"), #manual bad participants
         !Subject %in% vrmid1_bad_participants) 

vrmid1_subjects <- unique(vrmid1_pupil_data$Subject)
vrmid1_subject_n<-length(vrmid1_subjects)
vrmid1_subject_n

for (i in 1:vrmid1_subject_n){
  ggplot(vrmid1_pupil_data %>% filter(Subject == vrmid1_subjects[i]), aes(x = sample_in_trial_t, y = pupil_Avg))+
    geom_line()+
    facet_wrap(~trial)+
    labs(title = i)

  ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/vrmid1/examine_data/trial_figs/",vrmid1_subjects[i],".png"),dpi = 300, height = 7, width = 14)
}

vrmid1_pupil_data$trial_type <- factor(vrmid1_pupil_data$trial_type, levels = c("-$5","-$1","-$0","+$0","+$1","+$5"))

#zscoring
vrmid1_pupil_data <- vrmid1_pupil_data%>%
  group_by(Subject)%>%
  mutate_at(vars(pupil_L,pupil_R,pupil_Avg,pupil_L_baseline,pupil_R_baseline,pupil_Avg_baseline,pupil_L_bc,pupil_R_bc,pupil_Avg_bc), 
            list(scale = scale))

vrmid1_pupil_data <- vrmid1_pupil_data%>%
  mutate(sample_in_trial_t = round(sample_in_trial_t,4))

vrmid1_pupil_data<-vrmid1_pupil_data %>% 
  filter(abs(pupil_Avg_scale)<5)
```
## vrmid2
```{r}
vrmid2_pupil_data <- read_csv("~/Desktop/VRMID-analysis/mid-pupil/data/vrmid2/derivatives/pupillometry_baselineCorrected.csv")%>%
  group_by(Subject)%>%
  mutate(arousal_scaled = as.numeric(scale(arousal)),
         valence_scaled = as.numeric(scale(valence)))%>%
  ungroup()

vrmid2_bad_participants <- read_delim("../../data/vrmid2/subjects_list/subject_to_drop_pupil.txt", col_names = F, delim = " ")

vrmid2_pupil_data <- vrmid2_pupil_data %>% 
  filter(Subject != "ar230607",#only has 3 trials of data
         !Subject %in% vrmid2_bad_participants) 

vrmid2_subjects <- unique(vrmid2_pupil_data$Subject)
vrmid2_subject_n<-length(vrmid2_subjects)

for (i in 1:vrmid2_subject_n){
  ggplot(vrmid2_pupil_data %>% filter(Subject == vrmid2_subjects[i]), aes(x = sample_in_trial_t, y = pupil_Avg))+
    geom_line()+
    facet_wrap(~trial)+
    labs(title = i)

  ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/vrmid2/examine_data/trial_figs/",vrmid2_subjects[i],".png"),dpi = 300, height = 7, width = 14)
}


#zscoring
vrmid2_pupil_data <- vrmid2_pupil_data%>%
  group_by(Subject)%>%
  mutate_at(vars(pupil_L,pupil_R,pupil_Avg,pupil_L_baseline,pupil_R_baseline,pupil_Avg_baseline,pupil_L_bc,pupil_R_bc,pupil_Avg_bc), 
            list(scale = scale))

vrmid2_pupil_data <- vrmid2_pupil_data%>%
  mutate(sample_in_trial_t = round(sample_in_trial_t,4))

vrmid2_pupil_data <- vrmid2_pupil_data%>%
  group_by(Subject, sample_in_trial_n)%>%
  ungroup()%>%
  mutate(emotion_cat = ifelse(emotion %in% c("Angry","Anxious","Excited"),
                              "high_arous",
                              ifelse(emotion %in% c("Calm","Happy","Sad"),
                              "low_arous",NA)))

vrmid2_pupil_data$emotion <- factor(vrmid2_pupil_data$emotion, levels = c("Angry","Anxious","Excited",
                                                                            "Happy","Calm","Sad"))

vrmid2_pupil_data$trial_type <- factor(vrmid2_pupil_data$trial_type, levels = c("minus5","minus1","minus0","plus0","plus1","plus5"),
                                       labels = c("-$5","-$1","-$0","+$0","+$1","+$5"))

vrmid2_pupil_data<-vrmid2_pupil_data %>% 
  filter(abs(pupil_Avg_scale)<5)
```
## fmri3
```{r}
fmri3_pupil_data <- read_csv("~/Desktop/VRMID-analysis/mid-pupil/data/fmri3/derivatives/pupillometry_baselineCorrected.csv") %>% 
  mutate(cue_value = factor(trialtype, levels = 1:6, labels = c("-$0","-$1","-$5","+$0","+$1","+$5"))) %>% 
  filter(!is.na(subject)) %>% 
  ungroup() %>% 
  group_by(subject) %>% 
  mutate(pupilDiameter_scaled = as.numeric(scale(pupilDiameter)),
         pupilDiameter_bc_scaled = as.numeric(scale(pupilDiameter_bc)),
         pupilDiameter_baseline_scaled = as.numeric(scale(pupilDiameter_baseline)))

fmri3_bad_participants <- read_delim("../../data/fmri3/subjects_list/subject_to_drop_pupil.txt", col_names = F, delim = " ")

fmri3_pupil_data <- fmri3_pupil_data %>% 
  filter(!sub_id %in% fmri3_bad_participants) %>% 
  filter(!subject %in% c("sk240301","hc240324","js240311","jy240308","tc240311","el240312"))#these are manual exclusions based on data collection notes


 

fmri3_subjects <- unique(fmri3_pupil_data$subject)
fmri3_subject_n<-length(fmri3_subjects)
fmri3_subject_n

fmri3_pupil_data$cue_value <- factor(fmri3_pupil_data$cue_value,
                                levels = c("-$5","-$1","-$0","+$0","+$1","+$5"))

fmri3_pupil_data$emotion <- fmri3_pupil_data$erating

fmri3_pupil_data$emotion <- factor(fmri3_pupil_data$emotion, levels = 1:6, 
                           labels = c("Anxious","Angry","Sad","Calm","Happy","Excited"))

fmri3_pupil_data$arousal <- fmri3_pupil_data$arating
fmri3_pupil_data$valence <- fmri3_pupil_data$vrating

fmri3_pupil_data <- fmri3_pupil_data %>% 
  mutate(emotion_cat = ifelse(emotion %in% c("Anxious","Angry","Excited"),"higharous",
                              ifelse(emotion %in% c("Sad","Calm","Happy"),"lowarous",NA)))%>%
  ungroup()%>%
  group_by(subject) %>% 
  mutate(arousal_scaled = as.numeric(scale(arousal)),
         valence_scaled = as.numeric(scale(valence)))

for (i in 1:fmri3_subject_n){
  ggplot(fmri3_pupil_data %>% filter(subject == fmri3_subjects[i]), aes(x = sample_in_trial_t, y = pupilDiameter_scaled))+
    geom_line()+
    facet_wrap(~trial)+
    labs(title = i)

  ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fmri3/examine_data/trial_figs/",fmri3_subjects[i],".png"),dpi = 300, height = 7, width = 14)
}

fmri3_pupil_data$hit <- factor(fmri3_pupil_data$hit,levels = c(1,0), labels = c("Hit","Miss"))
fmri3_pupil_data$cue_size <- factor(fmri3_pupil_data$cue_size,levels = c(1,2), labels = c("small","large"))

fmri3_pupil_data<-fmri3_pupil_data %>% 
  filter(abs(pupilDiameter_scaled)<5) %>% 
  group_by(subject, trial, Time_sec) %>% 
  mutate(sample_in_sec = row_number())
```

# read in demographics
```{r}
vrmid1_subject_n+vrmid2_subject_n+fmri3_subject_n
```

# plot example time courses

## entire timeline (1 line)
```{r}
vrmid1_summary_nobc <- vrmid1_pupil_data%>%
  ungroup()%>%
  group_by(sample_in_trial_t,probe)%>%
  summarise(mean = mean(pupil_Avg_scale, na.rm = T),
            lower = mean(pupil_Avg_scale, na.rm = T) - qt(0.975, df = n() - 1) * sd(pupil_Avg_scale, na.rm = T) / sqrt(n()),
            upper = mean(pupil_Avg_scale, na.rm = T) + qt(0.975, df = n() - 1) * sd(pupil_Avg_scale, na.rm = T) / sqrt(n()))

p1a<-ggplot(vrmid1_summary_nobc%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == "anti"), aes(x = sample_in_trial_t,
                       y = mean))+
  geom_vline(xintercept = c(0,4,6,14,16,18), size = 1, color = "grey")+
  geom_line(size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2)+
  scale_color_manual(values = purpleOrange_palette6)+
  scale_fill_manual(values = purpleOrange_palette6)+
  annotate("text", x = 2,y = 0.7, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 0.7, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 15,y = 0.7, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 17,y = 0.7, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 10,y = 0.7, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "VR study 1",
       subtitle = "anticipation probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  ylim(-1.5,1.5)

p1b<-ggplot(vrmid1_summary_nobc%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == "out"), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,4,6,8,10,18), size = 1, color = "grey")+
  geom_line(size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2)+
  scale_color_manual(values = purpleOrange_palette6)+
  scale_fill_manual(values = purpleOrange_palette6)+
  annotate("text", x = 2,y = 0.7, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 0.7, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 7,y = 0.7, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 9,y = 0.7, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 14,y = 0.7, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "VR study 1",
       subtitle = "outcome probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  ylim(-1.3,1.0)

vrmid2_summary_nobc <- vrmid2_pupil_data%>%
  ungroup()%>%
  group_by(sample_in_trial_t,probe)%>%
  summarise(mean = mean(pupil_Avg_scale, na.rm = T),
            lower = mean(pupil_Avg_scale, na.rm = T) - qt(0.975, df = n() - 1) * sd(pupil_Avg_scale, na.rm = T) / sqrt(n()),
            upper = mean(pupil_Avg_scale, na.rm = T) + qt(0.975, df = n() - 1) * sd(pupil_Avg_scale, na.rm = T) / sqrt(n()))

p2a<-ggplot(vrmid2_summary_nobc%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == "anti"), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,4,6,14,16,18), size = 1, color = "grey")+
  geom_line(size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2)+
  annotate("text", x = 2,y = 0.7, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 0.7, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 15,y = 0.7, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 17,y = 0.7, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 10,y = 0.7, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "VR study 2",
       subtitle = "anticipation probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  ylim(-1.3,1.0)

p2b<-ggplot(vrmid2_summary_nobc%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == "out"), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,4,6,8,10,18), size = 1, color = "grey")+
  geom_line(size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2)+
  scale_color_manual(values = purpleOrange_palette6)+
  scale_fill_manual(values = purpleOrange_palette6)+
  annotate("text", x = 2,y = 0.7, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 0.7, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 7,y = 0.7, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 9,y = 0.7, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 13,y = 0.7, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "VR study 2",
       subtitle = "outcome probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  ylim(-1.3,1)

fmri3_summary_nobc <- fmri3_pupil_data%>%
  ungroup()%>%
  group_by(sample_in_trial_t,probe)%>%
  summarise(mean = mean(pupilDiameter_scaled, na.rm = T),
            lower = mean(pupilDiameter_scaled, na.rm = T) - qt(0.975, df = n() - 1) * sd(pupilDiameter_scaled, na.rm = T) / sqrt(n()),
            upper = mean(pupilDiameter_scaled, na.rm = T) + qt(0.975, df = n() - 1) * sd(pupilDiameter_scaled, na.rm = T) / sqrt(n()))

p3a<-ggplot(fmri3_summary_nobc%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == 1), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,2,4,12,14,16,18), size = 1, color = "grey")+
  geom_line(size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2)+

  annotate("text", x = 1,y = 0.7, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 3,y = 0.7, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 13,y = 0.7, label = "fix2",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 15,y = 0.7, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 17,y = 0.7, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 8,y = 0.7, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "FMRI study 3",
       subtitle = "anticipation probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  ylim(-1.3,1)

p3b<-ggplot(fmri3_summary_nobc%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == 2), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,2,4,6,8,16), size = 1, color = "grey")+
  geom_line(size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2)+
  scale_color_manual(values = purpleOrange_palette6)+
  scale_fill_manual(values = purpleOrange_palette6)+
  annotate("text", x = 1,y = 0.7, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 3,y = 0.7, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 0.7, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 7,y = 0.7, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 12,y = 0.7, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "FMRI study 3",
       subtitle = "outcome probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  ylim(-1.3,1)

pant<-p1a+p2a+p3a+
  plot_layout(nrow =1)

pout<-p1b+p2b+p3b+
  plot_layout(nrow =1)

pant/pout
ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig1_timecourse.tiff"),dpi = 300, height = 6, width = 8)
```

## time course by cue value

```{r}
vrmid1_summary_nobc <- vrmid1_pupil_data%>%
  ungroup()%>%
  group_by(sample_in_trial_t,probe,trial_type)%>%
  summarise(mean = mean(pupil_Avg_scale, na.rm = T),
            lower = mean(pupil_Avg_scale, na.rm = T) - qt(0.975, df = n() - 1) * sd(pupil_Avg_scale, na.rm = T) / sqrt(n()),
            upper = mean(pupil_Avg_scale, na.rm = T) + qt(0.975, df = n() - 1) * sd(pupil_Avg_scale, na.rm = T) / sqrt(n()))

p1a<-ggplot(vrmid1_summary_nobc%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == "anti"), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,4,6,14,16,18), size = 1, color = "grey")+
  geom_line(aes(group = trial_type, color = trial_type),size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t, fill = trial_type,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2)+
  scale_color_manual(values = purpleOrange_palette6)+
  scale_fill_manual(values = purpleOrange_palette6)+
  annotate("text", x = 2,y = 1, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 1, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 15,y = 1, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 17,y = 1, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 10,y = 1, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "VR study 1",
       subtitle = "anticipation probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  theme(legend.position = "top")+
  ylim(-1.5,1.5)

p1b<-ggplot(vrmid1_summary_nobc%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == "out"), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,4,6,8,10,18), size = 1, color = "grey")+
  geom_line(aes(group = trial_type, color = trial_type),size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t, fill = trial_type,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2)+
  scale_color_manual(values = purpleOrange_palette6)+
  scale_fill_manual(values = purpleOrange_palette6)+
  annotate("text", x = 2,y = 1, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 1, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 7,y = 1, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 9,y = 1, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 13,y = 1, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "VR study 1",
       subtitle = "outcome probe",
       x = "time (s)",
       y = "z-scored pupil size")+
   theme(legend.position = "none")+
  ylim(-1.5,1.5)

vrmid2_summary_nobc <- vrmid2_pupil_data%>%
  ungroup()%>%
  group_by(sample_in_trial_t,probe,trial_type)%>%
  summarise(mean = mean(pupil_Avg_scale, na.rm = T),
            lower = mean(pupil_Avg_scale, na.rm = T) - qt(0.975, df = n() - 1) * sd(pupil_Avg_scale, na.rm = T) / sqrt(n()),
            upper = mean(pupil_Avg_scale, na.rm = T) + qt(0.975, df = n() - 1) * sd(pupil_Avg_scale, na.rm = T) / sqrt(n()))

p2a<-ggplot(vrmid2_summary_nobc%>%
         filter(sample_in_trial_t > 0,sample_in_trial_t <= 20,probe == "anti"), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,4,6,14,16,18), size = 1, color = "grey")+
  geom_line(aes(group = trial_type, color = trial_type),size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t, fill = trial_type,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2)+
  scale_color_manual(values = purpleOrange_palette6)+
  scale_fill_manual(values = purpleOrange_palette6)+
  annotate("text", x = 2,y = 1, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 1, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 15,y = 1, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 17,y = 1, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 10,y = 1, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "VR study 2",
       subtitle = "anticipation probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  theme(legend.position = "none")+
  ylim(-1.5,1.5)

p2b<-ggplot(vrmid2_summary_nobc%>%
         filter(sample_in_trial_t > 0,sample_in_trial_t <= 20,probe == "out"), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,4,6,8,10,18), size = 1, color = "grey")+
  geom_line(aes(group = trial_type, color = trial_type),size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t, fill = trial_type,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2)+
  scale_color_manual(values = purpleOrange_palette6)+
  scale_fill_manual(values = purpleOrange_palette6)+
  annotate("text", x = 2,y = 1, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 1, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 7,y = 1, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 9,y = 1, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 13,y = 1, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "VR study 2",
       subtitle = "outcome probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  theme(legend.position = "none")+
  ylim(-1.5,1.5)

fmri3_summary_nobc <- fmri3_pupil_data%>%
  ungroup()%>%
  group_by(sample_in_trial_t,probe,cue_value)%>%
  summarise(mean = mean(pupilDiameter_scaled, na.rm = T),
            lower = mean(pupilDiameter_scaled, na.rm = T) - qt(0.975, df = n() - 1) * sd(pupilDiameter_scaled, na.rm = T) / sqrt(n()),
            upper = mean(pupilDiameter_scaled, na.rm = T) + qt(0.975, df = n() - 1) * sd(pupilDiameter_scaled, na.rm = T) / sqrt(n()))

p3a<-ggplot(fmri3_summary_nobc%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == 1), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,2,4,12,14,16,18), size = 1, color = "grey")+
  geom_line(aes(group = cue_value, color = cue_value),size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t, fill = cue_value,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2)+
  scale_color_manual(values = purpleOrange_palette6)+
  scale_fill_manual(values = purpleOrange_palette6)+
  annotate("text", x = 1,y = 1, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 3,y = 1, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 13,y = 1, label = "fix2",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 15,y = 1, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 17,y = 1, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 8,y = 1, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "FMRI study 3",
       subtitle = "anticipation probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  theme(legend.position = "none")+
  ylim(-1.6,1.5)

p3b<-ggplot(fmri3_summary_nobc%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == 2), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,2,4,6,8,16), size = 1, color = "grey")+
  geom_line(aes(group = cue_value, color = cue_value),size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t, fill = cue_value,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2)+
  scale_color_manual(values = purpleOrange_palette6)+
  scale_fill_manual(values = purpleOrange_palette6)+
  annotate("text", x = 1,y = 1, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 3,y = 1, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 1, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 7,y = 1, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 12,y = 1, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "FMRI study 3",
       subtitle = "outcome probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  theme(legend.position = "none")+
  ylim(-1.6,1.5)

pant<-p1a+p2a+p3a+
  plot_layout(nrow =1)

pout<-p1b+p2b+p3b+
  plot_layout(nrow =1)

pant/pout
ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig1_timecourse_bycue.tiff"),dpi = 300, height = 7, width = 8)
```

## time course by hit vs. miss

```{r}
vrmid1_summary_nobc <- vrmid1_pupil_data%>%
  ungroup()%>%
  group_by(sample_in_trial_t,probe,reaction_outcome)%>%
  summarise(mean = mean(pupil_Avg_scale, na.rm = T),
            lower = mean(pupil_Avg_scale, na.rm = T) - qt(0.975, df = n() - 1) * sd(pupil_Avg_scale, na.rm = T) / sqrt(n()),
            upper = mean(pupil_Avg_scale, na.rm = T) + qt(0.975, df = n() - 1) * sd(pupil_Avg_scale, na.rm = T) / sqrt(n()))

p1a<-ggplot(vrmid1_summary_nobc%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == "anti"), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,4,6,14,16,18), size = 1, color = "grey")+
  geom_line(aes(group = reaction_outcome, color = reaction_outcome, linetype = reaction_outcome),size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t, fill = reaction_outcome,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2)+
  scale_color_manual(values = c("navy","red"))+
  scale_fill_manual(values = c("navy","red"))+
  annotate("text", x = 2,y = 0.8, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 0.8, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 15,y = 0.8, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 17,y = 0.8, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 10,y = 0.8, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "VR study 1",
       subtitle = "anticipation probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  theme(legend.position = "top")+
  ylim(-1.3,1)

p1b<-ggplot(vrmid1_summary_nobc%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == "out"), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,4,6,8,10,18), size = 1, color = "grey")+
  geom_line(aes(group = reaction_outcome, color = reaction_outcome, linetype = reaction_outcome),size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t, fill = reaction_outcome,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2)+
  scale_color_manual(values = c("navy","red"))+
  scale_fill_manual(values = c("navy","red"))+
  annotate("text", x = 2,y = 0.8, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 0.8, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 7,y = 0.8, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 9,y = 0.8, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 13,y = 0.8, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "VR study 1",
       subtitle = "outcome probe",
       x = "time (s)",
       y = "z-scored pupil size")+
   theme(legend.position = "none")+
  ylim(-1.3,1)

vrmid2_summary_nobc <- vrmid2_pupil_data%>%
  ungroup()%>%
  group_by(sample_in_trial_t,probe,reaction_outcome)%>%
  summarise(mean = mean(pupil_Avg_scale, na.rm = T),
            lower = mean(pupil_Avg_scale, na.rm = T) - qt(0.975, df = n() - 1) * sd(pupil_Avg_scale, na.rm = T) / sqrt(n()),
            upper = mean(pupil_Avg_scale, na.rm = T) + qt(0.975, df = n() - 1) * sd(pupil_Avg_scale, na.rm = T) / sqrt(n()))

p2a<-ggplot(vrmid2_summary_nobc%>%
         filter(sample_in_trial_t > 0,sample_in_trial_t <= 20,probe == "anti"), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,4,6,14,16,18), size = 1, color = "grey")+
  geom_line(aes(group = reaction_outcome, color = reaction_outcome, linetype = reaction_outcome),size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t, fill = reaction_outcome,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2)+
  scale_color_manual(values = c("navy","red"))+
  scale_fill_manual(values = c("navy","red"))+
  annotate("text", x = 2,y = 0.8, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 0.8, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 15,y = 0.8, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 17,y = 0.8, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 10,y = 0.8, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "VR study 2",
       subtitle = "anticipation probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  theme(legend.position = "none")+
  ylim(-1.3,1)

p2b<-ggplot(vrmid2_summary_nobc%>%
         filter(sample_in_trial_t > 0,sample_in_trial_t <= 20,probe == "out"), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,4,6,8,10,18), size = 1, color = "grey")+
  geom_line(aes(group = reaction_outcome, color = reaction_outcome, linetype = reaction_outcome),size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t, fill = reaction_outcome,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2)+
  scale_color_manual(values = c("navy","red"))+
  scale_fill_manual(values = c("navy","red"))+
  annotate("text", x = 2,y = 0.8, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 0.8, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 7,y = 0.8, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 9,y = 0.8, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 13,y = 0.8, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "VR study 2",
       subtitle = "outcome probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  theme(legend.position = "none")+
  ylim(-1.3,1)

fmri3_summary_nobc <- fmri3_pupil_data%>%
  ungroup()%>%
  group_by(sample_in_trial_t,probe,hit)%>%
  summarise(mean = mean(pupilDiameter_scaled, na.rm = T),
            lower = mean(pupilDiameter_scaled, na.rm = T) - qt(0.975, df = n() - 1) * sd(pupilDiameter_scaled, na.rm = T) / sqrt(n()),
            upper = mean(pupilDiameter_scaled, na.rm = T) + qt(0.975, df = n() - 1) * sd(pupilDiameter_scaled, na.rm = T) / sqrt(n())) %>% 
  rename(reaction_outcome = hit)

p3a<-ggplot(fmri3_summary_nobc%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == 1), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,2,4,12,14,16,18), size = 1, color = "grey")+
  geom_line(aes(group = reaction_outcome, color = reaction_outcome, linetype = reaction_outcome),size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t, fill = reaction_outcome,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2)+
  scale_color_manual(values = c("navy","red"))+
  scale_fill_manual(values = c("navy","red"))+
  annotate("text", x = 1,y = 0.8, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 3,y = 0.8, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 13,y = 0.8, label = "fix2",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 15,y = 0.8, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 17,y = 0.8, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 8,y = 0.8, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "FMRI study 3",
       subtitle = "anticipation probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  theme(legend.position = "none")+
  ylim(-1.3,1)

p3b<-ggplot(fmri3_summary_nobc%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == 2), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,2,4,6,8,16), size = 1, color = "grey")+
  geom_line(aes(group = reaction_outcome, color = reaction_outcome, linetype = reaction_outcome),size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t, fill = reaction_outcome,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2)+
  scale_color_manual(values = c("navy","red"))+
  scale_fill_manual(values = c("navy","red"))+
  annotate("text", x = 1,y = 0.8, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 3,y = 0.8, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 0.8, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 7,y = 0.8, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 12,y = 0.8, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "FMRI study 3",
       subtitle = "outcome probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  theme(legend.position = "none")+
  ylim(-1.3,1)

pant<-p1a+p2a+p3a+
  plot_layout(nrow =1)

pout<-p1b+p2b+p3b+
  plot_layout(nrow =1)

pant/pout
ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig1_timecourse_byhit.tiff"),dpi = 300, height = 7, width = 8)
```


## time course by cue size and motion
```{r}
vrmid1_summary_nobc <- vrmid1_pupil_data%>%
  ungroup()%>%
  group_by(sample_in_trial_t,probe,condition)%>%
  summarise(mean = mean(pupil_Avg_scale, na.rm = T),
            lower = mean(pupil_Avg_scale, na.rm = T) - qt(0.975, df = n() - 1) * sd(pupil_Avg_scale, na.rm = T) / sqrt(n()),
            upper = mean(pupil_Avg_scale, na.rm = T) + qt(0.975, df = n() - 1) * sd(pupil_Avg_scale, na.rm = T) / sqrt(n())) %>% 
  rename(size = condition)

p1a<-ggplot(vrmid1_summary_nobc%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == "anti"), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,4,6,14,16,18), size = 1, color = "grey")+
  geom_line(aes(group = size, color = size),size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t, fill = size,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2)+
  ylim(-2.2,1)+
  scale_color_brewer(palette = "Set2")+
  scale_fill_brewer(palette = "Set2")+
  annotate("text", x = 2,y = 0.8, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 0.8, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 15,y = 0.8, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 17,y = 0.8, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 10,y = 0.8, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "VR study 1",
       subtitle = "anticipation probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  theme(legend.position = "top")

p1b<-ggplot(vrmid1_summary_nobc%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == "out"), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,4,6,8,10,18), size = 1, color = "grey")+
  geom_line(aes(group = size, color = size),size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t, fill = size,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2)+
  ylim(-2.2,1)+
  scale_color_brewer(palette = "Set2")+
  scale_fill_brewer(palette = "Set2")+
  annotate("text", x = 2,y = 0.8, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 0.8, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 7,y = 0.8, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 9,y = 0.8, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 13,y = 0.8, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "VR study 1",
       subtitle = "outcome probe",
       x = "time (s)",
       y = "z-scored pupil size")+
   theme(legend.position = "none")

vrmid2_summary_nobc <- vrmid2_pupil_data%>%
  ungroup()%>%
  group_by(sample_in_trial_t,probe,condition)%>%
  summarise(mean = mean(pupil_Avg_scale, na.rm = T),
            lower = mean(pupil_Avg_scale, na.rm = T) - qt(0.975, df = n() - 1) * sd(pupil_Avg_scale, na.rm = T) / sqrt(n()),
            upper = mean(pupil_Avg_scale, na.rm = T) + qt(0.975, df = n() - 1) * sd(pupil_Avg_scale, na.rm = T) / sqrt(n())) %>% 
  rename(size = condition)

p2a<-ggplot(vrmid2_summary_nobc%>%
         filter(sample_in_trial_t > 0,sample_in_trial_t <= 20,probe == "anti"), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,4,6,14,16,18), size = 1, color = "grey")+
  geom_line(aes(group = size, color = size),size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t, fill = size,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2)+
  ylim(-2.2,1)+
  scale_color_brewer(palette = "Set2")+
  scale_fill_brewer(palette = "Set2")+
  annotate("text", x = 2,y = 0.8, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 0.8, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 15,y = 0.8, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 17,y = 0.8, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 10,y = 0.8, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "VR study 2",
       subtitle = "anticipation probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  theme(legend.position = "none")

p2b<-ggplot(vrmid2_summary_nobc%>%
         filter(sample_in_trial_t > 0,sample_in_trial_t <= 20,probe == "out"), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,4,6,8,10,18), size = 1, color = "grey")+
  geom_line(aes(group = size, color = size),size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t, fill = size,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2)+
  ylim(-2.2,1.3)+
  scale_color_brewer(palette = "Set2")+
  scale_fill_brewer(palette = "Set2")+
  annotate("text", x = 2,y = 0.8, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 0.8, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 7,y = 0.8, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 9,y = 0.8, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 13,y = 0.8, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "VR study 2",
       subtitle = "outcome probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  theme(legend.position = "none")

fmri3_summary_nobc <- fmri3_pupil_data%>%
  ungroup()%>%
  group_by(sample_in_trial_t,probe,cue_size)%>%
  summarise(mean = mean(pupilDiameter_scaled, na.rm = T),
            lower = mean(pupilDiameter_scaled, na.rm = T) - qt(0.975, df = n() - 1) * sd(pupilDiameter_scaled, na.rm = T) / sqrt(n()),
            upper = mean(pupilDiameter_scaled, na.rm = T) + qt(0.975, df = n() - 1) * sd(pupilDiameter_scaled, na.rm = T) / sqrt(n())) %>% 
  rename(size = cue_size)

p3a<-ggplot(fmri3_summary_nobc%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == 1), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,2,4,12,14,16,18), size = 1, color = "grey")+
  geom_line(aes(group = size, color = size),size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t, fill = size,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2)+
  ylim(-2.2,1)+
  scale_color_manual(values = c("#e78ac3","#66c2a5"))+
  scale_fill_manual(values = c("#e78ac3","#66c2a5"))+
  annotate("text", x = 1,y = 0.8, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 3,y = 0.8, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 13,y = 0.8, label = "fix2",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 15,y = 0.8, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 17,y = 0.8, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 8,y = 0.8, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "FMRI study 3",
       subtitle = "anticipation probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  theme(legend.position = "none")

p3b<-ggplot(fmri3_summary_nobc%>%
         filter(sample_in_trial_t >0,sample_in_trial_t <= 20,probe == 2), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,2,4,6,8,16), size = 1, color = "grey")+
  geom_line(aes(group = size, color = size),size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t, fill = size,
                  ymin = lower, 
                  ymax = upper), 
              alpha = 0.2)+
  ylim(-2.2,1)+
  scale_color_manual(values = c("#e78ac3","#66c2a5"))+
  scale_fill_manual(values = c("#e78ac3","#66c2a5"))+
  annotate("text", x = 1,y = 0.8, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 3,y = 0.8, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 0.8, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 7,y = 0.8, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 12,y = 0.8, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(title = "FMRI study 3",
       subtitle = "outcome probe",
       x = "time (s)",
       y = "z-scored pupil size")+
  theme(legend.position = "none")

pant<-p1a+p2a+p3a+
  plot_layout(nrow =1)

pout<-p1b+p2b+p3b+
  plot_layout(nrow =1)

pant/pout
ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig1_timecourse_bysize.tiff"),dpi = 300, height = 7, width = 9)
```

## time course by emotion categories
```{r}
vrmid2_emo <- vrmid2_pupil_data%>%
  ungroup()%>%
  filter(!is.na(emotion))%>%
  group_by(emotion,sample_in_trial_t,Subject,probe)%>%
  summarise(pupil_Avg_scale = mean(pupil_Avg_scale, na.rm = T))%>%
  group_by(emotion,sample_in_trial_t,probe)%>%
  summarise(mean = mean(pupil_Avg_scale, na.rm = T),
            se = sd(pupil_Avg_scale, na.rm = T) / sqrt(n()))

pe1<-ggplot(vrmid2_emo%>%
         filter(sample_in_trial_t <= 20, sample_in_trial_t > 0,
                probe == "anti"), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,4,6,14,16,18), size = 1, color = "grey")+
  annotate("text", x = 2,y = 0.7, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 0.7, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 15,y = 0.7, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 17,y = 0.7, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 10,y = 0.7, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  geom_line(aes(color = emotion), size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t,
                  ymin = mean-se, 
                  ymax = mean+se, fill = emotion), 
              alpha = 0.2)+
  scale_color_manual(values = emotions_palette6)+
  scale_fill_manual(values = emotions_palette6)+
  labs(title = "VR study 2",
       subtitle = "anticipation probe",
       x = "time (s)",
       y = "pupil zscore")+
  theme(legend.position = "bottom")

pe2<-ggplot(vrmid2_emo%>%
         filter(sample_in_trial_t <= 20, sample_in_trial_t > 0,
                probe == "out"), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,4,6,8,10,18), size = 1, color = "grey")+
  geom_line(aes(color = emotion), size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t,
                  ymin = mean-se, 
                  ymax = mean+se, fill = emotion), 
              alpha = 0.2)+
  scale_color_manual(values = emotions_palette6)+
  scale_fill_manual(values = emotions_palette6)+
    annotate("text", x = 2,y = 1, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 1, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 7,y = 1, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 9,y = 1, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 14,y = 1, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(subtitle = "outcome probe",
       x = "time (s)",
       y = "pupil zscore")+
  theme(legend.position = "none")

fmri3_emo <- fmri3_pupil_data%>%
  ungroup()%>%
  filter(!is.na(emotion))%>%
  group_by(emotion,sample_in_trial_t,subject,probe)%>%
  summarise(pupilDiameter_scaled = mean(pupilDiameter_scaled, na.rm = T))%>%
  group_by(emotion,sample_in_trial_t,probe)%>%
  summarise(mean = mean(pupilDiameter_scaled, na.rm = T),
            se = sd(pupilDiameter_scaled, na.rm = T) / sqrt(n()))

pe3<-ggplot(fmri3_emo%>%
         filter(sample_in_trial_t <= 20, sample_in_trial_t > 0,
                probe == 1), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,2,4,12,14,16,18), size = 1, color = "grey")+
  annotate("text", x = 1,y = 0.7, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 3,y = 0.7, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 13,y = 0.7, label = "fix2",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 15,y = 0.7, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 17,y = 0.7, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 8,y = 0.7, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  geom_line(aes(color = emotion), size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t,
                  ymin = mean-se, 
                  ymax = mean+se, fill = emotion), 
              alpha = 0.2)+
  scale_color_manual(values = emotions_palette6)+
  scale_fill_manual(values = emotions_palette6)+
  labs(title = "FMRI study 3",
       subtitle = "outcome probe",
       x = "time (s)",
       y = "pupil zscore")+
  theme(legend.position = "none")

pe4 <-ggplot(fmri3_emo%>%
         filter(sample_in_trial_t <= 18, sample_in_trial_t > 0,
                probe == 2), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,2,4,6,8,16), size = 1, color = "grey")+
  annotate("text", x = 1,y = 0.7, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 3,y = 0.7, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 0.7, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 7,y = 0.7, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 12,y = 0.7, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  geom_line(aes(color = emotion), size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t,
                  ymin = mean-se, 
                  ymax = mean+se, fill = emotion), 
              alpha = 0.2)+
  scale_color_manual(values = emotions_palette6)+
  scale_fill_manual(values = emotions_palette6)+
  labs(subtitle = "anticipation probe",
       x = "time (s)",
       y = "pupil zscore")+
  theme(legend.position = "none")

vrmid2_emocat <- vrmid2_pupil_data%>%
  ungroup()%>%
  filter(!is.na(emotion))%>%
  group_by(emotion_cat,sample_in_trial_t,Subject,probe)%>%
  summarise(pupil_Avg_scale = mean(pupil_Avg_scale, na.rm = T))%>%
  group_by(emotion_cat,sample_in_trial_t,probe)%>%
  summarise(mean = mean(pupil_Avg_scale, na.rm = T),
            se = sd(pupil_Avg_scale, na.rm = T) / sqrt(n())) %>% 
  mutate(`emotions by arousal` = ifelse(emotion_cat == "high_arous","high","low"))

pe5<-ggplot(vrmid2_emocat%>%
         filter(sample_in_trial_t <= 20, sample_in_trial_t > 0,
                probe == "anti"), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,4,6,14,16,18), size = 1, color = "grey")+
  annotate("text", x = 2,y = 0.7, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 0.7, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 15,y = 0.7, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 17,y = 0.7, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 10,y = 0.7, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  geom_line(aes(color = `emotions by arousal`), size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t,
                  ymin = mean-se, 
                  ymax = mean+se, fill = `emotions by arousal`), 
              alpha = 0.2)+
  scale_color_manual(values = emotions_palette2)+
  scale_fill_manual(values = emotions_palette2)+
  labs(title = "VR study 2",
       subtitle = "anticipation probe",
       x = "time (s)",
       y = "pupil zscore")+
  theme(legend.position = "bottom")

pe6<-ggplot(vrmid2_emocat%>%
         filter(sample_in_trial_t <= 20, sample_in_trial_t > 0,
                probe == "out"), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,4,6,8,10,18), size = 1, color = "grey")+
  geom_line(aes(color = `emotions by arousal`), size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t,
                  ymin = mean-se, 
                  ymax = mean+se, fill = `emotions by arousal`), 
              alpha = 0.2)+
  scale_color_manual(values = emotions_palette2)+
  scale_fill_manual(values = emotions_palette2)+
    annotate("text", x = 2,y = 1, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 1, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 7,y = 1, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 9,y = 1, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 14,y = 1, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  labs(subtitle = "outcome probe",
       x = "time (s)",
       y = "pupil zscore")+
  theme(legend.position = "none")

fmri3_emocat <- fmri3_pupil_data%>%
  ungroup()%>%
  filter(!is.na(emotion))%>%
  group_by(emotion_cat,sample_in_trial_t,subject,probe)%>%
  summarise(pupilDiameter_scaled = mean(pupilDiameter_scaled, na.rm = T))%>%
  group_by(emotion_cat,sample_in_trial_t,probe)%>%
  summarise(mean = mean(pupilDiameter_scaled, na.rm = T),
            se = sd(pupilDiameter_scaled, na.rm = T) / sqrt(n())) %>% 
  mutate(`emotions by arousal` = ifelse(emotion_cat == "higharous","high","low"))

pe7<-ggplot(fmri3_emocat%>%
         filter(sample_in_trial_t <= 20, sample_in_trial_t > 0,
                probe == 1), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,2,4,12,14,16,18), size = 1, color = "grey")+
  annotate("text", x = 1,y = 0.5, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 3,y = 0.5, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 13,y = 0.5, label = "fix2",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 15,y = 0.5, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 17,y = 0.5, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 8,y = 0.5, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  geom_line(aes(color = `emotions by arousal`), size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t,
                  ymin = mean-se, 
                  ymax = mean+se, fill = `emotions by arousal`), 
              alpha = 0.2)+
  scale_color_manual(values = emotions_palette2)+
  scale_fill_manual(values = emotions_palette2)+
  labs(title = "FMRI study 3",
       subtitle = "anticipation probe",
       x = "time (s)",
       y = "pupil zscore")+
  theme(legend.position = "none")

pe8 <-ggplot(fmri3_emocat%>%
         filter(sample_in_trial_t <= 18, sample_in_trial_t > 0,
                probe == 2), aes(x = sample_in_trial_t,
                       y = mean))+
    geom_vline(xintercept = c(0,2,4,6,8,16), size = 1, color = "grey")+
  annotate("text", x = 1,y = 0.5, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 3,y = 0.5, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5,y = 0.5, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 7,y = 0.5, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 12,y = 0.5, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  geom_line(aes(color = `emotions by arousal`), size = 1)+
  geom_ribbon(aes(x = sample_in_trial_t,
                  ymin = mean-se, 
                  ymax = mean+se, fill = `emotions by arousal`), 
              alpha = 0.2)+
  scale_color_manual(values = emotions_palette2)+
  scale_fill_manual(values = emotions_palette2)+
  labs(subtitle = "outcome probe",
       x = "time (s)",
       y = "pupil zscore")+
  theme(legend.position = "none")
```

```{r}
pe1+pe2+pe3+pe4+
pe5+pe6+pe7+pe8+
plot_layout(nrow = 2)

ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig1_emotions.tiff"),dpi = 300, height = 7, width = 10)
```


# pre-selected time window predicting affect
## define the time windows of interest
```{r}
vrmid1_ant_window = c(4,6)+1.5
vrmid2_ant_window = c(4,6)+1.5
fmri3_ant_window = c(2,4)+1.5

vrmid1_antprobe_out_window = c(16,18)+1.5
vrmid2_antprobe_out_window = c(16,18)+1.5
fmri3_antprobe_out_window = c(16,18)+1.5

vrmid1_outprobe_out_window = c(8,10)+1.5
vrmid2_outprobe_out_window = c(8,10)+1.5
fmri3_outprobe_out_window = c(6,8)+1.5
```

## calculate df
```{r}
vrmid1_data_antprobe <-  vrmid1_pupil_data%>%
  mutate(pupil_window = ifelse(sample_in_trial_t <= vrmid1_antprobe_out_window[2] & sample_in_trial_t > vrmid1_antprobe_out_window[1],
                               "out",
                               ifelse(sample_in_trial_t <= vrmid1_ant_window[2] & sample_in_trial_t > vrmid1_ant_window[1],
                                      "ant",NA)))%>%
  filter(probe == "anti", pupil_window %in% c("out","ant"))%>%
  ungroup()%>%
  group_by(probe,Subject,trial,reaction_outcome,trial_type,PosA_scaled,NegA_scaled,
           arousal,valence,pupil_window,last_ITI,
           arousal_scaled,valence_scaled,
           condition,reaction_time)%>%
  summarise(mean_pupil_bc = mean(pupil_Avg_bc_scale, na.rm = T),
            mean_pupil_nobc = mean(pupil_Avg_scale, na.rm = T),
            mean_pupil_baseline = mean(pupil_Avg_baseline_scale, na.rm = T))%>%
  filter(abs(mean_pupil_bc) < 4,
         abs(mean_pupil_nobc) < 4,
         abs(mean_pupil_baseline) < 4)  %>% 
  pivot_wider(values_from = mean_pupil_bc:mean_pupil_baseline, names_from = pupil_window)%>%
  ungroup()%>%
  group_by(Subject)%>%
  mutate(log_rt = log(reaction_time),
         log_rt = as.numeric(scale(log_rt))) 

vrmid1_data_outprobe <-  vrmid1_pupil_data%>%
  mutate(pupil_window = ifelse(probe == "out" & sample_in_trial_t <= vrmid1_outprobe_out_window[2] & 
                                  sample_in_trial_t > vrmid1_outprobe_out_window[1],
                               "out",
                               ifelse(sample_in_trial_t <= vrmid1_ant_window[2] & 
                                        sample_in_trial_t > vrmid1_ant_window[1],
                                      "ant",NA)))%>%
  filter(probe == "out",pupil_window %in% c("out","ant"))%>% #probe == "out"
  ungroup()%>%
  group_by(probe,Subject,trial,trial_type,PosA_scaled,NegA_scaled,
           arousal,valence,pupil_window,last_ITI,
           arousal_scaled,valence_scaled,
           condition,reaction_outcome,reaction_time)%>%
  summarise(mean_pupil_bc = mean(pupil_Avg_bc_scale, na.rm = T),
            mean_pupil_nobc = mean(pupil_Avg_scale, na.rm = T),
            mean_pupil_baseline = mean(pupil_Avg_baseline_scale, na.rm = T))%>%
  filter(abs(mean_pupil_bc) < 4,
         abs(mean_pupil_nobc) < 4,
         abs(mean_pupil_baseline) < 4)  %>% 
  pivot_wider(values_from = mean_pupil_bc:mean_pupil_baseline, names_from = pupil_window)%>%
  ungroup()%>%
  group_by(Subject)%>%
  mutate(log_rt = log(reaction_time),
         log_rt = as.numeric(scale(log_rt)))


vrmid2_data_antprobe <-  vrmid2_pupil_data%>%
  mutate(pupil_window = ifelse(sample_in_trial_t <= vrmid2_antprobe_out_window[2] & sample_in_trial_t > vrmid2_antprobe_out_window[1],
                               "out",
                               ifelse(sample_in_trial_t <= vrmid2_ant_window[2] & sample_in_trial_t > vrmid2_ant_window[1],
                                      "ant",NA)))%>%
  filter(probe == "anti", pupil_window %in% c("out","ant"))%>%
  ungroup()%>%
  group_by(probe,Subject,trial,reaction_outcome,trial_type,PosA_scaled,NegA_scaled,
           arousal,valence,pupil_window,last_ITI,emotion,emotion_cat,
           arousal_scaled,valence_scaled,rating_type,
           condition,reaction_time)%>%
  summarise(mean_pupil_bc = mean(pupil_Avg_bc_scale, na.rm = T),
            mean_pupil_nobc = mean(pupil_Avg_scale, na.rm = T),
            mean_pupil_baseline = mean(pupil_Avg_baseline_scale, na.rm = T))%>%
  filter(abs(mean_pupil_bc) < 4,
         abs(mean_pupil_nobc) < 4,
         abs(mean_pupil_baseline) < 4)  %>% 
  pivot_wider(values_from = mean_pupil_bc:mean_pupil_baseline, names_from = pupil_window)%>%
  ungroup()%>%
  group_by(Subject)%>%
  mutate(log_rt = log(reaction_time),
         log_rt = as.numeric(scale(log_rt))) 

vrmid2_data_outprobe <-  vrmid2_pupil_data%>%
  mutate(pupil_window = ifelse(probe == "out" & sample_in_trial_t <= vrmid2_outprobe_out_window[2] & 
                                  sample_in_trial_t > vrmid2_outprobe_out_window[1],
                               "out",
                               ifelse(sample_in_trial_t <= vrmid2_ant_window[2] & 
                                        sample_in_trial_t > vrmid2_ant_window[1],
                                      "ant",NA)))%>%
  filter(probe == "out",pupil_window %in% c("out","ant"))%>% #probe == "out"
  ungroup()%>%
  group_by(probe,Subject,trial,trial_type,PosA_scaled,NegA_scaled,
           arousal,valence,pupil_window,last_ITI,emotion,emotion_cat,
           arousal_scaled,valence_scaled,rating_type,
           condition,reaction_outcome,reaction_time)%>%
  summarise(mean_pupil_bc = mean(pupil_Avg_bc_scale, na.rm = T),
            mean_pupil_nobc = mean(pupil_Avg_scale, na.rm = T),
            mean_pupil_baseline = mean(pupil_Avg_baseline_scale, na.rm = T))%>%
  filter(abs(mean_pupil_bc) < 4,
         abs(mean_pupil_nobc) < 4,
         abs(mean_pupil_baseline) < 4)  %>% 
  pivot_wider(values_from = mean_pupil_bc:mean_pupil_baseline, names_from = pupil_window)%>%
  ungroup()%>%
  group_by(Subject)%>%
  mutate(log_rt = log(reaction_time),
         log_rt = as.numeric(scale(log_rt)))

fmri3_data_antprobe <-  fmri3_pupil_data%>%
  mutate(pupil_window = ifelse(sample_in_trial_t <= fmri3_antprobe_out_window[2] & 
                                 sample_in_trial_t > fmri3_antprobe_out_window[1],
                               "out",
                               ifelse(sample_in_trial_t <= fmri3_ant_window[2] & 
                                        sample_in_trial_t > fmri3_ant_window[1],
                                      "ant",NA)))%>%
  filter(probe == 1, pupil_window %in% c("out","ant"))%>%
  ungroup()%>%
  group_by(subject) %>% 
  mutate(arousal_scaled = as.numeric(scale(arousal)),
         valence_scaled = as.numeric(scale(valence)))%>% 
  group_by(probe,subject,trial,hit,cue_value,emotion,emotion_cat,
           arousal,valence,pupil_window,rating_type,
           arousal_scaled,valence_scaled,cue_size,rt,iti,last_iti)%>%
  summarise(mean_pupil_bc_scaled = mean(pupilDiameter_bc_scaled, na.rm = T),
            mean_pupil_nobc_scaled= mean(pupilDiameter_scaled, na.rm = T),
            mean_pupil_baseline_scaled = mean(pupilDiameter_baseline_scaled, na.rm = T))%>%
  pivot_wider(values_from = mean_pupil_bc_scaled:mean_pupil_nobc_scaled, names_from = pupil_window)%>%
  ungroup()%>%
  group_by(subject)%>%
  mutate(log_rt = log(rt),
         log_rt = as.numeric(scale(log_rt)))

fmri3_data_outprobe <-  fmri3_pupil_data%>%
    filter(!subject %in% c("tc240311","st240312")) %>% 
  mutate(pupil_window = ifelse(probe == 2 & sample_in_trial_t <= fmri3_outprobe_out_window[2] 
                               & sample_in_trial_t > fmri3_outprobe_out_window[1],
                               "out",
                               ifelse(probe == 2 &  sample_in_trial_t <= fmri3_ant_window[2] 
                                      & sample_in_trial_t > fmri3_ant_window[1],
                                      "ant",NA)))%>%
  filter(probe == 2, pupil_window %in% c("out","ant"))%>%
  ungroup()%>%
  group_by(subject) %>% 
  mutate(arousal_scaled = as.numeric(scale(arousal)),
         valence_scaled = as.numeric(scale(valence)))%>% 
  group_by(probe,subject,trial,hit,cue_value,emotion,emotion_cat,
           arousal,valence,pupil_window,rating_type,
           arousal_scaled,valence_scaled,cue_size,rt,iti,last_iti)%>%
  summarise(mean_pupil_bc_scaled = mean(pupilDiameter_bc_scaled, na.rm = T),
            mean_pupil_nobc_scaled= mean(pupilDiameter_scaled, na.rm = T),
            mean_pupil_baseline_scaled = mean(pupilDiameter_baseline_scaled, na.rm = T))%>%
  pivot_wider(values_from = mean_pupil_bc_scaled:mean_pupil_nobc_scaled, names_from = pupil_window)%>%
  ungroup()%>%
  group_by(subject)%>%
  mutate(log_rt = log(rt),
         log_rt = as.numeric(scale(log_rt)))
```

## calculate separate effect sizes for each study

### anticipation
```{r}
#vrmid1
da <- vrmid1_data_antprobe
t <- lmer(scale(arousal_scaled) ~  scale(mean_pupil_baseline_ant) +(1|Subject) + (1|condition),
              da)
summary(t)
p <-lmer(scale(arousal_scaled) ~  scale(mean_pupil_bc_ant) +(1|Subject) + (1|condition),
              da)
summary(p)
tp <- lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc_ant) +(1|Subject) + (1|condition),
              da)
summary(tp)
anova(t,p,tp)

v1a<- c(round(r.squaredGLMM(t)*100,2),
round(r.squaredGLMM(p)*100,2),
round(r.squaredGLMM(tp)*100,2),
t(EMAtools::lme.dscore(t,da,"lme4")),
t(EMAtools::lme.dscore(p,da,"lme4")),
t(EMAtools::lme.dscore(tp,da,"lme4")))
```

```{r}
#vrmid2
da <- vrmid2_data_antprobe
t <- lmer(scale(arousal_scaled) ~  scale(mean_pupil_baseline_ant) +(1|Subject) + (1|condition),
              da)
summary(t)
p <-lmer(scale(arousal_scaled) ~  scale(mean_pupil_bc_ant) +(1|Subject) + (1|condition) ,
              da)
summary(p)
tp <- lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc_ant) +(1|Subject) + (1|condition) ,
              da)
summary(tp)
anova(t,p,tp)

v2a<- c(round(r.squaredGLMM(t)*100,2),
round(r.squaredGLMM(p)*100,2),
round(r.squaredGLMM(tp)*100,2),
t(EMAtools::lme.dscore(t,da,"lme4")),
t(EMAtools::lme.dscore(p,da,"lme4")),
t(EMAtools::lme.dscore(tp,da,"lme4")))
```

```{r}
#fmri3
da <- fmri3_data_antprobe
t <- lmer(scale(arousal_scaled) ~  scale(mean_pupil_baseline_scaled) +(1|subject) + (1|cue_size),
              da)
summary(t)
p <-lmer(scale(arousal_scaled) ~  scale(mean_pupil_bc_scaled_ant) +(1|subject) + (1|cue_size),
              da)
summary(p)
tp <- lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc_scaled_ant) +(1|subject) + (1|cue_size),
              da)
summary(tp)
anova(t,p,tp)

v3a<- c(round(r.squaredGLMM(t)*100,2),
round(r.squaredGLMM(p)*100,2),
round(r.squaredGLMM(tp)*100,2),
t(EMAtools::lme.dscore(t,da,"lme4")),
t(EMAtools::lme.dscore(p,da,"lme4")),
t(EMAtools::lme.dscore(tp,da,"lme4")))
```

### outcome

```{r}
#vrmid1
do <- vrmid1_data_outprobe
t <- lmer(scale(arousal_scaled) ~  scale(mean_pupil_baseline_out) +(1|Subject) + (1|condition),
              do)
summary(t)
p <-lmer(scale(arousal_scaled) ~  scale(mean_pupil_bc_out) +(1|Subject) + (1|condition),
              do)
summary(p)
tp <- lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc_out) +(1|Subject) + (1|condition),
              do)
summary(tp)
anova(t,p,tp)

v1o<- c(round(r.squaredGLMM(t)*100,2),
round(r.squaredGLMM(p)*100,2),
round(r.squaredGLMM(tp)*100,2),
t(EMAtools::lme.dscore(t,do,"lme4")),
t(EMAtools::lme.dscore(p,do,"lme4")),
t(EMAtools::lme.dscore(tp,do,"lme4")))
```

```{r}
#vrmid2
do <- vrmid2_data_outprobe
t <- lmer(scale(arousal_scaled) ~  scale(mean_pupil_baseline_out) +(1|Subject) + (1|condition),
              do)
summary(t)
p <-lmer(scale(arousal_scaled) ~  scale(mean_pupil_bc_out) +(1|Subject) + (1|condition),
              do)
summary(p)
tp <- lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc_out) +(1|Subject) + (1|condition),
              do)
summary(tp)
anova(t,p,tp)

v2o<- c(round(r.squaredGLMM(t)*100,2),
round(r.squaredGLMM(p)*100,2),
round(r.squaredGLMM(tp)*100,2),
t(EMAtools::lme.dscore(t,do,"lme4")),
t(EMAtools::lme.dscore(p,do,"lme4")),
t(EMAtools::lme.dscore(tp,do,"lme4")))
```

```{r}
#fmri3
do <- fmri3_data_outprobe
t <- lmer(scale(arousal_scaled) ~  scale(mean_pupil_baseline_scaled) +(1|subject) + (1|cue_size),
              do)
summary(t)
p <-lmer(scale(arousal_scaled) ~  scale(mean_pupil_bc_scaled_out) +(1|subject) + (1|cue_size),
              do)
summary(p)
tp <- lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc_scaled_out)+(1|subject) + (1|cue_size),
              do)
summary(tp)
# anova(t,p,tp)

v3o<- c(round(r.squaredGLMM(t)*100,2),
round(r.squaredGLMM(p)*100,2),
round(r.squaredGLMM(tp)*100,2),
t(EMAtools::lme.dscore(t,do,"lme4")),
t(EMAtools::lme.dscore(p,do,"lme4")),
t(EMAtools::lme.dscore(tp,do,"lme4")))
```

```{r}
r2list <- as.data.frame(Reduce(rbind,list(v1a,v2a,v3a,v1o,v2o,v3o)))
names(r2list) <- c(paste0(c("R2m","R2c","R2m","R2c","R2m","R2c"),"_",c("tonic","tonic","phasic","phasic","t+p","t+p")),
                   paste0(c("t","df","d","t","df","d","t","df","d"),"_",c("tonic","tonic","tonic","phasic","phasic","phasic","t+p","t+p","t+p"))) 

r2list$study <- c("VR1","VR2",'FMRI3',"VR1","VR2",'FMRI3')

r2list$probe <- c("anticipation","anticipation","anticipation","outcome","outcome","outcome")

r2list<-remove_rownames(r2list) %>% 
  relocate(study, probe)

r2list_long <- r2list %>% 
  # select(study,probe,R2m_tonic,R2m_phasic,`R2m_t+p`,t_tonic:`df_t+p`) %>% 
  pivot_longer(R2m_tonic:`d_t+p`,names_to = c("measure","dataType"),values_to = "value", names_sep = "_") %>% 
  pivot_wider(names_from = dataType, values_from = "value") %>% 
  filter(measure %in% c("R2m","t","d"))

r2list_long %>% 
  arrange(probe,measure) %>% 
  kable(digits = 2) %>% 
  kable_styling()%>%
  save_kable(file = "../../data/r2.html", self_contained = T)
```

### make figures (all studies and probes)
```{r}
l1a<-lmer(arousal_scaled ~  mean_pupil_nobc_ant + (1|Subject) + (1|condition),vrmid1_data_antprobe)
l1b<-lmer(valence_scaled ~  mean_pupil_nobc_ant + (1|Subject) + (1|condition),vrmid1_data_antprobe)
l1c<-lmer(arousal_scaled ~  mean_pupil_nobc_out + (1|Subject) + (1|condition),vrmid1_data_outprobe)
l1d<-lmer(valence_scaled ~  mean_pupil_nobc_out + (1|Subject) + (1|condition),vrmid1_data_outprobe)

p1a<-plot_model(l1a, type = "pred", terms = "mean_pupil_nobc_ant",
           show.data = T, dot.size = 0.5, color = 'orange')+
  labs(y = "arousal zscore", x = "tonic+phasic pupil",
       title = "VR study 1",subtitle = "anticipation probe")

p1b<-plot_model(l1b, type = "pred", terms = "mean_pupil_nobc_ant",
           show.data = T, dot.size = 0.5, color = 'orange')+
  labs(y = "valence zscore", x = "tonic+phasic pupil",
       title = "VR study 1",subtitle = "anticipation probe")

p1c<-plot_model(l1c, type = "pred", terms = "mean_pupil_nobc_out",
           show.data = T, dot.size = 0.5, color = 'orange')+
  labs(y = "arousal zscore", x = "tonic+phasic pupil",
       title = "VR study 1",subtitle = "anticipation probe")

p1d<-plot_model(l1d, type = "pred", terms = "mean_pupil_nobc_out",
           show.data = T, dot.size = 0.5, color = 'orange')+
  labs(y = "valence zscore", x = "tonic+phasic pupil",
       title = "VR study 1",subtitle = "anticipation probe")

l2a<-lmer(arousal_scaled ~  mean_pupil_nobc_ant + (1|Subject) + (1|condition),vrmid2_data_antprobe)
l2b<-lmer(valence_scaled ~  mean_pupil_nobc_ant + (1|Subject) + (1|condition),vrmid2_data_antprobe)
l2c<-lmer(arousal_scaled ~  mean_pupil_nobc_out + (1|Subject) + (1|condition),vrmid2_data_outprobe)
l2d<-lmer(valence_scaled ~  mean_pupil_nobc_out + (1|Subject) + (1|condition),vrmid2_data_outprobe)

p2a<-plot_model(l2a, type = "pred", terms = "mean_pupil_nobc_ant",
           show.data = T, dot.size = 0.5, color = 'orange')+
  labs(y = "arousal zscore", x = "tonic+phasic pupil",
       title = "VR study 2",subtitle = "anticipation probe")

p2b<-plot_model(l2b, type = "pred", terms = "mean_pupil_nobc_ant",
           show.data = T, dot.size = 0.5, color = 'orange')+
  labs(y = "valence zscore", x = "tonic+phasic pupil",
       title = "VR study 2",subtitle = "anticipation probe")

p2c<-plot_model(l2c, type = "pred", terms = "mean_pupil_nobc_out",
           show.data = T, dot.size = 0.5, color = 'orange')+
  labs(y = "arousal zscore", x = "tonic+phasic pupil",
       title = "VR study 2",subtitle = "anticipation probe")

p2d<-plot_model(l2d, type = "pred", terms = "mean_pupil_nobc_out",
           show.data = T, dot.size = 0.5, color = 'orange')+
  labs(y = "valence zscore", x = "tonic+phasic pupil",
       title = "VR study 2",subtitle = "anticipation probe")

l3a<-lmer(arousal_scaled ~  mean_pupil_nobc_scaled_ant + (1|subject) + (1|cue_size),fmri3_data_antprobe)
l3b<-lmer(valence_scaled ~  mean_pupil_nobc_scaled_ant + (1|subject) + (1|cue_size),fmri3_data_antprobe)
l3c<-lmer(arousal_scaled ~  mean_pupil_nobc_scaled_out + (1|subject) + (1|cue_size),fmri3_data_outprobe)
l3d<-lmer(valence_scaled ~  mean_pupil_nobc_scaled_out + (1|subject) + (1|cue_size),fmri3_data_outprobe)

p3a<-plot_model(l3a, type = "pred", terms = "mean_pupil_nobc_scaled_ant",
           show.data = T, dot.size = 0.5, color = 'orange')+
  labs(y = "arousal zscore", x = "tonic+phasic pupil",
       title = "FMRI study 3",subtitle = "anticipation probe")

p3b<-plot_model(l3b, type = "pred", terms = "mean_pupil_nobc_scaled_ant",
           show.data = T, dot.size = 0.5, color = 'orange')+
  labs(y = "valence zscore", x = "tonic+phasic pupil",
       title = "FMRI study 3",subtitle = "anticipation probe")

p3c<-plot_model(l3c, type = "pred", terms = "mean_pupil_nobc_scaled_out",
           show.data = T, dot.size = 0.5, color = 'orange')+
  labs(y = "arousal zscore", x = "tonic+phasic pupil",
       title = "FMRI study 3",subtitle = "anticipation probe")

p3d<-plot_model(l3d, type = "pred", terms = "mean_pupil_nobc_scaled_out",
           show.data = T, dot.size = 0.5, color = 'orange')+
  labs(y = "valence zscore", x = "tonic+phasic pupil",
       title = "FMRI study 3",subtitle = "anticipation probe")

p1a+p1b+p1c+p1d+
  p2a+p2b+p2c+p2d+
  p3a+p3b+p3c+p3d+
  plot_layout(nrow = 3)
ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig4_scatter.tiff"),dpi = 300, height = 6, width = 8)
```

## pool the effect sizes and make summary plots
```{r}
data_antprobe <- Reduce(rbind,list(vrmid1_data_antprobe %>% select(Subject,trial,condition,arousal_scaled,valence_scaled,mean_pupil_nobc_ant) %>% 
                                     mutate(study="VRStudy1"),
                              vrmid2_data_antprobe %>% select(Subject,trial,condition,arousal_scaled,valence_scaled,mean_pupil_nobc_ant)%>% 
                                     mutate(study="VRStudy2"),
                              fmri3_data_antprobe %>% select(subject,trial,cue_size,arousal_scaled,valence_scaled,mean_pupil_nobc_scaled_ant) %>% 
                                rename(Subject = subject,condition= cue_size,mean_pupil_nobc_ant=mean_pupil_nobc_scaled_ant)%>% 
                                     mutate(study="FMRIStudy3")))

summary(l1<-lmer(arousal_scaled ~  mean_pupil_nobc_ant + (1|Subject/study) + (1|condition) + (mean_pupil_nobc_ant|study),data_antprobe))

fixed_effects <- ggpredict(l1)$mean_pupil_nobc_ant
# Extract random effects
combined_effects <- ranef(l1)$study
combined_effects$`(Intercept)` <- combined_effects$`(Intercept)`+summary(l1)$coefficient[1,1]
combined_effects$mean_pupil_nobc_ant <- combined_effects$mean_pupil_nobc_ant+summary(l1)$coefficient[2,1]

random_slopes_df <- data.frame(
  study = rownames(combined_effects),
  slope = combined_effects[, "mean_pupil_nobc_ant"],
  intercept = combined_effects[, "(Intercept)" ]
)

x_values <- seq(-5, 5, length.out = 100)
# Calculate y values for each study
df_plot <- do.call(rbind, lapply(1:nrow(random_slopes_df), function(i) {
  data.frame(
    x = x_values,
    y = random_slopes_df$slope[i] * x_values + random_slopes_df$intercept[i],
    study = random_slopes_df$study[i]
  )
}))

# Plot the regression lines
p1<-ggplot() +
  geom_point(data=data_antprobe, aes(x = mean_pupil_nobc_ant, y = arousal_scaled, color = study),
            size = 0.5, alpha = 0.4) +
  geom_line(data=df_plot, aes(x = x, y = y, color = study),
            size = 2) +
  geom_line(data = fixed_effects, aes(x = x, y = predicted),
            color = "black",size = 2,alpha = 0.7, linetype = "dashed")+
  geom_ribbon(data = fixed_effects, aes(x = x, y = predicted,
                                        ymin = conf.low,
                                        ymax = conf.high),
            color = "black",alpha = 0.1)+
  labs(title = "Anticipation arousal", 
       x = "tonic+phasic pupil", 
       y = "Arousal zscore")+
  scale_color_brewer(palette = "Dark2")+
  xlim(range(data_antprobe$mean_pupil_nobc_ant,na.rm = T))+
  xlim(range(data_antprobe$arousal_scaled,na.rm = T))+
  theme(legend.position = "left")

summary(l1<-lmer(valence_scaled ~  mean_pupil_nobc_ant + (1|Subject/study) + (1|condition) + (mean_pupil_nobc_ant|study),data_antprobe))

fixed_effects <- ggpredict(l1)$mean_pupil_nobc_ant
# Extract random effects
combined_effects <- ranef(l1)$study
combined_effects$`(Intercept)` <- combined_effects$`(Intercept)`+summary(l1)$coefficient[1,1]
combined_effects$mean_pupil_nobc_ant <- combined_effects$mean_pupil_nobc_ant+summary(l1)$coefficient[2,1]

random_slopes_df <- data.frame(
  study = rownames(combined_effects),
  slope = combined_effects[, "mean_pupil_nobc_ant"],
  intercept = combined_effects[, "(Intercept)" ]
)

x_values <- seq(-5, 5, length.out = 100)
# Calculate y values for each study
df_plot <- do.call(rbind, lapply(1:nrow(random_slopes_df), function(i) {
  data.frame(
    x = x_values,
    y = random_slopes_df$slope[i] * x_values + random_slopes_df$intercept[i],
    study = random_slopes_df$study[i]
  )
}))

# Plot the regression lines
p2<-ggplot() +
  geom_point(data=data_antprobe, aes(x = mean_pupil_nobc_ant, y = arousal_scaled, color = study),
            size = 0.5, alpha = 0.4) +
  geom_line(data=df_plot, aes(x = x, y = y, color = study),
            size = 2) +
  geom_line(data = fixed_effects, aes(x = x, y = predicted),
            color = "black",size = 2,alpha = 0.7, linetype = "dashed")+
  geom_ribbon(data = fixed_effects, aes(x = x, y = predicted,
                                        ymin = conf.low,
                                        ymax = conf.high),
            color = "black",alpha = 0.1)+
  labs(title = "Anticipation valence", 
       x = "tonic+phasic pupil", 
       y = "Valence zscore")+
  scale_color_brewer(palette = "Dark2")+
  xlim(range(data_antprobe$mean_pupil_nobc_ant,na.rm = T))+
  xlim(range(data_antprobe$arousal_scaled,na.rm = T))+
  theme(legend.position = "none")

data_outprobe <- Reduce(rbind,list(vrmid1_data_outprobe %>% select(Subject,trial,condition,arousal_scaled,valence_scaled,mean_pupil_nobc_out) %>% 
                                     mutate(study="VRStudy1"),
                              vrmid2_data_outprobe %>% select(Subject,trial,condition,arousal_scaled,valence_scaled,mean_pupil_nobc_out)%>% 
                                     mutate(study="VRStudy2"),
                              fmri3_data_outprobe %>% select(subject,trial,cue_size,arousal_scaled,valence_scaled,mean_pupil_nobc_scaled_out) %>% 
                                rename(Subject = subject,condition= cue_size,mean_pupil_nobc_out=mean_pupil_nobc_scaled_out)%>% 
                                     mutate(study="FMRIStudy3")))

summary(l1<-lmer(arousal_scaled ~  mean_pupil_nobc_out + (1|Subject/study) + (1|condition)+ (mean_pupil_nobc_out|study),data_outprobe))
fixed_effects <- ggpredict(l1)$mean_pupil_nobc_out
# Extract random effects
combined_effects <- ranef(l1)$study
combined_effects$`(Intercept)` <- combined_effects$`(Intercept)`+summary(l1)$coefficient[1,1]
combined_effects$mean_pupil_nobc_out <- combined_effects$mean_pupil_nobc_out+summary(l1)$coefficient[2,1]

random_slopes_df <- data.frame(
  study = rownames(combined_effects),
  slope = combined_effects[, "mean_pupil_nobc_out"],
  intercept = combined_effects[, "(Intercept)" ]
)

x_values <- seq(-5, 5, length.out = 100)
# Calculate y values for each study
df_plot <- do.call(rbind, lapply(1:nrow(random_slopes_df), function(i) {
  data.frame(
    x = x_values,
    y = random_slopes_df$slope[i] * x_values + random_slopes_df$intercept[i],
    study = random_slopes_df$study[i]
  )
}))

# Plot the regression lines
p3<-ggplot() +
  geom_point(data=data_outprobe, aes(x = mean_pupil_nobc_out, y = arousal_scaled, color = study),
            size = 0.5, alpha = 0.4) +
geom_line(data=df_plot, aes(x = x, y = y, color = study),
            size = 2) +
  geom_line(data = fixed_effects, aes(x = x, y = predicted),
            color = "black",size = 2,alpha = 0.7, linetype = "dashed")+
  geom_ribbon(data = fixed_effects, aes(x = x, y = predicted,
                                        ymin = conf.low,
                                        ymax = conf.high),
            color = "black",alpha = 0.1)+
  labs(title = "Outcome arousal", 
       x = "tonic+phasic pupil", 
       y = "Arousal zscore")+
  scale_color_brewer(palette = "Dark2")+
  xlim(range(data_antprobe$mean_pupil_nobc_ant,na.rm = T))+
  xlim(range(data_antprobe$arousal_scaled,na.rm = T))+
  theme(legend.position = "none")

summary(l1<-lmer(valence_scaled ~  mean_pupil_nobc_out + (1|Subject/study) + (1|condition)+ (mean_pupil_nobc_out|study),data_outprobe))
fixed_effects <- ggpredict(l1)$mean_pupil_nobc_out
# Extract random effects
combined_effects <- ranef(l1)$study
combined_effects$`(Intercept)` <- combined_effects$`(Intercept)`+summary(l1)$coefficient[1,1]
combined_effects$mean_pupil_nobc_out <- combined_effects$mean_pupil_nobc_out+summary(l1)$coefficient[2,1]

random_slopes_df <- data.frame(
  study = rownames(combined_effects),
  slope = combined_effects[, "mean_pupil_nobc_out"],
  intercept = combined_effects[, "(Intercept)" ]
)

x_values <- seq(-5, 5, length.out = 100)
# Calculate y values for each study
df_plot <- do.call(rbind, lapply(1:nrow(random_slopes_df), function(i) {
  data.frame(
    x = x_values,
    y = random_slopes_df$slope[i] * x_values + random_slopes_df$intercept[i],
    study = random_slopes_df$study[i]
  )
}))

# Plot the regression lines
p4<-ggplot() +
  geom_point(data=data_outprobe, aes(x = mean_pupil_nobc_out, y = arousal_scaled, color = study),
            size = 0.5, alpha = 0.4) +
geom_line(data=df_plot, aes(x = x, y = y, color = study),
            size = 2) +
  geom_line(data = fixed_effects, aes(x = x, y = predicted),
            color = "black",size = 2,alpha = 0.7, linetype = "dashed")+
  geom_ribbon(data = fixed_effects, aes(x = x, y = predicted,
                                        ymin = conf.low,
                                        ymax = conf.high),
            color = "black",alpha = 0.1)+
  labs(title = "Outcome valence", 
       x = "tonic+phasic pupil", 
       y = "Arousal zscore")+
  scale_color_brewer(palette = "Dark2")+
  xlim(range(data_antprobe$mean_pupil_nobc_ant,na.rm = T))+
  xlim(range(data_antprobe$arousal_scaled,na.rm = T))+
  theme(legend.position = "none")

p1+p2+p3+p4+plot_layout(nrow = 2)
ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig4_pooled_effects.tiff"),dpi = 300, height = 6, width = 8)
```


# show rating behavior on affective circumplex
```{r}
aff_traj_avg_ant_noRotat <- vrmid1_data_antprobe%>%
  mutate(probe == "anti") %>% 
  ungroup()%>%
  group_by(trial_type,probe)%>%
  summarise(valence_mean = mean(valence, na.rm = T),
            arousal_mean = mean(arousal, na.rm = T),
            valence_sd = sd(valence, na.rm = T)/sqrt(n()),
            arousal_sd = sd(arousal, na.rm = T)/sqrt(n()))%>%
  mutate(report_type = "anticipation")%>%
  select(report_type,trial_type,valence_mean:arousal_sd)

aff_traj_avg_out_noRotat <- vrmid1_data_outprobe%>%
  mutate(probe == "out") %>% 
  ungroup()%>%
  group_by(trial_type,probe,reaction_outcome)%>%
  summarise(valence_mean = mean(valence, na.rm = T),
            arousal_mean = mean(arousal, na.rm = T),
            valence_sd = sd(valence, na.rm = T)/sqrt(n()),
            arousal_sd = sd(arousal, na.rm = T)/sqrt(n()))%>%
  select(reaction_outcome,trial_type,valence_mean:arousal_sd)%>%
  mutate(report_type = ifelse(reaction_outcome == "Hit","hit","miss"))

aff_traj_avg_noRotat <- rbind(aff_traj_avg_ant_noRotat,aff_traj_avg_out_noRotat)

p1<-ggplot(data = aff_traj_avg_noRotat, aes(x = valence_mean, y = arousal_mean, color = trial_type, 
                                        group = report_type))+
    geom_segment(aes(x = 1, y = 3,
                   xend =5, yend = 3),
               size = 0.5, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  geom_segment(aes(x = 3, y = 1,
                   xend =3, yend = 5),
               size = 0.5, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  geom_point(aes(shape = report_type),
             size = 2)+
  geom_segment(aes(y=arousal_mean-arousal_sd, yend=arousal_mean+arousal_sd,
                    x=valence_mean, xend = valence_mean, group = report_type, linetype = report_type), width=.5)+
  geom_segment(aes(y=arousal_mean, yend=arousal_mean,
                    x=valence_mean + valence_sd, xend = valence_mean - valence_sd,
                   group = report_type, linetype = report_type),
               width=.5)+
  scale_color_manual(values = purpleOrange_palette6)+
  geom_line(aes(group = trial_type, color = trial_type), linetype = "dotted")+
  labs(title = "VR study 1",
       x = "",
       y = "",
       color = "cue value")+
  annotate("text",x = 4, y = 3.2, label = "valence",size = unit(4,"pt"),
           color = "grey")+
  annotate("text",x = 2.8, y = 1.5, label = "arousal",size = unit(4,"pt"),
           color = "grey", angle = 90)+
  theme_blank()+
  xlim(1,5)+
  theme(legend.position = "left")

aff_traj_avg_ant_noRotat <- vrmid2_data_antprobe%>%
  mutate(probe == "anti") %>% 
  ungroup()%>%
  group_by(trial_type,probe)%>%
  summarise(valence_mean = mean(valence, na.rm = T),
            arousal_mean = mean(arousal, na.rm = T),
            valence_sd = sd(valence, na.rm = T)/sqrt(n()),
            arousal_sd = sd(arousal, na.rm = T)/sqrt(n()))%>%
  mutate(report_type = "anticipation")%>%
  select(report_type,trial_type,valence_mean:arousal_sd)

aff_traj_avg_out_noRotat <- vrmid2_data_outprobe%>%
  mutate(probe == "out") %>% 
  ungroup()%>%
  group_by(trial_type,probe,reaction_outcome)%>%
  summarise(valence_mean = mean(valence, na.rm = T),
            arousal_mean = mean(arousal, na.rm = T),
            valence_sd = sd(valence, na.rm = T)/sqrt(n()),
            arousal_sd = sd(arousal, na.rm = T)/sqrt(n()))%>%
  select(reaction_outcome,trial_type,valence_mean:arousal_sd)%>%
  mutate(report_type = ifelse(reaction_outcome == "Hit","hit","miss"))

aff_traj_avg_noRotat <- rbind(aff_traj_avg_ant_noRotat,aff_traj_avg_out_noRotat)

p2<-ggplot(data = aff_traj_avg_noRotat, aes(x = valence_mean, y = arousal_mean, color = trial_type, 
                                        group = report_type))+
    geom_segment(aes(x = 1, y = 3,
                   xend =5, yend = 3),
               size = 0.5, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  geom_segment(aes(x = 3, y = 1,
                   xend =3, yend = 5),
               size = 0.5, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  geom_point(aes(shape = report_type),
             size = 2)+
  geom_segment(aes(y=arousal_mean-arousal_sd, yend=arousal_mean+arousal_sd,
                    x=valence_mean, xend = valence_mean, group = report_type, linetype = report_type), width=.5)+
  geom_segment(aes(y=arousal_mean, yend=arousal_mean,
                    x=valence_mean + valence_sd, xend = valence_mean - valence_sd,
                   group = report_type, linetype = report_type),
               width=.5)+
  scale_color_manual(values = purpleOrange_palette6)+
  geom_line(aes(group = trial_type, color = trial_type), linetype = "dotted")+
  labs(title = "VR study 2",
       x = "",
       y = "",
       color = "cue value")+
  annotate("text",x = 4, y = 3.2, label = "valence",size = unit(4,"pt"),
           color = "grey")+
  annotate("text",x = 2.8, y = 1.5, label = "arousal",size = unit(4,"pt"),
           color = "grey", angle = 90)+
  theme_blank()+
  xlim(1,5)+
  theme(legend.position = "none")

aff_traj_avg_ant_noRotat <- fmri3_data_antprobe%>%
  mutate(probe == 1) %>% 
  ungroup()%>%
  group_by(cue_value,probe)%>%
  summarise(valence_mean = mean(valence, na.rm = T),
            arousal_mean = mean(arousal, na.rm = T),
            valence_sd = sd(valence, na.rm = T)/sqrt(n()),
            arousal_sd = sd(arousal, na.rm = T)/sqrt(n()))%>%
  mutate(report_type = "anticipation")%>%
  select(report_type,cue_value,valence_mean:arousal_sd)

aff_traj_avg_out_noRotat <- fmri3_data_outprobe%>%
  ungroup()%>%
  group_by(cue_value,probe, hit)%>%
  summarise(valence_mean = mean(valence, na.rm = T),
            arousal_mean = mean(arousal, na.rm = T),
            valence_sd = sd(valence, na.rm = T)/sqrt(30),
            arousal_sd = sd(arousal, na.rm = T)/sqrt(30))%>%
  mutate(report_type = ifelse(hit==1,"hit","miss"))%>%
  select(report_type,cue_value,valence_mean:arousal_sd)

aff_traj_avg_noRotat <- rbind(aff_traj_avg_ant_noRotat,aff_traj_avg_out_noRotat)

p3<-ggplot(data = aff_traj_avg_noRotat, aes(x = valence_mean, y = arousal_mean, color = cue_value, 
                                        group = report_type))+
    geom_segment(aes(x = 1, y = 3,
                   xend =5, yend = 3),
               size = 0.5, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  geom_segment(aes(x = 3, y = 1,
                   xend =3, yend = 5),
               size = 0.5, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  geom_point(aes(shape = report_type),
             size = 2)+
  geom_segment(aes(y=arousal_mean-arousal_sd, yend=arousal_mean+arousal_sd,
                    x=valence_mean, xend = valence_mean, group = report_type, linetype = report_type), width=.5)+
  geom_segment(aes(y=arousal_mean, yend=arousal_mean,
                    x=valence_mean + valence_sd, xend = valence_mean - valence_sd,
                   group = report_type, linetype = report_type),
               width=.5)+
  scale_color_manual(values = purpleOrange_palette6)+
  geom_line(aes(group = cue_value, color = cue_value), linetype = "dotted")+
  labs(title = "FMRI study 3",
       x = "",
       y = "",
       color = "cue value")+
  annotate("text",x = 4, y = 3.2, label = "valence",size = unit(4,"pt"),
           color = "grey")+
  annotate("text",x = 2.8, y = 1.5, label = "arousal",size = unit(4,"pt"),
           color = "grey", angle = 90)+
  theme_blank()+
  xlim(1,5)+
  theme(legend.position = "none")

p1+p2+p3+plot_layout(nrow = 1)
ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig6_affspace.tiff"), height = 3, width = 9)
```


# is arousal better explained by pupil dilation than emotion categories?

## vrmid2
```{r}
summary(la<-lmer(mean_pupil_nobc_ant ~  arousal_scaled +(1|Subject) + (1|condition),
         vrmid2_data_antprobe))
summary(lv<-lmer(mean_pupil_nobc_ant ~  valence_scaled +(1|Subject) + (1|condition),
         vrmid2_data_antprobe))
summary(le<-lmer(mean_pupil_nobc_ant ~  emotion +(1|Subject) + (1|condition),
         vrmid2_data_antprobe))
summary(lec<-lmer(mean_pupil_nobc_ant ~  emotion_cat +(1|Subject) + (1|condition),
         vrmid2_data_antprobe))

modcomp_results <- data.frame(
  anova = anova(la),
  r_squaredGLMM = r.squaredGLMM(la)*100,
  AIC = AIC(la),
  BIC = BIC(la)
)

modcomp_results<- 
  rbind(modcomp_results,
data.frame(
  anova = anova(lv),
  r_squaredGLMM = r.squaredGLMM(lv)*100,
  AIC = AIC(lv),
  BIC = BIC(lv)
))

modcomp_results<- 
  rbind(modcomp_results,
data.frame(
  anova = anova(le),
  r_squaredGLMM = r.squaredGLMM(le)*100,
  AIC = AIC(le),
  BIC = BIC(le)
))

modcomp_results<- 
  rbind(modcomp_results,
data.frame(
  anova = anova(lec),
  r_squaredGLMM = r.squaredGLMM(lec)*100,
  AIC = AIC(lec),
  BIC = BIC(lec)
))
modcomp_results1 <- modcomp_results %>% 
  rownames_to_column()

modcomp_results1$probe = "anticipation"

summary(la<-lmer(mean_pupil_nobc_out ~  arousal_scaled +(1|Subject) + (1|condition),
         vrmid2_data_outprobe))
summary(lv<-lmer(mean_pupil_nobc_out ~  valence_scaled +(1|Subject) + (1|condition),
         vrmid2_data_outprobe))
summary(le<-lmer(mean_pupil_nobc_out ~  emotion +(1|Subject) + (1|condition),
         vrmid2_data_outprobe))
summary(lec<-lmer(mean_pupil_nobc_out ~  emotion_cat +(1|Subject) + (1|condition),
         vrmid2_data_outprobe))

modcomp_results <- data.frame(
  anova = anova(la),
  r_squaredGLMM = r.squaredGLMM(la)*100,
  AIC = AIC(la),
  BIC = BIC(la)
)

modcomp_results<- 
  rbind(modcomp_results,
data.frame(
  anova = anova(lv),
  r_squaredGLMM = r.squaredGLMM(lv)*100,
  AIC = AIC(lv),
  BIC = BIC(lv)
))

modcomp_results<- 
  rbind(modcomp_results,
data.frame(
  anova = anova(le),
  r_squaredGLMM = r.squaredGLMM(le)*100,
  AIC = AIC(le),
  BIC = BIC(le)
))

modcomp_results<- 
  rbind(modcomp_results,
data.frame(
  anova = anova(lec),
  r_squaredGLMM = r.squaredGLMM(lec)*100,
  AIC = AIC(lec),
  BIC = BIC(lec)
))
modcomp_results2 <- modcomp_results %>% 
  rownames_to_column()

modcomp_results2$probe = "outcome"


modcomp_results <- rbind(modcomp_results1,modcomp_results2)

modcomp_results %>% 
  kable(digits = 2) %>% 
  kable_styling()%>%
  save_kable(file = "../../data/modelcomp_vrmid2.html", self_contained = T)
```

## fmri3
```{r}
summary(la<-lmer(mean_pupil_nobc_scaled_ant ~  arousal_scaled +(1|subject) + (1|cue_size),
         fmri3_data_antprobe))
summary(lv<-lmer(mean_pupil_nobc_scaled_ant ~  valence_scaled +(1|subject) + (1|cue_size),
         fmri3_data_antprobe))
summary(le<-lmer(mean_pupil_nobc_scaled_ant ~  emotion +(1|subject) + (1|cue_size),
         fmri3_data_antprobe))
summary(lec<-lmer(mean_pupil_nobc_scaled_ant ~  emotion_cat +(1|subject) + (1|cue_size),
         fmri3_data_antprobe))

modcomp_results <- data.frame(
  anova = anova(la),
  r_squaredGLMM = r.squaredGLMM(la)*100,
  AIC = AIC(la),
  BIC = BIC(la)
)

modcomp_results<- 
  rbind(modcomp_results,
data.frame(
  anova = anova(lv),
  r_squaredGLMM = r.squaredGLMM(lv)*100,
  AIC = AIC(lv),
  BIC = BIC(lv)
))

modcomp_results<- 
  rbind(modcomp_results,
data.frame(
  anova = anova(le),
  r_squaredGLMM = r.squaredGLMM(le)*100,
  AIC = AIC(le),
  BIC = BIC(le)
))

modcomp_results<- 
  rbind(modcomp_results,
data.frame(
  anova = anova(lec),
  r_squaredGLMM = r.squaredGLMM(lec)*100,
  AIC = AIC(lec),
  BIC = BIC(lec)
))
modcomp_results1 <- modcomp_results %>% 
  rownames_to_column()

modcomp_results1$probe = "anticipation"

summary(la<-lmer(mean_pupil_nobc_scaled_out ~  arousal_scaled +(1|subject) + (1|cue_size),
         fmri3_data_outprobe))
summary(lv<-lmer(mean_pupil_nobc_scaled_out ~  valence_scaled +(1|subject) + (1|cue_size),
         fmri3_data_outprobe))
summary(le<-lmer(mean_pupil_nobc_scaled_out ~  emotion +(1|subject) + (1|cue_size),
         fmri3_data_outprobe))
summary(lec<-lmer(mean_pupil_nobc_scaled_out ~  emotion_cat +(1|subject) + (1|cue_size),
         fmri3_data_outprobe))

modcomp_results <- data.frame(
  anova = anova(la),
  r_squaredGLMM = r.squaredGLMM(la)*100,
  AIC = AIC(la),
  BIC = BIC(la)
)

modcomp_results<- 
  rbind(modcomp_results,
data.frame(
  anova = anova(lv),
  r_squaredGLMM = r.squaredGLMM(lv)*100,
  AIC = AIC(lv),
  BIC = BIC(lv)
))

modcomp_results<- 
  rbind(modcomp_results,
data.frame(
  anova = anova(le),
  r_squaredGLMM = r.squaredGLMM(le)*100,
  AIC = AIC(le),
  BIC = BIC(le)
))

modcomp_results<- 
  rbind(modcomp_results,
data.frame(
  anova = anova(lec),
  r_squaredGLMM = r.squaredGLMM(lec)*100,
  AIC = AIC(lec),
  BIC = BIC(lec)
))
modcomp_results2 <- modcomp_results %>% 
  rownames_to_column()

modcomp_results2$probe = "outcome"


modcomp_results <- rbind(modcomp_results1,modcomp_results2)

modcomp_results %>% 
  kable(digits = 2) %>% 
  kable_styling()%>%
  save_kable(file = "../../data/modelcomp_fmri3.html", self_contained = T)
```
# finding the affective dimension that best matches pupil dilation (full signal)
```{r message = F, warning=F}
da <- vrmid1_data_antprobe
do <- vrmid1_data_outprobe

nbins = 360
angles = seq(0,pi/2, by = pi/(2*nbins))
angles = data.frame(angle1d = angles*180/pi,
                    angle1r = angles,
                    sin1 = sin(angles),
                    cos1 = cos(angles))

angles <- angles%>%
  mutate(angle2d = angle1d + 90,
         angle2r = angle1r + pi/2,
         sin2 = sin(angle2r),
         cos2 = cos(angle2r))

lmer_out1 <- {}

for (i in 1:nrow(angles)){
  angle_info = angles[i,]
  data_lm_anti_temp <- da%>%
    mutate(axis1 = valence_scaled * angle_info$cos1 + arousal_scaled * angle_info$sin1,
           axis2 = valence_scaled * angle_info$cos2 + arousal_scaled * angle_info$sin2)
  sum_temp1 <- summary(lmer(scale(axis1) ~ scale(mean_pupil_nobc_ant) + (1|Subject) + (1|condition),
              data_lm_anti_temp))
  sum_temp2 <- summary(lmer(scale(axis2) ~ scale(mean_pupil_nobc_ant) + (1|Subject) + (1|condition),
              data_lm_anti_temp))
  lmer_out1 <- rbind(lmer_out1, sum_temp1$coefficients[2,],sum_temp2$coefficients[2,])
}

lmer_out1 <- as.data.frame(lmer_out1)
lmer_out1$axis = rep(c("axis1","axis2"),nrow(angles))
  
lmer_out1[seq(1,nrow(angles)*2,by = 2),"angle"] = angles$angle1d
lmer_out1[seq(2,nrow(angles)*2,by = 2),"angle"] = angles$angle2d

lmer_out1[seq(1,nrow(angles)*2,by = 2),"sin"] = angles$sin1
lmer_out1[seq(2,nrow(angles)*2,by = 2),"sin"] = angles$sin2

lmer_out1[seq(1,nrow(angles)*2,by = 2),"cos"] = angles$cos1
lmer_out1[seq(2,nrow(angles)*2,by = 2),"cos"] = angles$cos2

lmer_out1$p_val <- (lmer_out1$`Pr(>|t|)` < 0.001)

a1f <- lmer_out1[which.max(abs(lmer_out1$Estimate)),]

lmer_out2 <- {}

for (i in 1:nrow(angles)){
  angle_info = angles[i,]
  data_lm_out_temp <- do%>%
    mutate(axis1 = valence_scaled * angle_info$cos1 + arousal_scaled * angle_info$sin1,
           axis2 = valence_scaled * angle_info$cos2 + arousal_scaled * angle_info$sin2)
  sum_temp1 <- summary(lmer(scale(axis1) ~ scale(mean_pupil_nobc_out) + (1|Subject) + (1|condition),
              data_lm_out_temp))
  sum_temp2 <- summary(lmer(scale(axis2) ~ scale(mean_pupil_nobc_out) + (1|Subject) + (1|condition),
              data_lm_out_temp))
  lmer_out2 <- rbind(lmer_out2, sum_temp1$coefficients[2,],sum_temp2$coefficients[2,])
}

lmer_out2 <- as.data.frame(lmer_out2)
lmer_out2$axis = rep(c("axis1","axis2"),nrow(angles))
  
lmer_out2[seq(1,nrow(angles)*2,by = 2),"angle"] = angles$angle1d
lmer_out2[seq(2,nrow(angles)*2,by = 2),"angle"] = angles$angle2d

lmer_out2[seq(1,nrow(angles)*2,by = 2),"sin"] = angles$sin1
lmer_out2[seq(2,nrow(angles)*2,by = 2),"sin"] = angles$sin2

lmer_out2[seq(1,nrow(angles)*2,by = 2),"cos"] = angles$cos1
lmer_out2[seq(2,nrow(angles)*2,by = 2),"cos"] = angles$cos2

lmer_out2$p_val <- (lmer_out2$`Pr(>|t|)` < 0.001)

a2f <- lmer_out2[which.max(abs(lmer_out2$Estimate)),]

vrmid1_axes <- rbind(a1f,a2f)
vrmid1_axes$condition <- c("anti","outcome")

vrmid1_axes <- vrmid1_axes%>%
  mutate(rad = angle/180 *pi,
         cos = cos(rad),
         sin = sin(rad))
```

```{r message = F, warning=F}
da <- vrmid2_data_antprobe
do <- vrmid2_data_outprobe

nbins = 360
angles = seq(0,pi/2, by = pi/(2*nbins))
angles = data.frame(angle1d = angles*180/pi,
                    angle1r = angles,
                    sin1 = sin(angles),
                    cos1 = cos(angles))

angles <- angles%>%
  mutate(angle2d = angle1d + 90,
         angle2r = angle1r + pi/2,
         sin2 = sin(angle2r),
         cos2 = cos(angle2r))

lmer_out1 <- {}

for (i in 1:nrow(angles)){
  angle_info = angles[i,]
  data_lm_anti_temp <- da%>%
    mutate(axis1 = valence_scaled * angle_info$cos1 + arousal_scaled * angle_info$sin1,
           axis2 = valence_scaled * angle_info$cos2 + arousal_scaled * angle_info$sin2)
  sum_temp1 <- summary(lmer(scale(axis1) ~ scale(mean_pupil_nobc_ant) + (1|Subject) + (1|condition),
              data_lm_anti_temp))
  sum_temp2 <- summary(lmer(scale(axis2) ~ scale(mean_pupil_nobc_ant) + (1|Subject) + (1|condition),
              data_lm_anti_temp))
  lmer_out1 <- rbind(lmer_out1, sum_temp1$coefficients[2,],sum_temp2$coefficients[2,])
}

lmer_out1 <- as.data.frame(lmer_out1)
lmer_out1$axis = rep(c("axis1","axis2"),nrow(angles))
  
lmer_out1[seq(1,nrow(angles)*2,by = 2),"angle"] = angles$angle1d
lmer_out1[seq(2,nrow(angles)*2,by = 2),"angle"] = angles$angle2d

lmer_out1[seq(1,nrow(angles)*2,by = 2),"sin"] = angles$sin1
lmer_out1[seq(2,nrow(angles)*2,by = 2),"sin"] = angles$sin2

lmer_out1[seq(1,nrow(angles)*2,by = 2),"cos"] = angles$cos1
lmer_out1[seq(2,nrow(angles)*2,by = 2),"cos"] = angles$cos2

lmer_out1$p_val <- (lmer_out1$`Pr(>|t|)` < 0.001)

a1f <- lmer_out1[which.max(abs(lmer_out1$Estimate)),]

lmer_out2 <- {}

for (i in 1:nrow(angles)){
  angle_info = angles[i,]
  data_lm_out_temp <- do%>%
    mutate(axis1 = valence_scaled * angle_info$cos1 + arousal_scaled * angle_info$sin1,
           axis2 = valence_scaled * angle_info$cos2 + arousal_scaled * angle_info$sin2)
  sum_temp1 <- summary(lmer(scale(axis1) ~ scale(mean_pupil_nobc_out) + (1|Subject) + (1|condition),
              data_lm_out_temp))
  sum_temp2 <- summary(lmer(scale(axis2) ~ scale(mean_pupil_nobc_out) + (1|Subject) + (1|condition),
              data_lm_out_temp))
  lmer_out2 <- rbind(lmer_out2, sum_temp1$coefficients[2,],sum_temp2$coefficients[2,])
}

lmer_out2 <- as.data.frame(lmer_out2)
lmer_out2$axis = rep(c("axis1","axis2"),nrow(angles))
  
lmer_out2[seq(1,nrow(angles)*2,by = 2),"angle"] = angles$angle1d
lmer_out2[seq(2,nrow(angles)*2,by = 2),"angle"] = angles$angle2d

lmer_out2[seq(1,nrow(angles)*2,by = 2),"sin"] = angles$sin1
lmer_out2[seq(2,nrow(angles)*2,by = 2),"sin"] = angles$sin2

lmer_out2[seq(1,nrow(angles)*2,by = 2),"cos"] = angles$cos1
lmer_out2[seq(2,nrow(angles)*2,by = 2),"cos"] = angles$cos2

lmer_out2$p_val <- (lmer_out2$`Pr(>|t|)` < 0.001)

a2f <- lmer_out2[which.max(abs(lmer_out2$Estimate)),]

vrmid2_axes <- rbind(a1f,a2f)
vrmid2_axes$condition <- c("anti","outcome")

vrmid2_axes <- vrmid2_axes%>%
  mutate(rad = angle/180 *pi,
         cos = cos(rad),
         sin = sin(rad))
```

```{r message = F, warning=F}
da <- fmri3_data_antprobe
do <- fmri3_data_outprobe

nbins = 360
angles = seq(0,pi/2, by = pi/(2*nbins))
angles = data.frame(angle1d = angles*180/pi,
                    angle1r = angles,
                    sin1 = sin(angles),
                    cos1 = cos(angles))

angles <- angles%>%
  mutate(angle2d = angle1d + 90,
         angle2r = angle1r + pi/2,
         sin2 = sin(angle2r),
         cos2 = cos(angle2r))

lmer_out1 <- {}

for (i in 1:nrow(angles)){
  angle_info = angles[i,]
  data_lm_anti_temp <- da%>%
    mutate(axis1 = valence_scaled * angle_info$cos1 + arousal_scaled * angle_info$sin1,
           axis2 = valence_scaled * angle_info$cos2 + arousal_scaled * angle_info$sin2)
  sum_temp1 <- summary(lmer(scale(axis1) ~ scale(mean_pupil_nobc_scaled_ant) + (1|subject) + (1|cue_size),
              data_lm_anti_temp))
  sum_temp2 <- summary(lmer(scale(axis2) ~ scale(mean_pupil_nobc_scaled_ant) + (1|subject) + (1|cue_size),
              data_lm_anti_temp))
  lmer_out1 <- rbind(lmer_out1, sum_temp1$coefficients[2,],sum_temp2$coefficients[2,])
}

lmer_out1 <- as.data.frame(lmer_out1)
lmer_out1$axis = rep(c("axis1","axis2"),nrow(angles))
  
lmer_out1[seq(1,nrow(angles)*2,by = 2),"angle"] = angles$angle1d
lmer_out1[seq(2,nrow(angles)*2,by = 2),"angle"] = angles$angle2d

lmer_out1[seq(1,nrow(angles)*2,by = 2),"sin"] = angles$sin1
lmer_out1[seq(2,nrow(angles)*2,by = 2),"sin"] = angles$sin2

lmer_out1[seq(1,nrow(angles)*2,by = 2),"cos"] = angles$cos1
lmer_out1[seq(2,nrow(angles)*2,by = 2),"cos"] = angles$cos2

lmer_out1$p_val <- (lmer_out1$`Pr(>|t|)` < 0.001)

a1f <- lmer_out1[which.max(abs(lmer_out1$Estimate)),]

lmer_out2 <- {}

for (i in 1:nrow(angles)){
  angle_info = angles[i,]
  data_lm_out_temp <- do%>%
    mutate(axis1 = valence_scaled * angle_info$cos1 + arousal_scaled * angle_info$sin1,
           axis2 = valence_scaled * angle_info$cos2 + arousal_scaled * angle_info$sin2)
  sum_temp1 <- summary(lmer(scale(axis1) ~ scale(mean_pupil_nobc_scaled_out) + (1|Subject) + (1|cue_size),
              data_lm_out_temp))
  sum_temp2 <- summary(lmer(scale(axis2) ~ scale(mean_pupil_nobc_scaled_out) + (1|Subject) + (1|cue_size),
              data_lm_out_temp))
  lmer_out2 <- rbind(lmer_out2, sum_temp1$coefficients[2,],sum_temp2$coefficients[2,])
}

lmer_out2 <- as.data.frame(lmer_out2)
lmer_out2$axis = rep(c("axis1","axis2"),nrow(angles))
  
lmer_out2[seq(1,nrow(angles)*2,by = 2),"angle"] = angles$angle1d
lmer_out2[seq(2,nrow(angles)*2,by = 2),"angle"] = angles$angle2d

lmer_out2[seq(1,nrow(angles)*2,by = 2),"sin"] = angles$sin1
lmer_out2[seq(2,nrow(angles)*2,by = 2),"sin"] = angles$sin2

lmer_out2[seq(1,nrow(angles)*2,by = 2),"cos"] = angles$cos1
lmer_out2[seq(2,nrow(angles)*2,by = 2),"cos"] = angles$cos2

lmer_out2$p_val <- (lmer_out2$`Pr(>|t|)` < 0.001)

a2f <- lmer_out2[which.max(abs(lmer_out2$Estimate)),]

fmri3_axes <- rbind(a1f,a2f)
fmri3_axes$condition <- c("anti","outcome")

fmri3_axes <- fmri3_axes%>%
  mutate(rad = angle/180 *pi,
         cos = cos(rad),
         sin = sin(rad))
```

## plot the axes
```{r}
p1<-ggplot(vrmid1_axes%>%
         mutate(cos = cos * abs(Estimate),
                sin = sin * abs(Estimate)))+
  geom_segment(aes(x = -0.4, y = 0,
                   xend = 0.4, yend = 0),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "grey")+
  geom_segment(aes(x = 0, y = -0.4,
                   xend = 0, yend = 0.4),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "grey")+
  geom_segment(aes(x = 0,y = 0,
                   xend = cos, yend = sin,
                   color = condition),
               size = 2, arrow = arrow(length = unit(0.03, "npc")))+
  geom_segment(aes(x = 0, y = 0,
                   xend = -0.3, yend = 0.3),
               size = 1, linetype = "dashed",
               color = "grey")+ #45 degree line
  geom_text(aes(x = cos * 1.2, y = sin * 1.1, color = condition, label = round(Estimate,2)),
            size = 5,check_overlap = F)+
  scale_color_manual(values = c("purple","skyblue"))+
  scale_y_continuous()+
  labs(x = "",
       y = "",
       title = "VR study 1")+
  theme_blank()+
  theme(legend.position = "none",
         axis.ticks = element_blank(),
    axis.text = element_blank())+
  annotate("text",x=0.21,y = -0.1, label = "anticipation probe", color = "purple")+
  annotate("text",x=0.2,y = -0.15, label = "outcome probe", color = "skyblue")+
  annotate("text",x=0.2,y = 0.05, label = "valence zscore", color = "grey")+
  annotate("text",x=-0.05,y = -0.25, label = "arousal zscore", color = "grey", angle = 90)


p2<-ggplot(vrmid2_axes%>%
         mutate(cos = cos * abs(Estimate),
                sin = sin * abs(Estimate)))+
  geom_segment(aes(x = -0.4, y = 0,
                   xend = 0.4, yend = 0),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "grey")+
  geom_segment(aes(x = 0, y = -0.4,
                   xend = 0, yend = 0.4),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "grey")+
    geom_segment(aes(x = 0, y = 0,
                   xend = -0.3, yend = 0.3),
               size = 1, linetype = "dashed",
               color = "grey")+
  geom_segment(aes(x = 0,y = 0,
                   xend = cos, yend = sin,
                   color = condition),
               size = 2, arrow = arrow(length = unit(0.03, "npc")))+
  geom_text(aes(x = cos * 1.2, y = sin * 1.2, color = condition, label = round(Estimate,2)),
            size = 5,check_overlap = F)+
  scale_color_manual(values = c("purple","skyblue"))+
  labs(x = "",
       y = "",
       title = "VR study 2")+
  theme_blank() +
  theme(legend.position = "none",
         axis.ticks = element_blank(),
    axis.text = element_blank())+
  annotate("text",x=0.2,y = 0.05, label = "valence zscore", color = "grey")+
  annotate("text",x=-0.05,y = -0.25, label = "arousal zscore", color = "grey", angle = 90)

p3<-ggplot(fmri3_axes%>%
         mutate(cos = cos * abs(Estimate),
                sin = sin * abs(Estimate)))+
  geom_segment(aes(x = -0.4, y = 0,
                   xend = 0.4, yend = 0),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "grey")+
  geom_segment(aes(x = 0, y = -0.4,
                   xend = 0, yend = 0.4),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "grey")+
    geom_segment(aes(x = 0, y = 0,
                   xend = -0.3, yend = 0.3),
               size = 1, linetype = "dashed",
               color = "grey")+
  geom_segment(aes(x = 0,y = 0,
                   xend = cos, yend = sin,
                   color = condition),
               size = 2, arrow = arrow(length = unit(0.03, "npc")))+
  geom_text(aes(x = cos * 1.2, y = sin * 1.2, color = condition, label = round(Estimate,2)),
            size = 5,check_overlap = F)+
  scale_color_manual(values = c("purple","skyblue"))+
  labs(x = "",
       y = "",
       title = "FMRI study 3")+
  theme_blank()+
  theme(legend.position = "none",
         axis.ticks = element_blank(),
    axis.text = element_blank())+
  annotate("text",x=0.2,y = 0.05, label = "valence zscore", color = "grey")+
  annotate("text",x=-0.05,y = -0.25, label = "arousal zscore", color = "grey", angle = 90)

p1+p2+p3

ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig2_axes.tiff"),dpi = 300, height = 4, width = 10)
```


# time course correlation

## get the correlation time series
```{r warning = F, message=F}
vrmid1_regression_coefs_ant_nobc <- {}

for (t in 1:20) {
  coefs <- {}
  print(t)
  for (s in 1:120){
  df_ant_temp <- vrmid1_pupil_data%>%
  filter(probe == "anti",Time_sec == t, sample_in_sec == s)
  lm_ant_temp <- lmer(scale(arousal_scaled) ~ scale(pupil_Avg_scale) + (1|Subject) + (1|condition),df_ant_temp)
  lm_out <- c(summary(lm_ant_temp)$coefficient[2,],'r2m' = r.squaredGLMM(lm_ant_temp)[1])
  coefs <- rbind(coefs,lm_out)
  }
  coefs <- as.data.frame(coefs)%>%
    mutate(sample_in_sec = row_number(),
           Time_sec = t)
  rownames(coefs) <- NULL
  vrmid1_regression_coefs_ant_nobc <- rbind(vrmid1_regression_coefs_ant_nobc,coefs)
}

vrmid1_regression_coefs_ant_nobc <- vrmid1_regression_coefs_ant_nobc%>%
  mutate(sample_point = row_number(),
         p_val = (`Pr(>|t|)` < .001))

write.csv(vrmid1_regression_coefs_ant_nobc, "../../data/vrmid1/derivatives/vrmid1_regression_coefs_ant_nobc.csv")

vrmid1_regression_coefs_out_nobc <- {}

for (t in 1:20) {
  coefs <- {}
  print(t)
  for (s in 1:120){
  df_out_temp <- vrmid1_pupil_data%>%
  filter(probe == "out",Time_sec == t, sample_in_sec == s)
  lm_out_temp <- lmer(scale(arousal_scaled) ~ scale(pupil_Avg_bc_scale) + (1|Subject) + (1|condition),df_out_temp)
  lm_out <- summary(lm_out_temp)$coefficient[2,]
  coefs <- rbind(coefs,lm_out) 
  }
  coefs <- as.data.frame(coefs)%>%
    mutate(sample_in_sec = row_number(),
           Time_sec = t)
  rownames(coefs) <- NULL
  vrmid1_regression_coefs_out_nobc <- rbind(vrmid1_regression_coefs_out_nobc,coefs)
}

vrmid1_regression_coefs_out_nobc <- vrmid1_regression_coefs_out_nobc%>%
  mutate(sample_point = row_number(),
         p_val = (`Pr(>|t|)` < .001))

write.csv(vrmid1_regression_coefs_out_nobc,  "../../data/vrmid1/derivatives/vrmid1_regression_coefs_out_nobc.csv")

vrmid2_regression_coefs_ant_nobc <- {}

for (t in 1:20) {
  coefs <- {}
  print(t)
  for (s in 1:120){
  df_ant_temp <- vrmid2_pupil_data%>%
  filter(probe == "anti",Time_sec == t, sample_in_sec == s)
  lm_ant_temp <- lmer(scale(arousal_scaled) ~ scale(pupil_Avg_scale) + (1|Subject) + (1|condition),df_ant_temp)
  lm_out <- c(summary(lm_ant_temp)$coefficient[2,],'r2m' = r.squaredGLMM(lm_ant_temp)[1])
  coefs <- rbind(coefs,lm_out)
  }
  coefs <- as.data.frame(coefs)%>%
    mutate(sample_in_sec = row_number(),
           Time_sec = t)
  rownames(coefs) <- NULL
  vrmid2_regression_coefs_ant_nobc <- rbind(vrmid2_regression_coefs_ant_nobc,coefs)
}

vrmid2_regression_coefs_ant_nobc <- vrmid2_regression_coefs_ant_nobc%>%
  mutate(sample_point = row_number(),
         p_val = (`Pr(>|t|)` < .001))

write.csv(vrmid2_regression_coefs_ant_nobc, "../../data/vrmid2/derivatives/vrmid2_regression_coefs_ant_nobc.csv")

vrmid2_regression_coefs_out_nobc <- {}

for (t in 1:20) {
  coefs <- {}
  print(t)
  for (s in 1:120){
  df_out_temp <- vrmid2_pupil_data%>%
  filter(probe == "out",Time_sec == t, sample_in_sec == s)
  lm_out_temp <- lmer(scale(arousal_scaled) ~ scale(pupil_Avg_bc_scale) + (1|Subject) + (1|condition),df_out_temp)
  lm_out <- summary(lm_out_temp)$coefficient[2,]
  coefs <- rbind(coefs,lm_out) 
  }
  coefs <- as.data.frame(coefs)%>%
    mutate(sample_in_sec = row_number(),
           Time_sec = t)
  rownames(coefs) <- NULL
  vrmid2_regression_coefs_out_nobc <- rbind(vrmid2_regression_coefs_out_nobc,coefs)
}

vrmid2_regression_coefs_out_nobc <- vrmid2_regression_coefs_out_nobc%>%
  mutate(sample_point = row_number(),
         p_val = (`Pr(>|t|)` < .001))

write.csv(vrmid2_regression_coefs_out_nobc,  "../../data/vrmid2/derivatives/vrmid2_regression_coefs_out_nobc.csv")

fmri3_regression_coefs_ant_nobc <- {}

for (t in 1:20) {
  coefs <- {}
  print(t)
  for (s in 1:200){
  df_ant_temp <- fmri3_pupil_data%>%
  filter(probe == 1,Time_sec == t, sample_in_sec == s)
  lm_ant_temp <- lmer(scale(arousal_scaled) ~ scale(pupilDiameter_scaled) + (1|subject) + (1|cue_size),df_ant_temp)
  lm_out <- c(summary(lm_ant_temp)$coefficient[2,],'r2m' = r.squaredGLMM(lm_ant_temp)[1])
  coefs <- rbind(coefs,lm_out)
  }
  coefs <- as.data.frame(coefs)%>%
    mutate(sample_in_sec = row_number(),
           Time_sec = t)
  rownames(coefs) <- NULL
  fmri3_regression_coefs_ant_nobc <- rbind(fmri3_regression_coefs_ant_nobc,coefs)
}

fmri3_regression_coefs_ant_nobc <- fmri3_regression_coefs_ant_nobc%>%
  mutate(sample_point = row_number(),
         p_val = (`Pr(>|t|)` < .001))

write.csv(fmri3_regression_coefs_ant_nobc, "../../data/fmri3//derivatives/fmri3_regression_coefs_ant_nobc.csv")

fmri3_regression_coefs_out_nobc <- {}

for (t in 1:20) {
  coefs <- {}
  print(t)
  for (s in 1:200){
  df_out_temp <- fmri3_pupil_data%>%
  filter(probe == 2,Time_sec == t, sample_in_sec == s)
  lm_out_temp <-  lmer(scale(arousal_scaled) ~ scale(pupilDiameter_scaled) + (1|subject) + (1|cue_size),df_out_temp)
  lm_out <- summary(lm_out_temp)$coefficient[2,]
  coefs <- rbind(coefs,lm_out) 
  }
  coefs <- as.data.frame(coefs)%>%
    mutate(sample_in_sec = row_number(),
           Time_sec = t)
  rownames(coefs) <- NULL
  fmri3_regression_coefs_out_nobc <- rbind(fmri3_regression_coefs_out_nobc,coefs)
}

fmri3_regression_coefs_out_nobc <- fmri3_regression_coefs_out_nobc%>%
  mutate(sample_point = row_number(),
         p_val = (`Pr(>|t|)` < .001))

write.csv(fmri3_regression_coefs_out_nobc,  "../../data/fmri3/derivatives/fmri3_regression_coefs_out_bc.csv")
```

## plots
```{r}
vrmid1_regression_coefs_ant_nobc_smoothed <- vrmid1_regression_coefs_ant_nobc %>% 
  mutate(smoothed_beta = zoo::rollmean(Estimate, k = 60, fill = NA))
vrmid1_regression_coefs_out_nobc_smoothed <- vrmid1_regression_coefs_out_nobc %>% 
  mutate(smoothed_beta = zoo::rollmean(Estimate, k = 60, fill = NA))

vrmid2_regression_coefs_ant_nobc_smoothed <- vrmid2_regression_coefs_ant_nobc %>% 
  mutate(smoothed_beta = zoo::rollmean(Estimate, k = 60, fill = NA))
vrmid2_regression_coefs_out_nobc_smoothed <- vrmid2_regression_coefs_out_nobc %>% 
  mutate(smoothed_beta = zoo::rollmean(Estimate, k = 60, fill = NA))

fmri3_regression_coefs_ant_nobc_smoothed <- fmri3_regression_coefs_ant_nobc %>% 
  mutate(smoothed_beta = zoo::rollmean(Estimate, k = 100, fill = NA))
fmri3_regression_coefs_out_nobc_smoothed <- fmri3_regression_coefs_out_nobc %>% 
  mutate(smoothed_beta = zoo::rollmean(Estimate, k = 100, fill = NA))

p1a<-ggplot(vrmid1_regression_coefs_ant_nobc_smoothed, aes(x = sample_point,y = smoothed_beta))+
    geom_vline(xintercept = c(0,4,6,14,16,18)*120, size = 1, color = "grey")+
  annotate("text", x = 2*120,y = 0.15, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5*120,y = 0.15, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 15*120,y = 0.15, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 17*120,y = 0.15, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 10*120,y = 0.15, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
    geom_segment(aes(x = vrmid1_ant_window[1]*120, xend = vrmid1_ant_window[2]*120, y = 0.3, yend = 0.3), color = 'purple',size = 2)+
  geom_point(aes(color = smoothed_beta),
             size = 1)+
  scale_x_continuous(breaks = seq(0,120*20,5*120), labels =  seq(0,20,5))+
  labs(x = "time (sec)",
       y =  "Correlation strength (beta)",
       title = "VR study 1",
       subtitle = "anticipation probe",
       color = "")+
  scale_color_viridis_c(limits=c(-0.05,0.45))+
  theme_blank()+
  theme(legend.position = "left")

p1b<-ggplot(vrmid1_regression_coefs_out_nobc_smoothed, aes(x = sample_point,y = smoothed_beta))+
    geom_vline(xintercept = c(0,4,6,8,10,18)*120, size = 1, color = "grey")+
  annotate("text", x = 2*120,y = 0.02, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5*120,y =0.02, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 7*120,y = 0.02, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 9*120,y = 0.02, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 14*120,y = 0.02, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
   geom_point(aes(color = smoothed_beta),
             size = 1)+
  geom_segment(aes(x = vrmid1_outprobe_out_window[1]*120, xend = vrmid1_outprobe_out_window[2]*120, y = 0.14, yend = 0.14), color = 'skyblue',size = 2)+
  scale_x_continuous(breaks = seq(0,120*20,5*120), label = seq(0,20,5))+
  labs(x = "time (sec)",
       y =  "Correlation strength (beta)",
       title = "VR study 1",
       subtitle = "outcome probe")+
  scale_color_viridis_c(limits=c(-0.05,0.45))+
  theme(legend.position = "none")+
  theme_blank()+
  theme(legend.position = "none")

p2a<-ggplot(vrmid2_regression_coefs_ant_nobc_smoothed, aes(x = sample_point,y = smoothed_beta))+
    geom_vline(xintercept = c(0,4,6,14,16,18)*120, size = 1, color = "grey")+

  annotate("text", x = 2*120,y = 0.14, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5*120,y = 0.14, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 15*120,y = 0.14, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 17*120,y = 0.14, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 10*120,y = 0.14, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  geom_point(aes(color = smoothed_beta),
             size = 1)+
  geom_segment(aes(x = vrmid2_ant_window[1]*120, xend = vrmid2_ant_window[2]*120, y = 0.3, yend = 0.3), color = 'purple',size = 2)+
  scale_x_continuous(breaks = seq(0,120*20,5*120), labels = seq(0,20,5))+
  labs(x = "time (sec)",
       y =  "",
       title = "VR study 2",
       subtitle = "anticipation probe")+
  scale_color_viridis_c(limits=c(-0.05,0.45))+
  theme(legend.position = "none")+
  theme_blank()+
  theme(legend.position = "none")

p2b<-ggplot(vrmid2_regression_coefs_out_nobc_smoothed, aes(x = sample_point,y = smoothed_beta))+
    geom_vline(xintercept = c(0,4,6,8,10,18)*120, size = 1, color = "grey")+
  
  annotate("text", x = 2*120,y = 0.05, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5*120,y =0.05, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 7*120,y = 0.05, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 9*120,y = 0.05, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 13*120,y = 0.05, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
    geom_point(aes(color = smoothed_beta),
             size = 1)+
  geom_segment(aes(x = vrmid2_outprobe_out_window[1]*120, xend = vrmid2_outprobe_out_window[2]*120, y = 0.12, yend = 0.12), color = 'skyblue',size = 2)+
  scale_x_continuous(breaks = seq(0,120*20,5*120), labels = seq(0,20,5))+
  labs(x = "time (sec)",
       y =  "",
       title = "VR study 2",
       subtitle = "outcome probe")+
  scale_color_viridis_c(limits=c(-0.05,0.45))+
  theme(legend.position = "none")+
  theme_blank()+
  theme(legend.position = "none")

p3a<-ggplot(fmri3_regression_coefs_ant_nobc_smoothed, aes(x = sample_point,y = smoothed_beta))+
  geom_vline(xintercept = c(0,2,4,12,14,16,18)*200, size = 1, color = "grey")+
  annotate("text", x = 1*200,y = 0.08, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 3*200,y = 0.08, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 13*200,y = 0.08, label = "fix2",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 15*200,y = 0.08, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 17*200,y = 0.08, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 8*200,y = 0.08, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
  geom_point(aes(color = smoothed_beta),
             size = 1)+
    geom_segment(aes(x = fmri3_ant_window[1]*200, xend = fmri3_ant_window[2]*200, y = 0.15, yend = 0.15), color = 'purple',size = 2)+
  scale_x_continuous(breaks = seq(0,200*20,5*200), labels =  seq(0,20,5))+
  labs(x = "time (sec)",
       y =  "",
       title = "FMRI study 3",
       subtitle = "anticipation probe")+
  scale_color_viridis_c(limits=c(-0.05,0.45))+
  theme(legend.position = "none")+
  theme_blank()+
  theme(legend.position = "none")

p3b<-ggplot(fmri3_regression_coefs_out_nobc_smoothed %>% filter(sample_point <= 18*200), aes(x = sample_point,y = smoothed_beta))+
  geom_vline(xintercept = c(0,2,4,6,8,16)*200, size = 1, color = "grey")+
  annotate("text", x = 1*200,y = 0.02, label = "cue",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 3*200,y = 0.02, label = "fix",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 5*200,y = 0.02, label = "probe",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 7*200,y = 0.02, label = "out",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 12*200,y = 0.02, label = "rate",
          color = "black",size = unit(4,"pt"),angle = 90)+
    geom_point(aes(color = smoothed_beta),
             size = 1)+
  geom_segment(aes(x = fmri3_outprobe_out_window[1]*200, xend = fmri3_outprobe_out_window[2]*200, y = 0.06, yend = 0.06), color = 'skyblue',size = 2)+
 scale_x_continuous(breaks = seq(0,200*20,5*200), labels =  seq(0,20,5))+
  labs(x = "time (sec)",
       y =  "",
       title = "FMRI study 3",
       subtitle = "outcome probe")+
  scale_color_viridis_c(limits=c(-0.05,0.45))+
  theme(legend.position = "none")+
  theme_blank()+
  theme(legend.position = "none")
```

```{r}
(p1a+p2a+p3a)/(p1b+p2b+p3b)
ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig3_regression_timeseries.tiff"),dpi = 300, height = 5, width = 9)
```

# combining two probes, timing = relative to rating period

## time window analysis
```{r}
vrmid1_data_2probes <- rbind(vrmid1_data_antprobe %>% 
                               select(probe:reaction_time,mean_pupil_nobc_ant) %>% 
                               rename(mean_pupil_nobc=mean_pupil_nobc_ant),
                             vrmid1_data_outprobe %>% 
                               select(probe:reaction_time,mean_pupil_nobc_out) %>% 
                               rename(mean_pupil_nobc=mean_pupil_nobc_out))

vrmid2_data_2probes <- rbind(vrmid2_data_antprobe %>% 
                               select(probe:reaction_time,mean_pupil_nobc_ant) %>% 
                               rename(mean_pupil_nobc=mean_pupil_nobc_ant),
                             vrmid2_data_outprobe %>% 
                               select(probe:reaction_time,mean_pupil_nobc_out) %>% 
                               rename(mean_pupil_nobc=mean_pupil_nobc_out))

fmri3_data_2probes <- rbind(fmri3_data_antprobe %>% 
                               select(probe:rt,mean_pupil_nobc_scaled_ant) %>% 
                               rename(mean_pupil_nobc=mean_pupil_nobc_scaled_ant),
                             fmri3_data_outprobe %>% 
                               select(probe:rt,mean_pupil_nobc_scaled_out) %>% 
                               rename(mean_pupil_nobc=mean_pupil_nobc_scaled_out))

summary(l1<-lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc) +(1|Subject) + (1|condition),
              vrmid1_data_2probes))
summary(l2<-lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc) +(1|Subject) + (1|condition),
              vrmid2_data_2probes))
summary(l3<-lmer(scale(arousal_scaled) ~  scale(mean_pupil_nobc) +(1|subject) + (1|cue_size),
              fmri3_data_2probes))
```

## time course analysis
### add new column to dataframe corresponding to time-relative-to-rating
```{r}
vrmid1_pupil_data_ <- vrmid1_pupil_data %>% 
  mutate(rating_start_sec = ifelse(probe == "anti",6,
                ifelse(probe == "out",10,NA))) %>% 
  mutate(Time_sec_from_rating = Time_sec - rating_start_sec) %>% 
  relocate(Time_sec_from_rating,.after = sample_in_sec)

ggplot(vrmid1_pupil_data_, aes(x = Time_sec_from_rating, y = Time_sec))+
  geom_point()+
  facet_wrap(~probe)

vrmid2_pupil_data_ <- vrmid2_pupil_data %>% 
  mutate(rating_start_sec = ifelse(probe == "anti",6,
                ifelse(probe == "out",10,NA))) %>% 
  mutate(Time_sec_from_rating = Time_sec - rating_start_sec)

ggplot(vrmid2_pupil_data_, aes(x = Time_sec_from_rating, y = stat(density)))+
  geom_histogram(binwidth = 2)+
  facet_wrap(~probe)

fmri3_pupil_data_ <- fmri3_pupil_data %>% 
  mutate(rating_start_sec = ifelse(probe == 1,4,
                ifelse(probe == 2,8,NA))) %>% 
  mutate(Time_sec_from_rating = Time_sec - rating_start_sec)%>% 
  relocate(Time_sec_from_rating,.after = sample_in_sec)

ggplot(fmri3_pupil_data_, aes(x = Time_sec_from_rating, y = stat(density)))+
  geom_histogram(binwidth = 1)+
  facet_wrap(~probe)+
  scale_x_continuous(breaks = -10:10)
```

## get the correlation time series for each study separately
```{r warning = F, message=F}
vrmid1_regression_coefs_all_nobc <- {}

for (t in -6:10) {
  coefs <- {}
  print(t)
  for (s in 1:120){
  df_ant_temp <- vrmid1_pupil_data_%>%
  filter(Time_sec_from_rating == t, sample_in_sec == s)
  lm_ant_temp <- lmer(scale(arousal_scaled) ~ scale(pupil_Avg_scale) + (1|Subject) + (1|condition) + (1|probe),df_ant_temp)
  lm_out <- c(summary(lm_ant_temp)$coefficient[2,],'r2m' = r.squaredGLMM(lm_ant_temp)[1])
  coefs <- rbind(coefs,lm_out)
  }
  coefs <- as.data.frame(coefs)%>%
    mutate(sample_in_sec = row_number(),
           Time_sec_from_rating = t)
  rownames(coefs) <- NULL
  vrmid1_regression_coefs_all_nobc <- rbind(vrmid1_regression_coefs_all_nobc,coefs)
}

vrmid1_regression_coefs_all_nobc <- vrmid1_regression_coefs_all_nobc%>%
  mutate(sample_point = row_number(),
         p_val = (`Pr(>|t|)` < .001))

write.csv(vrmid1_regression_coefs_all_nobc, "../../data/vrmid1/derivatives/vrmid1_regression_coefs_all_nobc.csv")

vrmid2_regression_coefs_all_nobc <- {}

for (t in -6:10) {
  coefs <- {}
  print(t)
  for (s in 1:120){
  df_ant_temp <- vrmid2_pupil_data_%>%
  filter(Time_sec_from_rating == t, sample_in_sec == s)
  lm_ant_temp <- lmer(scale(arousal_scaled) ~ scale(pupil_Avg_scale) + (1|Subject) + (1|condition)+ (1|probe),df_ant_temp)
  lm_out <- c(summary(lm_ant_temp)$coefficient[2,],'r2m' = r.squaredGLMM(lm_ant_temp)[1])
  coefs <- rbind(coefs,lm_out)
  }
  coefs <- as.data.frame(coefs)%>%
    mutate(sample_in_sec = row_number(),
           Time_sec_from_rating = t)
  rownames(coefs) <- NULL
  vrmid2_regression_coefs_all_nobc <- rbind(vrmid2_regression_coefs_all_nobc,coefs)
}

vrmid2_regression_coefs_all_nobc <- vrmid2_regression_coefs_all_nobc%>%
  mutate(sample_point = row_number(),
         p_val = (`Pr(>|t|)` < .001))

write.csv(vrmid2_regression_coefs_all_nobc, "../../data/vrmid2/derivatives/vrmid2_regression_coefs_all_nobc.csv")

fmri3_regression_coefs_all_nobc <- {}

for (t in -5:10) {
  coefs <- {}
  print(t)
  for (s in 1:200){
  df_ant_temp <- fmri3_pupil_data_%>%
  filter(Time_sec_from_rating == t, sample_in_sec == s)
  lm_ant_temp <- lmer(scale(arousal_scaled) ~ scale(pupilDiameter_scaled) + (1|subject) + (1|cue_size)+ (1|probe),df_ant_temp)
  lm_out <- c(summary(lm_ant_temp)$coefficient[2,],'r2m' = r.squaredGLMM(lm_ant_temp)[1])
  coefs <- rbind(coefs,lm_out)
  }
  coefs <- as.data.frame(coefs)%>%
    mutate(sample_in_sec = row_number(),
           Time_sec_from_rating = t)
  rownames(coefs) <- NULL
  fmri3_regression_coefs_all_nobc <- rbind(fmri3_regression_coefs_all_nobc,coefs)
}

fmri3_regression_coefs_all_nobc <- fmri3_regression_coefs_all_nobc%>%
  mutate(sample_point = row_number(),
         p_val = (`Pr(>|t|)` < .001))

write.csv(fmri3_regression_coefs_all_nobc, "../../data/fmri3/derivatives/fmri3_regression_coefs_all_nobc.csv")
```

## plot the 3 studies separately
```{r}
vrmid1_regression_coefs_all_nobc_smoothed <- vrmid1_regression_coefs_all_nobc %>% 
  mutate(smoothed_beta = zoo::rollmean(Estimate, k = 60, fill = NA))

p1<-ggplot(vrmid1_regression_coefs_all_nobc_smoothed, aes(x = sample_point,y = smoothed_beta))+
    geom_vline(xintercept = c(6,10,14)*120, size = 1, color = "grey")+
  geom_point(aes(color = smoothed_beta),
             size = 1)+
    annotate("text", x = 6.5*120,y = 0.2, label = "valence rating",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 10.5*120,y = 0.2, label = "arousal rating",
          color = "black",size = unit(4,"pt"),angle = 90)+
  scale_x_continuous(breaks = seq(0*120,16*120,120), labels =  seq(-6,10,1))+
  labs(x = "time since rating period starts (sec)",
       y =  "Correlation strength (beta)",
       title = "VR study 1",
       subtitle = "collapsed across probes",
       color = "")+
  scale_color_viridis_c(limits=c(-0.05,0.45))+
  theme_blank()+
  theme(legend.position = "left")

vrmid2_regression_coefs_all_nobc_smoothed <- vrmid2_regression_coefs_all_nobc %>% 
  mutate(smoothed_beta = zoo::rollmean(Estimate, k = 60, fill = NA))

p2<-ggplot(vrmid2_regression_coefs_all_nobc_smoothed, aes(x = sample_point,y = smoothed_beta))+
    geom_vline(xintercept = c(6,10,14)*120, size = 1, color = "grey")+
  geom_point(aes(color = smoothed_beta),
             size = 1)+
    annotate("text", x = 6.5*120,y = 0.17, label = "valence rating",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 10.5*120,y = 0.17, label = "arousal rating",
          color = "black",size = unit(4,"pt"),angle = 90)+
  scale_x_continuous(breaks = seq(0*120,16*120,120), labels =  seq(-6,10,1))+
  labs(x = "time since rating period starts (sec)",
       y =  "Correlation strength (beta)",
       title = "VR study 2",
       subtitle = "collapsed across probes",
       color = "")+
  scale_color_viridis_c(limits=c(-0.05,0.45))+
  theme_blank()+
  theme(legend.position = "none")

fmri3_regression_coefs_all_nobc_smoothed <- fmri3_regression_coefs_all_nobc %>% 
  mutate(smoothed_beta = zoo::rollmean(Estimate, k = 100, fill = NA))

p3<-ggplot(fmri3_regression_coefs_all_nobc_smoothed, aes(x = sample_point,y = smoothed_beta))+
    geom_vline(xintercept = c(6,10,14)*200, size = 1, color = "grey")+
  geom_point(aes(color = smoothed_beta),
             size = 1)+
  annotate("text", x = 6.5*200,y = 0.07, label = "valence rating",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 10.5*200,y = 0.07, label = "arousal rating",
          color = "black",size = unit(4,"pt"),angle = 90)+
  scale_x_continuous(breaks = seq(0*200,16*200,200), labels =  seq(-6,10,1))+
  labs(x = "time since rating period starts (sec)",
       y =  "Correlation strength (beta)",
       title = "FMRI study 3",
       subtitle = "collapsed across probes",
       color = "")+
  scale_color_viridis_c(limits=c(-0.05,0.45))+
  theme_blank()+
  theme(legend.position = "none")

p1+p2+p3
ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig7_howlongago.tiff"),dpi = 300, height = 3, width = 12)
```

## group all 3 studies together for a master correlation
```{r}
all_pupil_data <- Reduce(rbind,list(vrmid1_pupil_data_ %>% 
                                      mutate(study = "VRstudy1") %>% 
                                      select(Time_sec_from_rating,sample_in_sec,arousal_scaled,Subject,condition,study,pupil_Avg_scale,probe),
                                    vrmid2_pupil_data_ %>% 
                                      mutate(study = "VRstudy2")%>% 
                                      select(Time_sec_from_rating,sample_in_sec,arousal_scaled,Subject,condition,study,pupil_Avg_scale,probe),
                                    fmri3_pupil_data_ %>% 
                                      mutate(study = "FMRIstudy3")%>% 
                                      rename(Subject = subject,condition = cue_size,pupil_Avg_scale=pupilDiameter_scaled) %>% 
                                      mutate(probe = ifelse(probe == 1, "anti",
                                                            ifelse(probe == 2, "out"))) %>% 
                                      select(Time_sec_from_rating,sample_in_sec,arousal_scaled,Subject,condition,study,pupil_Avg_scale,probe)))

all_regression_coefs_all_nobc <- {}

for (t in -6:10) {
  coefs <- {}
  print(t)
  for (s in 1:120){ #FMRI3 will be downsampled
  df_ant_temp <- all_pupil_data%>%
  filter(Time_sec_from_rating == t, sample_in_sec == s)
  lm_ant_temp <- lmer(scale(arousal_scaled) ~ scale(pupil_Avg_scale) + (1|Subject) + (1|condition) + (1|probe) + (1+pupil_Avg_scale|study),df_ant_temp)
  lm_out <- c(summary(lm_ant_temp)$coefficient[2,],'r2m' = r.squaredGLMM(lm_ant_temp)[1])
  coefs <- rbind(coefs,lm_out)
  }
  coefs <- as.data.frame(coefs)%>%
    mutate(sample_in_sec = row_number(),
           Time_sec_from_rating = t)
  rownames(coefs) <- NULL
  all_regression_coefs_all_nobc <- rbind(all_regression_coefs_all_nobc,coefs)
}

all_regression_coefs_all_nobc <- all_regression_coefs_all_nobc%>%
  mutate(sample_point = row_number(),
         p_val = (`Pr(>|t|)` < .001))

all_regression_coefs_all_nobc_smoothed <- all_regression_coefs_all_nobc %>% 
  mutate(smoothed_beta = zoo::rollmean(Estimate, k = 60, fill = NA))

(p1+p2+p3)/
ggplot(all_regression_coefs_all_nobc_smoothed, aes(x = sample_point,y = smoothed_beta))+
    geom_vline(xintercept = c(4,6,10,14)*120, size = 1, color = "grey")+
  geom_point(aes(color = smoothed_beta),
             size = 1)+
     annotate("text", x = 4.5*120,y = 0.2, label = "onset of fixation / outcome",
          color = "black",size = unit(4,"pt"),angle = 90)+
    annotate("text", x = 6.5*120,y = 0.2, label = "valence rating",
          color = "black",size = unit(4,"pt"),angle = 90)+
  annotate("text", x = 10.5*120,y = 0.2, label = "arousal rating",
          color = "black",size = unit(4,"pt"),angle = 90)+
  scale_x_continuous(breaks = seq(0*120,16*120,120), labels =  seq(-6,10,1))+
  labs(x = "time since rating period starts (sec)",
       y =  "Correlation strength (beta)",
       title = "3 studies combined",
       subtitle = "collapsed across probes",
       color = "")+
  scale_color_viridis_c(limits=c(-0.05,0.45))+
  theme_blank()+
  theme(legend.position = "none")+
plot_layout(heights = c(1,2))

ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig7_howlongago2.tiff"),dpi = 300, height = 7, width = 12)
```

# behavioral implications of pupil-linked arousal
## fatigue: visualise tonic activity over time
```{r}
vrmid1_pupil_data_tonic <- vrmid1_pupil_data%>%
  filter(Time_sec >= vrmid1_ant_window[1], Time_sec <= vrmid1_ant_window[2])%>% 
  select(Subject,probe,trial,pupil_Avg_baseline_scale,pupil_Avg_bc_scale,
         last_ITI,arousal_scaled,valence_scaled)%>%
  group_by(Subject,trial,
         arousal_scaled,valence_scaled)%>%
  summarise(pupil_Avg_baseline_scale = mean(pupil_Avg_baseline_scale,na.rm = T),
                   pupil_Avg_bc_scale = mean(pupil_Avg_bc_scale,na.rm=T)) %>% 
  group_by(Subject) %>% 
  mutate(pupilDiameter_baseline_scale = as.numeric(scale(pupil_Avg_baseline_scale)),
         pupil_Avg_bc_scale = as.numeric(scale(pupil_Avg_bc_scale)))%>%
  ungroup()%>%
  group_by(Subject,trial,
         arousal_scaled,valence_scaled)%>%
  dplyr::summarise(pupil_Avg_baseline_scale = mean(pupil_Avg_baseline_scale,na.rm = T),
                   pupil_Avg_bc_scale = mean(pupil_Avg_bc_scale,na.rm=T))%>%
  mutate(half = ifelse(trial >= 48,"second","first"))

vrmid1_pupil_data_phasicarousal <- vrmid1_pupil_data%>%
  mutate(half = ifelse(trial >= 48,"second","first"))%>%
  select(Subject,probe,trial,half,
         last_ITI,arousal_scaled,valence_scaled,
         trial_type)%>%
  group_by(Subject,trial,trial_type,
         arousal_scaled,valence_scaled)%>%
  mutate(rowid = row_number()) %>% 
  filter(rowid == 1) %>% 
  group_by(Subject,half,trial_type)%>%
  summarise(arousal_scaled = mean(arousal_scaled,na.rm = T)) %>% 
  pivot_wider(names_from = trial_type, values_from = arousal_scaled) %>% 
  mutate(plus5_plus0 = `+$5` - `+$0`,
         minus5_minus0 = `-$5` - `-$0`,
         five_vs_zero = (plus5_plus0+minus5_minus0)/2)
  
mytext=summary(lmer(pupil_Avg_baseline_scale ~ half + (1|Subject),vrmid1_pupil_data_tonic))$coefficients

pt11 <- ggplot(vrmid1_pupil_data_tonic)+
  geom_hline(yintercept = 0, linetype = 'dashed')+
  stat_summary(aes(group = Subject, x = half, y = pupil_Avg_baseline_scale),geom = "line",size = 0.3, alpha = 0.3,
            color = "grey")+
  stat_summary(aes(x = half, y = pupil_Avg_baseline_scale),fun.data = "mean_cl_boot",geom = "pointrange",
               size = 0.2)+
  labs(y = "pupil zscore",
       title = "VR study 1",
       subtitle = "Tonic pupil")+
  annotate("text",x = 1.5, y = 0.1,label = paste0("t = ", round(mytext[2,4],2),", p = ",round(mytext[2,5],4)))

mytext=summary(lmer(pupil_Avg_bc_scale ~ half + (1|Subject),vrmid1_pupil_data_tonic))$coefficients

pt12 <- ggplot(vrmid1_pupil_data_tonic)+
  geom_hline(yintercept = 0, linetype = 'dashed')+
  stat_summary(aes(group = Subject, x = half, y = pupil_Avg_bc_scale),geom = "line",size = 0.3, alpha = 0.3,
            color = "grey")+
  stat_summary(aes(x = half, y = pupil_Avg_bc_scale),fun.data = "mean_cl_boot",geom = "pointrange",
               size = 0.2)+
  labs(y = "pupil zscore",
       subtitle = "Phasic anticipatory pupil")+
  annotate("text",x = 1.5, y = 0.1,label = paste0("t = ", round(mytext[2,4],2),", p = ",round(mytext[2,5],2)))

# summary(lmer(arousal_scaled ~ half + (1|Subject),vrmid1_pupil_data_tonic))
# summary(lmer(valence_scaled ~ half + (1|Subject),vrmid1_pupil_data_tonic))
mytext=summary(lmer(arousal_scaled ~ half + (1|Subject),vrmid1_pupil_data_tonic))$coefficients

pt13 <- ggplot(vrmid1_pupil_data_tonic)+
  geom_hline(yintercept = 0, linetype = 'dashed')+
  stat_summary(aes(group = Subject, x = half, y = arousal_scaled),geom = "line",size = 0.3, alpha = 0.3,
            color = "grey")+
  stat_summary(aes(x = half, y = arousal_scaled),fun.data = "mean_cl_boot",geom = "pointrange",
               size = 0.2)+
  labs(y = "arousal",
       subtitle = "arousal")+
  annotate("text",x = 1.5, y = 0.1,label = paste0("t = ", round(mytext[2,4],2),", p = ",round(mytext[2,5],2)))

mytext=summary(lmer(valence_scaled ~ half + (1|Subject),vrmid1_pupil_data_tonic))$coefficients
pt14 <- ggplot(vrmid1_pupil_data_tonic)+
  geom_hline(yintercept = 0, linetype = 'dashed')+
  stat_summary(aes(group = Subject, x = half, y = valence_scaled),geom = "line",size = 0.3, alpha = 0.3,
            color = "grey")+
  stat_summary(aes(x = half, y = valence_scaled),fun.data = "mean_cl_boot",geom = "pointrange",
               size = 0.2)+
  labs(y = "valence",
       subtitle = "valence")+
  annotate("text",x = 1.5, y = 0.1,label = paste0("t = ", round(mytext[2,4],2),", p = ",round(mytext[2,5],2)))

mytext=summary(lmer(five_vs_zero ~ half + (1|Subject),vrmid1_pupil_data_phasicarousal))$coefficients
pt15 <- ggplot(vrmid1_pupil_data_phasicarousal)+
  geom_hline(yintercept = 0, linetype = 'dashed')+
  stat_summary(aes(group = Subject, x = half, y = five_vs_zero),geom = "line",size = 0.3, alpha = 0.3,
            color = "grey")+
  stat_summary(aes(x = half, y = five_vs_zero),fun.data = "mean_cl_boot",geom = "pointrange",
               size = 0.2)+
  labs(y = "arousal $5-$0",
       subtitle = "arousal $5 minus $0")+
  annotate("text",x = 1.5, y = 0.4,label = paste0("t = ", round(mytext[2,4],2),", p = ",round(mytext[2,5],2)))

vrmid2_pupil_data_tonic <- vrmid2_pupil_data%>%
  filter(Time_sec >= vrmid2_ant_window[1], Time_sec <= vrmid2_ant_window[2])%>% 
  select(Subject,probe,trial,pupil_Avg_baseline_scale,pupil_Avg_bc_scale,
         last_ITI,arousal_scaled,valence_scaled)%>%
  group_by(Subject,trial,
         arousal_scaled,valence_scaled)%>%
  summarise(pupil_Avg_baseline_scale = mean(pupil_Avg_baseline_scale,na.rm = T),
                   pupil_Avg_bc_scale = mean(pupil_Avg_bc_scale,na.rm=T)) %>% 
  group_by(Subject) %>% 
  mutate(pupilDiameter_baseline_scale = as.numeric(scale(pupil_Avg_baseline_scale)),
         pupil_Avg_bc_scale = as.numeric(scale(pupil_Avg_bc_scale)))%>%
  ungroup()%>%
  group_by(Subject,trial,
         arousal_scaled,valence_scaled)%>%
  dplyr::summarise(pupil_Avg_baseline_scale = mean(pupil_Avg_baseline_scale,na.rm = T),
                   pupil_Avg_bc_scale = mean(pupil_Avg_bc_scale,na.rm=T))%>%
  mutate(half = ifelse(trial >= 48,"second","first"))

vrmid2_pupil_data_phasicarousal <- vrmid2_pupil_data%>%
  filter(rating_type == "affect") %>%
  group_by(Subject,trial,trial_type,
         arousal_scaled,valence_scaled)%>%
  mutate(rowid = row_number()) %>% 
  filter(rowid == 1) %>% 
  group_by(Subject)%>%
  mutate(trial = row_number()) %>% 
  mutate(half = ifelse(trial >= 24,"second","first"))%>%
  select(Subject,probe,trial,half,
         last_ITI,arousal_scaled,valence_scaled,
         trial_type)%>%
  group_by(Subject,half,trial_type)%>%
  summarise(arousal_scaled = mean(arousal_scaled,na.rm = T)) %>% 
  pivot_wider(names_from = trial_type, values_from = arousal_scaled) %>% 
  mutate(plus5_plus0 = `+$5` - `+$0`,
         minus5_minus0 = `-$5` - `-$0`,
         five_vs_zero = (plus5_plus0+minus5_minus0)/2)

mytext=summary(lmer(pupil_Avg_baseline_scale ~ half + (1|Subject),vrmid2_pupil_data_tonic))$coefficients
pt21 <- ggplot(vrmid2_pupil_data_tonic)+
  geom_hline(yintercept = 0, linetype = 'dashed')+
  stat_summary(aes(group = Subject, x = half, y = pupil_Avg_baseline_scale),geom = "line",size = 0.3, alpha = 0.3,
            color = "grey")+
  stat_summary(aes(x = half, y = pupil_Avg_baseline_scale),fun.data = "mean_cl_boot",geom = "pointrange",
               size = 0.2)+
  labs(y = "pupil zscore",
       title = "VR study 2",
       subtitle = "Tonic pupil")+
  annotate("text",x = 1.5, y = 0.1,label = paste0("t = ", round(mytext[2,4],2),", p = ",round(mytext[2,5],2)))

mytext=summary(lmer(pupil_Avg_bc_scale ~ half + (1|Subject),vrmid2_pupil_data_tonic))$coefficients
pt22 <- ggplot(vrmid2_pupil_data_tonic)+
  geom_hline(yintercept = 0, linetype = 'dashed')+
  stat_summary(aes(group = Subject, x = half, y = pupil_Avg_bc_scale),geom = "line",size = 0.3, alpha = 0.3,
            color = "grey")+
  stat_summary(aes(x = half, y = pupil_Avg_bc_scale),fun.data = "mean_cl_boot",geom = "pointrange",
               size = 0.2)+
  labs(y = "pupil zscore",
       subtitle = "Phasic anticipatory pupil")+
  annotate("text",x = 1.5, y = 0.1,label = paste0("t = ", round(mytext[2,4],2),", p = ",round(mytext[2,5],2)))

mytext=summary(lmer(arousal_scaled ~ half + (1|Subject),vrmid2_pupil_data_tonic))$coefficients
pt23 <- ggplot(vrmid2_pupil_data_tonic)+
  geom_hline(yintercept = 0, linetype = 'dashed')+
  stat_summary(aes(group = Subject, x = half, y = arousal_scaled),geom = "line",size = 0.3, alpha = 0.3,
            color = "grey")+
  stat_summary(aes(x = half, y = arousal_scaled),fun.data = "mean_cl_boot",geom = "pointrange",
               size = 0.2)+
  labs(y = "arousal",
       subtitle = "arousal")+
  annotate("text",x = 1.5, y = 0.1,label = paste0("t = ", round(mytext[2,4],2),", p = ",round(mytext[2,5],2)))

mytext=summary(lmer(valence_scaled ~ half + (1|Subject),vrmid2_pupil_data_tonic))$coefficients
pt24 <- ggplot(vrmid2_pupil_data_tonic)+
  geom_hline(yintercept = 0, linetype = 'dashed')+
  stat_summary(aes(group = Subject, x = half, y = valence_scaled),geom = "line",size = 0.3, alpha = 0.3,
            color = "grey")+
  stat_summary(aes(x = half, y = valence_scaled),fun.data = "mean_cl_boot",geom = "pointrange",
               size = 0.2)+
  labs(y = "valence",
       subtitle = "valence")+
  annotate("text",x = 1.5, y = 0.1,label = paste0("t = ", round(mytext[2,4],2),", p = ",round(mytext[2,5],2)))

mytext=summary(lmer(five_vs_zero ~ half + (1|Subject),vrmid2_pupil_data_phasicarousal))$coefficients
pt25 <- ggplot(vrmid2_pupil_data_phasicarousal)+
  geom_hline(yintercept = 0, linetype = 'dashed')+
  stat_summary(aes(group = Subject, x = half, y = five_vs_zero),geom = "line",size = 0.3, alpha = 0.3,
            color = "grey")+
  stat_summary(aes(x = half, y = five_vs_zero),fun.data = "mean_cl_boot",geom = "pointrange",
               size = 0.2)+
  labs(y = "arousal $5-$0",
       subtitle = "arousal $5 minus $0")+
  annotate("text",x = 1.5, y = 0.4,label = paste0("t = ", round(mytext[2,4],2),", p = ",round(mytext[2,5],2)))

fmri3_pupil_data_tonic <- fmri3_pupil_data%>%
  filter(rating_type==1) %>% 
  filter(Time_sec >= fmri3_ant_window[1], Time_sec <= fmri3_ant_window[2])%>% 
  select(subject,probe,trial,pupilDiameter_baseline_scaled,pupilDiameter_bc_scaled,
         last_iti,arousal_scaled,valence_scaled)%>%
  group_by(subject,trial,
         arousal_scaled,valence_scaled)%>%
  filter(last_iti != 0) %>% 
  summarise(pupilDiameter_baseline_scaled = mean(pupilDiameter_baseline_scaled,na.rm = T),
                   pupilDiameter_bc_scaled = mean(pupilDiameter_bc_scaled,na.rm=T)) %>% 
  group_by(subject) %>% 
  mutate(pupilDiameter_baseline_scaled = as.numeric(scale(pupilDiameter_baseline_scaled)),
         pupilDiameter_bc_scaled = as.numeric(scale(pupilDiameter_bc_scaled)))%>%
  ungroup()%>%
  group_by(subject,trial,
         arousal_scaled,valence_scaled)%>%
  dplyr::summarise(pupilDiameter_baseline_scaled = mean(pupilDiameter_baseline_scaled,na.rm = T),
                   pupilDiameter_bc_scaled = mean(pupilDiameter_bc_scaled,na.rm=T))%>%
  mutate(half = ifelse(trial >= 48,"second","first"))

fmri3_pupil_data_phasicarousal <- fmri3_pupil_data%>% 
   filter(!subject %in% c("tc240311","st240312"))%>%
  filter(rating_type == 1) %>%
  group_by(subject,trial,cue_value,
         arousal_scaled,valence_scaled)%>%
  mutate(rowid = row_number()) %>% 
  filter(rowid == 1) %>% 
  group_by(subject)%>%
  mutate(trial = row_number()) %>% 
  mutate(half = ifelse(trial >= 24,"second","first"))%>%
  group_by(subject,half,cue_value)%>%
  summarise(arousal_scaled = mean(arousal_scaled,na.rm = T)) %>% 
  pivot_wider(names_from = cue_value, values_from = arousal_scaled) %>% 
  mutate(plus5_plus0 = `+$5` - `+$0`,
         minus5_minus0 = `-$5` - `-$0`,
         five_vs_zero = (plus5_plus0+minus5_minus0)/2)

mytext=summary(lmer(pupilDiameter_baseline_scaled ~ half + (1|subject),fmri3_pupil_data_tonic))$coefficients
pt31 <- ggplot(fmri3_pupil_data_tonic)+
  geom_hline(yintercept = 0, linetype = 'dashed')+
  stat_summary(aes(group = subject, x = half, y = pupilDiameter_baseline_scaled),geom = "line",size = 0.3, alpha = 0.3,
            color = "grey")+
  stat_summary(aes(x = half, y = pupilDiameter_baseline_scaled),fun.data = "mean_cl_boot",geom = "pointrange",
               size = 0.2)+
  labs(y = "pupil zscore",
       title = "FMRI study 3",
       subtitle = "Tonic pupil")+
  annotate("text",x = 1.5, y = 0.1,label = paste0("t = ", round(mytext[2,4],2),", p = ",round(mytext[2,5],2)))

mytext=summary(lmer(pupilDiameter_bc_scaled ~ half + (1|subject),fmri3_pupil_data_tonic))$coefficients
pt32 <- ggplot(fmri3_pupil_data_tonic)+ #these two people had problematic ratings (missed too much)
  geom_hline(yintercept = 0, linetype = 'dashed')+
  stat_summary(aes(group = subject, x = half, y = pupilDiameter_bc_scaled),geom = "line",size = 0.3, alpha = 0.3,
            color = "grey")+
  stat_summary(aes(x = half, y = pupilDiameter_bc_scaled),fun.data = "mean_cl_boot",geom = "pointrange",
               size = 0.2)+
  labs(y = "pupil zscore",
       subtitle = "Phasic anticipatory pupil")+
  annotate("text",x = 1.5, y = 0.1,label = paste0("t = ", round(mytext[2,4],2),", p = ",round(mytext[2,5],2)))

# summary(lmer(arousal_scaled ~ half + (1|subject),fmri3_pupil_data_tonic))
mytext=summary(lmer(arousal_scaled ~ half + (1|subject),fmri3_pupil_data_tonic%>% 
                 filter(!subject %in% c("tc240311","st240312"))))$coefficients
pt33 <- ggplot(fmri3_pupil_data_tonic %>% 
                 filter(!subject %in% c("tc240311","st240312")))+
  geom_hline(yintercept = 0, linetype = 'dashed')+
  stat_summary(aes(group = subject, x = half, y = arousal_scaled),geom = "line",size = 0.3, alpha = 0.3,
            color = "grey")+
  stat_summary(aes(x = half, y = arousal_scaled),fun.data = "mean_cl_boot",geom = "pointrange",
               size = 0.2)+
  labs(y = "arousal",
       subtitle = "arousal")+
  annotate("text",x = 1.5, y = 0.1,label = paste0("t = ", round(mytext[2,4],2),", p = ",round(mytext[2,5],2)))

mytext=summary(lmer(valence_scaled ~ half + (1|subject),fmri3_pupil_data_tonic%>% 
                 filter(!subject %in% c("tc240311","st240312"))))$coefficients
pt34 <- ggplot(fmri3_pupil_data_tonic %>% 
                 filter(!subject %in% c("tc240311","st240312")))+
  geom_hline(yintercept = 0, linetype = 'dashed')+
  stat_summary(aes(group = subject, x = half, y = valence_scaled),geom = "line",size = 0.3, alpha = 0.3,
            color = "grey")+
  stat_summary(aes(x = half, y = valence_scaled),fun.data = "mean_cl_boot",geom = "pointrange",
               size = 0.2)+
  labs(y = "valence",
       subtitle = "valence")+
  annotate("text",x = 1.5, y = 0.1,label = paste0("t = ", round(mytext[2,4],2),", p = ",round(mytext[2,5],2)))

mytext=summary(lmer(five_vs_zero ~ half + (1|subject),fmri3_pupil_data_phasicarousal))$coefficients
pt35 <- ggplot(fmri3_pupil_data_phasicarousal)+
  geom_hline(yintercept = 0, linetype = 'dashed')+
  stat_summary(aes(group = subject, x = half, y = five_vs_zero),geom = "line",size = 0.3, alpha = 0.3,
            color = "grey")+
  stat_summary(aes(x = half, y = five_vs_zero),fun.data = "mean_cl_boot",geom = "pointrange",
               size = 0.2)+
  labs(y = "arousal $5-$0",
       subtitle = "arousal $5 minus $0")+
  annotate("text",x = 1.5, y = 0.4,label = paste0("t = ", round(mytext[2,4],2),", p = ",round(mytext[2,5],2)))
```

## rt: should be predicted by arousal and pupil dilation
```{r}
vrmid1_data_rt <- vrmid1_pupil_data%>%
  filter(sample_in_trial_t <= vrmid1_ant_window[2] & sample_in_trial_t > vrmid1_ant_window[1]) %>% 
  group_by(probe,Subject,trial,reaction_outcome,trial_type,PosA_scaled,NegA_scaled,
           arousal,valence,last_ITI,
           arousal_scaled,valence_scaled,
           condition,reaction_time)%>%
  summarise(mean_pupil_bc = mean(pupil_Avg_bc_scale, na.rm = T),
            mean_pupil_nobc = mean(pupil_Avg_scale, na.rm = T),
            mean_pupil_baseline = mean(pupil_Avg_baseline_scale, na.rm = T))%>%
  filter(abs(mean_pupil_bc) < 4,
         abs(mean_pupil_nobc) < 4,
         abs(mean_pupil_baseline) < 4)  %>% 
  group_by(Subject)%>%
  mutate(log_rt = log(reaction_time),
         log_rt = as.numeric(scale(log_rt)),
         hit = ifelse(reaction_outcome == "Hit",1,0)) 

vrmid2_data_rt <- vrmid2_pupil_data%>%
  filter(sample_in_trial_t <= vrmid2_ant_window[2] & sample_in_trial_t > vrmid2_ant_window[1]) %>% 
  group_by(probe,Subject,trial,reaction_outcome,trial_type,PosA_scaled,NegA_scaled,
           arousal,valence,last_ITI,
           arousal_scaled,valence_scaled,
           condition,reaction_time)%>%
  summarise(mean_pupil_bc = mean(pupil_Avg_bc_scale, na.rm = T),
            mean_pupil_nobc = mean(pupil_Avg_scale, na.rm = T),
            mean_pupil_baseline = mean(pupil_Avg_baseline_scale, na.rm = T))%>%
  filter(abs(mean_pupil_bc) < 4,
         abs(mean_pupil_nobc) < 4,
         abs(mean_pupil_baseline) < 4)  %>% 
  group_by(Subject)%>%
  mutate(log_rt = log(reaction_time),
         log_rt = as.numeric(scale(log_rt)),
         hit = ifelse(reaction_outcome == "Hit",1,0)) 

fmri3_data_rt <- fmri3_pupil_data%>%
  filter(sample_in_trial_t <= fmri3_ant_window[2] & sample_in_trial_t > fmri3_ant_window[1]) %>% 
  group_by(probe,subject,trial,hit,cue_value,
           arousal,valence,last_iti,
           arousal_scaled,valence_scaled,
           cue_size,rt)%>%
  summarise(mean_pupil_bc = mean(pupilDiameter_bc_scaled, na.rm = T),
            mean_pupil_nobc = mean(pupilDiameter_scaled, na.rm = T),
            mean_pupil_baseline = mean(pupilDiameter_baseline_scaled, na.rm = T))%>%
  filter(abs(mean_pupil_bc) < 4,
         abs(mean_pupil_nobc) < 4,
         abs(mean_pupil_baseline) < 4)  %>% 
  group_by(subject)%>%
  mutate(log_rt = log(rt),
         log_rt = as.numeric(scale(log_rt)),
         hit = ifelse(hit == "Hit",1,0)) 

rt_reg_coef <- as.data.frame(
  Reduce(rbind,list(
  summary(lmer(scale(log_rt) ~ scale(mean_pupil_bc) + (1|Subject),vrmid1_data_rt %>% filter(hit == 1)))$coefficients,
summary(lmer(scale(log_rt) ~ scale(mean_pupil_baseline) + (1|Subject),vrmid1_data_rt %>% filter(hit == 1)))$coefficients,
summary(lmer(scale(log_rt) ~ scale(arousal_scaled) + (1|Subject),vrmid1_data_rt %>% filter(hit == 1)))$coefficients,

summary(lmer(scale(log_rt) ~ scale(mean_pupil_bc) + (1|Subject),vrmid2_data_rt%>% filter(hit == 1)))$coefficients,
summary(lmer(scale(log_rt) ~ scale(mean_pupil_baseline) + (1|Subject),vrmid2_data_rt%>% filter(hit == 1)))$coefficients,
summary(lmer(scale(log_rt) ~ scale(arousal_scaled) + (1|Subject),vrmid2_data_rt %>% filter(hit == 1)))$coefficients,

summary(lmer(scale(log_rt) ~ scale(mean_pupil_bc) + (1|subject),fmri3_data_rt%>% filter(hit == 1)))$coefficients,
summary(lmer(scale(log_rt) ~ scale(mean_pupil_baseline) + (1|subject),fmri3_data_rt%>% filter(hit == 1)))$coefficients,
summary(lmer(scale(log_rt) ~ scale(arousal_scaled) + (1|subject),fmri3_data_rt %>% filter(hit == 1)))$coefficients))
) %>% 
  rownames_to_column() %>% 
  filter(!grepl("Intercept",rowname))

rt_reg_coef$study <- c("VRstudy1","VRstudy1","VRstudy1","VRstudy2","VRstudy2","VRstudy2","FMRIstudy3","FMRIstudy3","FMRIstudy3")
rt_reg_coef$predictor <- rep(c("phasic_pupil","tonic_pupil","arousal"),3)

rt_reg_coef<-rt_reg_coef %>% 
  mutate(sig = ifelse(`Pr(>|t|)` >= .1, "n.s.",
                      ifelse(`Pr(>|t|)` >= .05, "+",
                      ifelse(`Pr(>|t|)` >= .01, "*",
                             ifelse(`Pr(>|t|)` >= .005,"**","***")))))

rt_reg_coef$predictor <- factor(rt_reg_coef$predictor, levels = c("phasic_pupil","tonic_pupil","arousal"),
                                labels = c("phasic pupil","tonic pupil","subjective arousal"))
rt_reg_coef$study <- factor(rt_reg_coef$study, levels = c("VRstudy1","VRstudy2","FMRIstudy3"),
                                labels = c("VR study 1","VR study 2","FMRI study 3"))
pp<-ggplot(rt_reg_coef, aes(x = study, y = Estimate,
                        color = study))+
  geom_hline(yintercept = 0, linetype = "dashed")+
  geom_text(aes(x = study, y = Estimate-0.01,
                        color = study, label = sig))+
  # geom_errorbar(aes(x = study, y = Estimate,ymin = Estimate-`Std. Error`,
  #                   ymax = Estimate+`Std. Error`,
  #                       color = study), width = 0.1)+
  geom_point(size = 3, shape = 5)+
  facet_wrap(~predictor)+
  scale_color_brewer(palette = "Dark2")+
  theme(legend.position = "none")+
  labs(y = "Regression beta on reaction time",
       x = "",
       title = "Reaction time")

(pt11+pt12+pt13+pt15+
pt21+pt22+pt23+pt25+
pt31+pt32+pt33+pt35)/
  pp+
  plot_layout(heights = c(3,1))+
  plot_annotation(tag_levels = "a")

ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig5_beh.tiff"),dpi = 300, height = 10, width = 9)
ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig5_beh.svg"), height = 10, width = 9)
```

