---
title: "template_similarity"
output: html_document
date: "2025-11-15"
---

## first, look at correlation between two regressors
```{r}
subjects_list<-read_delim('~/Desktop/midaffemo/analyses/subjects-pupil-fmri.txt',delim = '\t', col_names = F)

reg_corr_list <- NULL
all_reg <- NULL
for (sub in subjects_list$X1){
  file_pupil <- paste0("~/Desktop/midaffemo/regs_corr/",sub,"_pupil_scaled_c.1D")
  pupil_reg <- read_delim(file_pupil,delim = '\t', col_names = F)
  file_rating <- paste0("~/Desktop/midaffemo/regs_corr/",sub,"_report_param_arous_c.1D")
  rating_reg <- read_delim(file_rating,delim = '\t', col_names = F)
  reg_corr_list <- rbind(reg_corr_list,
                         summary(lm(scale(pupil_reg$X1)~scale(rating_reg$X1)))$coefficients[2,])
  all_reg <- rbind(all_reg, cbind(pupil_reg,rating_reg, subject = sub))
}

reg_corr_list <- as.data.frame(reg_corr_list)
reg_corr_list$subject <- subjects_list$X1
mean(reg_corr_list$Estimate)
sd(reg_corr_list$Estimate)
t.test(reg_corr_list$Estimate,mu=0)

all_reg <- as.data.frame(all_reg)
names(all_reg) <- c("pupil","rating","subject")
summary(lmer(scale(pupil)~scale(rating)+ (1|subject),all_reg))
```

## midaffemo 1 (only pupil GLM; in SI)

### make dataframe of all similarities, all thresholds
```{r}
subjects_list<-read_delim('~/Desktop/midaffemo/analyses/subjects-pupil-fmri.txt',delim = '\t', col_names = F)
thresh_str <- c("0","05","1","15","2","25","3","35")
thresh <- c(0,0.5,1,1.5,2,2.5,3,3.5)

glmArousal_array <- NULL
glmPupil_array <- NULL
glmPupil_posonly_array <- NULL
pupil_array <- NULL

for (t in 1:length(thresh_str)){
  filepath = paste0("~/Desktop/midaffemo/glm_maps/glm27_array_threshold",thresh_str[t],".csv")
  glmArousal_array<-rbind(glmArousal_array,
                          as.data.frame(t(read_csv(filepath, 
                                           col_names = F))) %>% 
                            mutate(type = "glmArousal", 
                                   tr = row_number(), 
                                   threshold = thresh[t]) #self-reported arousal GLM
  )
  
  filepath = paste0("~/Desktop/midaffemo/glm_maps/glm33b_array_threshold",thresh_str[t],".csv")
  glmPupil_array<-rbind(glmPupil_array,
                        as.data.frame(t(read_csv(filepath, 
             col_names = F))) %>% 
    mutate(type = "glmPupil", tr = row_number(), 
                                   threshold = thresh[t])) #pupil GLM
  
  filepath = paste0("~/Desktop/midaffemo/glm_maps/glm33b_posonly_array_threshold",thresh_str[t],".csv")
  glmPupil_posonly_array<-rbind(glmPupil_posonly_array,
                        as.data.frame(t(read_csv(filepath, 
             col_names = F))) %>% 
    mutate(type = "glmPupil_posonly", tr = row_number(), 
                                   threshold = thresh[t])) #pupil GLM (pos only)
  
  pupil_array<-rbind(pupil_array,
                     as.data.frame(t(read_csv("~/Desktop/midaffemo/glm_maps/pupil_array.csv", col_names = F))) %>% 
    mutate(type = "pupil", tr = row_number(), 
                                   threshold = thresh[t])) #pupil time series
}


my_array_s1<-Reduce(rbind,list(glmArousal_array,glmPupil_array,glmPupil_posonly_array,pupil_array))
names(my_array_s1) <- c(subjects_list$X1,"type","tr","threshold")
my_array_s1<-my_array_s1%>% 
  pivot_longer(ab240324:yz240312,names_to = "subject",values_to = "val") %>% 
  pivot_wider(names_from = type, values_from = val)

my_array_s1_ <- my_array_s1 %>% 
  mutate(pupil_lead10 = lead(pupil,10),
         pupil_lead9 = lead(pupil,9),
         pupil_lead8 = lead(pupil,8),
    pupil_lead7 = lead(pupil,7),
    pupil_lead6 = lead(pupil,6),
    pupil_lead5 = lead(pupil,5),
         pupil_lead4 = lead(pupil,4),
         pupil_lead3 = lead(pupil,3),
         pupil_lead2 = lead(pupil,2),
         pupil_lead1 = lead(pupil,1),
         pupil_lead0 = pupil,
         pupil_lag1 = lag(pupil,1),
         pupil_lag2 = lag(pupil,2),
         pupil_lag3 = lag(pupil,3),
         pupil_lag4 = lag(pupil,4),
         pupil_lag5 = lag(pupil,5),
         pupil_lag6 = lag(pupil,6),
         pupil_lag7 = lag(pupil,7),
         pupil_lag8 = lag(pupil,8),
         pupil_lag9 = lag(pupil,9),
         pupil_lag10 = lag(pupil,10),
         pupil_lag11 = lag(pupil,11),
         pupil_lag12 = lag(pupil,12))

df.1sub <- read_csv("~/Desktop/midaffemo/analyses/timecourses/data/realsubj/MIDaffemo/timecourses_b4_woOutliers_long.csv") %>% 
  filter(subject == "ab240324", voi == "nacc",coreg == "ants") %>% 
  mutate(trial_tr_noiti = ifelse(probe == 1, 9,8),
         trial_tr = trial_tr_noiti + iti/2) %>% 
  # select(trial,trial_tr,tr,run) %>% 
  filter(tr <= trial_tr)

end_run1 <- df.1sub %>%
  subset(trial == 24) %>%
  .[1:5,] %>%
  mutate(tr = tr + 10)

# create the 5 TRs at the tail of run 2
end_run2 <- df.1sub %>%
        filter(run == "run-02")%>%
        subset(trial == 24) %>%
        .[1:5,] %>%
        mutate(tr = tr + 9)

# create the 5 TRs at the tail of run 3
end_run3 <- df.1sub %>%
        filter(run == "run-03")%>%
        subset(trial == 24) %>%
        .[1:5,] %>%
        mutate(tr = tr + 10)

# create the 5 TRs at the tail of run 4
end_run4 <- df.1sub %>%
        filter(run == "run-04")%>%
        subset(trial == 24) %>%
        .[1:5,] %>%
        mutate(tr = tr + 11)

df.1sub <- df.1sub %>%
        # insert 5 rows at the end of each run
        add_row(end_run1, .after = 240) %>%
        add_row(end_run2, .after = 485) %>%
        add_row(end_run3, .after = 730) %>%
        add_row(end_run4, .after = 975)
      
df.1sub <- df.1sub %>% 
  mutate(block = as.numeric(substr(run,6,6))) %>% 
  mutate(trial = trial + (block - 1) * 24) %>% 
  mutate(tr = row_number())

my_array_s1 <- left_join(my_array_s1,df.1sub %>% 
                         select(trial:erating_t,time,tr,trial_tr)) %>% 
  group_by(subject,trial,threshold) %>% 
  mutate(tr_in_trial = row_number())%>% 
  relocate(tr_in_trial,.after = tr)
```

### self-reported arousal template (circular; just for visualisation)
```{r}
my_array_s1__ <- my_array_s1%>% 
  ungroup() %>% 
  select(trial,subject,tr_in_trial,glmArousal,trial_tr,threshold) %>% 
  pivot_wider(names_from = c(tr_in_trial), values_from = c(glmArousal), names_prefix = "glmArousal_TR_") %>% 
  arrange(subject,trial)

TR_DELAY = 14

for (t in thresh){
  for (sub in unique(my_array_s1__$subject)){
    for(tr in 9:11){
      replace_idx = my_array_s1__$subject == sub & my_array_s1__$trial_tr == tr & my_array_s1__$threshold == t & is.na(my_array_s1__[,paste0("glmArousal_TR_",tr+1)])
      #early TRs were TRs from the previous trial
      my_array_s1__[replace_idx,paste0("glmArousal_TR_",(tr+1):TR_DELAY)] <- my_array_s1__[lag(replace_idx) %>% replace_na(FALSE),paste0("glmArousal_TR_",1:(TR_DELAY-tr))]
  } # tr loop
  }
}


my_array_s1__ <- my_array_s1__ %>% mutate(glmArousal_TR_17 = NA, glmArousal_TR_18 = NA, glmArousal_TR_19 = NA, glmArousal_TR_20 = NA)

my_array_s1__<-left_join(my_array_s1__ %>% 
                        pivot_longer(glmArousal_TR_1:glmArousal_TR_20,
                                     names_to = "tr_in_trial",names_prefix = "glmArousal_TR_",
                                     values_to = "glmArousal"),fmri3_data_2probes,
                      by = c("subject","trial")) %>% 
  filter(tr <= 975)%>%
  mutate(half = ifelse(trial >= 48,"second","first"))%>% #last bit was interpolated
  mutate(probe = ifelse(probe == 1, "anticipation probe","outcome probe"))

my_array_s1__ <- my_array_s1__ %>% 
  mutate(tr_in_trial = as.numeric(tr_in_trial),
         time = (tr_in_trial-1) * 2)
```

#### predicting performance
```{r warning=F}
df_performance <- NULL
for (t in thresh){
  for (tr in 1:14){
    l1<-summary(glm(hit_num ~ scale(glmArousal),family = binomial,
                    my_array_s1__ %>% 
                      filter(tr_in_trial == tr,threshold == t, probe == "anticipation probe") %>% 
                      mutate(hit_num = as.factor(hit == 1))))
    
    l2<-summary(glm(hit_num ~ scale(glmArousal),family = binomial,
                    my_array_s1__ %>% 
                      filter(tr_in_trial == tr,threshold == t, probe == "outcome probe") %>% 
                      mutate(hit_num = as.factor(hit == 1))))
  
    df_performance <- rbind(df_performance,
                          l1$coefficients[2,],
                          l2$coefficients[2,])
  }
  
}

df_performance <- as.data.frame(df_performance)
df_performance$probe <- rep(c("anticipation","outcome"), length(thresh))
df_performance$threshold <- rep(thresh, each = 2*14)
df_performance$tr <- rep(rep(1:14,each=2),2)

ggplot(df_performance, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  facet_wrap(~threshold)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

ggplot(df_performance, aes(x = threshold, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  facet_wrap(~tr)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)
```

```{r warning=F}
df_performance <- NULL

for (t in thresh){
  for (tr in 1:14){
    l1<-summary(lm(scale(rt) ~ scale(glmArousal),
                   my_array_s1__ %>% 
                   filter(tr_in_trial == tr, hit == "Hit",threshold == t, probe == "anticipation probe")))
    
    l2<-summary(lm(scale(rt) ~ scale(glmArousal),
                   my_array_s1__ %>% 
                   filter(tr_in_trial == tr, hit == "Hit",threshold == t, probe == "outcome probe")))
  
    df_performance <- rbind(df_performance,
                          l1$coefficients[2,],
                          l2$coefficients[2,])
  }
  
}

df_performance <- as.data.frame(df_performance)
df_performance$probe <- rep(c("anticipation","outcome"), length(thresh))
df_performance$threshold <- rep(thresh, each = 2*14)
df_performance$tr <- rep(rep(1:14,each=2),2)

ggplot(df_performance, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  facet_wrap(~threshold)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

summary(lm(scale(rt) ~ scale(glmArousal),
                   my_array_s1__ %>% 
                   filter(tr_in_trial == 5, hit == "Hit",threshold == 0.5)))
```


#### predicting cue value (abs)
```{r warning=F}
df_cue <- NULL
for (t in thresh){
  for (tr in 1:14){
    l1<-summary(lm(cue_value_abs ~ scale(glmArousal),
                    my_array_s1__ %>% 
                      filter(tr_in_trial == tr,threshold == t, probe == "anticipation probe") %>% 
                      mutate(cue_value_abs = ifelse(cue_value %in% c("+$5","-$5"),5,
                                                    ifelse(cue_value %in% c("+$1","-$1"),1,
                                                           ifelse(cue_value %in% 
                                                                    c("+$0","-$0"),1,NA))))))
    
    l2<-summary(lm(cue_value_abs ~ scale(glmArousal),
                    my_array_s1__ %>% 
                      filter(tr_in_trial == tr,threshold == t, probe == "outcome probe") %>% 
                      mutate(cue_value_abs = ifelse(cue_value %in% c("+$5","-$5"),5,
                                                    ifelse(cue_value %in% c("+$1","-$1"),1,
                                                           ifelse(cue_value %in% 
                                                                    c("+$0","-$0"),1,NA))))))
  
    df_cue <- rbind(df_cue,
                          l1$coefficients[2,],
                          l2$coefficients[2,])
  }
  
}

df_cue <- as.data.frame(df_cue)
df_cue$probe <- rep(c("anticipation","outcome"), length(thresh))
df_cue$threshold <- rep(thresh, each = 2*14)
df_cue$tr <- rep(rep(1:14,each=2),2)

ggplot(df_cue, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  facet_wrap(~threshold)+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

```

#### predicting self-reports
```{r}
df_rating <- NULL
for (t in thresh){
  for (tr in 1:14){
    l1<-summary(lm(scale(arousal) ~ scale(glmArousal),
                    my_array_s1__ %>% 
                      filter(tr_in_trial == tr,threshold == t, probe == "anticipation probe")))
    l2<-summary(lm(scale(arousal) ~ scale(glmArousal),
                   my_array_s1__ %>% 
                   filter(tr_in_trial == tr, threshold == t, probe == "outcome probe")))
  
    df_rating <- rbind(df_rating,
                          l1$coefficients[2,],
                          l2$coefficients[2,])
  }
  
}

df_rating <- as.data.frame(df_rating)
df_rating$probe <- rep(c("anticipation","outcome"), length(thresh))
df_rating$threshold <- rep(thresh, each = 2*14)
df_rating$tr <- rep(rep(1:14,each=2),2)

ggplot(df_rating, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  geom_ribbon(aes(x = tr, ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`,fill = probe),
              alpha = 0.1)+
  facet_wrap(~threshold)+
  labs(title = "FMRI study")+
  scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  scale_x_continuous(breaks = 1:14)+
  geom_vline(xintercept = 5, color = "purple",label = "F")+
  geom_vline(xintercept = 6, color = "skyblue",label = "T")+
  geom_vline(xintercept = 7, color = "purple", linetype = "dashed")+
  geom_vline(xintercept = 9, color = "skyblue", linetype = "dashed")
```

#### visualize peak correlation
```{r}
coefs1 = NULL
for (t in 1:14){
  l1<-summary(lm(scale(glmArousal) ~ scale(arousal),my_array_s1__ %>% filter(tr_in_trial == t, probe == "anticipation probe", threshold == 0)))
  coefs1 <- rbind(coefs1,l1$coefficients[2,])
}
coefs1<-as.data.frame(coefs1)
coefs1$TR <- 1:14
coefs1$probe = "anticipation probe"

coefs2 = NULL
for (t in 1:14){
  l1<-summary(lm(scale(glmArousal) ~ scale(arousal),my_array_s1__ %>% filter(tr_in_trial == t, probe == "outcome probe", threshold == 0)))
  coefs2 <- rbind(coefs2,l1$coefficients[2,])
}
coefs2<-as.data.frame(coefs2)
coefs2$TR <- 1:14
coefs2$probe = "outcome probe"

coefs <- rbind(coefs1,coefs2) %>% 
  mutate(sig = ifelse(`Pr(>|t|)` >= 0.05, "",
                      ifelse(`Pr(>|t|)` >= 0.01, "*",
                             ifelse(`Pr(>|t|)` >= 0.001, "**","***"))))

p4a<-ggplot(coefs %>% filter(probe == "anticipation probe"),aes(x = TR, y =Estimate))+
  geom_hline(yintercept = 0, linetype = "dashed")+
  geom_vline(xintercept = c(3.5,4.5,5.5,9.5,10.5,11.5,12.5), size = 1, color = "grey")+
  annotate("text",x = 4, y = 0.05, label = "C")+
  annotate("text",x = 5, y = 0.05, label = "F")+
  annotate("text",x = 10, y = 0.05, label = "F")+
  annotate("text",x = 11, y = 0.05, label = "T")+
  annotate("text",x = 12, y = 0.05, label = "O")+
  annotate("text",x = 7.5, y = 0.05, label = "R")+
  scale_x_continuous(breaks = seq(0,14,2), labels = seq(0,28,4))+
  scale_color_manual(values = c("purple"))+
  scale_fill_manual(values = c("purple"))+
  geom_line(aes(color = probe), size = 2, alpha = 0.5)+
  geom_ribbon(aes(fill = probe, ymin = Estimate - `Std. Error`,
                  ymax = Estimate + `Std. Error`), alpha = 0.1)+
  geom_line(aes(color = probe), size = 2, alpha = 0.5)+
  geom_segment(aes(x = 7, y = 0.15,
                   xend =7, yend = 0.1),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  annotate("text",x = 7, y = 0.16, label ="arousal rating")+
  geom_text(aes(x = TR, y = Estimate+0.01, label = sig, color = probe))+
  labs(x = "time (s)",
       y = "Correlation with arousal ratings",
       title = "Regression weights on arousal",
       subtitle = "anticipation probe")+
  theme(legend.position = "none")

p4b<-ggplot(coefs%>% filter(probe == "outcome probe"),aes(x = TR, y =Estimate))+
  geom_hline(yintercept = 0, linetype = "dashed")+
  geom_vline(xintercept = c(3.5,4.5,5.5,6.5,7.5), size = 1, color = "grey")+
  annotate("text",x = 4, y = 0.05, label = "C")+
  annotate("text",x = 5, y = 0.05, label = "F")+
  annotate("text",x = 6, y = 0.05, label = "T")+
  annotate("text",x = 7, y = 0.05, label = "O")+
  annotate("text",x = 10, y = 0.05, label = "R")+
  scale_x_continuous(breaks = seq(0,14,2), labels = seq(0,28,4))+
  scale_color_manual(values = c("skyblue"))+
  scale_fill_manual(values = c("skyblue"))+
  geom_line(aes(color = probe), size = 2, alpha = 0.5)+
  geom_ribbon(aes(fill = probe, ymin = Estimate - `Std. Error`,
                  ymax = Estimate + `Std. Error`), alpha = 0.1)+
  geom_line(aes(color = probe), size = 2, alpha = 0.5)+
  geom_segment(aes(x = 10, y = 0.17,
                   xend =10, yend = 0.12),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  annotate("text",x = 10, y = 0.18, label ="arousal rating")+
  geom_segment(aes(x = 10, y = 0.17,
                   xend =10, yend = 0.12),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  annotate("text",x = 10, y = 0.18, label ="arousal rating")+
  geom_text(aes(x = TR, y = Estimate+0.01, label = sig, color = probe))+
  labs(x = "time (s)",
       subtitle = "outcome probe")+
  theme(legend.position = "none")

p4a+p4b
```


### pupil glm template
```{r}
my_array_s1_ <- my_array_s1%>% 
  ungroup() %>% 
  select(trial,subject,tr_in_trial,glmPupil,trial_tr,threshold) %>% 
  pivot_wider(names_from = c(tr_in_trial), values_from = c(glmPupil), names_prefix = "glmPupil_TR_") %>% 
  arrange(subject,trial)

for (t in thresh){
  for (sub in unique(my_array_s1_$subject)){
    for(tr in 9:11){
      replace_idx = my_array_s1_$subject == sub & my_array_s1_$trial_tr == tr & my_array_s1_$threshold == t & is.na(my_array_s1_[,paste0("glmPupil_TR_",tr+1)])
      #early TRs were TRs from the previous trial
      my_array_s1_[replace_idx,paste0("glmPupil_TR_",(tr+1):TR_DELAY)] <- my_array_s1_[lag(replace_idx) %>% replace_na(FALSE),paste0("glmPupil_TR_",1:(TR_DELAY-tr))]
  } # tr loop
  }
}

TR_DELAY = 14
my_array_s1_ <- my_array_s1_ %>% mutate(glmPupil_TR_17 = NA, glmPupil_TR_18 = NA, glmPupil_TR_19 = NA, glmPupil_TR_20 = NA)

my_array_s1_<-left_join(my_array_s1_ %>% 
                        pivot_longer(glmPupil_TR_1:glmPupil_TR_20,
                                     names_to = "tr_in_trial",names_prefix = "glmPupil_TR_",
                                     values_to = "glmPupil"),fmri3_data_2probes,
                      by = c("subject","trial")) %>% 
  filter(tr <= 975)%>%
  mutate(half = ifelse(trial >= 48,"second","first"))%>% #last bit was interpolated
  mutate(probe = ifelse(probe == 1, "anticipation probe","outcome probe"))

my_array_s1_ <- my_array_s1_ %>% 
  mutate(tr_in_trial = as.numeric(tr_in_trial),
         time = (tr_in_trial-1) * 2)
```

#### diffentiating cue vs. outcome
```{r}
d1<-my_array_s1_ %>% 
         filter(!is.na(hit)) %>% 
         group_by(tr_in_trial,subject,threshold,probe) %>% 
         summarise(glmPupil = mean(glmPupil,na.rm = T)) %>% 
         group_by(tr_in_trial,threshold,probe) %>% 
         summarise(mean = mean(glmPupil,na.rm = T),
                   se = sd(glmPupil,na.rm = T)/sqrt(n())) %>% 
  filter(tr_in_trial <= 14)

p1<-ggplot(d1 %>% filter(probe == "anticipation probe",threshold == 0.5),
       aes(x = tr_in_trial, y = mean))+
  geom_vline(xintercept = c(3.5,4.5,5.5,9.5,10.5,11.5,12.5), size = 1, color = "grey")+
  annotate("text",x = 4, y = 0.05, label = "C")+
  annotate("text",x = 5, y = 0.05, label = "F")+
  annotate("text",x = 10, y = 0.05, label = "F")+
  annotate("text",x = 11, y = 0.05, label = "T")+
  annotate("text",x = 12, y = 0.05, label = "O")+
  annotate("text",x = 7.5, y = 0.05, label = "R")+
  geom_line(size = 0.5) +
  geom_point()+
  geom_errorbar(aes(x = tr_in_trial, ymin = mean-se,ymax = mean+se), width = 0.3)+
    scale_x_continuous(breaks = seq(0,14,2), labels = seq(0,28,4))+
  labs(y = "Simalirty to pupil template",
       x = "time (s)",
       subtitle = "anticipation probe")+
  scale_color_manual(values = redOrange_palette6)+
  theme(legend.position = "top")+
  ylim(-0.1,0.15)+
ggplot(d1 %>% filter(probe == "outcome probe",threshold == 0.5),
       aes(x = tr_in_trial, y = mean))+
  geom_vline(xintercept = c(3.5,4.5,5.5,6.5,7.5,11.5), size = 1, color = "grey")+
    scale_x_continuous(breaks = seq(0,14,2), labels = seq(0,28,4))+
  annotate("text",x = 4, y = 0.05, label = "C")+
  annotate("text",x = 5, y = 0.05, label = "F")+
  annotate("text",x = 6, y = 0.05, label = "T")+
  annotate("text",x = 7, y = 0.05, label = "O")+
  annotate("text",x = 10, y = 0.05, label = "R")+
  geom_line(size = 0.5) +
  geom_point()+
  geom_errorbar(aes(x = tr_in_trial, ymin = mean-se,ymax = mean+se), width = 0.3)+
  labs(y = "Simalirty to self-report template",
       x = "time (s)",
       subtitle = "outcome probe",
      caption = "C = Cue, F = Fixation, \nT = Target, O = Outcome, R = Rating")+
  scale_color_manual(values = redOrange_palette6)+
  theme(legend.position = "top")+
  ylim(-0.1,0.15)

d2<-my_array_s1_ %>% 
         filter(!is.na(hit),
                tr_in_trial == 5) %>% 
         group_by(subject,threshold,cue_value) %>% 
         summarise(glmPupil = mean(glmPupil,na.rm = T)) %>% 
         group_by(threshold,cue_value) %>% 
         summarise(mean = mean(glmPupil,na.rm = T),
                   se = sd(glmPupil,na.rm = T)/sqrt(n()))%>% 
  mutate(cue_value = factor(cue_value, levels = c("-$5","-$1","-$0","+$0","+$1","+$5")))

p2<-ggplot(d2 %>% filter(threshold == 0.5),
       aes(x = cue_value, y = mean,color = cue_value))+
  geom_point(size = 0.5) +
  geom_point()+
  geom_errorbar(aes(x = cue_value, ymin = mean-se,ymax = mean+se), width = 0.3)+
  labs(y = "Simalirty to self-report template",
       x = "time (s)",
       subtitle = "Inferred arousal (8s)")+
  scale_color_manual(values = redOrange_palette6)+
  theme(legend.position = "none")+  # show shape legend
  scale_x_discrete(breaks =c("-$5","-$1","-$0","+$0","+$1","+$5"))

d3<-my_array_s1_ %>% 
         filter(!is.na(hit),
                ifelse(probe == "anticipation probe", tr_in_trial == 12,
                       ifelse(probe == "outcome probe",tr_in_trial == 7,NA))) %>% 
         group_by(subject,threshold,hit,cue_value) %>% 
         summarise(glmPupil = mean(glmPupil,na.rm = T)) %>% 
         group_by(threshold,hit,cue_value) %>% 
         summarise(mean = mean(glmPupil,na.rm = T),
                   se = sd(glmPupil,na.rm = T)/sqrt(n()))

ggplot(d3 %>% filter(threshold == 0.5),
       aes(x = cue_value, y = mean, color = cue_value, shape = hit)) +
  geom_point(position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(x = cue_value, group = hit, ymin = mean - se, ymax = mean + se),
                width = 0.3, position = position_dodge(width = 0.5)) +
  labs(y = "Similarity to self-report template",
       x = "time (s)",
       subtitle = "arousal index during outcome") +
  theme(legend.position = "top") +
  scale_color_manual(values = redOrange_palette6) +
  guides(color = "none",  # hide color legend
         shape = guide_legend())  # show shape legend

```

#### predicting performance
```{r warning=F}
df_performance <- NULL
for (t in thresh){
  for (tr in 1:14){
    l1<-summary(glm(hit_num ~ scale(glmPupil),family = binomial,
                    my_array_s1_ %>% 
                      filter(tr_in_trial == tr,threshold == t, probe == "anticipation probe") %>% 
                      mutate(hit_num = as.factor(hit == 1))))
    
    l2<-summary(glm(hit_num ~ scale(glmPupil),family = binomial,
                    my_array_s1_ %>% 
                      filter(tr_in_trial == tr,threshold == t, probe == "outcome probe") %>% 
                      mutate(hit_num = as.factor(hit == 1))))
  
    df_performance <- rbind(df_performance,
                          l1$coefficients[2,],
                          l2$coefficients[2,])
  }
  
}

df_performance <- as.data.frame(df_performance)
df_performance$probe <- rep(c("anticipation","outcome"), length(thresh))
df_performance$threshold <- rep(thresh, each = 2*14)
df_performance$tr <- rep(rep(1:14,each=2),2)

ggplot(df_performance, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  facet_wrap(~threshold)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

ggplot(df_performance %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)+
  geom_vline(xintercept = 0.5)

summary(l1<-glm(hit_num ~ scale(glmPupil),family = binomial,
                    my_array_s1_ %>% 
                      filter(tr_in_trial == 5,threshold == 0.5) %>% 
                      mutate(hit_num = as.factor(hit == "Hit"))))

# Get effect size (standardized beta)
beta <- summary(l1)$coefficients["scale(glmPupil)", "Estimate"]
r2   <- pscl::pR2(l1)["McFadden"]

# Create base plot
p3m1p <- plot_model(l1, type = "pred", terms = "glmPupil",color = "darkgrey") +
  labs(x = "similarity (z-score)",
       y = "p(hit)",title = "p(hit)") +
  annotate("text",x = Inf, y = -Inf, label = paste0("β = ", round(beta, 2), "\npseudo-R² = ", round(r2, 2)),
    hjust = 1.1, vjust = -0.5, size = 4)
```

```{r warning=F}
df_performance <- NULL

for (t in thresh){
  for (tr in 1:14){
    l1<-summary(lm(scale(rt) ~ scale(glmPupil),
                   my_array_s1_ %>% 
                   filter(tr_in_trial == tr, hit == "Hit",threshold == t, probe == "anticipation probe")))
    
    l2<-summary(lm(scale(rt) ~ scale(glmPupil),
                   my_array_s1_ %>% 
                   filter(tr_in_trial == tr, hit == "Hit",threshold == t, probe == "outcome probe")))
  
    df_performance <- rbind(df_performance,
                          l1$coefficients[2,],
                          l2$coefficients[2,])
  }
  
}

df_performance <- as.data.frame(df_performance)
df_performance$probe <- rep(c("anticipation","outcome"), length(thresh))
df_performance$threshold <- rep(thresh, each = 2*14)
df_performance$tr <- rep(rep(1:14,each=2),2)

ggplot(df_performance, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  facet_wrap(~threshold)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

ggplot(df_performance %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

summary(l1<-lm(scale(rt) ~ scale(glmPupil),
                   my_array_s1_ %>% 
                   filter(tr_in_trial == 5, hit == "Hit",threshold == 0.5)))

# Get effect size (standardized beta)
beta <- summary(l1)$coefficients["scale(glmPupil)", "Estimate"]
r2   <- summary(l1)$r.squared

# Create base plot
p4m1p <- plot_model(l1, type = "pred", terms = "glmPupil",color = "darkgrey") +
  labs(x = "similarity (z-score)",
    y = "rt (z-score)",
    title = "rt (hit trials)"
  ) +
  annotate("text",x = Inf, y = -Inf, label = paste0("β = ", round(beta, 2), "\nR² = ", round(r2, 2)),
    hjust = 1.1, vjust = -1.5, size = 4)
```


#### predicting cue value (abs)
```{r warning=F}
df_cue <- NULL
for (t in thresh){
  for (tr in 1:14){
    l1<-summary(lm(cue_value_abs ~ scale(glmPupil),
                    my_array_s1_ %>% 
                      filter(tr_in_trial == tr,threshold == t, probe == "anticipation probe") %>% 
                      mutate(cue_value_abs = ifelse(cue_value %in% c("+$5","-$5"),5,
                                                    ifelse(cue_value %in% c("+$1","-$1"),1,
                                                           ifelse(cue_value %in% 
                                                                    c("+$0","-$0"),1,NA))))))
    
    l2<-summary(lm(cue_value_abs ~ scale(glmPupil),
                    my_array_s1_ %>% 
                      filter(tr_in_trial == tr,threshold == t, probe == "outcome probe") %>% 
                      mutate(cue_value_abs = ifelse(cue_value %in% c("+$5","-$5"),5,
                                                    ifelse(cue_value %in% c("+$1","-$1"),1,
                                                           ifelse(cue_value %in% 
                                                                    c("+$0","-$0"),1,NA))))))
  
    df_cue <- rbind(df_cue,
                          l1$coefficients[2,],
                          l2$coefficients[2,])
  }
  
}

df_cue <- as.data.frame(df_cue)
df_cue$probe <- rep(c("anticipation","outcome"), length(thresh))
df_cue$threshold <- rep(thresh, each = 2*14)
df_cue$tr <- rep(rep(1:14,each=2),2)

ggplot(df_cue, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  facet_wrap(~threshold)+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

ggplot(df_cue %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

```
### predicting self-reports
```{r}
df_rating <- NULL
for (t in thresh){
  for (tr in 1:14){
    l1<-summary(lm(scale(arousal) ~ scale(glmPupil),
                    my_array_s1_ %>% 
                      filter(tr_in_trial == tr,threshold == t, probe == "anticipation probe")))
    l2<-summary(lm(scale(arousal) ~ scale(glmPupil),
                   my_array_s1_ %>% 
                   filter(tr_in_trial == tr, threshold == t, probe == "outcome probe")))
  
    df_rating <- rbind(df_rating,
                          l1$coefficients[2,],
                          l2$coefficients[2,])
  }
  
}

df_rating <- as.data.frame(df_rating)
df_rating$probe <- rep(c("anticipation","outcome"), length(thresh))
df_rating$threshold <- rep(thresh, each = 2*14)
df_rating$tr <- rep(rep(1:14,each=2),2)

ggplot(df_rating, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  geom_ribbon(aes(x = tr, ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`,fill = probe),
              alpha = 0.1)+
  facet_wrap(~threshold)+
  labs(title = "FMRI study")+
  scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  scale_x_continuous(breaks = 1:14)+
  geom_vline(xintercept = 5, color = "purple",label = "F")+
  geom_vline(xintercept = 6, color = "skyblue",label = "T")+
  geom_vline(xintercept = 7, color = "purple", linetype = "dashed")+
  geom_vline(xintercept = 9, color = "skyblue", linetype = "dashed")


ggplot(df_rating %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)
```

### visualize peak correlation
```{r}
coefs1 = NULL
for (t in 1:14){
  l1<-summary(lm(scale(glmPupil) ~ scale(arousal),my_array_s1_ %>% filter(tr_in_trial == t, probe == "anticipation probe", threshold == 0.5)))
  coefs1 <- rbind(coefs1,l1$coefficients[2,])
}
coefs1<-as.data.frame(coefs1)
coefs1$TR <- 1:14
coefs1$probe = "anticipation probe"

coefs2 = NULL
for (t in 1:14){
  l1<-summary(lm(scale(glmPupil) ~ scale(arousal),my_array_s1_ %>% filter(tr_in_trial == t, probe == "outcome probe", threshold == 0.5)))
  coefs2 <- rbind(coefs2,l1$coefficients[2,])
}
coefs2<-as.data.frame(coefs2)
coefs2$TR <- 1:14
coefs2$probe = "outcome probe"

coefs <- rbind(coefs1,coefs2) %>% 
  mutate(sig = ifelse(`Pr(>|t|)` >= 0.05, "",
                      ifelse(`Pr(>|t|)` >= 0.01, "*",
                             ifelse(`Pr(>|t|)` >= 0.001, "**","***"))))

p_m1_pupil_a<-ggplot(coefs %>% filter(probe == "anticipation probe"),aes(x = TR, y =Estimate))+
  geom_hline(yintercept = 0, linetype = "dashed")+
  geom_vline(xintercept = c(3.5,4.5,5.5,9.5,10.5,11.5,12.5), size = 1, color = "grey")+
  annotate("text",x = 4, y = 0.05, label = "C")+
  annotate("text",x = 5, y = 0.05, label = "F")+
  annotate("text",x = 10, y = 0.05, label = "F")+
  annotate("text",x = 11, y = 0.05, label = "T")+
  annotate("text",x = 12, y = 0.05, label = "O")+
  annotate("text",x = 7.5, y = 0.05, label = "R")+
  scale_x_continuous(breaks = seq(0,14,2), labels = seq(0,28,4))+
  scale_color_manual(values = c("purple"))+
  scale_fill_manual(values = c("purple"))+
  geom_line(aes(color = probe), size = 2, alpha = 0.5)+
  geom_ribbon(aes(fill = probe, ymin = Estimate - `Std. Error`,
                  ymax = Estimate + `Std. Error`), alpha = 0.1)+
  geom_line(aes(color = probe), size = 2, alpha = 0.5)+
  geom_segment(aes(x = 7, y = 0.15,
                   xend =7, yend = 0.1),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  annotate("text",x = 7, y = 0.16, label ="arousal rating")+
  geom_text(aes(x = TR, y = Estimate+0.01, label = sig, color = probe))+
  labs(x = "time (s)",
       y = "std. beta",
       title = "Regression weights on arousal",
       subtitle = "anticipation probe")+
  theme(legend.position = "none")

p_m1_pupil_b<-ggplot(coefs%>% filter(probe == "outcome probe"),aes(x = TR, y =Estimate))+
  geom_hline(yintercept = 0, linetype = "dashed")+
  geom_vline(xintercept = c(3.5,4.5,5.5,6.5,7.5), size = 1, color = "grey")+
  annotate("text",x = 4, y = 0.05, label = "C")+
  annotate("text",x = 5, y = 0.05, label = "F")+
  annotate("text",x = 6, y = 0.05, label = "T")+
  annotate("text",x = 7, y = 0.05, label = "O")+
  annotate("text",x = 10, y = 0.05, label = "R")+
  scale_x_continuous(breaks = seq(0,14,2), labels = seq(0,28,4))+
  scale_color_manual(values = c("skyblue"))+
  scale_fill_manual(values = c("skyblue"))+
  geom_line(aes(color = probe), size = 2, alpha = 0.5)+
  geom_ribbon(aes(fill = probe, ymin = Estimate - `Std. Error`,
                  ymax = Estimate + `Std. Error`), alpha = 0.1)+
  geom_line(aes(color = probe), size = 2, alpha = 0.5)+
  geom_segment(aes(x = 10, y = 0.17,
                   xend =10, yend = 0.12),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  annotate("text",x = 10, y = 0.18, label ="arousal rating")+
  geom_segment(aes(x = 10, y = 0.17,
                   xend =10, yend = 0.12),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  annotate("text",x = 10, y = 0.18, label ="arousal rating")+
  geom_text(aes(x = TR, y = Estimate+0.01, label = sig, color = probe))+
  labs(x = "time (s)",
        y = "std. beta",
       subtitle = "outcome probe")+
  theme(legend.position = "none")

p_m1_pupil_a+p_m1_pupil_b


# Prepare data
d1 <- my_array_s1_ %>% filter(tr_in_trial == 5, threshold == 0.5)
d2 <- my_array_s1_ %>% filter(tr_in_trial == 5, probe == "anticipation probe", threshold == 0.5)
d3 <- my_array_s1_ %>% filter(tr_in_trial == 7, probe == "outcome probe", threshold == 0.5)

# Fit models
l1 <- lm(scale(arousal_scaled) ~ scale(glmPupil), d1)
l2 <- lm(scale(arousal_scaled) ~ scale(glmPupil), d2)
l3 <- lm(scale(arousal_scaled) ~ scale(glmPupil), d3)
# Extract coefficients and p-values
get_stats <- function(model) {
  b <- coef(summary(model))["scale(glmPupil)", "Estimate"]
  p <- coef(summary(model))["scale(glmPupil)", "Pr(>|t|)"]
  list(beta = round(b, 3), p = signif(p, 3))
}

s1 <- get_stats(l1)
s2 <- get_stats(l2)
s3 <- get_stats(l3)

# Create prediction data with CI ribbons
make_pred_df <- function(data, model) {
  new <- data.frame(glmPupil = seq(min(data$glmPupil, na.rm = TRUE),
                                     max(data$glmPupil, na.rm = TRUE),
                                     length.out = 100))
  preds <- predict(model, newdata = new, interval = "confidence")
  new$fit <- preds[, "fit"]
  new$lwr <- preds[, "lwr"]
  new$upr <- preds[, "upr"]
  new
}

new1 <- make_pred_df(d1, l1)
new2 <- make_pred_df(d2, l2)
new3 <- make_pred_df(d3, l3)

# Plot
p_m1_pupil_c <- ggplot() +
  ## Model 1 -- black
  geom_ribbon(data = new1,
              aes(x = scale(glmPupil), ymin = lwr, ymax = upr),
              fill = "black", alpha = 0.15) +
  geom_line(data = new1,
            aes(x = scale(glmPupil), y = fit),
            color = "black", size = 1) +

  ## Model 2 -- purple
  geom_ribbon(data = new2,
              aes(x = scale(glmPupil), ymin = lwr, ymax = upr),
              fill = "purple", alpha = 0.15) +
  geom_line(data = new2,
            aes(x = scale(glmPupil), y = fit),
            color = "purple", size = 1) +

  ## Model 3 -- skyblue
  geom_ribbon(data = new3,
              aes(x = scale(glmPupil), ymin = lwr, ymax = upr),
              fill = "skyblue", alpha = 0.15) +
  geom_line(data = new3,
            aes(x = scale(glmPupil), y = fit),
            color = "skyblue", size = 1) +

  # Add beta + p-value text with < .001 formatting
  annotate("text", x = -1.5, y = max(new1$upr)+0.6, size=4,
           label = paste0("both (8s): β=", round(s1$beta,2), 
                          ", p", ifelse(s1$p < 0.001, "< .001", paste0("= ",round(s1$p, 3)))),
           color = "black", hjust = 0) +
  annotate("text", x = -1.5, y = max(new1$upr)+0.2, size=4,
           label = paste0("ant (8s): β=", round(s2$beta,2), 
                          ", p", ifelse(s2$p < 0.001, "< .001",paste0("= ",round(s2$p, 3)))),
           color = "purple", hjust = 0) +
  annotate("text", x = -1.5, y = max(new1$upr)+0.4, size=4,
           label = paste0("out (12s): β=", round(s3$beta,2), 
                          ", p", ifelse(s3$p < 0.001, "< .001", paste0("= ",round(s3$p, 3)))),
           color = "skyblue", hjust = 0)+

  labs(
    x = "similarity (scaled)",
    y = "Predicted arousal (scaled)",
    title = "Pupil template",
    subtitle = "FMRI Study"
  )
```

```{r}
(p1+p2+plot_layout(nrow = 1,widths = c(2,2,1)))/
(p_m1_pupil_a+p_m1_pupil_b)

(p1+p2+plot_layout(widths = c(2,2,1.5)))/
(p3m1p+p4m1p+p_m1_pupil_c+plot_layout(widths = c(1,1,2)))+
plot_annotation(title = "Pupil template",
                  tag_levels = "A")


ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig_glmPupil_s1.png"),dpi = 300, height = 6, width = 10)
```


### pupil glm template (positive values only)
```{r}
my_array_s1_ <- my_array_s1%>% 
  ungroup() %>% 
  select(trial,subject,tr_in_trial,glmPupil_posonly,trial_tr,threshold) %>% 
  pivot_wider(names_from = c(tr_in_trial), values_from = c(glmPupil_posonly), names_prefix = "glmPupil_TR_") %>% 
  arrange(subject,trial)

for (t in thresh){
  for (sub in unique(my_array_s1_$subject)){
    for(tr in 9:11){
      replace_idx = my_array_s1_$subject == sub & my_array_s1_$trial_tr == tr & my_array_s1_$threshold == t & is.na(my_array_s1_[,paste0("glmPupil_TR_",tr+1)])
      #early TRs were TRs from the previous trial
      my_array_s1_[replace_idx,paste0("glmPupil_TR_",(tr+1):TR_DELAY)] <- my_array_s1_[lag(replace_idx) %>% replace_na(FALSE),paste0("glmPupil_TR_",1:(TR_DELAY-tr))]
  } # tr loop
  }
}

TR_DELAY = 14
my_array_s1_ <- my_array_s1_ %>% mutate(glmPupil_TR_17 = NA, glmPupil_TR_18 = NA, glmPupil_TR_19 = NA, glmPupil_TR_20 = NA)

my_array_s1_<-left_join(my_array_s1_ %>% 
                        pivot_longer(glmPupil_TR_1:glmPupil_TR_20,
                                     names_to = "tr_in_trial",names_prefix = "glmPupil_TR_",
                                     values_to = "glmPupil"),fmri3_data_2probes,
                      by = c("subject","trial")) %>% 
  filter(tr <= 975)%>%
  mutate(half = ifelse(trial >= 48,"second","first"))%>% #last bit was interpolated
  mutate(probe = ifelse(probe == 1, "anticipation probe","outcome probe"))

my_array_s1_ <- my_array_s1_ %>% 
  mutate(tr_in_trial = as.numeric(tr_in_trial),
         time = (tr_in_trial-1) * 2)
```


### predicting self-reports
```{r}
df_rating <- NULL
for (t in thresh){
  for (tr in 1:14){
    l1<-summary(lm(scale(arousal) ~ scale(glmPupil),
                    my_array_s1_ %>% 
                      filter(tr_in_trial == tr,threshold == t, probe == "anticipation probe")))
    l2<-summary(lm(scale(arousal) ~ scale(glmPupil),
                   my_array_s1_ %>% 
                   filter(tr_in_trial == tr, threshold == t, probe == "outcome probe")))
  
    df_rating <- rbind(df_rating,
                          l1$coefficients[2,],
                          l2$coefficients[2,])
  }
  
}

df_rating <- as.data.frame(df_rating)
df_rating$probe <- rep(c("anticipation","outcome"), length(thresh))
df_rating$threshold <- rep(thresh, each = 2*14)
df_rating$tr <- rep(rep(1:14,each=2),2)

ggplot(df_rating, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  geom_ribbon(aes(x = tr, ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`,fill = probe),
              alpha = 0.1)+
  facet_wrap(~threshold)+
  labs(title = "FMRI study")+
  scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  scale_x_continuous(breaks = 1:14)+
  geom_vline(xintercept = 5, color = "purple",label = "F")+
  geom_vline(xintercept = 6, color = "skyblue",label = "T")+
  geom_vline(xintercept = 7, color = "purple", linetype = "dashed")+
  geom_vline(xintercept = 9, color = "skyblue", linetype = "dashed")


ggplot(df_rating %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)
```

### visualize peak correlation
```{r}
coefs1 = NULL
for (t in 1:14){
  l1<-summary(lm(scale(glmPupil) ~ scale(arousal),my_array_s1_ %>% filter(tr_in_trial == t, probe == "anticipation probe", threshold == 3.5)))
  coefs1 <- rbind(coefs1,l1$coefficients[2,])
}
coefs1<-as.data.frame(coefs1)
coefs1$TR <- 1:14
coefs1$probe = "anticipation probe"

coefs2 = NULL
for (t in 1:14){
  l1<-summary(lm(scale(glmPupil) ~ scale(arousal),my_array_s1_ %>% filter(tr_in_trial == t, probe == "outcome probe", threshold == 3.5)))
  coefs2 <- rbind(coefs2,l1$coefficients[2,])
}
coefs2<-as.data.frame(coefs2)
coefs2$TR <- 1:14
coefs2$probe = "outcome probe"

coefs <- rbind(coefs1,coefs2) %>% 
  mutate(sig = ifelse(`Pr(>|t|)` >= 0.05, "",
                      ifelse(`Pr(>|t|)` >= 0.01, "*",
                             ifelse(`Pr(>|t|)` >= 0.001, "**","***"))))

p_m1_pupil_posonly_a<-ggplot(coefs %>% filter(probe == "anticipation probe"),aes(x = TR, y =Estimate))+
  geom_hline(yintercept = 0, linetype = "dashed")+
  geom_vline(xintercept = c(3.5,4.5,5.5,9.5,10.5,11.5,12.5), size = 1, color = "grey")+
  annotate("text",x = 4, y = 0.05, label = "C")+
  annotate("text",x = 5, y = 0.05, label = "F")+
  annotate("text",x = 10, y = 0.05, label = "F")+
  annotate("text",x = 11, y = 0.05, label = "T")+
  annotate("text",x = 12, y = 0.05, label = "O")+
  annotate("text",x = 7.5, y = 0.05, label = "R")+
  scale_x_continuous(breaks = seq(0,14,2), labels = seq(0,28,4))+
  scale_color_manual(values = c("purple"))+
  scale_fill_manual(values = c("purple"))+
  geom_line(aes(color = probe), size = 2, alpha = 0.5)+
  geom_ribbon(aes(fill = probe, ymin = Estimate - `Std. Error`,
                  ymax = Estimate + `Std. Error`), alpha = 0.1)+
  geom_line(aes(color = probe), size = 2, alpha = 0.5)+
  geom_segment(aes(x = 7, y = 0.15,
                   xend =7, yend = 0.1),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  annotate("text",x = 7, y = 0.16, label ="arousal rating")+
  geom_text(aes(x = TR, y = Estimate+0.01, label = sig, color = probe))+
  labs(x = "time (s)",
       y = "Correlation with arousal ratings",
       title = "Regression weights on arousal",
       subtitle = "anticipation probe")+
  theme(legend.position = "none")

p_m1_pupil_posonly_b<-ggplot(coefs%>% filter(probe == "outcome probe"),aes(x = TR, y =Estimate))+
  geom_hline(yintercept = 0, linetype = "dashed")+
  geom_vline(xintercept = c(3.5,4.5,5.5,6.5,7.5), size = 1, color = "grey")+
  annotate("text",x = 4, y = 0.05, label = "C")+
  annotate("text",x = 5, y = 0.05, label = "F")+
  annotate("text",x = 6, y = 0.05, label = "T")+
  annotate("text",x = 7, y = 0.05, label = "O")+
  annotate("text",x = 10, y = 0.05, label = "R")+
  scale_x_continuous(breaks = seq(0,14,2), labels = seq(0,28,4))+
  scale_color_manual(values = c("skyblue"))+
  scale_fill_manual(values = c("skyblue"))+
  geom_line(aes(color = probe), size = 2, alpha = 0.5)+
  geom_ribbon(aes(fill = probe, ymin = Estimate - `Std. Error`,
                  ymax = Estimate + `Std. Error`), alpha = 0.1)+
  geom_line(aes(color = probe), size = 2, alpha = 0.5)+
  geom_segment(aes(x = 10, y = 0.17,
                   xend =10, yend = 0.12),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  annotate("text",x = 10, y = 0.18, label ="arousal rating")+
  geom_segment(aes(x = 10, y = 0.17,
                   xend =10, yend = 0.12),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  annotate("text",x = 10, y = 0.18, label ="arousal rating")+
  geom_text(aes(x = TR, y = Estimate+0.01, label = sig, color = probe))+
  labs(x = "time (s)",
       subtitle = "outcome probe")+
  theme(legend.position = "none")

p_m1_pupil_posonly_a+p_m1_pupil_posonly_b
```

## split-half validation

### make dataframe of all similarities, all thresholds
#### first half (using h2 template)
```{r}
subjects_list<-read_delim('~/Desktop/midaffemo/analyses/subjects-pupil-fmri.txt',delim = '\t', col_names = F)
thresh_str <- c("0","05","1","15","2","25","3","35")
thresh <- c(0,0.5,1,1.5,2,2.5,3,3.5)
splits = c("run12","run34")
glmArousal_array <- NULL
glmPupil_array <- NULL
pupil_array <- NULL

for (t in 1:length(thresh_str)){
  filepath = paste0("~/Desktop/midaffemo/glm_maps/glm27c_h2_array_threshold",thresh_str[t],".csv")
  glmArousal_array<-rbind(glmArousal_array,
                          as.data.frame(t(read_csv(filepath, 
                                           col_names = F))) %>% 
                            mutate(type = "glmArousal", 
                                   tr = row_number(), 
                                   threshold = thresh[t]) #self-reported arousal GLM
  )
  
  filepath = paste0("~/Desktop/midaffemo/glm_maps/glm33b_h2_array_threshold",thresh_str[t],".csv")
  glmPupil_array<-rbind(glmPupil_array,
                        as.data.frame(t(read_csv(filepath, 
             col_names = F))) %>% 
    mutate(type = "glmPupil", tr = row_number(), 
                                   threshold = thresh[t])) #pupil GLM
  
  pupil_array<-rbind(pupil_array,
                     as.data.frame(t(read_csv("~/Desktop/midaffemo/glm_maps/pupil_array.csv", col_names = F))) %>% slice(1:490) %>% 
    mutate(type = "pupil", tr = row_number(), 
                                   threshold = thresh[t])) #pupil time series
}


my_array_s1_run12<-Reduce(rbind,list(glmArousal_array,glmPupil_array,pupil_array))
names(my_array_s1_run12) <- c(subjects_list$X1,"type","tr","threshold")
my_array_s1_run12<-my_array_s1_run12%>% 
  pivot_longer(ab240324:yz240312,names_to = "subject",values_to = "val") %>% 
  pivot_wider(names_from = type, values_from = val)

df.1sub <- read_csv("~/Desktop/midaffemo/analyses/timecourses/data/realsubj/MIDaffemo/timecourses_b4_woOutliers_long.csv") %>% 
  filter(subject == "ab240324", voi == "nacc",coreg == "ants") %>% 
  mutate(trial_tr_noiti = ifelse(probe == 1, 9,8),
         trial_tr = trial_tr_noiti + iti/2) %>% 
  # select(trial,trial_tr,tr,run) %>% 
  filter(tr <= trial_tr) %>% 
  filter(run %in% c("run-01","run-02"))

end_run1 <- df.1sub %>%
  subset(trial == 24) %>%
  .[1:5,] %>%
  mutate(tr = tr + 10)

# create the 5 TRs at the tail of run 2
end_run2 <- df.1sub %>%
        filter(run == "run-02")%>%
        subset(trial == 24) %>%
        .[1:5,] %>%
        mutate(tr = tr + 9)

# # create the 5 TRs at the tail of run 3
# end_run3 <- df.1sub %>%
#         filter(run == "run-03")%>%
#         subset(trial == 24) %>%
#         .[1:5,] %>%
#         mutate(tr = tr + 10)
# 
# # create the 5 TRs at the tail of run 4
# end_run4 <- df.1sub %>%
#         filter(run == "run-04")%>%
#         subset(trial == 24) %>%
#         .[1:5,] %>%
#         mutate(tr = tr + 11)

df.1sub <- df.1sub %>%
        # insert 5 rows at the end of each run
        add_row(end_run1, .after = 240) %>%
        add_row(end_run2, .after = 485)
        # add_row(end_run3, .after = 730) %>%
        # add_row(end_run4, .after = 975)
      
df.1sub <- df.1sub %>% 
  mutate(block = as.numeric(substr(run,6,6))) %>% 
  mutate(trial = trial + (block - 1) * 24) %>% 
  mutate(tr = row_number())

my_array_s1_run12 <- left_join(my_array_s1_run12,df.1sub %>% 
                         select(trial:erating_t,time,tr,trial_tr)) %>% 
  group_by(subject,trial,threshold) %>% 
  mutate(tr_in_trial = row_number())%>% 
  relocate(tr_in_trial,.after = tr) %>% 
  mutate(split = "run12")
```

#### second half (using h1 template)
```{r}
glmArousal_array <- NULL
glmPupil_array <- NULL
pupil_array <- NULL

for (t in 1:length(thresh_str)){
  filepath = paste0("~/Desktop/midaffemo/glm_maps/glm27c_h1_array_threshold",thresh_str[t],".csv")
  glmArousal_array<-rbind(glmArousal_array,
                          as.data.frame(t(read_csv(filepath, 
                                           col_names = F))) %>% 
                            mutate(type = "glmArousal", 
                                   tr = row_number(), 
                                   threshold = thresh[t]) #self-reported arousal GLM
  )
  
  filepath = paste0("~/Desktop/midaffemo/glm_maps/glm33b_h1_array_threshold",thresh_str[t],".csv")
  glmPupil_array<-rbind(glmPupil_array,
                        as.data.frame(t(read_csv(filepath, 
             col_names = F))) %>% 
    mutate(type = "glmPupil", tr = row_number(), 
                                   threshold = thresh[t])) #pupil GLM
  
  pupil_array<-rbind(pupil_array,
                     as.data.frame(t(read_csv("~/Desktop/midaffemo/glm_maps/pupil_array.csv", col_names = F))) %>% slice(491:980) %>% 
    mutate(type = "pupil", tr = row_number(), 
                                   threshold = thresh[t])) #pupil time series
}


my_array_s1_run34<-Reduce(rbind,list(glmArousal_array,glmPupil_array,pupil_array))
names(my_array_s1_run34) <- c(subjects_list$X1,"type","tr","threshold")
my_array_s1_run34<-my_array_s1_run34%>% 
  pivot_longer(ab240324:yz240312,names_to = "subject",values_to = "val") %>% 
  pivot_wider(names_from = type, values_from = val)

df.1sub <- read_csv("~/Desktop/midaffemo/analyses/timecourses/data/realsubj/MIDaffemo/timecourses_b4_woOutliers_long.csv") %>% 
  filter(subject == "ab240324", voi == "nacc",coreg == "ants") %>% 
  mutate(trial_tr_noiti = ifelse(probe == 1, 9,8),
         trial_tr = trial_tr_noiti + iti/2) %>% 
  # select(trial,trial_tr,tr,run) %>% 
  filter(tr <= trial_tr) %>% 
  filter(run %in% c("run-03","run-04"))

# create the 5 TRs at the tail of run 3
end_run3 <- df.1sub %>%
        filter(run == "run-03")%>%
        subset(trial == 24) %>%
        .[1:5,] %>%
        mutate(tr = tr + 10)

# create the 5 TRs at the tail of run 4
end_run4 <- df.1sub %>%
        filter(run == "run-04")%>%
        subset(trial == 24) %>%
        .[1:5,] %>%
        mutate(tr = tr + 11)

df.1sub <- df.1sub %>%
        #insert 5 rows at the end of each run
        add_row(end_run3, .after = 240) %>%
        add_row(end_run4, .after = 485)
      
df.1sub <- df.1sub %>% 
  mutate(block = as.numeric(substr(run,6,6))) %>% 
  mutate(trial = trial + (block - 1) * 24) %>% 
  mutate(tr = row_number())

my_array_s1_run34 <- left_join(my_array_s1_run34,df.1sub %>% 
                         select(trial:erating_t,time,tr,trial_tr)) %>% 
  group_by(subject,trial,threshold) %>% 
  mutate(tr_in_trial = row_number())%>% 
  relocate(tr_in_trial,.after = tr) %>% 
  mutate(split = "run34")
```

```{r}
my_array_s1 <- rbind(my_array_s1_run12,my_array_s1_run34)
```


## get self-reported arousal template
```{r}
my_array_s1__ <- my_array_s1%>% 
  ungroup() %>% 
  select(trial,subject,tr_in_trial,glmArousal,trial_tr,threshold,split) %>% 
  pivot_wider(names_from = c(tr_in_trial), values_from = c(glmArousal), names_prefix = "glmArousal_TR_") %>% 
  arrange(subject,trial)

TR_DELAY = 14

for (s in splits){
  for (t in thresh){
  for (sub in unique(my_array_s1__$subject)){
    for(tr in 9:11){
      replace_idx = my_array_s1__$subject == sub & my_array_s1__$trial_tr == tr & my_array_s1__$threshold == t & is.na(my_array_s1__[,paste0("glmArousal_TR_",tr+1)]) & my_array_s1__$split == s
      #early TRs were TRs from the previous trial
      my_array_s1__[replace_idx,paste0("glmArousal_TR_",(tr+1):TR_DELAY)] <- my_array_s1__[lag(replace_idx) %>% replace_na(FALSE),paste0("glmArousal_TR_",1:(TR_DELAY-tr))]
  } # tr loop
  }
}
}


my_array_s1__ <- my_array_s1__ %>% 
  mutate(glmArousal_TR_17 = NA, glmArousal_TR_18 = NA, glmArousal_TR_19 = NA, glmArousal_TR_20 = NA)

my_array_s1__<-left_join(my_array_s1__ %>% 
                        pivot_longer(glmArousal_TR_1:glmArousal_TR_20,
                                     names_to = "tr_in_trial",names_prefix = "glmArousal_TR_",
                                     values_to = "glmArousal"),fmri3_data_2probes,
                      by = c("subject","trial")) %>% 
  filter(tr <= 975)%>%
  mutate(half = ifelse(trial >= 24,"second","first"))%>% #last bit was interpolated
  mutate(probe = ifelse(probe == 1, "anticipation probe","outcome probe"))

my_array_s1__ <- my_array_s1__ %>% 
  mutate(tr_in_trial = as.numeric(tr_in_trial),
         time = (tr_in_trial-1) * 2)
```


## plot as function of cue value / outcome value
```{r}
d1<-my_array_s1__ %>% 
         filter(!is.na(hit)) %>% 
         group_by(tr_in_trial,subject,threshold,probe) %>% 
         summarise(glmArousal = mean(glmArousal,na.rm = T)) %>% 
         group_by(tr_in_trial,threshold,probe) %>% 
         summarise(mean = mean(glmArousal,na.rm = T),
                   se = sd(glmArousal,na.rm = T)/sqrt(n())) %>% 
  filter(tr_in_trial <= 14)

p1m2a<-plot_spacer()+ggplot(d1 %>% filter(probe == "anticipation probe",threshold == 0.5),
       aes(x = tr_in_trial, y = mean))+
  geom_vline(xintercept = c(3.5,4.5,5.5,9.5,10.5,11.5,12.5), size = 1, color = "grey")+
  annotate("text",x = 4, y = 0.05, label = "C")+
  annotate("text",x = 5, y = 0.05, label = "F")+
  annotate("text",x = 10, y = 0.05, label = "F")+
  annotate("text",x = 11, y = 0.05, label = "T")+
  annotate("text",x = 12, y = 0.05, label = "O")+
  annotate("text",x = 7.5, y = 0.05, label = "R")+
  geom_line(size = 0.5) +
  geom_point()+
  geom_errorbar(aes(x = tr_in_trial, ymin = mean-se,ymax = mean+se), width = 0.3)+
  labs(y = "Simalirty",
       x = "time (s)",
       subtitle = "anticipation probe")+
  scale_color_manual(values = redOrange_palette6)+
  theme(legend.position = "top")+
  ylim(-0.1,0.1)+
  scale_x_continuous(breaks = seq(1,15,5),labels = seq(1,28,10))+
plot_spacer()+
ggplot(d1 %>% filter(probe == "outcome probe",threshold == 0.5),
       aes(x = tr_in_trial, y = mean))+
  geom_vline(xintercept = c(3.5,4.5,5.5,6.5,7.5,11.5), size = 1, color = "grey")+
  annotate("text",x = 4, y = 0.05, label = "C")+
  annotate("text",x = 5, y = 0.05, label = "F")+
  annotate("text",x = 6, y = 0.05, label = "T")+
  annotate("text",x = 7, y = 0.05, label = "O")+
  annotate("text",x = 10, y = 0.05, label = "R")+
  geom_line(size = 0.5) +
  geom_point()+
  geom_errorbar(aes(x = tr_in_trial, ymin = mean-se,ymax = mean+se), width = 0.3)+
  labs(y = "Simalirty",
       x = "time (s)",
       subtitle = "outcome probe",
      caption = "C = Cue, F = Fixation, \nT = Target, O = Outcome, R = Rating")+
  scale_color_manual(values = redOrange_palette6)+
  theme(legend.position = "top")+
  ylim(-0.1,0.1)+
  scale_x_continuous(breaks = seq(1,15,5),labels = seq(0,28,10))+plot_spacer()+
  plot_layout(widths = c(0.3,1,0.3,1,0.3))

d2<-my_array_s1__ %>% 
         filter(!is.na(hit),
                tr_in_trial == 5) %>% 
         group_by(subject,threshold,cue_value) %>% 
         summarise(glmArousal = mean(glmArousal,na.rm = T)) %>% 
         group_by(threshold,cue_value) %>% 
         summarise(mean = mean(glmArousal,na.rm = T),
                   se = sd(glmArousal,na.rm = T)/sqrt(n())) %>% 
  mutate(cue_value = factor(cue_value, levels = c("-$5","-$1","-$0","+$0","+$1","+$5")))

summary(l1<-lmer(scale(glmArousal) ~ cue_value + (1|split),
                   my_array_s1__ %>% 
                   filter(tr_in_trial == 5, threshold == 0.5)))

# Get effect size (standardized beta)
r2   <- r.squaredGLMM(l1)[1]

p2m2a<-ggplot(d2 %>% filter(threshold == 0.5),
       aes(x = cue_value, y = mean,color = cue_value))+
  geom_point(size = 0.5) +
  geom_point()+
  geom_errorbar(aes(x = cue_value, ymin = mean-se,ymax = mean+se), width = 0.3)+
  labs(y = "Simalirty",
       x = "time (s)",
       subtitle = "Inferred arousal (8s)")+
  scale_color_manual(values = redOrange_palette6)+
  theme(legend.position = "none")+  # show shape legend
  scale_x_discrete(breaks =c("-$5","-$1","-$0","+$0","+$1","+$5"))+
  annotate("text",x = Inf, y = -Inf, label = paste0("R² = ", round(r2, 2)),
    hjust = 1.1, vjust = -1.5, size = 4)

d3<-my_array_s1__ %>% 
         filter(!is.na(hit),
                ifelse(probe == "anticipation probe", tr_in_trial == 12,
                       ifelse(probe == "outcome probe",tr_in_trial == 7,NA))) %>% 
         group_by(subject,threshold,hit,cue_value) %>% 
         summarise(glmArousal = mean(glmArousal,na.rm = T)) %>% 
         group_by(threshold,hit,cue_value) %>% 
         summarise(mean = mean(glmArousal,na.rm = T),
                   se = sd(glmArousal,na.rm = T)/sqrt(n())) %>% 
  mutate(cue_value = factor(cue_value, levels = c("-$5","-$1","-$0","+$0","+$1","+$5")))

ggplot(d3 %>% filter(threshold == 0.5),
       aes(x = cue_value, y = mean, color = cue_value, shape = hit)) +
  geom_point(position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(x = cue_value, group = hit, ymin = mean - se, ymax = mean + se),
                width = 0.3, position = position_dodge(width = 0.5)) +
  labs(y = "Similarity",
       x = "time (s)",
       subtitle = "arousal index during outcome") +
  theme(legend.position = "top") +
  scale_color_manual(values = redOrange_palette6) +
  guides(color = "none",  # hide color legend
         shape = guide_legend())+  # show shape legend
  scale_x_discrete(breaks =c("-$5","-$1","-$0","+$0","+$1","+$5"))

summary(l2<-lmer(glmArousal~cue_value*hit+(1|split),my_array_s1__ %>% filter(ifelse(
  probe == "anticipation probe", tr_in_trial == 12,
                       ifelse(probe == "outcome probe",tr_in_trial == 7,NA)))))
anova(l2)
```

#### predicting performance
```{r warning=F}
df_performance <- NULL
i<-1
for (s in splits){
  for (t in thresh){
    for (tr in 1:14){

      dat <- my_array_s1__ %>% 
        filter(tr_in_trial == tr,
               threshold == t,
               split == s)

      l1 <- summary(glm(
        hit_num ~ scale(glmArousal),
        family = binomial,
        dat %>%
          filter(probe == "anticipation probe") %>%
          mutate(hit_num = as.numeric(hit == 1))
      ))

      l2 <- summary(glm(
        hit_num ~ scale(glmArousal),
        family = binomial,
        dat %>%
          filter(probe == "outcome probe") %>%
          mutate(hit_num = as.numeric(hit == 1))
      ))

      df_performance[[i]] <- data.frame(
        Estimate = l1$coefficients[2, 1],
        se       = l1$coefficients[2, 2],
        z        = l1$coefficients[2, 3],
        p        = l1$coefficients[2, 4],
        probe    = "anticipation",
        split    = s,
        threshold= t,
        tr       = tr
      )

      df_performance[[i + 1]] <- data.frame(
        Estimate = l2$coefficients[2, 1],
        se       = l2$coefficients[2, 2],
        z        = l2$coefficients[2, 3],
        p        = l2$coefficients[2, 4],
        probe    = "outcome",
        split    = s,
        threshold= t,
        tr       = tr
      )

      i <- i + 2
    }
  }
}

df_performance <- dplyr::bind_rows(df_performance)

ggplot(df_performance, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe,linetype = split))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  facet_wrap(~threshold)+
  scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

ggplot(df_performance %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_line(aes(color= probe,linetype = split))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

summary(l1<-glmer(hit_num ~ scale(glmArousal) + (1|split),family = binomial,
                    my_array_s1__ %>% 
                      filter(tr_in_trial == 5,threshold == 0.5) %>% 
                      mutate(hit_num = as.factor(hit == "Hit"))))

# Get effect size (standardized beta)
beta <- summary(l1)$coefficients["scale(glmArousal)", "Estimate"]
r2   <- r.squaredGLMM(l1)[1,1]

# Create base plot
p3m2a <- plot_model(l1, type = "pred", terms = "glmArousal[all]",color = "darkgrey") +
  labs(x = "similarity (z-score)",
       y = "p(hit)",title = "p(hit)") +
  annotate("text",x = Inf, y = -Inf, label = paste0("β = ", round(beta, 2), "\nR²m = ", round(r2, 2)),
    hjust = 1.1, vjust = -0.5, size = 4)
```

```{r warning=F}
df_performance <- NULL
i<-1
for (s in splits){
  for (t in thresh){
    for (tr in 1:14){

      dat <- my_array_s1__ %>% 
        filter(tr_in_trial == tr,
               threshold == t,
               split == s)

      l1 <- summary(lm(scale(rt) ~ scale(glmArousal),
        dat %>%
          filter(probe == "anticipation probe",hit == "Hit")
      ))

      l2 <- summary(lm(scale(rt) ~ scale(glmArousal),
        dat %>%
          filter(probe == "outcome probe",hit == "Hit")
      ))

      df_performance[[i]] <- data.frame(
        Estimate = l1$coefficients[2, 1],
        se       = l1$coefficients[2, 2],
        z        = l1$coefficients[2, 3],
        p        = l1$coefficients[2, 4],
        probe    = "anticipation",
        split    = s,
        threshold= t,
        tr       = tr
      )

      df_performance[[i + 1]] <- data.frame(
        Estimate = l2$coefficients[2, 1],
        se       = l2$coefficients[2, 2],
        z        = l2$coefficients[2, 3],
        p        = l2$coefficients[2, 4],
        probe    = "outcome",
        split    = s,
        threshold= t,
        tr       = tr
      )

      i <- i + 2
    }
  }
}

df_performance <- dplyr::bind_rows(df_performance)

ggplot(df_performance, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe,linetype = split))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  facet_wrap(~threshold)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

ggplot(df_performance %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_line(aes(color= probe,linetype = split))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

summary(l1<-lmer(scale(rt) ~ scale(glmArousal) + (1|split),
                   my_array_s1__ %>% 
                   filter(tr_in_trial == 5, hit == "Hit",threshold == 0.5)))

# Get effect size (standardized beta)
beta <- summary(l1)$coefficients["scale(glmArousal)", "Estimate"]
r2   <- r.squaredGLMM(l1)[1]

# Create base plot
p4m2a <- plot_model(l1, type = "pred", terms = "glmArousal",color = "darkgrey") +
  labs(x = "similarity (z-score)",
    y = "rt (z-score)",
    title = "rt (hit trials)"
  ) +
  annotate("text",x = Inf, y = -Inf, label = paste0("β = ", round(beta, 2), "\nR²m = ", round(r2, 2)),
    hjust = 1.1, vjust = -1.5, size = 4)

```


#### predicting cue value (abs)
```{r warning=F}
df_cue <- list()
i <- 1

for (s in splits){
  for (t in thresh){
    for (tr in 1:14){
      for (p in c("anticipation probe", "outcome probe")){

        dat <- my_array_s1__ %>%
          filter(tr_in_trial == tr,
                 threshold == t,
                 split == s,
                 probe == p) %>%
          mutate(
            cue_value_abs = case_when(
              cue_value %in% c("+$5", "-$5") ~ 5,
              cue_value %in% c("+$1", "-$1") ~ 1,
              cue_value %in% c("+$0", "-$0") ~ 0,
              TRUE ~ NA_real_
            )
          )

        fit <- summary(lm(cue_value_abs ~ scale(glmArousal), dat))

        df_cue[[i]] <- data.frame(
          Estimate  = fit$coefficients[2, 1],
          se        = fit$coefficients[2, 2],
          t         = fit$coefficients[2, 3],
          p         = fit$coefficients[2, 4],
          probe     = sub(" probe", "", p),
          split     = s,
          threshold = t,
          tr        = tr
        )

        i <- i + 1
      }
    }
  }
}

df_cue <- dplyr::bind_rows(df_cue)


ggplot(df_cue, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe,linetype = split))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  facet_wrap(~threshold)+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

ggplot(df_cue %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_line(aes(color= probe,linetype = split))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

summary(l1<-lmer(scale(cue_value_abs) ~ scale(glmArousal) + (1|split),
                    my_array_s1__ %>% 
                      filter(tr_in_trial == 5,threshold == 0.5) %>% 
                      mutate(cue_value_abs = ifelse(cue_value %in% c("+$5","-$5"),5,
                                                    ifelse(cue_value %in% c("+$1","-$1"),1,
                                                           ifelse(cue_value %in% 
                                                                    c("+$0","-$0"),1,NA))))))

# Get effect size (standardized beta)
beta <- summary(l1)$coefficients["scale(glmArousal)", "Estimate"]
r2   <- r.squaredGLMM(l1)[1]

# Create base plot
p5m2a <- plot_model(l1, type = "pred", terms = "glmArousal") +
  labs(x = "similarity to arousal template (z-score)",
    y = "abs. cue value (z-score)",
    title = "abs. cue value (z-score)"
  ) +
  annotate("text",x = Inf, y = -Inf, label = paste0("β = ", round(beta, 2), ", R²m = ", round(r2, 2)),
    hjust = 1.1, vjust = -1.5, size = 4)
```

#### predicting self-reports
```{r}
df_rating <- list()
i <- 1

for (s in splits){
  for (t in thresh){
    for (tr in 1:14){
      for (p in c("anticipation probe", "outcome probe")){

        dat <- my_array_s1__ %>%
          filter(tr_in_trial == tr,
                 threshold == t,
                 split == s,
                 probe == p)

        fit <- summary(
          lm(scale(arousal_scaled) ~ scale(glmArousal), dat)
        )

        df_rating[[i]] <- data.frame(
          Estimate  = fit$coefficients[2, 1],
          se        = fit$coefficients[2, 2],
          t         = fit$coefficients[2, 3],
          p         = fit$coefficients[2, 4],
          probe     = sub(" probe", "", p),
          split     = s,
          threshold = t,
          tr        = tr
        )

        i <- i + 1
      }
    }
  }
}

df_rating <- dplyr::bind_rows(df_rating)


ggplot(df_rating, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe,linetype= split))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  # geom_ribbon(aes(x = tr, ymin = Estimate - se,
  #                   ymax = Estimate + se,fill = probe),
  #             alpha = 0.1)+
  facet_wrap(~threshold)+
  labs(title = "FMRI study")+
  scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  scale_x_continuous(breaks = 1:14)+
  geom_vline(xintercept = 5, color = "purple",label = "F")+
  geom_vline(xintercept = 6, color = "skyblue",label = "T")+
  geom_vline(xintercept = 7, color = "purple", linetype = "dashed")+
  geom_vline(xintercept = 9, color = "skyblue", linetype = "dashed")

ggplot(df_rating %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_line(aes(color= probe,linetype= split))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)
```

#### visualize peak correlation
```{r}
# Prepare data
d1 <- my_array_s1__ %>% filter(tr_in_trial == 5, threshold == 0.5)
d2 <- my_array_s1__ %>% filter(tr_in_trial == 5, probe == "anticipation probe", threshold == 0.5)
d3 <- my_array_s1__ %>% filter(tr_in_trial == 7, probe == "outcome probe", threshold == 0.5)

# Fit models
l1 <- lmer(scale(arousal_scaled) ~ scale(glmArousal) + (1|split), d1)
l2 <- lmer(scale(arousal_scaled) ~ scale(glmArousal) + (1|split), d2)
l3 <- lmer(scale(arousal_scaled) ~ scale(glmArousal) + (1|split), d3)
# Extract coefficients and p-values
get_stats <- function(model) {
  b <- coef(summary(model))["scale(glmArousal)", "Estimate"]
  p <- coef(summary(model))["scale(glmArousal)", "Pr(>|t|)"]
  list(beta = round(b, 3), p = signif(p, 3))
}

s1 <- get_stats(l1)
s2 <- get_stats(l2)
s3 <- get_stats(l3)

predict_ci <- function(model, newdata, confirm = FALSE) {
  X <- model.matrix(delete.response(terms(model)), newdata)
  beta <- fixef(model)
  V <- vcov(model)
  
  fit <- as.vector(X %*% beta)
  se  <- sqrt(diag(X %*% V %*% t(X)))
  
  newdata %>%
    mutate(
      fit = fit,
      lwr = fit - 1.96 * se,
      upr = fit + 1.96 * se
    )
}


new1_dat <- d1 %>%
  summarise(
    glmArousal = seq(min(glmArousal, na.rm = TRUE),
                     max(glmArousal, na.rm = TRUE),
                     length.out = 100)
  )

new2_dat <- d2 %>%
  summarise(
    glmArousal = seq(min(glmArousal, na.rm = TRUE),
                     max(glmArousal, na.rm = TRUE),
                     length.out = 100)
  )

new3_dat <- d3 %>%
  summarise(
    glmArousal = seq(min(glmArousal, na.rm = TRUE),
                     max(glmArousal, na.rm = TRUE),
                     length.out = 100)
  )

new1 <- predict_ci(l1, new1_dat)
new2 <- predict_ci(l2, new2_dat)
new3 <- predict_ci(l3, new3_dat)


# Plot
p_m2_arousal_c <- ggplot() +
  ## Model 1 -- black
  geom_ribbon(data = new1,
              aes(x = scale(glmArousal), ymin = lwr, ymax = upr),
              fill = "black", alpha = 0.15) +
  geom_line(data = new1,
            aes(x = scale(glmArousal), y = fit),
            color = "black", size = 1) +

  ## Model 2 -- purple
  geom_ribbon(data = new2,
              aes(x = scale(glmArousal), ymin = lwr, ymax = upr),
              fill = "purple", alpha = 0.15) +
  geom_line(data = new2,
            aes(x = scale(glmArousal), y = fit),
            color = "purple", size = 1) +

  ## Model 3 -- skyblue
  geom_ribbon(data = new3,
              aes(x = scale(glmArousal), ymin = lwr, ymax = upr),
              fill = "skyblue", alpha = 0.15) +
  geom_line(data = new3,
            aes(x = scale(glmArousal), y = fit),
            color = "skyblue", size = 1) +

  # Add beta + p-value text with < .001 formatting
  annotate("text", x = -1.5, y = max(new1$upr)+0.6, size=3.5,
           label = paste0("both (8s): β=", round(s1$beta,2), 
                          ", p", ifelse(s1$p < 0.001, "< .001", round(s1$p, 3))),
           color = "black", hjust = 0) +
  annotate("text", x = -1.5, y = max(new1$upr)+0.2, size=3.5,
           label = paste0("ant (8s): β=", round(s2$beta,2), 
                          ", p", ifelse(s2$p < 0.001, "< .001", round(s2$p, 3))),
           color = "purple", hjust = 0) +
  annotate("text", x = -1.5, y = max(new1$upr)+0.4, size=3.5,
           label = paste0("out (12s): β=", round(s3$beta,2), 
                          ", p", ifelse(s3$p < 0.001, "< .001", round(s3$p, 3))),
           color = "skyblue", hjust = 0)+
  labs(
    x = "similarity (scaled)",
    y = "Predicted arousal (scaled)"
  )
```

```{r}
(p1m2a)/
(p2m2a+p3m2a+p4m2a+p_m2_arousal_c+plot_layout(widths = c(1.2,1,1,1.2)))+
plot_annotation(title = "Arousal template",
                  tag_levels = "A")

ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig_glmArousal.png"),dpi = 300, height = 6, width = 11)
```

## get pupil glm template
```{r}
my_array_s1_ <- my_array_s1%>% 
  ungroup() %>% 
  select(trial,subject,tr_in_trial,glmPupil,trial_tr,threshold,split) %>% 
  pivot_wider(names_from = c(tr_in_trial), values_from = c(glmPupil), names_prefix = "glmPupil_TR_") %>% 
  arrange(subject,trial)

for (s in splits){
  for (t in thresh){
  for (sub in unique(my_array_s1_$subject)){
    for(tr in 9:11){
      replace_idx = my_array_s1_$subject == sub & my_array_s1_$trial_tr == tr & my_array_s1_$threshold == t & is.na(my_array_s1_[,paste0("glmPupil_TR_",tr+1)]) & my_array_s1_$split == s
      #early TRs were TRs from the previous trial
      my_array_s1_[replace_idx,paste0("glmPupil_TR_",(tr+1):TR_DELAY)] <- my_array_s1_[lag(replace_idx) %>% replace_na(FALSE),paste0("glmPupil_TR_",1:(TR_DELAY-tr))]
  } # tr loop
  }
}
}


TR_DELAY = 14
my_array_s1_ <- my_array_s1_ %>% mutate(glmPupil_TR_17 = NA, glmPupil_TR_18 = NA, glmPupil_TR_19 = NA, glmPupil_TR_20 = NA)

my_array_s1_<-left_join(my_array_s1_ %>% 
                        pivot_longer(glmPupil_TR_1:glmPupil_TR_20,
                                     names_to = "tr_in_trial",names_prefix = "glmPupil_TR_",
                                     values_to = "glmPupil"),fmri3_data_2probes,
                      by = c("subject","trial")) %>% 
  filter(tr <= 975)%>%
  mutate(half = ifelse(trial >= 48,"second","first"))%>% #last bit was interpolated
  mutate(probe = ifelse(probe == 1, "anticipation probe","outcome probe"))

my_array_s1_ <- my_array_s1_ %>% 
  mutate(tr_in_trial = as.numeric(tr_in_trial),
         time = (tr_in_trial-1) * 2)
```

## plot as function of cue value / outcome value
```{r}
d1<-my_array_s1_ %>% 
         filter(!is.na(hit)) %>% 
         group_by(tr_in_trial,subject,threshold,probe) %>% 
         summarise(glmPupil = mean(glmPupil,na.rm = T)) %>% 
         group_by(tr_in_trial,threshold,probe) %>% 
         summarise(mean = mean(glmPupil,na.rm = T),
                   se = sd(glmPupil,na.rm = T)/sqrt(n())) %>% 
  filter(tr_in_trial <= 14)

p1m2p<-plot_spacer()+ggplot(d1 %>% filter(probe == "anticipation probe",threshold == 0.5),
       aes(x = tr_in_trial, y = mean))+
  geom_vline(xintercept = c(3.5,4.5,5.5,9.5,10.5,11.5,12.5), size = 1, color = "grey")+
  annotate("text",x = 4, y = 0.05, label = "C")+
  annotate("text",x = 5, y = 0.05, label = "F")+
  annotate("text",x = 10, y = 0.05, label = "F")+
  annotate("text",x = 11, y = 0.05, label = "T")+
  annotate("text",x = 12, y = 0.05, label = "O")+
  annotate("text",x = 7.5, y = 0.05, label = "R")+
  geom_line(size = 0.5) +
  geom_point()+
  geom_errorbar(aes(x = tr_in_trial, ymin = mean-se,ymax = mean+se), width = 0.3)+
  labs(y = "Simalirty",
       x = "time (s)",
       subtitle = "anticipation probe")+
  scale_color_manual(values = redOrange_palette6)+
  theme(legend.position = "top")+
  ylim(-0.1,0.1)+
  scale_x_continuous(breaks = seq(1,15,5),labels = seq(1,28,10))+
  plot_spacer()+
ggplot(d1 %>% filter(probe == "outcome probe",threshold == 0.5),
       aes(x = tr_in_trial, y = mean))+
  geom_vline(xintercept = c(3.5,4.5,5.5,6.5,7.5,11.5), size = 1, color = "grey")+
  annotate("text",x = 4, y = 0.05, label = "C")+
  annotate("text",x = 5, y = 0.05, label = "F")+
  annotate("text",x = 6, y = 0.05, label = "T")+
  annotate("text",x = 7, y = 0.05, label = "O")+
  annotate("text",x = 10, y = 0.05, label = "R")+
  geom_line(size = 0.5) +
  geom_point()+
  geom_errorbar(aes(x = tr_in_trial, ymin = mean-se,ymax = mean+se), width = 0.3)+
  labs(y = "Simalirty",
       x = "time (s)",
       subtitle = "outcome probe",
      caption = "C = Cue, F = Fixation, \nT = Target, O = Outcome, R = Rating")+
  scale_color_manual(values = redOrange_palette6)+
  theme(legend.position = "top")+
  ylim(-0.1,0.1)+
  scale_x_continuous(breaks = seq(1,15,5),labels = seq(0,28,10))+
  plot_spacer()+
  plot_layout(widths = c(0.3,1,0.3,1,0.3))

d2<-my_array_s1_ %>% 
         filter(!is.na(hit),
                tr_in_trial == 5) %>% 
         group_by(subject,threshold,cue_value) %>% 
         summarise(glmPupil = mean(glmPupil,na.rm = T)) %>% 
         group_by(threshold,cue_value) %>% 
         summarise(mean = mean(glmPupil,na.rm = T),
                   se = sd(glmPupil,na.rm = T)/sqrt(n())) %>% 
  mutate(cue_value = factor(cue_value, levels = c("-$5","-$1","-$0","+$0","+$1","+$5")))

summary(l1<-lmer(scale(glmPupil) ~ cue_value + (1|split),
                   my_array_s1_ %>% 
                   filter(tr_in_trial == 5, threshold == 0.5)))
anova(l1)
# Get effect size 
r2   <- r.squaredGLMM(l1)[1]

p2m2p<-ggplot(d2 %>% filter(threshold == 0.5),
       aes(x = cue_value, y = mean,color = cue_value))+
  geom_point(size = 0.5) +
  geom_point()+
  geom_errorbar(aes(x = cue_value, ymin = mean-se,ymax = mean+se), width = 0.3)+
  labs(y = "Simalirty",
       x = "time (s)",
       subtitle = "Inferred arousal (8s)")+
  scale_color_manual(values = redOrange_palette6)+
  theme(legend.position = "none")+  # show shape legend
  scale_x_discrete(breaks =c("-$5","-$1","-$0","+$0","+$1","+$5"))+
  annotate("text",x = Inf, y = -Inf, label = paste0("R² = ", round(r2, 2)),
    hjust = 1.1, vjust = -1.5, size = 4)

d3<-my_array_s1_ %>% 
         filter(!is.na(hit),
                ifelse(probe == "anticipation probe", tr_in_trial == 12,
                       ifelse(probe == "outcome probe",tr_in_trial == 7,NA))) %>% 
         group_by(subject,threshold,hit,cue_value) %>% 
         summarise(glmPupil = mean(glmPupil,na.rm = T)) %>% 
         group_by(threshold,hit,cue_value) %>% 
         summarise(mean = mean(glmPupil,na.rm = T),
                   se = sd(glmPupil,na.rm = T)/sqrt(n())) %>% 
  mutate(cue_value = factor(cue_value, levels = c("-$5","-$1","-$0","+$0","+$1","+$5")))

ggplot(d3 %>% filter(threshold == 0.5),
       aes(x = cue_value, y = mean, color = cue_value, shape = hit)) +
  geom_point(position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(x = cue_value, group = hit, ymin = mean - se, ymax = mean + se),
                width = 0.3, position = position_dodge(width = 0.5)) +
  labs(y = "Similarity",
       x = "time (s)",
       subtitle = "arousal index during outcome") +
  theme(legend.position = "top") +
  scale_color_manual(values = redOrange_palette6) +
  guides(color = "none",  # hide color legend
         shape = guide_legend())+  # show shape legend
  scale_x_discrete(breaks =c("-$5","-$1","-$0","+$0","+$1","+$5"))

summary(l2<-lmer(glmPupil~cue_value*hit+(1|split),my_array_s1_ %>% filter(ifelse(
  probe == "anticipation probe", tr_in_trial == 12,
                       ifelse(probe == "outcome probe",tr_in_trial == 7,NA)))))
anova(l2)
```

#### predicting performance
```{r warning=F}
df_performance <- NULL
i<-1

for (t in thresh){
    for (tr in 1:14){
      dat <- my_array_s1_ %>% 
        filter(tr_in_trial == tr,
               threshold == t)

      l1 <- summary(glmer(
        hit_num ~ scale(glmPupil) + (1|split),
        family = binomial,
        dat %>%
          filter(probe == "anticipation probe") %>%
          mutate(hit_num = as.numeric(hit == "Hit"))
      ))

      l2 <- summary(glmer(
        hit_num ~ scale(glmPupil) + (1|split),
        family = binomial,
        dat %>%
          filter(probe == "outcome probe") %>%
          mutate(hit_num = as.numeric(hit == "Hit"))
      ))

      df_performance[[i]] <- data.frame(
        Estimate = l1$coefficients[2, 1],
        se       = l1$coefficients[2, 2],
        z        = l1$coefficients[2, 3],
        p        = l1$coefficients[2, 4],
        probe    = "anticipation",
        threshold= t,
        tr       = tr
      )

      df_performance[[i + 1]] <- data.frame(
        Estimate = l2$coefficients[2, 1],
        se       = l2$coefficients[2, 2],
        z        = l2$coefficients[2, 3],
        p        = l2$coefficients[2, 4],
        probe    = "outcome",
        threshold= t,
        tr       = tr
      )

      i <- i + 2
    }
}


df_performance <- dplyr::bind_rows(df_performance)

ggplot(df_performance, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  facet_wrap(~threshold)+
  scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

p_thresh_hit<-ggplot(df_performance %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_point(aes(color= probe))+
  geom_errorbar(aes(color= probe, x = threshold, ymin = Estimate - se,
                    ymax = Estimate + se), width = 0.1)+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "p(hit)")+
  scale_x_continuous(breaks = 1:14)+
  annotate("rect",xmin = 0.25,xmax = 0.75, ymin = -0.05,ymax = 0.4,alpha = 0.1)

summary(l1<-glmer(hit_num ~ scale(glmPupil) + (1|split),family = binomial,
                    my_array_s1_ %>% 
                      filter(tr_in_trial == 5,threshold == 0.5) %>% 
                      mutate(hit_num = as.factor(hit == "Hit"))))

# Get effect size (standardized beta)
beta <- summary(l1)$coefficients["scale(glmPupil)", "Estimate"]
r2   <- r.squaredGLMM(l1)[1,1]

# Create base plot
p3m2p <- plot_model(l1, type = "pred", terms = "glmPupil[all]",color = "darkgrey") +
  labs(x = "similarity (z-score)",
       y = "p(hit)",title = "p(hit)") +
  annotate("text",x = Inf, y = -Inf, label = paste0("β = ", round(beta, 2), "\nR²m = ", round(r2, 2)),
    hjust = 1.1, vjust = -0.5, size = 4)
```

### predictive performance
```{r}
# Subset the data exactly as used in your model
data_used <- my_array_s1_ %>%
  filter(tr_in_trial == 5, threshold == 0.5) %>%
  mutate(hit_num = as.factor(hit == "Hit"))

# Keep only rows with no missing values in the predictors or outcome
data_used <- data_used[complete.cases(data_used[, c("glmPupil", "hit_num")]), ]

# Predicted probabilities
pred_probs <- predict(l1, newdata = data_used, type = "response")

# Convert probabilities to predicted classes
pred_class <- ifelse(pred_probs > 0.5, 1, 0)

# Actual classes
actual_class <- as.numeric(data_used$hit_num)-1

# Accuracy
accuracy <- mean(pred_class == actual_class,na.rm=T)
accuracy

# Confusion matrix
table(Predicted = pred_class, Actual = actual_class)

# Optional: AUC
library(pROC)
roc_obj <- roc(actual_class, pred_probs)
auc(roc_obj)

# Bootstrap test for AUC > 0.5
set.seed(777)
ci <- ci.auc(roc_obj, method = "bootstrap", boot.n = 2000) # 95% CI
ci  # If the lower bound > 0.5, AUC is significantly above chance

```


```{r warning=F}
df_performance <- NULL
i<-1

for (t in thresh){
    for (tr in 1:14){

      dat <- my_array_s1_ %>% 
        filter(tr_in_trial == tr,
               threshold == t)

      l1 <- summary(lmer(scale(rt) ~ scale(glmPupil) + (1|split),
        dat %>%
          filter(probe == "anticipation probe",hit == "Hit")
      ))

      l2 <- summary(lmer(scale(rt) ~ scale(glmPupil) + (1|split),
        dat %>%
          filter(probe == "outcome probe",hit == "Hit")
      ))

      df_performance[[i]] <- data.frame(
        Estimate = l1$coefficients[2, 1],
        se       = l1$coefficients[2, 2],
        z        = l1$coefficients[2, 3],
        p        = l1$coefficients[2, 4],
        probe    = "anticipation",
        threshold= t,
        tr       = tr
      )

      df_performance[[i + 1]] <- data.frame(
        Estimate = l2$coefficients[2, 1],
        se       = l2$coefficients[2, 2],
        z        = l2$coefficients[2, 3],
        p        = l2$coefficients[2, 4],
        probe    = "outcome",
        threshold= t,
        tr       = tr
      )

      i <- i + 2
    }
}

df_performance <- dplyr::bind_rows(df_performance)

ggplot(df_performance, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  facet_wrap(~threshold)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

p_thresh_rt<-ggplot(df_performance %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_point(aes(color= probe))+
  geom_errorbar(aes(color= probe, x = threshold, ymin = Estimate - se,
                    ymax = Estimate + se), width = 0.1)+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "RT")+
  scale_x_continuous(breaks = 1:14)+
  annotate("rect",xmin = 0.25,xmax = 0.75, ymin = -0.3,ymax = 0,alpha = 0.1)+
  theme(legend.position = "none")

summary(l1<-lmer(scale(rt) ~ scale(glmPupil) + (1|split),
                   my_array_s1_ %>% 
                   filter(tr_in_trial == 5, hit == "Hit",threshold == 0.5)))

# Get effect size (standardized beta)
beta <- summary(l1)$coefficients["scale(glmPupil)", "Estimate"]
r2   <- r.squaredGLMM(l1)[1]

# Create base plot
p4m2p <- plot_model(l1, type = "pred", terms = "glmPupil",color = "darkgrey") +
  labs(x = "similarity (z-score)",
    y = "rt (z-score)",
    title = "rt (hit trials)"
  ) +
  annotate("text",x = Inf, y = -Inf, label = paste0("β = ", round(beta, 2), "\nR²m = ", round(r2, 2)),
    hjust = 1.1, vjust = -1.5, size = 4)

```

#### predicting cue value (abs)
```{r warning=F}
df_cue <- list()
i <- 1


for (t in thresh){
    for (tr in 1:14){
      for (p in c("anticipation probe", "outcome probe")){

        dat <- my_array_s1_ %>%
          filter(tr_in_trial == tr,
                 threshold == t,
                 probe == p) %>%
          mutate(
            cue_value_abs = case_when(
              cue_value %in% c("+$5", "-$5") ~ 5,
              cue_value %in% c("+$1", "-$1") ~ 1,
              cue_value %in% c("+$0", "-$0") ~ 0,
              TRUE ~ NA_real_
            )
          )

        fit <- summary(lmer(cue_value_abs ~ scale(glmPupil) + (1|split), dat))

        df_cue[[i]] <- data.frame(
          Estimate  = fit$coefficients[2, 1],
          se        = fit$coefficients[2, 2],
          t         = fit$coefficients[2, 3],
          p         = fit$coefficients[2, 4],
          probe     = sub(" probe", "", p),
          threshold = t,
          tr        = tr
        )

        i <- i + 1
      }
    }
}

df_cue <- dplyr::bind_rows(df_cue)


ggplot(df_cue, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  facet_wrap(~threshold)+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

p_thresh_cue<-ggplot(df_cue %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_point(aes(color= probe))+
  geom_errorbar(aes(color= probe, x = threshold, ymin = Estimate - se,
                    ymax = Estimate + se), width = 0.1)+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "Abs cue value")+
  scale_x_continuous(breaks = 1:14)+
  annotate("rect",xmin = 0.25,xmax = 0.75, ymin = 0.1,ymax = 0.8,alpha = 0.1)+
  theme(legend.position = "none")

summary(l1<-lmer(scale(cue_value_abs) ~ scale(glmPupil) + (1|split),
                    my_array_s1_ %>% 
                      filter(tr_in_trial == 5,threshold == 0.5) %>% 
                      mutate(cue_value_abs = ifelse(cue_value %in% c("+$5","-$5"),5,
                                                    ifelse(cue_value %in% c("+$1","-$1"),1,
                                                           ifelse(cue_value %in% 
                                                                    c("+$0","-$0"),1,NA))))))

# Get effect size (standardized beta)
beta <- summary(l1)$coefficients["scale(glmPupil)", "Estimate"]
r2   <- r.squaredGLMM(l1)[1]

# Create base plot
p5m2p <- plot_model(l1, type = "pred", terms = "glmPupil") +
  labs(x = "similarity to arousal template (z-score)",
    y = "abs. cue value (z-score)",
    title = "abs. cue value (z-score)"
  ) +
  annotate("text",x = Inf, y = -Inf, label = paste0("β = ", round(beta, 2), ", R²m = ", round(r2, 2)),
    hjust = 1.1, vjust = -1.5, size = 4)
```

#### predicting self-reports
```{r}
df_rating <- list()
i <- 1


for (t in thresh){
    for (tr in 1:14){
      for (p in c("anticipation probe", "outcome probe")){

        dat <- my_array_s1_ %>%
          filter(tr_in_trial == tr,
                 threshold == t,
                 probe == p)

        fit <- summary(
          lmer(scale(arousal_scaled) ~ scale(glmPupil) + (1|split), dat)
        )

        df_rating[[i]] <- data.frame(
          Estimate  = fit$coefficients[2, 1],
          se        = fit$coefficients[2, 2],
          t         = fit$coefficients[2, 3],
          p         = fit$coefficients[2, 4],
          probe     = sub(" probe", "", p),
          threshold = t,
          tr        = tr
        )

        i <- i + 1
      }
    }
}


df_rating <- dplyr::bind_rows(df_rating)


ggplot(df_rating, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  # geom_ribbon(aes(x = tr, ymin = Estimate - se,
  #                   ymax = Estimate + se,fill = probe),
  #             alpha = 0.1)+
  facet_wrap(~threshold)+
  labs(title = "FMRI study")+
  scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  scale_x_continuous(breaks = 1:14)+
  geom_vline(xintercept = 5, color = "purple",label = "F")+
  geom_vline(xintercept = 6, color = "skyblue",label = "T")+
  geom_vline(xintercept = 7, color = "purple", linetype = "dashed")+
  geom_vline(xintercept = 9, color = "skyblue", linetype = "dashed")

p_thresh_rate<-ggplot(df_rating, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_point(aes(color= probe))+
  geom_errorbar(aes(color= probe, x = tr, ymin = Estimate - se,
                    ymax = Estimate + se), width = 0.1)+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "Arousal rating")+
  scale_x_continuous(breaks = 1:14)+
  theme(legend.position = "none")+
  facet_wrap(~threshold,nrow = 2)
```

```{r}
(p_thresh_hit+p_thresh_cue+p_thresh_rt)/
  p_thresh_rate+
  plot_layout(heights = c(1,2))+
  plot_annotation(tag_levels = "A")

ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/si_pattern_threshold.png"),dpi = 300, height = 5, width = 7)
```

#### visualize peak correlation
```{r}
# Prepare data
d1 <- my_array_s1_ %>% filter(tr_in_trial == 5, threshold == 0.5)
d2 <- my_array_s1_ %>% filter(tr_in_trial == 5, probe == "anticipation probe", threshold == 0.5)
d3 <- my_array_s1_ %>% filter(tr_in_trial == 7, probe == "outcome probe", threshold == 0.5)

# Fit models
l1 <- lmer(scale(arousal_scaled) ~ scale(glmPupil) + (1|split), d1)
l2 <- lmer(scale(arousal_scaled) ~ scale(glmPupil) + (1|split), d2)
l3 <- lmer(scale(arousal_scaled) ~ scale(glmPupil) + (1|split), d3)
# Extract coefficients and p-values
get_stats <- function(model) {
  b <- coef(summary(model))["scale(glmPupil)", "Estimate"]
  p <- coef(summary(model))["scale(glmPupil)", "Pr(>|t|)"]
  list(beta = round(b, 3), p = signif(p, 3))
}

s1 <- get_stats(l1)
s2 <- get_stats(l2)
s3 <- get_stats(l3)

predict_ci <- function(model, newdata, confirm = FALSE) {
  X <- model.matrix(delete.response(terms(model)), newdata)
  beta <- fixef(model)
  V <- vcov(model)
  
  fit <- as.vector(X %*% beta)
  se  <- sqrt(diag(X %*% V %*% t(X)))
  
  newdata %>%
    mutate(
      fit = fit,
      lwr = fit - 1.96 * se,
      upr = fit + 1.96 * se
    )
}


new1_dat <- d1 %>%
  summarise(
    glmPupil = seq(min(glmPupil, na.rm = TRUE),
                     max(glmPupil, na.rm = TRUE),
                     length.out = 100)
  )

new2_dat <- d2 %>%
  summarise(
    glmPupil = seq(min(glmPupil, na.rm = TRUE),
                     max(glmPupil, na.rm = TRUE),
                     length.out = 100)
  )

new3_dat <- d3 %>%
  summarise(
    glmPupil = seq(min(glmPupil, na.rm = TRUE),
                     max(glmPupil, na.rm = TRUE),
                     length.out = 100)
  )

new1 <- predict_ci(l1, new1_dat)
new2 <- predict_ci(l2, new2_dat)
new3 <- predict_ci(l3, new3_dat)


# Plot
p_m2_pupil_c <- ggplot() +
  ## Model 1 -- black
  geom_ribbon(data = new1,
              aes(x = scale(glmPupil), ymin = lwr, ymax = upr),
              fill = "black", alpha = 0.15) +
  geom_line(data = new1,
            aes(x = scale(glmPupil), y = fit),
            color = "black", size = 1) +

  ## Model 2 -- purple
  geom_ribbon(data = new2,
              aes(x = scale(glmPupil), ymin = lwr, ymax = upr),
              fill = "purple", alpha = 0.15) +
  geom_line(data = new2,
            aes(x = scale(glmPupil), y = fit),
            color = "purple", size = 1) +

  ## Model 3 -- skyblue
  geom_ribbon(data = new3,
              aes(x = scale(glmPupil), ymin = lwr, ymax = upr),
              fill = "skyblue", alpha = 0.15) +
  geom_line(data = new3,
            aes(x = scale(glmPupil), y = fit),
            color = "skyblue", size = 1) +

  # Add beta + p-value text with < .001 formatting
  annotate("text", x = -1.5, y = max(new1$upr)+0.6, size=3.5,
           label = paste0("both (8s): β=", round(s1$beta,2), 
                          ", p", ifelse(s1$p < 0.001, "< .001", paste0("= ",round(s1$p, 3)))),
           color = "black", hjust = 0) +
  annotate("text", x = -1.5, y = max(new1$upr)+0.2, size=3.5,
           label = paste0("ant (8s): β=", round(s2$beta,2), 
                          ", p", ifelse(s2$p < 0.001, "< .001",paste0("= ",round(s2$p, 3)))),
           color = "purple", hjust = 0) +
  annotate("text", x = -1.5, y = max(new1$upr)+0.4, size=3.5,
           label = paste0("out (12s): β=", round(s3$beta,2), 
                          ", p", ifelse(s3$p < 0.001, "< .001", paste0("= ",round(s3$p, 3)))),
           color = "skyblue", hjust = 0)+
  labs(
    x = "similarity (scaled)",
    y = "Predicted arousal (scaled)"
  )
```


#### correlation with pupil size
```{r}
cor(my_array_s1 %>% 
      filter(threshold == 0.5) %>% 
      group_by(subject) %>% 
      mutate(pupil_lag2= lag(pupil,2))%>% 
      ungroup() %>% 
      select(glmPupil,glmArousal,pupil_lag2),use = "complete.obs")

# cor(my_array_s2 %>% 
#       filter(threshold == 1.5) %>% 
#       group_by(subject) %>% 
#       mutate(pupil_lag2= lag(pupil,2))%>% 
#       ungroup() %>% 
#       select(glmPupil,glmPupil_posonly,glmPupil,pupil_lag2),use = "complete.obs")

# continuous correlation
#the neural arousal index needs to be lagged for 3 TRs, and pupil 1TR. Thus, it's a relative lag of 2TRs.
summary(lmer(scale(glmPupil) ~ scale(pupil_lag2) + (1|split),my_array_s1 %>% 
              filter(threshold == 0.5) %>% 
          group_by(subject,split) %>% mutate(pupil_lag2= lag(pupil,2))))

# TR5 with the pre-defined window's pupil size
summary(lmer(scale(glmPupil) ~ scale(mean_pupil_nobc)+ (1|split),my_array_s1_ %>% 
              filter(threshold == 0.5,tr_in_trial == 4)))

corr_mat <- my_array_s1 %>%
  filter(threshold == 0.5) %>%
  group_by(subject) %>%
  mutate(pupil_lag2 = lag(pupil, 2)) %>%
  ungroup() %>%
  select(glmPupil, glmArousal, pupil_lag2) %>%
  cor(use = "complete.obs")

# Convert to long format for ggplot
corr_long <- reshape2::melt(corr_mat)

# Plot correlation heatmap
ggplot(corr_long, aes(Var1, Var2, fill = value)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(value, 2)), color = "black", size = 5) +
  scale_fill_gradient2(low = "blue", high = "red", mid = "white",
                       midpoint = 0, limit = c(-1, 1), name = "Correlation") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    panel.grid = element_blank()
  ) +
  coord_fixed() +
  labs(x = "", y = "", title = "Correlation Matrix (threshold = 0.5)")

ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/arousal_index_corr_s1.png"),dpi = 300, height = 5, width = 6)


corr_mat1 <- my_array_s1 %>%
  filter(threshold == 0.5,split == "run12") %>%
  group_by(subject) %>%
  mutate(pupil_lag2 = lag(pupil, 2)) %>%
  ungroup() %>%
  select(glmPupil, glmArousal, pupil_lag2) %>%
  cor(use = "complete.obs")
corr_mat2 <- my_array_s1 %>%
  filter(threshold == 0.5,split == "run34") %>%
  group_by(subject) %>%
  mutate(pupil_lag2 = lag(pupil, 2)) %>%
  ungroup() %>%
  select(glmPupil, glmArousal, pupil_lag2) %>%
  cor(use = "complete.obs")
# Convert to long format for ggplot
corr_long1 <- reshape2::melt(corr_mat1)
corr_long2 <- reshape2::melt(corr_mat2)
# Plot correlation heatmap
new_labels <- c("glm_pupil", "glm_arousal", "pupil_size")

ggplot(corr_long1, aes(Var1, Var2, fill = value)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(value, 2)), color = "black", size = 5) +
  scale_fill_gradient2(
    low = "blue", high = "red", mid = "white",
    midpoint = 0, limit = c(-1, 1), name = "Correlation"
  ) +
  scale_x_discrete(labels = new_labels) +
  scale_y_discrete(labels = new_labels) +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    panel.grid = element_blank()
  ) +
  coord_fixed() +
  labs(x = "", y = "", title = "Correlation Matrix (threshold = 0.5)",
       subtitle = "test 1st half")+


ggplot(corr_long2, aes(Var1, Var2, fill = value)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(value, 2)), color = "black", size = 5) +
  scale_fill_gradient2(
    low = "blue", high = "red", mid = "white",
    midpoint = 0, limit = c(-1, 1), name = "Correlation"
  ) +
  scale_x_discrete(labels = new_labels) +
  scale_y_discrete(labels = new_labels) +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    panel.grid = element_blank()
  ) +
  coord_fixed() +
  labs(x = "", y = "",
       subtitle = "test 2nd half")


ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/arousal_index_corr_s2_split.png"),dpi = 300, height = 5, width = 10)
```

```{r}
brain_img <- image_read("../../figures/brain_fig_a.png")

# Convert to raster
brain_raster <- as.raster(brain_img)

# Turn it into a ggplot object
p_brain <- ggplot() +
  annotation_raster(brain_raster, xmin = -Inf, xmax = Inf,
                    ymin = -Inf, ymax = Inf) +
  theme_void()
```

```{r}
p_brain/
(p1m2p)/
(p2m2p+p3m2p+p4m2p+p_m2_pupil_c+
  plot_layout(nrow=1,widths = c(1.2,1,1,1.2)))+
plot_annotation(title = "Pupil template",
                  tag_levels = "A")+
  plot_layout(heights = c(1.5,1,1))


ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig_glmPupil.png"),dpi = 300, height = 8.5, width = 10)
```

## based on midaffemo 2 (validation sample)
```{r}
fmri4_data_2probes <- read_csv("~/Desktop/VRMID-analysis/mid-pupil/data/fmri4/derivatives/fmri4_data_2probes.csv")

# demonstrate baseline association

summary(lmer(scale(mean_pupil_nobc) ~ scale(arousal_scaled) + (1|subject),fmri4_data_2probes %>% 
               filter(probe == 1)))

summary(lmer(scale(mean_pupil_nobc) ~ scale(arousal_scaled) + (1|subject),fmri4_data_2probes %>% 
               filter(probe == 2)))

summary(lm(scale(mean_pupil_nobc) ~ scale(arousal_scaled),fmri4_data_2probes))
```

### load fmri study 4
```{r}
fmri4_data_2probes <- read_csv("~/Desktop/VRMID-analysis/mid-pupil/data/fmri4/derivatives/fmri4_data_2probes.csv")

# demonstrate baseline association

summary(lmer(scale(mean_pupil_nobc) ~ scale(arousal_scaled) + (1|subject),fmri4_data_2probes %>% 
               filter(probe == 1)))

summary(lmer(scale(mean_pupil_nobc) ~ scale(arousal_scaled) + (1|subject),fmri4_data_2probes %>% 
               filter(probe == 2)))

summary(lm(scale(mean_pupil_nobc) ~ scale(arousal_scaled),fmri4_data_2probes))
```

### make dataframe of all similarities, all thresholds
```{r}
subjects_list<-read_delim('~/Desktop/midaffemo2/analyses/subjects-pupil-fmri.txt',delim = '\t', col_names = F)
thresh_str <- c("0","05","1","15","2","25","3","35")
thresh <- c(0,0.5,1,1.5,2,2.5,3,3.5)

glmArousal_array <- NULL
glmPupil_array <- NULL
glmPupil_posonly_array <- NULL
pupil_array <- NULL

for (t in 1:length(thresh_str)){
  filepath = paste0("~/Desktop/midaffemo2/glm_maps/glm27_array_templatefromstudy1_threshold",thresh_str[t],".csv")
  glmArousal_array<-rbind(glmArousal_array,
                          as.data.frame(t(read_csv(filepath, 
                                           col_names = F))) %>% 
                            mutate(type = "glmArousal", 
                                   tr = row_number(), 
                                   threshold = thresh[t]) #self-reported arousal GLM
  )
  
  filepath = paste0("~/Desktop/midaffemo2/glm_maps/glm33b_array_templatefromstudy1_threshold",thresh_str[t],".csv")
  glmPupil_array<-rbind(glmPupil_array,
                        as.data.frame(t(read_csv(filepath, 
             col_names = F))) %>% 
    mutate(type = "glmPupil", tr = row_number(), 
                                   threshold = thresh[t])) #pupil GLM
  
  filepath = paste0("~/Desktop/midaffemo2/glm_maps/glm33b_posonly_array_templatefromstudy1_threshold",thresh_str[t],".csv")
  glmPupil_posonly_array<-rbind(glmPupil_posonly_array,
                        as.data.frame(t(read_csv(filepath, 
             col_names = F))) %>% 
    mutate(type = "glmPupil_posonly", tr = row_number(), 
                                   threshold = thresh[t])) #pupil GLM
  
  pupil_array<-rbind(pupil_array,
                     as.data.frame(t(read_csv("~/Desktop/midaffemo2/glm_maps/pupil_array.csv", col_names = F))) %>% 
    mutate(type = "pupil", tr = row_number(), 
                                   threshold = thresh[t])) #pupil time series
}


my_array_s2<-Reduce(rbind,list(glmArousal_array,glmPupil_array,glmPupil_posonly_array,pupil_array))
names(my_array_s2) <- c(subjects_list$X1,"type","tr","threshold")
my_array_s2<-my_array_s2%>% 
  pivot_longer(ad241211:yc250206,names_to = "subject",values_to = "val") %>% 
  pivot_wider(names_from = type, values_from = val)

my_array_s2_ <- my_array_s2 %>% 
  mutate(pupil_lead10 = lead(pupil,10),
         pupil_lead9 = lead(pupil,9),
         pupil_lead8 = lead(pupil,8),
    pupil_lead7 = lead(pupil,7),
    pupil_lead6 = lead(pupil,6),
    pupil_lead5 = lead(pupil,5),
         pupil_lead4 = lead(pupil,4),
         pupil_lead3 = lead(pupil,3),
         pupil_lead2 = lead(pupil,2),
         pupil_lead1 = lead(pupil,1),
         pupil_lead0 = pupil,
         pupil_lag1 = lag(pupil,1),
         pupil_lag2 = lag(pupil,2),
         pupil_lag3 = lag(pupil,3),
         pupil_lag4 = lag(pupil,4),
         pupil_lag5 = lag(pupil,5),
         pupil_lag6 = lag(pupil,6),
         pupil_lag7 = lag(pupil,7),
         pupil_lag8 = lag(pupil,8),
         pupil_lag9 = lag(pupil,9),
         pupil_lag10 = lag(pupil,10),
         pupil_lag11 = lag(pupil,11),
         pupil_lag12 = lag(pupil,12))

df.1sub <- read_csv("~/Desktop/midaffemo2/data/timecourses/timecourses_b4_woOutliers_long.csv") %>% 
  filter(subject == "yc250206", voi == "nacc",coreg == "ants") %>% 
  mutate(trial_tr_noiti = ifelse(probe == 1, 9,8),
         trial_tr = trial_tr_noiti + iti/2) %>% 
  # select(trial,trial_tr,tr,run) %>% 
  filter(tr <= trial_tr)

end_run1 <- df.1sub %>%
  subset(trial == 24) %>%
  .[1:5,] %>%
  mutate(tr = tr + 10)

# create the 5 TRs at the tail of run 2
end_run2 <- df.1sub %>%
        filter(run == "run-02")%>%
        subset(trial == 48) %>%
        .[1:5,] %>%
        mutate(tr = tr + 9)

df.1sub <- df.1sub %>%
        # insert 5 rows at the end of each run
        add_row(end_run1, .after = 240) %>%
        add_row(end_run2, .after = 485)
      
df.1sub <- df.1sub %>% 
  mutate(block = as.numeric(substr(run,6,6))) %>% 
  mutate(tr = row_number())

my_array_s2 <- left_join(my_array_s2,df.1sub %>% 
                         select(trial:rating_t,time,tr,trial_tr)) %>% 
  group_by(subject,trial,threshold) %>% 
  mutate(tr_in_trial = row_number())%>% 
  relocate(tr_in_trial,.after = tr)%>%
  mutate(half = ifelse(trial >= 24,"second","first"))

my_array_s2$cue_value <- factor(my_array_s2$cue_value, levels = c("-$5","-$1","-$0","+$0","+$1","+$5"))
```

#### plot 1 example pupil sequence
```{r}
ggplot(my_array_s2 %>% 
         filter(subject == "ad241211",threshold == 0),
       aes(x = tr, y = glmPupil))+
  geom_line()+
  theme_void()

ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/example_pupil_glm.png"),dpi = 300, height = 1, width = 3)

```



### self-reported arousal template
```{r}
my_array_s2__ <- my_array_s2%>% 
  ungroup() %>% 
  select(trial,subject,tr_in_trial,glmArousal,trial_tr,threshold) %>% 
  pivot_wider(names_from = c(tr_in_trial), values_from = c(glmArousal), names_prefix = "glmArousal_TR_") %>% 
  arrange(subject,trial)

for (t in thresh){
  for (sub in unique(my_array_s2__$subject)){
    for(tr in 9:11){
      replace_idx = my_array_s2__$subject == sub & my_array_s2__$trial_tr == tr & my_array_s2__$threshold == t & is.na(my_array_s2__[,paste0("glmArousal_TR_",tr+1)])
      #early TRs were TRs from the previous trial
      my_array_s2__[replace_idx,paste0("glmArousal_TR_",(tr+1):TR_DELAY)] <- my_array_s2__[lag(replace_idx) %>% replace_na(FALSE),paste0("glmArousal_TR_",1:(TR_DELAY-tr))]
  } # tr loop
  }
}

TR_DELAY = 14
my_array_s2__ <- my_array_s2__ %>% mutate(glmArousal_TR_17 = NA, glmArousal_TR_18 = NA, glmArousal_TR_19 = NA, glmArousal_TR_20 = NA)

my_array_s2__<-left_join(my_array_s2__ %>% 
                        pivot_longer(glmArousal_TR_1:glmArousal_TR_20,
                                     names_to = "tr_in_trial",names_prefix = "glmArousal_TR_",
                                     values_to = "glmArousal"),fmri4_data_2probes,
                      by = c("subject","trial")) %>% 
  filter(tr <= 975)%>%
  mutate(half = ifelse(trial >= 24,"second","first"))%>% #last bit was interpolated
  mutate(probe = ifelse(probe == 1, "anticipation probe","outcome probe"))

my_array_s2__ <- my_array_s2__ %>% 
  mutate(tr_in_trial = as.numeric(tr_in_trial),
         time = (tr_in_trial-1) * 2)
```


## plot as function of cue value / outcome value
```{r}
d1<-my_array_s2__ %>% 
         filter(!is.na(hit)) %>% 
         group_by(tr_in_trial,subject,threshold,probe) %>% 
         summarise(glmArousal = mean(glmArousal,na.rm = T)) %>% 
         group_by(tr_in_trial,threshold,probe) %>% 
         summarise(mean = mean(glmArousal,na.rm = T),
                   se = sd(glmArousal,na.rm = T)/sqrt(n())) %>% 
  filter(tr_in_trial <= 14)

p1m2a<-ggplot(d1 %>% filter(probe == "anticipation probe",threshold == 0.5),
       aes(x = tr_in_trial, y = mean))+
  geom_vline(xintercept = c(3.5,4.5,5.5,9.5,10.5,11.5,12.5), size = 1, color = "grey")+
  annotate("text",x = 4, y = 0.05, label = "C")+
  annotate("text",x = 5, y = 0.05, label = "F")+
  annotate("text",x = 10, y = 0.05, label = "F")+
  annotate("text",x = 11, y = 0.05, label = "T")+
  annotate("text",x = 12, y = 0.05, label = "O")+
  annotate("text",x = 7.5, y = 0.05, label = "R")+
  geom_line(size = 0.5) +
  geom_point()+
  geom_errorbar(aes(x = tr_in_trial, ymin = mean-se,ymax = mean+se), width = 0.3)+
  labs(y = "Simalirty",
       x = "time (s)",
       subtitle = "anticipation probe")+
  scale_color_manual(values = redOrange_palette6)+
  theme(legend.position = "top")+
  ylim(-0.1,0.1)+
  scale_x_continuous(breaks = seq(1,15,5),labels = seq(1,28,10))+
ggplot(d1 %>% filter(probe == "outcome probe",threshold == 0.5),
       aes(x = tr_in_trial, y = mean))+
  geom_vline(xintercept = c(3.5,4.5,5.5,6.5,7.5,11.5), size = 1, color = "grey")+
  annotate("text",x = 4, y = 0.05, label = "C")+
  annotate("text",x = 5, y = 0.05, label = "F")+
  annotate("text",x = 6, y = 0.05, label = "T")+
  annotate("text",x = 7, y = 0.05, label = "O")+
  annotate("text",x = 10, y = 0.05, label = "R")+
  geom_line(size = 0.5) +
  geom_point()+
  geom_errorbar(aes(x = tr_in_trial, ymin = mean-se,ymax = mean+se), width = 0.3)+
  labs(y = "Simalirty",
       x = "time (s)",
       subtitle = "outcome probe",
      caption = "C = Cue, F = Fixation, \nT = Target, O = Outcome, R = Rating")+
  scale_color_manual(values = redOrange_palette6)+
  theme(legend.position = "top")+
  ylim(-0.1,0.1)+
  scale_x_continuous(breaks = seq(1,15,5),labels = seq(0,28,10))

d2<-my_array_s2__ %>% 
         filter(!is.na(hit),
                tr_in_trial == 5) %>% 
         group_by(subject,threshold,cue_value) %>% 
         summarise(glmArousal = mean(glmArousal,na.rm = T)) %>% 
         group_by(threshold,cue_value) %>% 
         summarise(mean = mean(glmArousal,na.rm = T),
                   se = sd(glmArousal,na.rm = T)/sqrt(n())) %>% 
  mutate(cue_value = factor(cue_value, levels = c("-$5","-$1","-$0","+$0","+$1","+$5")))

summary(l1<-lm(scale(glmArousal) ~ cue_value,
                   my_array_s2__ %>% 
                   filter(tr_in_trial == 5, threshold == 0.5)))

# Get effect size (standardized beta)
r2   <- summary(l1)$r.squared

p2m2a<-ggplot(d2 %>% filter(threshold == 0.5),
       aes(x = cue_value, y = mean,color = cue_value))+
  geom_point(size = 0.5) +
  geom_point()+
  geom_errorbar(aes(x = cue_value, ymin = mean-se,ymax = mean+se), width = 0.3)+
  labs(y = "Simalirty",
       x = "time (s)",
       subtitle = "Inferred arousal (8s)")+
  scale_color_manual(values = redOrange_palette6)+
  theme(legend.position = "none")+  # show shape legend
  scale_x_discrete(breaks =c("-$5","-$1","-$0","+$0","+$1","+$5"))+
  annotate("text",x = Inf, y = -Inf, label = paste0("R² = ", round(r2, 2)),
    hjust = 1.1, vjust = -1.5, size = 4)

d3<-my_array_s2__ %>% 
         filter(!is.na(hit),
                ifelse(probe == "anticipation probe", tr_in_trial == 12,
                       ifelse(probe == "outcome probe",tr_in_trial == 7,NA))) %>% 
         group_by(subject,threshold,hit,cue_value) %>% 
         summarise(glmArousal = mean(glmArousal,na.rm = T)) %>% 
         group_by(threshold,hit,cue_value) %>% 
         summarise(mean = mean(glmArousal,na.rm = T),
                   se = sd(glmArousal,na.rm = T)/sqrt(n())) %>% 
  mutate(hit = factor(hit, levels = c(0,1), labels = c("Miss","Hit")))%>% 
  mutate(cue_value = factor(cue_value, levels = c("-$5","-$1","-$0","+$0","+$1","+$5")))

ggplot(d3 %>% filter(threshold == 0.5),
       aes(x = cue_value, y = mean, color = cue_value, shape = hit)) +
  geom_point(position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(x = cue_value, group = hit, ymin = mean - se, ymax = mean + se),
                width = 0.3, position = position_dodge(width = 0.5)) +
  labs(y = "Similarity",
       x = "time (s)",
       subtitle = "arousal index during outcome") +
  theme(legend.position = "top") +
  scale_color_manual(values = redOrange_palette6) +
  guides(color = "none",  # hide color legend
         shape = guide_legend())+  # show shape legend
  scale_x_discrete(breaks =c("-$5","-$1","-$0","+$0","+$1","+$5"))

summary(l2<-lm(glmArousal~cue_value*hit,my_array_s2__ %>% filter(ifelse(
  probe == "anticipation probe", tr_in_trial == 12,
                       ifelse(probe == "outcome probe",tr_in_trial == 7,NA)))))
anova(l2)
```

#### predicting performance
```{r warning=F}
df_performance <- NULL
for (t in thresh){
  for (tr in 1:14){
    l1<-summary(glm(hit_num ~ scale(glmArousal),family = binomial,
                    my_array_s2__ %>% 
                      filter(tr_in_trial == tr,threshold == t, probe == "anticipation probe") %>% 
                      mutate(hit_num = as.factor(hit == 1))))
    
    l2<-summary(glm(hit_num ~ scale(glmArousal),family = binomial,
                    my_array_s2__ %>% 
                      filter(tr_in_trial == tr,threshold == t, probe == "outcome probe") %>% 
                      mutate(hit_num = as.factor(hit == 1))))
  
    df_performance <- rbind(df_performance,
                          l1$coefficients[2,],
                          l2$coefficients[2,])
  }
  
}

df_performance <- as.data.frame(df_performance)
df_performance$probe <- rep(c("anticipation","outcome"), length(thresh))
df_performance$threshold <- rep(thresh, each = 2*14)
df_performance$tr <- rep(rep(1:14,each=2),2)

ggplot(df_performance, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  facet_wrap(~threshold)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

ggplot(df_performance %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

summary(l1<-glm(hit_num ~ scale(glmArousal),family = binomial,
                    my_array_s2__ %>% 
                      filter(tr_in_trial == 5,threshold == 0.5) %>% 
                      mutate(hit_num = as.factor(hit == 1))))

# Get effect size (standardized beta)
beta <- summary(l1)$coefficients["scale(glmArousal)", "Estimate"]
r2   <- pscl::pR2(l1)["McFadden"]

# Create base plot
p3m2a <- plot_model(l1, type = "pred", terms = "glmArousal",color = "darkgrey") +
  labs(x = "similarity (z-score)",
       y = "p(hit)",title = "p(hit)") +
  annotate("text",x = Inf, y = -Inf, label = paste0("β = ", round(beta, 2), "\npseudo-R² = ", round(r2, 2)),
    hjust = 1.1, vjust = -0.5, size = 4)

```

```{r warning=F}
df_performance <- NULL

for (t in thresh){
  for (tr in 1:14){
    l1<-summary(lm(scale(rt) ~ scale(glmArousal),
                   my_array_s2__ %>% 
                   filter(tr_in_trial == tr, hit == 1,threshold == t, probe == "anticipation probe")))
    
    l2<-summary(lm(scale(rt) ~ scale(glmArousal),
                   my_array_s2__ %>% 
                   filter(tr_in_trial == tr, hit == 1,threshold == t, probe == "outcome probe")))
  
    df_performance <- rbind(df_performance,
                          l1$coefficients[2,],
                          l2$coefficients[2,])
  }
  
}

df_performance <- as.data.frame(df_performance)
df_performance$probe <- rep(c("anticipation","outcome"), length(thresh))
df_performance$threshold <- rep(thresh, each = 2*14)
df_performance$tr <- rep(rep(1:14,each=2),2)

ggplot(df_performance, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  facet_wrap(~threshold)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

ggplot(df_performance %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

summary(l1<-lm(scale(rt) ~ scale(glmArousal),
                   my_array_s2__ %>% 
                   filter(tr_in_trial == 5, hit == 1,threshold == 0.5)))

# Get effect size (standardized beta)
beta <- summary(l1)$coefficients["scale(glmArousal)", "Estimate"]
r2   <- summary(l1)$r.squared

# Create base plot
p4m2a <- plot_model(l1, type = "pred", terms = "glmArousal",color = "darkgrey") +
  labs(x = "similarity (z-score)",
    y = "rt (z-score)",
    title = "rt (hit trials)"
  ) +
  annotate("text",x = Inf, y = -Inf, label = paste0("β = ", round(beta, 2), "\nR² = ", round(r2, 2)),
    hjust = 1.1, vjust = -1.5, size = 4)

```


#### predicting cue value (abs)
```{r warning=F}
df_cue <- NULL
for (t in thresh){
  for (tr in 1:14){
    l1<-summary(lm(cue_value_abs ~ scale(glmArousal),
                    my_array_s2__ %>% 
                      filter(tr_in_trial == tr,threshold == t, probe == "anticipation probe") %>% 
                      mutate(cue_value_abs = ifelse(cue_value %in% c("+$5","-$5"),5,
                                                    ifelse(cue_value %in% c("+$1","-$1"),1,
                                                           ifelse(cue_value %in% 
                                                                    c("+$0","-$0"),1,NA))))))
    
    l2<-summary(lm(cue_value_abs ~ scale(glmArousal),
                    my_array_s2__ %>% 
                      filter(tr_in_trial == tr,threshold == t, probe == "outcome probe") %>% 
                      mutate(cue_value_abs = ifelse(cue_value %in% c("+$5","-$5"),5,
                                                    ifelse(cue_value %in% c("+$1","-$1"),1,
                                                           ifelse(cue_value %in% 
                                                                    c("+$0","-$0"),1,NA))))))
  
    df_cue <- rbind(df_cue,
                          l1$coefficients[2,],
                          l2$coefficients[2,])
  }
  
}

df_cue <- as.data.frame(df_cue)
df_cue$probe <- rep(c("anticipation","outcome"), length(thresh))
df_cue$threshold <- rep(thresh, each = 2*14)
df_cue$tr <- rep(rep(1:14,each=2),2)

ggplot(df_cue, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  facet_wrap(~threshold)+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

ggplot(df_cue %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

summary(l1<-lm(scale(cue_value_abs) ~ scale(glmArousal),
                    my_array_s2__ %>% 
                      filter(tr_in_trial == 5,threshold == 0.5) %>% 
                      mutate(cue_value_abs = ifelse(cue_value %in% c("+$5","-$5"),5,
                                                    ifelse(cue_value %in% c("+$1","-$1"),1,
                                                           ifelse(cue_value %in% 
                                                                    c("+$0","-$0"),1,NA))))))

# Get effect size (standardized beta)
beta <- summary(l1)$coefficients["scale(glmArousal)", "Estimate"]
r2   <- summary(l1)$r.squared

# Create base plot
p5m2a <- plot_model(l1, type = "pred", terms = "glmArousal") +
  labs(x = "similarity to arousal template (z-score)",
    y = "abs. cue value (z-score)",
    title = "abs. cue value (z-score)"
  ) +
  annotate("text",x = Inf, y = -Inf, label = paste0("β = ", round(beta, 2), ", R² = ", round(r2, 2)),
    hjust = 1.1, vjust = -1.5, size = 4)
```

#### predicting self-reports
```{r}
df_rating <- NULL
for (t in thresh){
  for (tr in 1:14){
    l1<-summary(lm(scale(arousal_scaled) ~ scale(glmArousal),
                    my_array_s2__ %>% 
                      filter(tr_in_trial == tr,threshold == t, probe == "anticipation probe")))
    l2<-summary(lm(scale(arousal_scaled) ~ scale(glmArousal),
                   my_array_s2__ %>% 
                   filter(tr_in_trial == tr,threshold == t, probe == "outcome probe")))
  
    df_rating <- rbind(df_rating,
                          l1$coefficients[2,],
                          l2$coefficients[2,])
  }
  
}

df_rating <- as.data.frame(df_rating)
df_rating$probe <- rep(c("anticipation","outcome"), length(thresh))
df_rating$threshold <- rep(thresh, each = 2*14)
df_rating$tr <- rep(rep(1:14,each=2),2)

ggplot(df_rating, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  geom_ribbon(aes(x = tr, ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`,fill = probe),
              alpha = 0.1)+
  facet_wrap(~threshold)+
  labs(title = "FMRI study")+
  scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  scale_x_continuous(breaks = 1:14)+
  geom_vline(xintercept = 5, color = "purple",label = "F")+
  geom_vline(xintercept = 6, color = "skyblue",label = "T")+
  geom_vline(xintercept = 7, color = "purple", linetype = "dashed")+
  geom_vline(xintercept = 9, color = "skyblue", linetype = "dashed")

ggplot(df_rating %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)
```

#### visualize peak correlation
```{r}
coefs1 = NULL
for (t in 1:14){
  l1<-summary(lm(scale(glmArousal) ~ scale(arousal_scaled),my_array_s2__ %>% filter(tr_in_trial == t, probe == "anticipation probe", threshold == 0.5)))
  coefs1 <- rbind(coefs1,l1$coefficients[2,])
}
coefs1<-as.data.frame(coefs1)
coefs1$TR <- 1:14
coefs1$probe = "anticipation probe"

coefs2 = NULL
for (t in 1:14){
  l1<-summary(lm(scale(glmArousal) ~ scale(arousal_scaled),my_array_s2__ %>% filter(tr_in_trial == t, probe == "outcome probe", threshold == 0.5)))
  coefs2 <- rbind(coefs2,l1$coefficients[2,])
}
coefs2<-as.data.frame(coefs2)
coefs2$TR <- 1:14
coefs2$probe = "outcome probe"

coefs <- rbind(coefs1,coefs2) %>% 
  mutate(sig = ifelse(`Pr(>|t|)` >= 0.05, "",
                      ifelse(`Pr(>|t|)` >= 0.01, "*",
                             ifelse(`Pr(>|t|)` >= 0.001, "**","***"))))

p_m2_arousal_a<-ggplot(coefs %>% filter(probe == "anticipation probe"),aes(x = TR, y =Estimate))+
  geom_hline(yintercept = 0, linetype = "dashed")+
  geom_vline(xintercept = c(3.5,4.5,5.5,9.5,10.5,11.5,12.5), size = 1, color = "grey")+
  annotate("text",x = 4, y = 0.05, label = "C")+
  annotate("text",x = 5, y = 0.05, label = "F")+
  annotate("text",x = 10, y = 0.05, label = "F")+
  annotate("text",x = 11, y = 0.05, label = "T")+
  annotate("text",x = 12, y = 0.05, label = "O")+
  annotate("text",x = 7.5, y = 0.05, label = "R")+
  scale_x_continuous(breaks = seq(0,14,2), labels = seq(0,28,4))+
  scale_color_manual(values = c("purple"))+
  scale_fill_manual(values = c("purple"))+
  geom_line(aes(color = probe), size = 2, alpha = 0.5)+
  geom_ribbon(aes(fill = probe, ymin = Estimate - `Std. Error`,
                  ymax = Estimate + `Std. Error`), alpha = 0.1)+
  geom_line(aes(color = probe), size = 2, alpha = 0.5)+
  geom_segment(aes(x = 7, y = 0.15,
                   xend =7, yend = 0.1),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  annotate("text",x = 7, y = 0.16, label ="arousal rating")+
  geom_text(aes(x = TR, y = Estimate+0.01, label = sig, color = probe))+
  labs(x = "time (s)",
       y = "Correlation with arousal ratings",
       title = "Regression weights on arousal",
       subtitle = "anticipation probe")+
  theme(legend.position = "none")+
  theme(legend.position = "none")+
  annotation_custom(
    grob = grid::rectGrob(gp = grid::gpar(fill = "white", alpha = 1, col = NA)),
    xmin = 9.6, xmax = 15, ymin = -Inf, ymax = Inf
  )

p_m2_arousal_b<-ggplot(coefs%>% filter(probe == "outcome probe"),aes(x = TR, y =Estimate))+
  geom_hline(yintercept = 0, linetype = "dashed")+
  geom_vline(xintercept = c(3.5,4.5,5.5,6.5,7.5), size = 1, color = "grey")+
  annotate("text",x = 4, y = 0.05, label = "C")+
  annotate("text",x = 5, y = 0.05, label = "F")+
  annotate("text",x = 6, y = 0.05, label = "T")+
  annotate("text",x = 7, y = 0.05, label = "O")+
  annotate("text",x = 10, y = 0.05, label = "R")+
  scale_x_continuous(breaks = seq(0,14,2), labels = seq(0,28,4))+
  scale_color_manual(values = c("skyblue"))+
  scale_fill_manual(values = c("skyblue"))+
  geom_line(aes(color = probe), size = 2, alpha = 0.5)+
  geom_ribbon(aes(fill = probe, ymin = Estimate - `Std. Error`,
                  ymax = Estimate + `Std. Error`), alpha = 0.1)+
  geom_line(aes(color = probe), size = 2, alpha = 0.5)+
  geom_segment(aes(x = 10, y = 0.17,
                   xend =10, yend = 0.12),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  annotate("text",x = 10, y = 0.18, label ="arousal rating")+
  geom_segment(aes(x = 10, y = 0.17,
                   xend =10, yend = 0.12),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  annotate("text",x = 10, y = 0.18, label ="arousal rating")+
  geom_text(aes(x = TR, y = Estimate+0.01, label = sig, color = probe))+
  labs(x = "time (s)",
       subtitle = "outcome probe")+
  theme(legend.position = "none")

p_m2_arousal_a+p_m2_arousal_b

# Prepare data
d1 <- my_array_s2__ %>% filter(tr_in_trial == 5, threshold == 0.5)
d2 <- my_array_s2__ %>% filter(tr_in_trial == 5, probe == "anticipation probe", threshold == 0.5)
d3 <- my_array_s2__ %>% filter(tr_in_trial == 7, probe == "outcome probe", threshold == 0.5)

# Fit models
l1 <- lm(scale(arousal_scaled) ~ scale(glmArousal), d1)
l2 <- lm(scale(arousal_scaled) ~ scale(glmArousal), d2)
l3 <- lm(scale(arousal_scaled) ~ scale(glmArousal), d3)
# Extract coefficients and p-values
get_stats <- function(model) {
  b <- coef(summary(model))["scale(glmArousal)", "Estimate"]
  p <- coef(summary(model))["scale(glmArousal)", "Pr(>|t|)"]
  list(beta = round(b, 3), p = signif(p, 3))
}

s1 <- get_stats(l1)
s2 <- get_stats(l2)
s3 <- get_stats(l3)

# Create prediction data with CI ribbons
make_pred_df <- function(data, model) {
  new <- data.frame(glmArousal = seq(min(data$glmArousal, na.rm = TRUE),
                                     max(data$glmArousal, na.rm = TRUE),
                                     length.out = 100))
  preds <- predict(model, newdata = new, interval = "confidence")
  new$fit <- preds[, "fit"]
  new$lwr <- preds[, "lwr"]
  new$upr <- preds[, "upr"]
  new
}

new1 <- make_pred_df(d1, l1)
new2 <- make_pred_df(d2, l2)
new3 <- make_pred_df(d3, l3)

# Plot
p_m2_arousal_c <- ggplot() +
  ## Model 1 -- black
  geom_ribbon(data = new1,
              aes(x = scale(glmArousal), ymin = lwr, ymax = upr),
              fill = "black", alpha = 0.15) +
  geom_line(data = new1,
            aes(x = scale(glmArousal), y = fit),
            color = "black", size = 1) +

  ## Model 2 -- purple
  geom_ribbon(data = new2,
              aes(x = scale(glmArousal), ymin = lwr, ymax = upr),
              fill = "purple", alpha = 0.15) +
  geom_line(data = new2,
            aes(x = scale(glmArousal), y = fit),
            color = "purple", size = 1) +

  ## Model 3 -- skyblue
  geom_ribbon(data = new3,
              aes(x = scale(glmArousal), ymin = lwr, ymax = upr),
              fill = "skyblue", alpha = 0.15) +
  geom_line(data = new3,
            aes(x = scale(glmArousal), y = fit),
            color = "skyblue", size = 1) +

  ## Add beta + p-value text
  annotate("text", x = -1.5, y = max(new1$upr)-0.3, size=3,
           label = paste0("both: β=", round(s1$beta,2), ", p=", s1$p),
           color = "black", hjust = 0) +
  annotate("text", x = -1.5, y = max(new1$upr),size=3,
           label = paste0("ant (8s): β=", round(s2$beta,2), ", p=", s2$p),
           color = "purple", hjust = 0) +
  annotate("text", x = -1.5, y = max(new1$upr)-0.15,size=3,
           label = paste0("out (12s): β=", round(s3$beta,2), ", p=", s3$p),
           color = "skyblue", hjust = 0) +

  labs(
    x = "similarity (scaled)",
    y = "Predicted arousal (scaled)"
  )
```

```{r}
(p1m2a)/
(p2m2a+p3m2a+p4m2a+p_m2_arousal_c+plot_layout(widths = c(1.2,1,1,1.2)))+
plot_annotation(title = "Arousal template",
                  tag_levels = "A")

ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig_glmArousal.png"),dpi = 300, height = 6, width = 11)
```
#### does it change with fatigue?
```{r}
summary(lmer(glmArousal~trial+(1|subject),my_array_s2__))
```

### pupil glm template
```{r}
my_array_s2_ <- my_array_s2%>% 
  ungroup() %>% 
  select(trial,subject,tr_in_trial,glmPupil,trial_tr,threshold) %>% 
  pivot_wider(names_from = c(tr_in_trial), values_from = c(glmPupil), names_prefix = "glmPupil_TR_") %>% 
  arrange(subject,trial)

for (t in thresh){
  for (sub in unique(my_array_s2_$subject)){
    for(tr in 9:11){
      replace_idx = my_array_s2_$subject == sub & my_array_s2_$trial_tr == tr & my_array_s2_$threshold == t & is.na(my_array_s2_[,paste0("glmPupil_TR_",tr+1)])
      #early TRs were TRs from the previous trial
      my_array_s2_[replace_idx,paste0("glmPupil_TR_",(tr+1):TR_DELAY)] <- my_array_s2_[lag(replace_idx) %>% replace_na(FALSE),paste0("glmPupil_TR_",1:(TR_DELAY-tr))]
  } # tr loop
  }
}

TR_DELAY = 14
my_array_s2_ <- my_array_s2_ %>% mutate(glmPupil_TR_17 = NA, glmPupil_TR_18 = NA, glmPupil_TR_19 = NA, glmPupil_TR_20 = NA)

my_array_s2_<-left_join(my_array_s2_ %>% 
                        pivot_longer(glmPupil_TR_1:glmPupil_TR_20,
                                     names_to = "tr_in_trial",names_prefix = "glmPupil_TR_",
                                     values_to = "glmPupil"),fmri4_data_2probes,
                      by = c("subject","trial")) %>% 
  filter(tr <= 975)%>%
  mutate(half = ifelse(trial >= 48,"second","first"))%>% #last bit was interpolated
  mutate(probe = ifelse(probe == 1, "anticipation probe","outcome probe"))

my_array_s2_ <- my_array_s2_ %>% 
  mutate(tr_in_trial = as.numeric(tr_in_trial),
         time = (tr_in_trial-1) * 2)
```

#### diffentiating cue vs. outcome
```{r}
d1<-my_array_s2_ %>% 
         filter(!is.na(hit)) %>% 
         group_by(tr_in_trial,subject,threshold,probe) %>% 
         summarise(glmPupil = mean(glmPupil,na.rm = T)) %>% 
         group_by(tr_in_trial,threshold,probe) %>% 
         summarise(mean = mean(glmPupil,na.rm = T),
                   se = sd(glmPupil,na.rm = T)/sqrt(n())) %>% 
  filter(tr_in_trial <= 14)

p1m2p<-ggplot(d1 %>% filter(probe == "anticipation probe",threshold == 0.5),
       aes(x = tr_in_trial, y = mean))+
  geom_vline(xintercept = c(3.5,4.5,5.5,9.5,10.5,11.5,12.5), size = 1, color = "grey")+
  annotate("text",x = 4, y = 0.05, label = "C")+
  annotate("text",x = 5, y = 0.05, label = "F")+
  annotate("text",x = 10, y = 0.05, label = "F")+
  annotate("text",x = 11, y = 0.05, label = "T")+
  annotate("text",x = 12, y = 0.05, label = "O")+
  annotate("text",x = 7.5, y = 0.05, label = "R")+
  geom_line(size = 0.5) +
  geom_point()+
  geom_errorbar(aes(x = tr_in_trial, ymin = mean-se,ymax = mean+se), width = 0.3)+
  labs(y = "Simalirty",
       x = "time (s)",
       subtitle = "anticipation probe")+
  scale_color_manual(values = redOrange_palette6)+
    scale_x_continuous(breaks = seq(0,14,2), labels = seq(0,28,4))+
  theme(legend.position = "top")+
  ylim(-0.1,0.1)+
ggplot(d1 %>% filter(probe == "outcome probe",threshold == 0.5),
       aes(x = tr_in_trial, y = mean))+
  geom_vline(xintercept = c(3.5,4.5,5.5,6.5,7.5,11.5), size = 1, color = "grey")+
  annotate("text",x = 4, y = 0.05, label = "C")+
  annotate("text",x = 5, y = 0.05, label = "F")+
  annotate("text",x = 6, y = 0.05, label = "T")+
  annotate("text",x = 7, y = 0.05, label = "O")+
  annotate("text",x = 10, y = 0.05, label = "R")+
    scale_x_continuous(breaks = seq(0,14,2), labels = seq(0,28,4))+
  geom_line(size = 0.5) +
  geom_point()+
  geom_errorbar(aes(x = tr_in_trial, ymin = mean-se,ymax = mean+se), width = 0.3)+
  labs(y = "Simalirty",
       x = "time (s)",
       subtitle = "outcome probe",
      caption = "C = Cue, F = Fixation, \nT = Target, O = Outcome, R = Rating")+
  scale_color_manual(values = redOrange_palette6)+
  theme(legend.position = "top")+
  ylim(-0.1,0.1)

d2<-my_array_s2_ %>% 
         filter(!is.na(hit),
                tr_in_trial == 5) %>% 
         group_by(subject,threshold,cue_value) %>% 
         summarise(glmPupil = mean(glmPupil,na.rm = T)) %>% 
         group_by(threshold,cue_value) %>% 
         summarise(mean = mean(glmPupil,na.rm = T),
                   se = sd(glmPupil,na.rm = T)/sqrt(n())) %>% 
  mutate(cue_value = factor(cue_value,levels = c("-$5","-$1","-$0","+$0","+$1","+$5")))

summary(l1<-lm(glmPupil~cue_value,my_array_s2_ %>% filter(tr_in_trial == 5)))
anova(l1)
r2   <- summary(l1)$r.squared

p2m2p<-ggplot(d2 %>% filter(threshold == 0.5),
       aes(x = cue_value, y = mean,color = cue_value))+
  geom_point(size = 0.5) +
  geom_point()+
  geom_errorbar(aes(x = cue_value, ymin = mean-se,ymax = mean+se), width = 0.3)+
  labs(y = "Simalirty",
       x = "time (s)",
       subtitle = "Inferred arousal (8s)")+
  scale_color_manual(values = redOrange_palette6)+
  theme(legend.position = "none")+  # show shape legend
  scale_x_discrete(breaks =c("-$5","-$1","-$0","+$0","+$1","+$5"))+
  annotate("text",x = Inf, y = -Inf, label = paste0("R² = ", round(r2, 3)),
    hjust = 1.1, vjust = -1.5, size = 4)# Get effect size (standardized beta)

d3<-my_array_s2_ %>% 
         filter(!is.na(hit),
                ifelse(probe == "anticipation probe", tr_in_trial == 12,
                       ifelse(probe == "outcome probe",tr_in_trial == 7,NA))) %>% 
         group_by(subject,threshold,hit,cue_value) %>% 
         summarise(glmPupil = mean(glmPupil,na.rm = T)) %>% 
         group_by(threshold,hit,cue_value) %>% 
         summarise(mean = mean(glmPupil,na.rm = T),
                   se = sd(glmPupil,na.rm = T)/sqrt(n())) %>% 
  mutate(hit = factor(hit, levels = c(0,1), labels = c("Miss","Hit")))%>% 
  mutate(cue_value = factor(cue_value,levels = c("-$5","-$1","-$0","+$0","+$1","+$5")))

ggplot(d3 %>% filter(threshold == 0.5),
       aes(x = cue_value, y = mean, color = cue_value, shape = hit)) +
  geom_point(position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(x = cue_value, group = hit, ymin = mean - se, ymax = mean + se),
                width = 0.3, position = position_dodge(width = 0.5)) +
  labs(y = "Similarity to self-report template",
       x = "time (s)",
       subtitle = "arousal index during outcome") +
  theme(legend.position = "top") +
  scale_color_manual(values = redOrange_palette6) +
  guides(color = "none",  # hide color legend
         shape = guide_legend())+  # show shape legend
  scale_x_discrete(breaks =c("-$5","-$1","-$0","+$0","+$1","+$5"))

summary(l2<-lm(glmPupil~cue_value*hit,my_array_s2_ %>% filter(ifelse(
  probe == "anticipation probe", tr_in_trial == 12,
                       ifelse(probe == "outcome probe",tr_in_trial == 7,NA)))))
anova(l2)
r2   <- summary(l2)$r.squared
```

#### predicting performance
```{r warning=F}
df_performance <- NULL
for (t in thresh){
  for (tr in 1:14){
    l1<-summary(glm(hit_num ~ scale(glmPupil),family = binomial,
                    my_array_s2_ %>% 
                      filter(tr_in_trial == tr,threshold == t, probe == "anticipation probe") %>% 
                      mutate(hit_num = as.factor(hit == 1))))
    
    l2<-summary(glm(hit_num ~ scale(glmPupil),family = binomial,
                    my_array_s2_ %>% 
                      filter(tr_in_trial == tr,threshold == t, probe == "outcome probe") %>% 
                      mutate(hit_num = as.factor(hit == 1))))
  
    df_performance <- rbind(df_performance,
                          l1$coefficients[2,],
                          l2$coefficients[2,])
  }
  
}

df_performance <- as.data.frame(df_performance)
df_performance$probe <- rep(c("anticipation","outcome"), length(thresh))
df_performance$threshold <- rep(thresh, each = 2*14)
df_performance$tr <- rep(rep(1:14,each=2),2)

ggplot(df_performance, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  facet_wrap(~threshold)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)


ggplot(df_performance %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

summary(l1<-glm(hit_num ~ scale(glmPupil),family = binomial,
                    my_array_s2_ %>% 
                      filter(tr_in_trial == 5,threshold == 0.5) %>% 
                      mutate(hit_num = as.factor(hit == 1))))

# Get effect size (standardized beta)
beta <- summary(l1)$coefficients["scale(glmPupil)", "Estimate"]
r2   <- pscl::pR2(l1)["McFadden"]

# Create base plot
p3m2p <- plot_model(l1, type = "pred", terms = "glmPupil",color = "darkgrey") +
  labs(x = "similarity (z-score)",
       y = "p(hit)",title = "p(hit)") +
  annotate("text",x = Inf, y = -Inf, label = paste0("β = ", round(beta, 2), "\npseudo-R² = ", round(r2, 2)),
    hjust = 1.1, vjust = -0.5, size = 4)
```
### predictive performance
```{r}
# Subset the data exactly as used in your model
data_used <- my_array_ %>%
  filter(tr_in_trial == 5, threshold == 0.5) %>%
  mutate(hit_num = as.factor(hit == 1))

# Keep only rows with no missing values in the predictors or outcome
data_used <- data_used[complete.cases(data_used[, c("glmPupil", "hit_num")]), ]

# Predicted probabilities
pred_probs <- predict(l1, newdata = data_used, type = "response")

# Convert probabilities to predicted classes
pred_class <- ifelse(pred_probs > 0.5, 1, 0)

# Actual classes
actual_class <- as.numeric(data_used$hit_num)-1

# Accuracy
accuracy <- mean(pred_class == actual_class,na.rm=T)
accuracy

# Confusion matrix
table(Predicted = pred_class, Actual = actual_class)

# Optional: AUC
library(pROC)
roc_obj <- roc(actual_class, pred_probs)
auc(roc_obj)

# Bootstrap test for AUC > 0.5
set.seed(777)
ci <- ci.auc(roc_obj, method = "bootstrap", boot.n = 2000) # 95% CI
ci  # If the lower bound > 0.5, AUC is significantly above chance

```


```{r warning=F}
df_performance <- NULL

for (t in thresh){
  for (tr in 1:14){
    l1<-summary(lm(scale(rt) ~ scale(glmPupil),
                   my_array_s2_ %>% 
                   filter(tr_in_trial == tr, hit == 1,threshold == t, probe == "anticipation probe")))
    
    l2<-summary(lm(scale(rt) ~ scale(glmPupil),
                   my_array_s2_ %>% 
                   filter(tr_in_trial == tr, hit == 1,threshold == t, probe == "outcome probe")))
  
    df_performance <- rbind(df_performance,
                          l1$coefficients[2,],
                          l2$coefficients[2,])
  }
  
}

df_performance <- as.data.frame(df_performance)
df_performance$probe <- rep(c("anticipation","outcome"), length(thresh))
df_performance$threshold <- rep(thresh, each = 2*14)
df_performance$tr <- rep(rep(1:14,each=2),2)

ggplot(df_performance, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  facet_wrap(~threshold)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

ggplot(df_performance %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

summary(l1<-lm(scale(rt) ~ scale(glmPupil),
                   my_array_s2_ %>% 
                   filter(tr_in_trial == 5, hit == 1,threshold == 0.5)))

# Get effect size (standardized beta)
beta <- summary(l1)$coefficients["scale(glmPupil)", "Estimate"]
r2   <- summary(l1)$r.squared

# Create base plot
p4m1p <- plot_model(l1, type = "pred", terms = "glmPupil",color = "darkgrey") +
  labs(x = "similarity (z-score)",
    y = "rt (z-score)",
    title = "rt (hit trials)"
  ) +
  annotate("text",x = Inf, y = -Inf, label = paste0("β = ", round(beta, 2), "\nR² = ", round(r2, 2)),
    hjust = 1.1, vjust = -1.5, size = 4)
```


#### predicting cue value (abs)
```{r warning=F}
df_cue <- NULL
for (t in thresh){
  for (tr in 1:14){
    l1<-summary(lm(cue_value_abs ~ scale(glmPupil),
                    my_array_s2_ %>% 
                      filter(tr_in_trial == tr,threshold == t, probe == "anticipation probe") %>% 
                      mutate(cue_value_abs = ifelse(cue_value %in% c("+$5","-$5"),5,
                                                    ifelse(cue_value %in% c("+$1","-$1"),1,
                                                           ifelse(cue_value %in% 
                                                                    c("+$0","-$0"),1,NA))))))
    
    l2<-summary(lm(cue_value_abs ~ scale(glmPupil),
                    my_array_s2_ %>% 
                      filter(tr_in_trial == tr,threshold == t, probe == "outcome probe") %>% 
                      mutate(cue_value_abs = ifelse(cue_value %in% c("+$5","-$5"),5,
                                                    ifelse(cue_value %in% c("+$1","-$1"),1,
                                                           ifelse(cue_value %in% 
                                                                    c("+$0","-$0"),1,NA))))))
  
    df_cue <- rbind(df_cue,
                          l1$coefficients[2,],
                          l2$coefficients[2,])
  }
  
}

df_cue <- as.data.frame(df_cue)
df_cue$probe <- rep(c("anticipation","outcome"), length(thresh))
df_cue$threshold <- rep(thresh, each = 2*14)
df_cue$tr <- rep(rep(1:14,each=2),2)

ggplot(df_cue, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  facet_wrap(~threshold)+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

ggplot(df_cue %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)
```

### predicting self-reports
```{r}
df_rating <- NULL
for (t in thresh){
  for (tr in 1:14){
    l1<-summary(lm(scale(arousal_scaled) ~ scale(glmPupil),
                    my_array_s2_ %>% 
                      filter(tr_in_trial == tr,threshold == t, probe == "anticipation probe")))
    l2<-summary(lm(scale(arousal_scaled) ~ scale(glmPupil),
                   my_array_s2_ %>% 
                   filter(tr_in_trial == tr, threshold == t, probe == "outcome probe")))
  
    df_rating <- rbind(df_rating,
                          l1$coefficients[2,],
                          l2$coefficients[2,])
  }
  
}

df_rating <- as.data.frame(df_rating)
df_rating$probe <- rep(c("anticipation","outcome"), length(thresh))
df_rating$threshold <- rep(thresh, each = 2*14)
df_rating$tr <- rep(rep(1:14,each=2),2)

ggplot(df_rating, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  geom_ribbon(aes(x = tr, ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`,fill = probe),
              alpha = 0.1)+
  facet_wrap(~threshold)+
  labs(title = "FMRI study")+
  scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  scale_x_continuous(breaks = 1:14)+
  geom_vline(xintercept = 5, color = "purple",label = "F")+
  geom_vline(xintercept = 6, color = "skyblue",label = "T")+
  geom_vline(xintercept = 7, color = "purple", linetype = "dashed")+
  geom_vline(xintercept = 9, color = "skyblue", linetype = "dashed")
  
  ggplot(df_rating %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study",
       y = "Correlation strength")+
  scale_x_continuous(breaks = 1:14)
```

### visualize peak correlation
```{r}
coefs1 = NULL
for (t in 1:14){
  l1<-summary(lm(scale(glmPupil) ~ scale(arousal_scaled),my_array_s2_ %>% filter(tr_in_trial == t, probe == "anticipation probe", threshold == 0.5)))
  coefs1 <- rbind(coefs1,l1$coefficients[2,])
}

coefs1<-as.data.frame(coefs1)
coefs1$TR <- 1:14
coefs1$probe = "anticipation probe"

coefs2 = NULL
for (t in 1:14){
  l1<-summary(lm(scale(glmPupil) ~ scale(arousal_scaled),my_array_s2_ %>% filter(tr_in_trial == t, probe == "outcome probe", threshold == 0.5)))
  coefs2 <- rbind(coefs2,l1$coefficients[2,])
}
coefs2<-as.data.frame(coefs2)
coefs2$TR <- 1:14
coefs2$probe = "outcome probe"

coefs <- rbind(coefs1,coefs2) %>% 
  mutate(sig = ifelse(`Pr(>|t|)` >= 0.05, "",
                      ifelse(`Pr(>|t|)` >= 0.01, "*",
                             ifelse(`Pr(>|t|)` >= 0.001, "**","***"))))

p_m2_pupil_a<-ggplot(coefs %>% filter(probe == "anticipation probe"),aes(x = TR, y =Estimate))+
  geom_hline(yintercept = 0, linetype = "dashed")+
  geom_vline(xintercept = c(3.5,4.5,5.5,9.5,10.5,11.5,12.5), size = 1, color = "grey")+
  annotate("text",x = 4, y = 0.05, label = "C")+
  annotate("text",x = 5, y = 0.05, label = "F")+
  annotate("text",x = 10, y = 0.05, label = "F")+
  annotate("text",x = 11, y = 0.05, label = "T")+
  annotate("text",x = 12, y = 0.05, label = "O")+
  annotate("text",x = 7.5, y = 0.05, label = "R")+
  scale_x_continuous(breaks = seq(0,14,2), labels = seq(0,28,4))+
  scale_color_manual(values = c("purple"))+
  scale_fill_manual(values = c("purple"))+
  geom_line(aes(color = probe), size = 2, alpha = 0.5)+
  geom_ribbon(aes(fill = probe, ymin = Estimate - `Std. Error`,
                  ymax = Estimate + `Std. Error`), alpha = 0.1)+
  geom_line(aes(color = probe), size = 2, alpha = 0.5)+
  geom_segment(aes(x = 7, y = 0.15,
                   xend =7, yend = 0.1),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  annotate("text",x = 7, y = 0.16, label ="arousal rating")+
  geom_text(aes(x = TR, y = Estimate+0.01, label = sig, color = probe))+
  labs(x = "time (s)",
       y = "Correlation with arousal ratings",
       title = "Regression weights on arousal",
       subtitle = "anticipation probe")+
  theme(legend.position = "none")+
  annotation_custom(
    grob = grid::rectGrob(gp = grid::gpar(fill = "white", alpha = 1, col = NA)),
    xmin = 9.6, xmax = 15, ymin = -Inf, ymax = Inf
  )

p_m2_pupil_b<-ggplot(coefs%>% filter(probe == "outcome probe"),aes(x = TR, y =Estimate))+
  geom_hline(yintercept = 0, linetype = "dashed")+
  geom_vline(xintercept = c(3.5,4.5,5.5,6.5,7.5), size = 1, color = "grey")+
  annotate("text",x = 4, y = 0.05, label = "C")+
  annotate("text",x = 5, y = 0.05, label = "F")+
  annotate("text",x = 6, y = 0.05, label = "T")+
  annotate("text",x = 7, y = 0.05, label = "O")+
  annotate("text",x = 10, y = 0.05, label = "R")+
  scale_x_continuous(breaks = seq(0,14,2), labels = seq(0,28,4))+
  scale_color_manual(values = c("skyblue"))+
  scale_fill_manual(values = c("skyblue"))+
  geom_line(aes(color = probe), size = 2, alpha = 0.5)+
  geom_ribbon(aes(fill = probe, ymin = Estimate - `Std. Error`,
                  ymax = Estimate + `Std. Error`), alpha = 0.1)+
  geom_line(aes(color = probe), size = 2, alpha = 0.5)+
  geom_segment(aes(x = 10, y = 0.17,
                   xend =10, yend = 0.12),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  annotate("text",x = 10, y = 0.18, label ="arousal rating")+
  geom_segment(aes(x = 10, y = 0.17,
                   xend =10, yend = 0.12),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  annotate("text",x = 10, y = 0.18, label ="arousal rating")+
  geom_text(aes(x = TR, y = Estimate+0.01, label = sig, color = probe))+
  labs(x = "time (s)",
       subtitle = "outcome probe")+
  theme(legend.position = "none")

p_m2_pupil_a+p_m2_pupil_b

summary(lm(scale(glmPupil) ~ scale(arousal_scaled),my_array_s2_ %>% filter(tr_in_trial == 5, threshold == 0.5)))

summary(lmer(scale(glmPupil) ~ scale(arousal_scaled)+(1|subject),my_array_s2_ %>% filter(tr_in_trial == 5, threshold == 0.5)))

summary(lmer(scale(mean_pupil_nobc) ~ scale(arousal_scaled)+(1|subject),my_array_s2_ %>% filter(tr_in_trial == 5, threshold == 0.5)))

summary(lmer(scale(glmPupil) ~ scale(arousal_scaled)+(1|subject)+(1|probe),my_array_s2_ %>% filter(tr_in_trial == 5, threshold == 0.5)))

summary(lm(scale(glmPupil) ~ scale(arousal_scaled),my_array_s2_ %>% 
             filter(ifelse(probe == "anticipation probe", tr_in_trial == 5,
                           ifelse(probe == "outcome probe", tr_in_trial == 7,NA))) %>% 
             filter(threshold == 0.5)))


# Prepare data
d1 <- my_array_s2_ %>% filter(tr_in_trial == 5, threshold == 0.5)
d2 <- my_array_s2_ %>% filter(tr_in_trial == 5, probe == "anticipation probe", threshold == 0.5)
d3 <- my_array_s2_ %>% filter(tr_in_trial == 7, probe == "outcome probe", threshold == 0.5)

# Fit models
l1 <- lm(scale(arousal_scaled) ~ scale(glmPupil), d1)
l2 <- lm(scale(arousal_scaled) ~ scale(glmPupil), d2)
l3 <- lm(scale(arousal_scaled) ~ scale(glmPupil), d3)
# Extract coefficients and p-values
get_stats <- function(model) {
  b <- coef(summary(model))["scale(glmPupil)", "Estimate"]
  p <- coef(summary(model))["scale(glmPupil)", "Pr(>|t|)"]
  list(beta = round(b, 3), p = signif(p, 3))
}

s1 <- get_stats(l1)
s2 <- get_stats(l2)
s3 <- get_stats(l3)

# Create prediction data with CI ribbons
make_pred_df <- function(data, model) {
  new <- data.frame(glmPupil = seq(min(data$glmPupil, na.rm = TRUE),
                                     max(data$glmPupil, na.rm = TRUE),
                                     length.out = 100))
  preds <- predict(model, newdata = new, interval = "confidence")
  new$fit <- preds[, "fit"]
  new$lwr <- preds[, "lwr"]
  new$upr <- preds[, "upr"]
  new
}

new1 <- make_pred_df(d1, l1)
new2 <- make_pred_df(d2, l2)
new3 <- make_pred_df(d3, l3)

# Plot
p_m2_pupil_c <- ggplot() +
  ## Model 1 -- black
  geom_ribbon(data = new1,
              aes(x = scale(glmPupil), ymin = lwr, ymax = upr),
              fill = "black", alpha = 0.15) +
  geom_line(data = new1,
            aes(x = scale(glmPupil), y = fit),
            color = "black", size = 1) +

  ## Model 2 -- purple
  geom_ribbon(data = new2,
              aes(x = scale(glmPupil), ymin = lwr, ymax = upr),
              fill = "purple", alpha = 0.15) +
  geom_line(data = new2,
            aes(x = scale(glmPupil), y = fit),
            color = "purple", size = 1) +

  ## Model 3 -- skyblue
  geom_ribbon(data = new3,
              aes(x = scale(glmPupil), ymin = lwr, ymax = upr),
              fill = "skyblue", alpha = 0.15) +
  geom_line(data = new3,
            aes(x = scale(glmPupil), y = fit),
            color = "skyblue", size = 1) +

  ## Add beta + p-value text
  annotate("text", x = -1.5, y = max(new1$upr)-0.3, 
           label = paste0("both: β=", round(s1$beta,2), ", p=", s1$p),
           color = "black", hjust = 0) +
  annotate("text", x = -1.5, y = max(new1$upr),
           label = paste0("ant (8s): β=", round(s2$beta,2), ", p=", s2$p),
           color = "purple", hjust = 0) +
  annotate("text", x = -1.5, y = max(new1$upr)-0.15,
           label = paste0("out (12s): β=", round(s3$beta,2), ", p=", s3$p),
           color = "skyblue", hjust = 0) +

  labs(
    x = "similarity (scaled)",
    y = "Predicted arousal (scaled)"
  )
```

#### correlation with pupil size
```{r}
cor(my_array_s2 %>% 
      filter(threshold == 0.5) %>% 
      group_by(subject) %>% 
      mutate(pupil_lag2= lag(pupil,2))%>% 
      ungroup() %>% 
      select(glmPupil,glmPupil_posonly,glmArousal,pupil_lag2),use = "complete.obs")

# cor(my_array_s2 %>% 
#       filter(threshold == 1.5) %>% 
#       group_by(subject) %>% 
#       mutate(pupil_lag2= lag(pupil,2))%>% 
#       ungroup() %>% 
#       select(glmPupil,glmPupil_posonly,glmArousal,pupil_lag2),use = "complete.obs")

# continuous correlation
summary(lm(scale(glmPupil) ~ scale(pupil_lag2),my_array_s2 %>% 
              filter(threshold == 0.5) %>% 
          group_by(subject) %>% mutate(pupil_lag2= lag(pupil,3))))

# TR5 with the pre-defined window's pupil size
summary(lm(scale(glmPupil) ~ scale(mean_pupil_nobc),my_array_s2_ %>% 
              filter(threshold == 0.5,tr_in_trial == 4)))

corr_mat <- my_array_s2 %>%
  filter(threshold == 0.5) %>%
  group_by(subject) %>%
  mutate(pupil_lag2 = lag(pupil, 2)) %>%
  ungroup() %>%
  select(glmPupil, glmPupil_posonly, glmArousal, pupil_lag2) %>%
  cor(use = "complete.obs")

# Convert to long format for ggplot
corr_long <- reshape2::melt(corr_mat)

# Plot correlation heatmap
ggplot(corr_long, aes(Var1, Var2, fill = value)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(value, 2)), color = "black", size = 5) +
  scale_fill_gradient2(low = "blue", high = "red", mid = "white",
                       midpoint = 0, limit = c(-1, 1), name = "Correlation") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    panel.grid = element_blank()
  ) +
  coord_fixed() +
  labs(x = "", y = "", title = "Correlation Matrix (threshold = 0.5)")

ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/arousal_index_corr.png"),dpi = 300, height = 5, width = 6)
```

<!-- ```{r} -->
<!-- brain_img <- image_read("../../figures/brain_fig_a.png") -->

<!-- # Convert to raster -->
<!-- brain_raster <- as.raster(brain_img) -->

<!-- # Turn it into a ggplot object -->
<!-- p_brain <- ggplot() + -->
<!--   annotation_raster(brain_raster, xmin = -Inf, xmax = Inf, -->
<!--                     ymin = -Inf, ymax = Inf) + -->
<!--   theme_void() -->
<!-- ``` -->

```{r}
p_brain/
(p1m2p)/
(p2m2p+p3m2p+p4m2p+p_m2_pupil_c+
  plot_layout(nrow=1,widths = c(1.2,1,1,1.2)))+
plot_annotation(title = "Pupil template",
                  tag_levels = "A")+
  plot_layout(heights = c(1.5,1,1))


ggsave(paste0("~/Desktop/VRMID-analysis/mid-pupil/figures/fig_glmPupil.png"),dpi = 300, height = 8.5, width = 10)
```

#### does it change with fatigue?
```{r}
summary(lmer(glmPupil~trial+(1|subject),my_array_s2_ %>% filter(tr_in_trial == 5)))
summary(lmer(arousal_scaled~trial+(1|subject),my_array_s2_ %>% filter(tr_in_trial == 5)))
```

### pupil glm template (positive activations only)
```{r}
my_array_s2_ <- my_array_s2%>% 
  ungroup() %>% 
  select(trial,subject,tr_in_trial,glmPupil_posonly,trial_tr,threshold) %>% 
  pivot_wider(names_from = c(tr_in_trial), values_from = c(glmPupil_posonly), names_prefix = "glmPupil_TR_") %>% 
  arrange(subject,trial)

for (t in thresh){
  for (sub in unique(my_array_s2_$subject)){
    for(tr in 9:11){
      replace_idx = my_array_s2_$subject == sub & my_array_s2_$trial_tr == tr & my_array_s2_$threshold == t & is.na(my_array_s2_[,paste0("glmPupil_TR_",tr+1)])
      #early TRs were TRs from the previous trial
      my_array_s2_[replace_idx,paste0("glmPupil_TR_",(tr+1):TR_DELAY)] <- my_array_s2_[lag(replace_idx) %>% replace_na(FALSE),paste0("glmPupil_TR_",1:(TR_DELAY-tr))]
  } # tr loop
  }
}

TR_DELAY = 14
my_array_s2_ <- my_array_s2_ %>% mutate(glmPupil_TR_17 = NA, glmPupil_TR_18 = NA, glmPupil_TR_19 = NA, glmPupil_TR_20 = NA)

my_array_s2_<-left_join(my_array_s2_ %>% 
                        pivot_longer(glmPupil_TR_1:glmPupil_TR_20,
                                     names_to = "tr_in_trial",names_prefix = "glmPupil_TR_",
                                     values_to = "glmPupil"),fmri4_data_2probes,
                      by = c("subject","trial")) %>% 
  filter(tr <= 975)%>%
  mutate(half = ifelse(trial >= 48,"second","first"))%>% #last bit was interpolated
  mutate(probe = ifelse(probe == 1, "anticipation probe","outcome probe"))

my_array_s2_ <- my_array_s2_ %>% 
  mutate(tr_in_trial = as.numeric(tr_in_trial),
         time = (tr_in_trial-1) * 2)
```

#### diffentiating cue vs. outcome
```{r}
d1<-my_array_s2_ %>% 
         filter(!is.na(hit)) %>% 
         group_by(tr_in_trial,subject,threshold,probe) %>% 
         summarise(glmPupil = mean(glmPupil,na.rm = T)) %>% 
         group_by(tr_in_trial,threshold,probe) %>% 
         summarise(mean = mean(glmPupil,na.rm = T),
                   se = sd(glmPupil,na.rm = T)/sqrt(n())) %>% 
  filter(tr_in_trial <= 14)

ggplot(d1 %>% filter(probe == "anticipation probe",threshold == 0.5),
       aes(x = tr_in_trial, y = mean))+
  geom_vline(xintercept = c(3.5,4.5,5.5,9.5,10.5,11.5,12.5), size = 1, color = "grey")+
  annotate("text",x = 4, y = 0.05, label = "C")+
  annotate("text",x = 5, y = 0.05, label = "F")+
  annotate("text",x = 10, y = 0.05, label = "F")+
  annotate("text",x = 11, y = 0.05, label = "T")+
  annotate("text",x = 12, y = 0.05, label = "O")+
  annotate("text",x = 7.5, y = 0.05, label = "R")+
  geom_line(size = 0.5) +
  geom_point()+
  geom_errorbar(aes(x = tr_in_trial, ymin = mean-se,ymax = mean+se), width = 0.3)+
  labs(y = "Simalirty",
       x = "time (s)",
       subtitle = "anticipation probe")+
  scale_color_manual(values = redOrange_palette6)+
  theme(legend.position = "top")+
  ylim(-0.1,0.1)+
ggplot(d1 %>% filter(probe == "outcome probe",threshold == 0.5),
       aes(x = tr_in_trial, y = mean))+
  geom_vline(xintercept = c(3.5,4.5,5.5,6.5,7.5,11.5), size = 1, color = "grey")+
  annotate("text",x = 4, y = 0.05, label = "C")+
  annotate("text",x = 5, y = 0.05, label = "F")+
  annotate("text",x = 6, y = 0.05, label = "T")+
  annotate("text",x = 7, y = 0.05, label = "O")+
  annotate("text",x = 10, y = 0.05, label = "R")+
  geom_line(size = 0.5) +
  geom_point()+
  geom_errorbar(aes(x = tr_in_trial, ymin = mean-se,ymax = mean+se), width = 0.3)+
  labs(y = "Simalirty",
       x = "time (s)",
       subtitle = "outcome probe",
      caption = "C = Cue, F = Fixation, \nT = Target, O = Outcome, R = Rating")+
  scale_color_manual(values = redOrange_palette6)+
  theme(legend.position = "top")+
  ylim(-0.1,0.1)

d2<-my_array_s2_ %>% 
         filter(!is.na(hit),
                tr_in_trial == 5) %>% 
         group_by(subject,threshold,cue_value) %>% 
         summarise(glmPupil = mean(glmPupil,na.rm = T)) %>% 
         group_by(threshold,cue_value) %>% 
         summarise(mean = mean(glmPupil,na.rm = T),
                   se = sd(glmPupil,na.rm = T)/sqrt(n())) %>% 
  mutate(cue_value = factor(cue_value,levels = c("-$5","-$1","-$0","+$0","+$1","+$5")))

summary(l1<-lm(glmPupil~cue_value,my_array_s2_ %>% filter(tr_in_trial == 5)))
r2   <- summary(l1)$r.squared

ggplot(d2 %>% filter(threshold == 0.5),
       aes(x = cue_value, y = mean,color = cue_value))+
  geom_point(size = 0.5) +
  geom_point()+
  geom_errorbar(aes(x = cue_value, ymin = mean-se,ymax = mean+se), width = 0.3)+
  labs(y = "Simalirty",
       x = "time (s)",
       subtitle = "Inferred arousal (8s)")+
  scale_color_manual(values = redOrange_palette6)+
  theme(legend.position = "none")+  # show shape legend
  scale_x_discrete(breaks =c("-$5","-$1","-$0","+$0","+$1","+$5"))+
  annotate("text",x = Inf, y = -Inf, label = paste0("R² = ", round(r2, 3)),
    hjust = 1.1, vjust = -1.5, size = 4)# Get effect size (standardized beta)

d3<-my_array_s2_ %>% 
         filter(!is.na(hit),
                ifelse(probe == "anticipation probe", tr_in_trial == 12,
                       ifelse(probe == "outcome probe",tr_in_trial == 7,NA))) %>% 
         group_by(subject,threshold,hit,cue_value) %>% 
         summarise(glmPupil = mean(glmPupil,na.rm = T)) %>% 
         group_by(threshold,hit,cue_value) %>% 
         summarise(mean = mean(glmPupil,na.rm = T),
                   se = sd(glmPupil,na.rm = T)/sqrt(n())) %>% 
  mutate(hit = factor(hit, levels = c(0,1), labels = c("Miss","Hit")))%>% 
  mutate(cue_value = factor(cue_value,levels = c("-$5","-$1","-$0","+$0","+$1","+$5")))

ggplot(d3 %>% filter(threshold == 0.5),
       aes(x = cue_value, y = mean, color = cue_value, shape = hit)) +
  geom_point(position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(x = cue_value, group = hit, ymin = mean - se, ymax = mean + se),
                width = 0.3, position = position_dodge(width = 0.5)) +
  labs(y = "Similarity to self-report template",
       x = "time (s)",
       subtitle = "arousal index during outcome") +
  theme(legend.position = "top") +
  scale_color_manual(values = redOrange_palette6) +
  guides(color = "none",  # hide color legend
         shape = guide_legend())+  # show shape legend
  scale_x_discrete(breaks =c("-$5","-$1","-$0","+$0","+$1","+$5"))

```


#### predicting performance
```{r warning=F}
df_performance <- NULL
for (t in thresh){
  for (tr in 1:14){
    l1<-summary(glm(hit_num ~ scale(glmPupil),family = binomial,
                    my_array_s2_ %>% 
                      filter(tr_in_trial == tr,threshold == t, probe == "anticipation probe") %>% 
                      mutate(hit_num = as.factor(hit == 1))))
    
    l2<-summary(glm(hit_num ~ scale(glmPupil),family = binomial,
                    my_array_s2_ %>% 
                      filter(tr_in_trial == tr,threshold == t, probe == "outcome probe") %>% 
                      mutate(hit_num = as.factor(hit == 1))))
  
    df_performance <- rbind(df_performance,
                          l1$coefficients[2,],
                          l2$coefficients[2,])
  }
  
}

df_performance <- as.data.frame(df_performance)
df_performance$probe <- rep(c("anticipation","outcome"), length(thresh))
df_performance$threshold <- rep(thresh, each = 2*14)
df_performance$tr <- rep(rep(1:14,each=2),2)

ggplot(df_performance, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  facet_wrap(~threshold)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)


ggplot(df_performance %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

summary(l1<-glm(hit_num ~ scale(glmPupil),family = binomial,
                    my_array_s2_ %>% 
                      filter(tr_in_trial == 5,threshold == 0.5) %>% 
                      mutate(hit_num = as.factor(hit == 1))))

# Get effect size (standardized beta)
beta <- summary(l1)$coefficients["scale(glmPupil)", "Estimate"]
r2   <- pscl::pR2(l1)["McFadden"]

# Create base plot
plot_model(l1, type = "pred", terms = "glmPupil",color = "darkgrey") +
  labs(x = "similarity (z-score)",
       y = "p(hit)",title = "p(hit)") +
  annotate("text",x = Inf, y = -Inf, label = paste0("β = ", round(beta, 2), "\npseudo-R² = ", round(r2, 2)),
    hjust = 1.1, vjust = -0.5, size = 4)
```

```{r warning=F}
df_performance <- NULL

for (t in thresh){
  for (tr in 1:14){
    l1<-summary(lm(scale(rt) ~ scale(glmPupil),
                   my_array_s2_ %>% 
                   filter(tr_in_trial == tr, hit == 1,threshold == t, probe == "anticipation probe")))
    
    l2<-summary(lm(scale(rt) ~ scale(glmPupil),
                   my_array_s2_ %>% 
                   filter(tr_in_trial == tr, hit == 1,threshold == t, probe == "outcome probe")))
  
    df_performance <- rbind(df_performance,
                          l1$coefficients[2,],
                          l2$coefficients[2,])
  }
  
}

df_performance <- as.data.frame(df_performance)
df_performance$probe <- rep(c("anticipation","outcome"), length(thresh))
df_performance$threshold <- rep(thresh, each = 2*14)
df_performance$tr <- rep(rep(1:14,each=2),2)

ggplot(df_performance, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  facet_wrap(~threshold)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

ggplot(df_performance %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

summary(l1<-lm(scale(rt) ~ scale(glmPupil),
                   my_array_s2_ %>% 
                   filter(tr_in_trial == 5, hit == 1,threshold == 0.5)))

# Get effect size (standardized beta)
beta <- summary(l1)$coefficients["scale(glmPupil)", "Estimate"]
r2   <- summary(l1)$r.squared

# Create base plot
plot_model(l1, type = "pred", terms = "glmPupil",color = "darkgrey") +
  labs(x = "similarity (z-score)",
    y = "rt (z-score)",
    title = "rt (hit trials)"
  ) +
  annotate("text",x = Inf, y = -Inf, label = paste0("β = ", round(beta, 2), "\nR² = ", round(r2, 2)),
    hjust = 1.1, vjust = -1.5, size = 4)
```


#### predicting cue value (abs)
```{r warning=F}
df_cue <- NULL
for (t in thresh){
  for (tr in 1:14){
    l1<-summary(lm(cue_value_abs ~ scale(glmPupil),
                    my_array_s2_ %>% 
                      filter(tr_in_trial == tr,threshold == t, probe == "anticipation probe") %>% 
                      mutate(cue_value_abs = ifelse(cue_value %in% c("+$5","-$5"),5,
                                                    ifelse(cue_value %in% c("+$1","-$1"),1,
                                                           ifelse(cue_value %in% 
                                                                    c("+$0","-$0"),1,NA))))))
    
    l2<-summary(lm(cue_value_abs ~ scale(glmPupil),
                    my_array_s2_ %>% 
                      filter(tr_in_trial == tr,threshold == t, probe == "outcome probe") %>% 
                      mutate(cue_value_abs = ifelse(cue_value %in% c("+$5","-$5"),5,
                                                    ifelse(cue_value %in% c("+$1","-$1"),1,
                                                           ifelse(cue_value %in% 
                                                                    c("+$0","-$0"),1,NA))))))
  
    df_cue <- rbind(df_cue,
                          l1$coefficients[2,],
                          l2$coefficients[2,])
  }
  
}

df_cue <- as.data.frame(df_cue)
df_cue$probe <- rep(c("anticipation","outcome"), length(thresh))
df_cue$threshold <- rep(thresh, each = 2*14)
df_cue$tr <- rep(rep(1:14,each=2),2)

ggplot(df_cue, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  facet_wrap(~threshold)+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)

ggplot(df_cue %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)
```

### predicting self-reports
```{r}
df_rating <- NULL
for (t in thresh){
  for (tr in 1:14){
    l1<-summary(lm(scale(arousal_scaled) ~ scale(glmPupil),
                    my_array_s2_ %>% 
                      filter(tr_in_trial == tr,threshold == t, probe == "anticipation probe")))
    l2<-summary(lm(scale(arousal_scaled) ~ scale(glmPupil),
                   my_array_s2_ %>% 
                   filter(tr_in_trial == tr, threshold == t, probe == "outcome probe")))
  
    df_rating <- rbind(df_rating,
                          l1$coefficients[2,],
                          l2$coefficients[2,])
  }
  
}

df_rating <- as.data.frame(df_rating)
df_rating$probe <- rep(c("anticipation","outcome"), length(thresh))
df_rating$threshold <- rep(thresh, each = 2*14)
df_rating$tr <- rep(rep(1:14,each=2),2)

ggplot(df_rating, aes(x = tr, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
  geom_ribbon(aes(x = tr, ymin = Estimate - `Std. Error`,
                    ymax = Estimate + `Std. Error`,fill = probe),
              alpha = 0.1)+
  facet_wrap(~threshold)+
  labs(title = "FMRI study")+
  scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  scale_x_continuous(breaks = 1:14)+
  geom_vline(xintercept = 5, color = "purple",label = "F")+
  geom_vline(xintercept = 6, color = "skyblue",label = "T")+
  geom_vline(xintercept = 7, color = "purple", linetype = "dashed")+
  geom_vline(xintercept = 9, color = "skyblue", linetype = "dashed")
  
  ggplot(df_rating %>% filter(tr == 5), aes(x = threshold, y = Estimate))+
  geom_line(aes(color= probe))+
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey",
             size = 1)+
    scale_color_manual(values = c("purple","skyblue"))+
  scale_fill_manual(values = c("purple","skyblue"))+
  labs(title = "FMRI study")+
  scale_x_continuous(breaks = 1:14)
```

### visualize peak correlation
```{r}
coefs1 = NULL
for (t in 1:14){
  l1<-summary(lm(scale(glmPupil) ~ scale(arousal_scaled),my_array_s2_ %>% filter(tr_in_trial == t, probe == "anticipation probe", threshold == 0.5)))
  coefs1 <- rbind(coefs1,l1$coefficients[2,])
}

coefs1<-as.data.frame(coefs1)
coefs1$TR <- 1:14
coefs1$probe = "anticipation probe"

coefs2 = NULL
for (t in 1:14){
  l1<-summary(lm(scale(glmPupil) ~ scale(arousal_scaled),my_array_s2_ %>% filter(tr_in_trial == t, probe == "outcome probe", threshold == 0.5)))
  coefs2 <- rbind(coefs2,l1$coefficients[2,])
}
coefs2<-as.data.frame(coefs2)
coefs2$TR <- 1:14
coefs2$probe = "outcome probe"

coefs <- rbind(coefs1,coefs2) %>% 
  mutate(sig = ifelse(`Pr(>|t|)` >= 0.05, "",
                      ifelse(`Pr(>|t|)` >= 0.01, "*",
                             ifelse(`Pr(>|t|)` >= 0.001, "**","***"))))

p_m2_pupil_posonly_a<-ggplot(coefs %>% filter(probe == "anticipation probe"),aes(x = TR, y =Estimate))+
  geom_hline(yintercept = 0, linetype = "dashed")+
  geom_vline(xintercept = c(3.5,4.5,5.5,9.5,10.5,11.5,12.5), size = 1, color = "grey")+
  annotate("text",x = 4, y = 0.05, label = "C")+
  annotate("text",x = 5, y = 0.05, label = "F")+
  annotate("text",x = 10, y = 0.05, label = "F")+
  annotate("text",x = 11, y = 0.05, label = "T")+
  annotate("text",x = 12, y = 0.05, label = "O")+
  annotate("text",x = 7.5, y = 0.05, label = "R")+
  scale_x_continuous(breaks = seq(0,14,2), labels = seq(0,28,4))+
  scale_color_manual(values = c("purple"))+
  scale_fill_manual(values = c("purple"))+
  geom_line(aes(color = probe), size = 2, alpha = 0.5)+
  geom_ribbon(aes(fill = probe, ymin = Estimate - `Std. Error`,
                  ymax = Estimate + `Std. Error`), alpha = 0.1)+
  geom_line(aes(color = probe), size = 2, alpha = 0.5)+
  geom_segment(aes(x = 7, y = 0.15,
                   xend =7, yend = 0.1),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  annotate("text",x = 7, y = 0.16, label ="arousal rating")+
  geom_text(aes(x = TR, y = Estimate+0.01, label = sig, color = probe))+
  labs(x = "time (s)",
       y = "Correlation with arousal ratings",
       title = "Regression weights on arousal",
       subtitle = "anticipation probe")+
  theme(legend.position = "none")

p_m2_pupil_posonly_b<-ggplot(coefs%>% filter(probe == "outcome probe"),aes(x = TR, y =Estimate))+
  geom_hline(yintercept = 0, linetype = "dashed")+
  geom_vline(xintercept = c(3.5,4.5,5.5,6.5,7.5), size = 1, color = "grey")+
  annotate("text",x = 4, y = 0.05, label = "C")+
  annotate("text",x = 5, y = 0.05, label = "F")+
  annotate("text",x = 6, y = 0.05, label = "T")+
  annotate("text",x = 7, y = 0.05, label = "O")+
  annotate("text",x = 10, y = 0.05, label = "R")+
  scale_x_continuous(breaks = seq(0,14,2), labels = seq(0,28,4))+
  scale_color_manual(values = c("skyblue"))+
  scale_fill_manual(values = c("skyblue"))+
  geom_line(aes(color = probe), size = 2, alpha = 0.5)+
  geom_ribbon(aes(fill = probe, ymin = Estimate - `Std. Error`,
                  ymax = Estimate + `Std. Error`), alpha = 0.1)+
  geom_line(aes(color = probe), size = 2, alpha = 0.5)+
  geom_segment(aes(x = 10, y = 0.17,
                   xend =10, yend = 0.12),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  annotate("text",x = 10, y = 0.18, label ="arousal rating")+
  geom_segment(aes(x = 10, y = 0.17,
                   xend =10, yend = 0.12),
               size = 1, arrow = arrow(length = unit(0.03, "npc")),
               color = "darkgrey")+
  annotate("text",x = 10, y = 0.18, label ="arousal rating")+
  geom_text(aes(x = TR, y = Estimate+0.01, label = sig, color = probe))+
  labs(x = "time (s)",
       subtitle = "outcome probe")+
  theme(legend.position = "none")

p_m2_pupil_posonly_a+p_m2_pupil_posonly_b


summary(lm(scale(glmPupil) ~ scale(arousal_scaled),my_array_s2_ %>% filter(tr_in_trial == 5, threshold == 0.5)))

summary(lm(scale(glmPupil) ~ scale(arousal_scaled),my_array_s2_ %>% 
             filter(ifelse(probe == "anticipation probe", tr_in_trial == 5,
                           ifelse(probe == "outcome probe", tr_in_trial == 7,NA))) %>% 
             filter(threshold == 0.5)))
```